### 2024-01-18 index.qmd
init commit

---
title: Psp_conjunction
bibliography: files/references.bib
---

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)

> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth. Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.

> E8, C2, Q4, Q5, 24 April–1 May, 2021. Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb. In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April. STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude. This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.

[WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)

2021-05-09

![](images/paste-1.png)

### 2024-01-19 index.qmd
update

@@
 
+05/09/2021
+
+![](images/wind.png)
+
+![](images/psp.png)
+
+vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp&id=vp_moment_RTN\[:,0\];vp_moment_RTN\[:,1\];vp_moment_RTN\[:,2\]&timerange=2021-05-07+through+2021-05-08
+
+\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()
+
+\|rebundle(psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0)\|magnitude()
+
+-   ops: "\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()" title: "PSP/SWP_SPC Proton bulk velocity from the 1st moment of the reduced distribution function in \[inertial\] RTN coordinate system (All Qualities)" y: label: V (km/s)
+-   ops: "\|rebundle(B_R,B_T,B_N)\|magnitude()" y: label: B (nT) title: PSP_FLD/MAG_RTN_1min Magnetic field in RTN coordinates (1 minute cadence)
+
+PSP/PSP/SWEAP/SPAN Partial Moment Velocity in RTN Coordinates and Sun reference frame \|rebundle(Vx RTN,Vy RTN,Vz RTN)\|magnitude()
+
+Wind or ACE
+
 ![](images/paste-1.png)
+
+<!-- ![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_1day_plots/2021/05/20210509-day.png) -->
+
+::: {.column-page layout-nrow="1"}
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210510-3day.png)
+
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210513-3day.png)
+:::
+
+tr = '2021-05-06 22:46 to 2021-05-15 22:46' vp = getDataSet( 'vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp_SW&id=vp_moment_RTN', tr ) plot( 0, vp )
+
+density5min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/ace/mag/level_2_cdaweb/mfi_k0/2017/ac_k0_mfi_20170117_v01.cdf?Magnitude') dst60min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/omni/omni_cdaweb/hourly/2017/omni2_h0_mrg1hr_20170101_v01.cdf?DST')
+
+t5min= density5min.property(QDataSet.DEPEND_0)
+
+( density, flux, dst ) = synchronize( t5min, density5min, flux4min, dst60min, nn=1 ) \# experimental function (note there is a built-in function in Autoplot v2017a. plot( 1, flux ) plot( 2, dst )

### 2024-01-19 index.qmd
update

@@
 
+## PSP Encounter Infos
+
+[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)
+
+| Event | Distance                    | Time                         |
+|-------|-----------------------------|------------------------------|
+| E1    | 35.6 $R_{\odot}$            | Perihelion: 2018-11-06 03:27 |
+| E2    | 35.6 $R_{\odot}$            | Perihelion: 2019-04-04 22:39 |
+| E3    | 35.6 $R_{\odot}$            | Perihelion: 2019-09-01 17:50 |
+| E4    | 27.8 $R_{\odot}$            | Perihelion: 2020-01-29 09:37 |
+| E5    | 27.8 $R_{\odot}$            | Perihelion: 2020-06-07 08:23 |
+| E6    | 20.3 $R_{\odot}$            | Perihelion: 2020-09-27 09:16 |
+| E7    | 20.3 $R_{\odot}$            | Perihelion: 2021-01-17 17:40 |
+| E8    | 0.074 AU (15.9 $R_{\odot}$) | Perihelion: 2021-04-29 08:48 |
+| E9    | 15.9 $R_{\odot}$            | Perihelion: 2021-08-09 19:11 |
+| E10   | 13.3 $R_{\odot}$            | Perihelion: 2021-11-21 08:23 |
+| E11   | 13.3 $R_{\odot}$            | Perihelion: 2022-02-25 15:38 |
+| E12   | 13.3 $R_{\odot}$            | Perihelion: 2022-06-01 22:51 |
+| E13   | 13.3 $R_{\odot}$            | Perihelion: 2022-09-06 06:04 |
+| E14   | 13.3 $R_{\odot}$            | Perihelion: 2022-12-11 13:16 |
+| E15   | 13.3 $R_{\odot}$            | Perihelion: 2023-03-17 20:30 |
+| E16   | 13.3 $R_{\odot}$            | Perihelion: 2023-06-22 03:46 |
+| E17   | 11.4 $R_{\odot}$            | Perihelion: 2023-09-27 23:28 |
+| E18   | 11.4 $R_{\odot}$            | Perihelion: 2023-12-29 00:54 |
+| E19   | 11.4 $R_{\odot}$            | Perihelion: 2024-03-30 02:20 |
+| E20   | 11.4 $R_{\odot}$            | Perihelion: 2024-06-30 03:46 |
+| E21   | 11.4 $R_{\odot}$            | Perihelion: 2024-09-30 05:13 |
+| E22   | 9.9 $R_{\odot}$             | Perihelion: 2024-12-24 11:41 |
+| E23   | 9.9 $R_{\odot}$             | Perihelion: 2025-03-22 22:25 |
+| E24   | 9.9 $R_{\odot}$             | Perihelion: 2025-06-19 09:09 |
+
 > Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
 Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
+
+## Trange: Encounter 8
 
@@
 
-[WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)
+-   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
+-   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)
 
@@
 
+![](images/paste-2.png)
+
 ![](images/paste-1.png)
@@
 ( density, flux, dst ) = synchronize( t5min, density5min, flux4min, dst60min, nn=1 ) \# experimental function (note there is a built-in function in Autoplot v2017a. plot( 1, flux ) plot( 2, dst )
+
+## Trange
+
+> C4, 18 September, b 2021.
+This will be an inferior triple SO–PSP–STEREO-A conjunction, with SO inside the orbit of Venus around 0.6 AU, PSP at about 0.7 AU, and STEREO-A at 0.9 AU.
+This will be an occasion for joint in situ studies of the properties of turbulence and dynamics of a solar wind stream between 0.5 and 1 AU.
+
+https://solar-mach.streamlit.app/?embedded=true&date=20210925&time=0000&coord_sys=0&plot_spirals=1&plot_sun_body_line=1&plot_trans=0&plot_markers=Numbers&long_offset=270&bodies=STEREO+A&bodies=Earth&bodies=BepiColombo&bodies=Parker+Solar+Probe&bodies=Solar+Orbiter&speeds=346&speeds=485&speeds=400&speeds=300&speeds=287&
+
+![](images/paste-8.png)
+
+![](images/paste-9.png)
+
+![](images/paste-7.png)
+
+![](images/paste-6.png)
+
+![](images/paste-10.png)
+
+::: {.column-page layout-nrow="1"}
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210802-3day.png)
+
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210805-3day.png)
+:::
+
+## Trange: Encounter 11, 2022-02
+
+> E11, C6, Q8, Q9 23–27 February, 2022.
+PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth–
+
+![](images/paste-3.png)
+
+[![](images/paste-4.png)](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)
+
+![](images/paste-5.png)
+
+::: {.column-page layout-nrow="1"}
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220225-3day.png)
+
+![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220228-3day.png)
+:::

### 2024-01-25 index.qmd
update
add notes

@@
 ---
-title: Psp_conjunction
-bibliography: files/references.bib
+title: Evolution of solar wind discontinuities in the inner heliosphere
+subtitle: PSP and Earth conjunctions and alignments
+author:
+  - name: Zijin Zhang
+    email: zijin@ucla.edu
+    orcid: 0000-0002-9968-067X
+    affiliation: University of California, Los Angeles
+    roles: writing
+    corresponding: true
+  - name: Anton V. Artemyev
+    email: aartemyev@igpp.ucla.edu
+    orcid: 0000-0001-8823-4474
+    affiliation: University of California, Los Angeles
+  - name: Vassilis Angelopoulos
+    orcid: 0000-0001-7024-1561
+    affiliation: University of California, Los Angeles
+  - name: Shi Chen
+    orcid: 0000-0002-2582-7085
+    affiliation: University of California, Los Angeles
+code-links:
+  - repo
+  - href: https://app.tana.inc?nodeid=PZ6j7iriic2l
+    text: Tana
+  - href: zotero://select/library/collections/L9JC7XAI
+    text: Zotero
 ---
 
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
+# Updates
 
-## PSP Encounter Infos
+![](images/paste-11.png)
+
+![](images/paste-12.png)
+
+# References
+
+- @velliUnderstandingOriginsHeliosphere2020
+- @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
+    - > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
+
+# PSP Encounter Infos
 
@@
 
-| Event | Distance                    | Time                         |
-|-------|-----------------------------|------------------------------|
-| E1    | 35.6 $R_{\odot}$            | Perihelion: 2018-11-06 03:27 |
-| E2    | 35.6 $R_{\odot}$            | Perihelion: 2019-04-04 22:39 |
-| E3    | 35.6 $R_{\odot}$            | Perihelion: 2019-09-01 17:50 |
-| E4    | 27.8 $R_{\odot}$            | Perihelion: 2020-01-29 09:37 |
-| E5    | 27.8 $R_{\odot}$            | Perihelion: 2020-06-07 08:23 |
-| E6    | 20.3 $R_{\odot}$            | Perihelion: 2020-09-27 09:16 |
-| E7    | 20.3 $R_{\odot}$            | Perihelion: 2021-01-17 17:40 |
-| E8    | 0.074 AU (15.9 $R_{\odot}$) | Perihelion: 2021-04-29 08:48 |
-| E9    | 15.9 $R_{\odot}$            | Perihelion: 2021-08-09 19:11 |
-| E10   | 13.3 $R_{\odot}$            | Perihelion: 2021-11-21 08:23 |
-| E11   | 13.3 $R_{\odot}$            | Perihelion: 2022-02-25 15:38 |
-| E12   | 13.3 $R_{\odot}$            | Perihelion: 2022-06-01 22:51 |
-| E13   | 13.3 $R_{\odot}$            | Perihelion: 2022-09-06 06:04 |
-| E14   | 13.3 $R_{\odot}$            | Perihelion: 2022-12-11 13:16 |
-| E15   | 13.3 $R_{\odot}$            | Perihelion: 2023-03-17 20:30 |
-| E16   | 13.3 $R_{\odot}$            | Perihelion: 2023-06-22 03:46 |
-| E17   | 11.4 $R_{\odot}$            | Perihelion: 2023-09-27 23:28 |
-| E18   | 11.4 $R_{\odot}$            | Perihelion: 2023-12-29 00:54 |
-| E19   | 11.4 $R_{\odot}$            | Perihelion: 2024-03-30 02:20 |
-| E20   | 11.4 $R_{\odot}$            | Perihelion: 2024-06-30 03:46 |
-| E21   | 11.4 $R_{\odot}$            | Perihelion: 2024-09-30 05:13 |
-| E22   | 9.9 $R_{\odot}$             | Perihelion: 2024-12-24 11:41 |
-| E23   | 9.9 $R_{\odot}$             | Perihelion: 2025-03-22 22:25 |
-| E24   | 9.9 $R_{\odot}$             | Perihelion: 2025-06-19 09:09 |
+{{< embed notebooks/00_notes.ipynb#tbl-events >}}
 
@@
 ## Trange: Encounter 8
+
+![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
 

### 2024-01-29 index.qmd
update

@@
 
+Given timeseries $(R_a, \phi_a$, $R_b(t)$,
+
 ![](images/paste-11.png)
@@
 -   @velliUnderstandingOriginsHeliosphere2020
+
 -   @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
-    - > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
+
+    ```         
+    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
+    ```
 
@@
 
-> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
-Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
+## Events
+
+2018∕10∕24 PSP Earth
+
+```         
+file:/Users/zijin/projects/psp_conjunction/files/psp_v.vap?timerange=2018-10-23+through+2018-10-25
+```
+
+PSP plasma data is very sparse (6 data point/day)
+
+![](images/paste-13.png)
+
+### 2019∕04∕07
+
+``` txt
+file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
+file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
+file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
+file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
+file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
+```
+
+[ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 02](http://helioweather.net/missions/psp/per02/)
+
+::: {.column-page layout-nrow="1"}
+{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4 >}}
+
+{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4 >}}
+:::
+
+![](images/paste-15.png)
+
+![](images/paste-18.png)
+
+::: {.column-page layout-nrow="1"}
+![](images/paste-16.png)
+
+![](images/paste-17.png)
+:::
 
@@
 ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
+
+> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
+Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
 

### 2024-01-31 index.qmd
update

@@
 
-## Events
+# Events
 
-2018∕10∕24 PSP Earth
+## 2018-10-24 PSP Earth
 
@@
 
-### 2019∕04∕07
-
+## 2019-04-07
 ``` txt
@@
 
-![](images/paste-18.png)
+::: {.column-page layout-nrow="1"}
 
-::: {.column-page layout-nrow="1"}
-![](images/paste-16.png)
+![PSP observation](images/paste-18.png)
 
-![](images/paste-17.png)
+![ACE observation](images/paste-16.png)
+
+![ACE observation (continued)](images/paste-17.png)
 :::
 
-## Trange: Encounter 8
+# Trange: Encounter 8
 

### 2024-02-01 index.qmd
update

@@
 ## 2019-04-07
+
 ``` txt
+file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-01+through+2019-04-15
 file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
@@
 
+![](images/paste-19.png)
+
 ::: {.column-page layout-nrow="1"}
-
 ![PSP observation](images/paste-18.png)
@@
 ![ACE observation (continued)](images/paste-17.png)
+:::
+
+Summary plot
+
+::: {.column-screen-inset layout-nrow="1"}
+![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)
+
+![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)
+
+![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)
+
+![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
 :::

### 2024-02-05 presentations/grp.qmd
remove freeze

---
title: Presentation
format:
  html: default
  revealjs:
    output-file: 'grp-revealjs.html'
---

![](../figures/evolution/plasma-adiabatic-evolution-previous.svg)

![](../figures/evolution/plasma-adiabatic-evolution.svg)

![](../figures/evolution/plasma-adiabatic-evolution-next.svg)

### 2024-02-05 presentations/grp.qmd
update websites
update

@@
 ---
-title: Presentation
+title: Group Meeting
 format:
-  html: default
-  revealjs:
-    output-file: 'grp-revealjs.html'
+  dashboard:
+    nav-buttons: [github]
+navbar: false
 ---
+
+# #1 Overview {orientation="columns"}
+
+## Orbits
+
+::: {.card title="Orbit in Heliographic Coordinates"}
+![](../images/paste-15.png)
+:::
+
+## ENLIL simulation
+
+::: {.card title="ENLIL simulation"}
+### Normalized solar wind density at the ecliptic and the IMF lines
+
+![](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4){width="80%"}
+
+### Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft
+
+![](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4){width="80%"}
+:::
+
+# #2 Observation
+
+##  {.tabset}
+
+::: {.column-page layout-nrow="1"}
+![PSP Observation Overvall](../images/paste-19.png)
+
+![PSP observation](../images/paste-18.png){width="50%"}
+:::
+
+::: {.column-page layout-nrow="1"}
+![PSP observation](../images/paste-18.png)
+
+![ACE observation](../images/paste-16.png)
+
+![ACE observation (continued)](../images/paste-17.png)
+:::
+
+# #3 Plasma Adiabatic Evolution {orientation="columns"}
+
+##  {width="50%"}
+
+![](../figures/evolution/plasma-adiabatic-evolution.svg)
+
+###  {.tabset}
+
+![](../figures/evolution/plasma-adiabatic-evolution-next.svg)
 
@@
 
-![](../figures/evolution/plasma-adiabatic-evolution.svg)
+##  {.tabset}
 
-![](../figures/evolution/plasma-adiabatic-evolution-next.svg)
+::: card
+### @perroneRadialEvolutionSolar2019
+
+The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by
+
+$$n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}$$
+
+$$B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT$$
+
+The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation
+
+$$β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}.$$
+:::
+
+![](../images/sty3348fig5.jpeg){width="50%"}
+
+# #4 Examples of Discontinuities
+
+![](images/paste-1.png)
+
+![](images/paste-2.png)
+
+![](images/paste-3.png)

### 2024-02-08 article.qmd
update

---
title: Evolution of solar wind discontinuities in the inner heliosphere
subtitle: PSP and Earth conjunctions and alignments
author:
  - name: Zijin Zhang
    email: zijin@ucla.edu
    orcid: 0000-0002-9968-067X
    affiliation: University of California, Los Angeles
    roles: writing
    corresponding: true
  - name: Anton V. Artemyev
    email: aartemyev@igpp.ucla.edu
    orcid: 0000-0001-8823-4474
    affiliation: University of California, Los Angeles
  - name: Vassilis Angelopoulos
    orcid: 0000-0001-7024-1561
    affiliation: University of California, Los Angeles
affiliations:
  - id: ucla
    name: University of California, Los Angeles
---

![](./figures/density_distribution){#fig-distribution}

![](./figures/thickness_current){#fig-thickness-current}

::: {.column-page}
{{< embed notebooks/10_results.ipynb#fig-dn-db >}}

{{< embed notebooks/10_results.ipynb#fig-dv >}}
:::

### 2024-02-08 index.qmd
update
remove freeze
update websites

@@
     affiliation: University of California, Los Angeles
-  - name: Shi Chen
-    orcid: 0000-0002-2582-7085
-    affiliation: University of California, Los Angeles
 code-links:
@@
 # Updates
+
+## 02/08/2024
+
+![](./figures/density_distribution){#fig-distribution}
+
+![](./figures/thickness_current){#fig-thickness-current}
+
+::: {.column-page}
+{{< embed notebooks/10_results.ipynb#fig-dn-db >}}
+
+{{< embed notebooks/10_results.ipynb#fig-dv >}}
+:::
+
+##
+
+![](images/paste-20.png)
 
@@
 
-![](images/paste-19.png)
+![PSP Observation Overvall](images/paste-19.png)
 

### 2024-02-10 index.qmd
update

@@
 
+Why ARTEMIS electron data and Wind ion data?
+
+## 02/09/2024
+
+{{< embed notebooks/10_results.ipynb#fig-dvl >}}
+
+{{< embed notebooks/10_results.ipynb#fig-dn-dT >}}
+
+{{< embed notebooks/10_results.ipynb#fig-dT-dB >}}
+
 ## 02/08/2024
@@
 ::: {.column-page}
-{{< embed notebooks/10_results.ipynb#fig-dn-db >}}
+{{< embed notebooks/10_results.ipynb#fig-dn-dB >}}
 

### 2024-02-11 index.qmd
update

--- 2024-02-08 index.qmd
@@
 
-## 02/08/2024
+Why ARTEMIS electron data and Wind ion data?
 
-![](./figures/density_distribution){#fig-distribution}
+## 02/11/2024 (Encounter 4)
 
-![](./figures/thickness_current){#fig-thickness-current}
+::: {.column-screen-inset layout-nrow="1"}
 
-::: {.column-page}
-{{< embed notebooks/10_results.ipynb#fig-dn-db >}}
+![](figures/enc4/thickness_current)
 
-{{< embed notebooks/10_results.ipynb#fig-dv >}}
+![](figures/enc4/density_distribution)
+
+![](figures/enc4/dvl)
+:::
+
+::: {.column-screen-inset layout-nrow="1"}
+
+![](figures/enc4/dn-dT)
+
+![](figures/enc4/dT-dB)
+
+![](figures/enc4/dn-dB)
+:::
+
+## 02/09/2024 (Encounter 2)
+
+::: {.column-screen-inset layout-nrow="1"}
+
+![](figures/enc2/thickness_current)
+
+![](figures/enc2/density_distribution)
+
+![](figures/enc2/dvl)
+:::
+
+Pair plot
+
+::: {.column-screen-inset layout-nrow="1"}
+
+![](figures/enc2/dn-dT)
+
+![](figures/enc2/dT-dB)
+
+![](figures/enc2/dn-dB)
 :::
@@
     ```
-
-# PSP Encounter Infos
-
-[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)
-
-{{< embed notebooks/00_notes.ipynb#tbl-events >}}
-
-# Events
-
-## 2018-10-24 PSP Earth
-
-```         
-file:/Users/zijin/projects/psp_conjunction/files/psp_v.vap?timerange=2018-10-23+through+2018-10-25
-```
-
-PSP plasma data is very sparse (6 data point/day)
-
-![](images/paste-13.png)
-
-## 2019-04-07
-
-``` txt
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-01+through+2019-04-15
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
-file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
-```
-
-[ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 02](http://helioweather.net/missions/psp/per02/)
-
-::: {.column-page layout-nrow="1"}
-{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4 >}}
-
-{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4 >}}
-:::
-
-![](images/paste-15.png)
-
-![PSP Observation Overvall](images/paste-19.png)
-
-::: {.column-page layout-nrow="1"}
-![PSP observation](images/paste-18.png)
-
-![ACE observation](images/paste-16.png)
-
-![ACE observation (continued)](images/paste-17.png)
-:::
-
-Summary plot
-
-::: {.column-screen-inset layout-nrow="1"}
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)
-
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)
-
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)
-
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
-:::
-
-# Trange: Encounter 8
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
-
-> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
-Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
-
-> E8, C2, Q4, Q5, 24 April–1 May, 2021.
-Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb.
-In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April.
-STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude.
-This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.
-
--   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
--   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)
-
-2021-05-09
-
-05/09/2021
-
-![](images/wind.png)
-
-![](images/psp.png)
-
-vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp&id=vp_moment_RTN\[:,0\];vp_moment_RTN\[:,1\];vp_moment_RTN\[:,2\]&timerange=2021-05-07+through+2021-05-08
-
-\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()
-
-\|rebundle(psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0)\|magnitude()
-
--   ops: "\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()" title: "PSP/SWP_SPC Proton bulk velocity from the 1st moment of the reduced distribution function in \[inertial\] RTN coordinate system (All Qualities)" y: label: V (km/s)
--   ops: "\|rebundle(B_R,B_T,B_N)\|magnitude()" y: label: B (nT) title: PSP_FLD/MAG_RTN_1min Magnetic field in RTN coordinates (1 minute cadence)
-
-PSP/PSP/SWEAP/SPAN Partial Moment Velocity in RTN Coordinates and Sun reference frame \|rebundle(Vx RTN,Vy RTN,Vz RTN)\|magnitude()
-
-Wind or ACE
-
-![](images/paste-2.png)
-
-![](images/paste-1.png)
-
-<!-- ![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_1day_plots/2021/05/20210509-day.png) -->
-
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210510-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210513-3day.png)
-:::
-
-tr = '2021-05-06 22:46 to 2021-05-15 22:46' vp = getDataSet( 'vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp_SW&id=vp_moment_RTN', tr ) plot( 0, vp )
-
-density5min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/ace/mag/level_2_cdaweb/mfi_k0/2017/ac_k0_mfi_20170117_v01.cdf?Magnitude') dst60min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/omni/omni_cdaweb/hourly/2017/omni2_h0_mrg1hr_20170101_v01.cdf?DST')
-
-t5min= density5min.property(QDataSet.DEPEND_0)
-
-( density, flux, dst ) = synchronize( t5min, density5min, flux4min, dst60min, nn=1 ) \# experimental function (note there is a built-in function in Autoplot v2017a. plot( 1, flux ) plot( 2, dst )
-
-## Trange
-
-> C4, 18 September, b 2021.
-This will be an inferior triple SO–PSP–STEREO-A conjunction, with SO inside the orbit of Venus around 0.6 AU, PSP at about 0.7 AU, and STEREO-A at 0.9 AU.
-This will be an occasion for joint in situ studies of the properties of turbulence and dynamics of a solar wind stream between 0.5 and 1 AU.
-
-https://solar-mach.streamlit.app/?embedded=true&date=20210925&time=0000&coord_sys=0&plot_spirals=1&plot_sun_body_line=1&plot_trans=0&plot_markers=Numbers&long_offset=270&bodies=STEREO+A&bodies=Earth&bodies=BepiColombo&bodies=Parker+Solar+Probe&bodies=Solar+Orbiter&speeds=346&speeds=485&speeds=400&speeds=300&speeds=287&
-
-![](images/paste-8.png)
-
-![](images/paste-9.png)
-
-![](images/paste-7.png)
-
-![](images/paste-6.png)
-
-![](images/paste-10.png)
-
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210802-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210805-3day.png)
-:::
-
-## Trange: Encounter 11, 2022-02
-
-> E11, C6, Q8, Q9 23–27 February, 2022.
-PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth–
-
-![](images/paste-3.png)
-
-[![](images/paste-4.png)](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)
-
-![](images/paste-5.png)
-
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220225-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220228-3day.png)
-:::

### 2024-02-11 notebooks/events/01.qmd
update

# 2019-04-07

``` txt
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-01+through+2019-04-15
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

[ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 02](http://helioweather.net/missions/psp/per02/)

::: {.column-page layout-nrow="1"}
{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4 >}}

{{< video http://helioweather.net/missions/psp/per02/anim/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4 >}}
:::

![](../../images/paste-15.png)

![PSP Observation Overvall](../../images/paste-19.png)

::: {.column-page layout-nrow="1"}
![PSP observation](../../images/paste-18.png)

![ACE observation](../../images/paste-16.png)

![ACE observation (continued)](../../images/paste-17.png)
:::

Summary plot

::: {.column-screen-inset layout-nrow="1"}
![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
:::

### 2024-02-11 notebooks/events/index.qmd
update

---
title: Events
listing: default
---

Starting point for the PSP encounter analysis.

-   @telloniSpacecraftRadialAlignments2023
-   @velliUnderstandingOriginsHeliosphere2020

[Orbit Plotter - PSP Science Gateway](https://psp-gateway.jhuapl.edu/website/Tools/OrbitPlotter)

## 2020-01-28 PSP-Earth, E4

-   [WHPI - Campaign: 2226](https://whpi.hao.ucar.edu/whpi_campaign-cr2226.php)
    -   [WHPI - Parker Perihelion 4 Campaign Highlights](https://whpi.hao.ucar.edu/whpi_campaign-cr2226-highlights.php)
-   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)

> The orbit of Parker Solar Probe (Parker) during the 4th encounter with the Sun presented a unique opportunity for a multi-mission and multi-observatory collaboration as the 4th perihelion occurred nearly at the ***Sun-Earth*** line. This unprecedented configuration allowed ground-based solar observatories to measure the solar surface that Parker was magnetically connected to while Parker simultaneously measured the near-Sun environment at the closest distance to the Sun recorded to date (27.8 RS). Additionally, near-Earth missions (e.g., ACE, ARTEMIS, and MMS) could then measure this solar wind once it reached 1 au to study the evolution of solar wind structures as they propagate radially outward from the Sun. Probes within the magnetosphere of Earth, and observatories focused on the ionosphere, could then study how these structures affect the near-Earth environment. To take advantage of this great opportunity for large-scale coordinated science, the Parker Project Science team and the Whole Heliosphere and Planetary Interactions (WHPI) group organized a campaign that has brought together observatories and missions from across the world. This page is meant to contain information and links relevant to the Parker Solar Probe Encounter 4 campaign. For more information, please contact Robert C. Allen (Robert.Allen\@jhuapl.edu), the Parker Project Science team coordinator for this effort.

Conjunction with In Situ Observations

> In addition to magnetic footpoint mapping for solar observers, ballistic mappings were performed to estimate when solar wind observed at Parker may reach 1 au at either STEREO-A or near-Earth observers. This shows that the footpoints of STEREO-A and Parker may have been near each other from Jan 26th, 2020 to Jan 28th, 2020 (where the red lines cross the black horizontal line at 0), while the footpoints of Earth and Parker may have been close *from Jan 29th, 2020 until Jan 31st, 2020* (where the blue lines cross the zero-line).

::: {.column-page layout-nrow="1"}
![](images/paste-1.png)

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E4_orbit.png)
:::

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/Lag_from_PSP_to_STA_and_Earth.png)

Start Date: 20200125

End Date: 20200131

``` txt
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2020-01-20+through+2020-01-31
file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2020-01-27+through+2020-01-31
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

![](images/paste-2.png)

## ![](images/paste-5.png)![](images/paste-4.png)PSP Encounter Infos

[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)

{{< embed ../00_notes.ipynb#tbl-events >}}

## 2018-10-24 PSP Earth

```         
file:/Users/zijin/projects/psp_conjunction/files/psp_v.vap?timerange=2018-10-23+through+2018-10-25
```

PSP plasma data is very sparse (6 data point/day)

![](images/paste-13.png)

# Trange: Encounter 8

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)

> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth. Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.

> E8, C2, Q4, Q5, 24 April–1 May, 2021. Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb. In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April. STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude. This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.

-   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
-   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)

2021-05-09

05/09/2021

![](images/wind.png)

![](images/psp.png)

vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp&id=vp_moment_RTN\[:,0\];vp_moment_RTN\[:,1\];vp_moment_RTN\[:,2\]&timerange=2021-05-07+through+2021-05-08

\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()

\|rebundle(psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0)\|magnitude()

-   ops: "\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()" title: "PSP/SWP_SPC Proton bulk velocity from the 1st moment of the reduced distribution function in \[inertial\] RTN coordinate system (All Qualities)" y: label: V (km/s)
-   ops: "\|rebundle(B_R,B_T,B_N)\|magnitude()" y: label: B (nT) title: PSP_FLD/MAG_RTN_1min Magnetic field in RTN coordinates (1 minute cadence)

PSP/PSP/SWEAP/SPAN Partial Moment Velocity in RTN Coordinates and Sun reference frame \|rebundle(Vx RTN,Vy RTN,Vz RTN)\|magnitude()

Wind or ACE

![](images/paste-2.png)

![](images/paste-1.png)

<!-- ![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_1day_plots/2021/05/20210509-day.png) -->

::: {.column-page layout-nrow="1"}
![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210510-3day.png)

![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210513-3day.png)
:::

tr = '2021-05-06 22:46 to 2021-05-15 22:46' vp = getDataSet( 'vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp_SW&id=vp_moment_RTN', tr ) plot( 0, vp )

density5min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/ace/mag/level_2_cdaweb/mfi_k0/2017/ac_k0_mfi_20170117_v01.cdf?Magnitude') dst60min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/omni/omni_cdaweb/hourly/2017/omni2_h0_mrg1hr_20170101_v01.cdf?DST')

t5min= density5min.property(QDataSet.DEPEND_0)

( density, flux, dst ) = synchronize( t5min, density5min, flux4min, dst60min, nn=1 ) \# experimental function (note there is a built-in function in Autoplot v2017a. plot( 1, flux ) plot( 2, dst )

## Trange

> C4, 18 September, b 2021. This will be an inferior triple SO–PSP–STEREO-A conjunction, with SO inside the orbit of Venus around 0.6 AU, PSP at about 0.7 AU, and STEREO-A at 0.9 AU. This will be an occasion for joint in situ studies of the properties of turbulence and dynamics of a solar wind stream between 0.5 and 1 AU.

https://solar-mach.streamlit.app/?embedded=true&date=20210925&time=0000&coord_sys=0&plot_spirals=1&plot_sun_body_line=1&plot_trans=0&plot_markers=Numbers&long_offset=270&bodies=STEREO+A&bodies=Earth&bodies=BepiColombo&bodies=Parker+Solar+Probe&bodies=Solar+Orbiter&speeds=346&speeds=485&speeds=400&speeds=300&speeds=287&

![](images/paste-8.png)

![](images/paste-9.png)

![](images/paste-7.png)

![](images/paste-6.png)

![](images/paste-10.png)

::: {.column-page layout-nrow="1"}
![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210802-3day.png)

![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210805-3day.png)
:::

## Trange: Encounter 11, 2022-02

> E11, C6, Q8, Q9 23–27 February, 2022. PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth–

![](images/paste-3.png)

[![](images/paste-4.png)](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)

![](images/paste-5.png)

::: {.column-page layout-nrow="1"}
![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220225-3day.png)

![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220228-3day.png)
:::

### 2024-02-20 index.qmd
update

@@
 
-Why ARTEMIS electron data and Wind ion data?
+- [x] Why ARTEMIS electron data and Wind ion data?
+
+## 02/20/2024
+
+{{< embed notebooks/02_psp_events.ipynb#fig-data-products >}}
+
+{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}
+
+{{< embed notebooks/10_results.ipynb#fig-dvl >}}
+
+::: {.column-screen-inset layout-nrow="1"}
+{{< embed notebooks/10_results.ipynb#fig-dn-dT >}}
+{{< embed notebooks/10_results.ipynb#fig-dT-dB >}}
+{{< embed notebooks/10_results.ipynb#fig-dn-dB >}}
+:::
 

### 2024-02-22 index.qmd
update

@@
 - [x] Why ARTEMIS electron data and Wind ion data?
+- [ ] Disagreement between anisotropy observed and predicted by the theory
+
+## 02/22/2024
+
+::: {.column-screen-inset layout-nrow="1"}
+{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}
+
+{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp >}}
+:::
+
+::: {.column-screen-inset layout-nrow="1"}
+{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-2d >}}
+
+{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-i-e >}}
+:::
 
@@
 {{< embed notebooks/02_psp_events.ipynb#fig-data-products >}}
-
-{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}
 

### 2024-02-22 notebooks/events/01.qmd
update

@@
-# 2019-04-07
-
-``` txt
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-01+through+2019-04-15
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
-file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
-```
+# Encounter2 (2019-04-07)
 
@@
 
+## Observations
+
 ![PSP Observation Overvall](../../images/paste-19.png)
@@
 
-Summary plot
+### Summary plot
 
 ::: {.column-screen-inset layout-nrow="1"}
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)
+![2019-04-05](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)
 
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)
+![2019-04-06](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)
 
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)
+![2019-04-07](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)
 
-![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
+![2019-04-08](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
 :::
+
+## ARTEMIS
+
+::: {.column-page layout-nrow="1"}
+![](http://themis.ssl.berkeley.edu/themisdata/thg/l0/asi/2019/04/orbit_moon_2019-04-09_0024.gif)
+
+![](http://themis.ssl.berkeley.edu/themisdata/thg/l0/asi/2019/04/orbit_moon_2019-04-12_0024.gif)
+:::
+
+## Scripts
+
+``` txt
+file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-01+through+2019-04-15
+file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2019-04-06+through+2019-04-08
+file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
+file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
+file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
+file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
+```

### 2024-02-22 notebooks/utils/__init__.py

@@ -1,0 +1,319 @@
+from datetime import timedelta
+from sunpy.time import TimeRange
+from pydantic import BaseModel
+from typing import Literal
+
+from discontinuitypy.datasets import IDsDataset
+from space_analysis.utils.speasy import Variables
+from beforerr.polars import pl_norm
+import polars as pl
+
+from speasy import SpeasyVariable
+from rich import print
+
+from loguru import logger
+
+import astropy.units as u
+from astropy.constants import m_p, mu0
+
+from typing_extensions import TypedDict
+
+
+# class Meta(TypedDict):
+class Meta(BaseModel):
+    dataset: str = None
+    parameters: list[str] = None
+
+
+class PlasmaMeta(Meta):
+    density_col: str = None
+    velocity_cols: list[str] = None
+    speed_col: str = None
+    temperature_col: str = None
+
+
+class TempMeta(Meta):
+    para_col: str = None
+    perp_cols: list[str] = None
+
+
+def thermal_spd2temp(speed, speed_unit=u.km / u.s):
+    return (m_p * (speed * speed_unit) ** 2 / 2).to("eV").value
+
+
+def df_thermal_spd2temp(ldf: pl.LazyFrame, speed_col, speed_unit=u.km / u.s):
+    df = ldf.collect()
+    return df.with_columns(
+        plasma_temperature=thermal_spd2temp(df[speed_col].to_numpy(), speed_unit)
+    ).lazy()
+
+
+def df_p2temp(ldf: pl.LazyFrame, p_col, density_col):
+    """converts the pressure to temperature"""
+    return ldf.with_columns(plasma_temperature=pl.col(p_col) * pl.col(density_col))
+
+
+def validate(timerange):
+    if isinstance(timerange, TimeRange):
+        return [timerange.start.to_string(), timerange.end.to_string()]
+
+
+def _standardize_plasma_temperature(data: pl.LazyFrame, s_var: SpeasyVariable):
+    temperature_col = s_var.columns[0]
+
+    if s_var.unit == "km/s":
+        return data.pipe(df_thermal_spd2temp, temperature_col)
+    elif s_var.unit == "eV/cm^3":
+        return data.pipe(df_p2temp, temperature_col, "plasma_density")
+    else:
+        return data.rename({temperature_col: "plasma_temperature"})
+
+
[…]

### 2024-02-29 article.qmd
update

@@
 
-![](./figures/density_distribution){#fig-distribution}
+![](figures/density_distribution){#fig-distribution}
 
-![](./figures/thickness_current){#fig-thickness-current}
+![](figures/thickness_current){#fig-thickness-current}
 
-::: {.column-page}
-{{< embed notebooks/10_results.ipynb#fig-dn-db >}}
+::: {#fig-plasma-adiabatic-evolution .column-page}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
 
-{{< embed notebooks/10_results.ipynb#fig-dv >}}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+<!-- Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
+Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
+-->
 :::
+
+::: {#fig-examples .column-page}
+
+![](figures/examples/psp_e2_example.png)
+
+Solar wind discontinuities examples observed by PSP and ARTEMIS fitted by a logistic function in LMN coordinates.
+
+In general discontinuities observed by PSP is much shorter (1~5 secs) with larger current density.
+:::
+
+![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current_spc_n_spc.png){#fig-comp-map}
+
+Solar wind properties
+
+L:
+j:
+$\Delta v_l$

### 2024-02-29 notebooks/events/e4.qmd
update

--- 2024-02-11 notebooks/events/index.qmd
@@
----
-title: Events
-listing: default
----
-
-Starting point for the PSP encounter analysis.
-
--   @telloniSpacecraftRadialAlignments2023
--   @velliUnderstandingOriginsHeliosphere2020
-
-[Orbit Plotter - PSP Science Gateway](https://psp-gateway.jhuapl.edu/website/Tools/OrbitPlotter)
-
-## 2020-01-28 PSP-Earth, E4
+# Encounter 4 (2020-01-28)
 
@@
 
-## ![](images/paste-5.png)![](images/paste-4.png)PSP Encounter Infos
-
-[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)
-
-{{< embed ../00_notes.ipynb#tbl-events >}}
-
-## 2018-10-24 PSP Earth
-
-```         
-file:/Users/zijin/projects/psp_conjunction/files/psp_v.vap?timerange=2018-10-23+through+2018-10-25
-```
-
-PSP plasma data is very sparse (6 data point/day)
-
-![](images/paste-13.png)
-
-# Trange: Encounter 8
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
-
-> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
-Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
-
-> E8, C2, Q4, Q5, 24 April–1 May, 2021.
-Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb.
-In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April.
-STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude.
-This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.
-
--   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
--   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)
-
-2021-05-09
-
-05/09/2021
-
-![](images/wind.png)
-
-![](images/psp.png)
-
-vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp&id=vp_moment_RTN\[:,0\];vp_moment_RTN\[:,1\];vp_moment_RTN\[:,2\]&timerange=2021-05-07+through+2021-05-08
-
-\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()
-
-\|rebundle(psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0,psp_fld_l2_mag_RTN_1min\_\_0)\|magnitude()
-
--   ops: "\|rebundle(vp_moment_R,vp_moment_T,vp_moment_N)\|magnitude()" title: "PSP/SWP_SPC Proton bulk velocity from the 1st moment of the reduced distribution function in \[inertial\] RTN coordinate system (All Qualities)" y: label: V (km/s)
--   ops: "\|rebundle(B_R,B_T,B_N)\|magnitude()" y: label: B (nT) title: PSP_FLD/MAG_RTN_1min Magnetic field in RTN coordinates (1 minute cadence)
-
-PSP/PSP/SWEAP/SPAN Partial Moment Velocity in RTN Coordinates and Sun reference frame \|rebundle(Vx RTN,Vy RTN,Vz RTN)\|magnitude()
-
-Wind or ACE
-
-![](images/paste-2.png)
-
-![](images/paste-1.png)
-
-<!-- ![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_1day_plots/2021/05/20210509-day.png) -->
-
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210510-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210513-3day.png)
-:::
-
-tr = '2021-05-06 22:46 to 2021-05-15 22:46' vp = getDataSet( 'vap+cdaweb:ds=PSP_SWP_SPC_L3I&filter=psp_SW&id=vp_moment_RTN', tr ) plot( 0, vp )
-
-density5min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/ace/mag/level_2_cdaweb/mfi_k0/2017/ac_k0_mfi_20170117_v01.cdf?Magnitude') dst60min= getDataSet( 'http://cdaweb.gsfc.nasa.gov/pub/data/omni/omni_cdaweb/hourly/2017/omni2_h0_mrg1hr_20170101_v01.cdf?DST')
-
-t5min= density5min.property(QDataSet.DEPEND_0)
-
-( density, flux, dst ) = synchronize( t5min, density5min, flux4min, dst60min, nn=1 ) \# experimental function (note there is a built-in function in Autoplot v2017a. plot( 1, flux ) plot( 2, dst )
-
-## Trange
-
-> C4, 18 September, b 2021.
-This will be an inferior triple SO–PSP–STEREO-A conjunction, with SO inside the orbit of Venus around 0.6 AU, PSP at about 0.7 AU, and STEREO-A at 0.9 AU.
-This will be an occasion for joint in situ studies of the properties of turbulence and dynamics of a solar wind stream between 0.5 and 1 AU.
-
-https://solar-mach.streamlit.app/?embedded=true&date=20210925&time=0000&coord_sys=0&plot_spirals=1&plot_sun_body_line=1&plot_trans=0&plot_markers=Numbers&long_offset=270&bodies=STEREO+A&bodies=Earth&bodies=BepiColombo&bodies=Parker+Solar+Probe&bodies=Solar+Orbiter&speeds=346&speeds=485&speeds=400&speeds=300&speeds=287&
-
-![](images/paste-8.png)
-
-![](images/paste-9.png)
-
-![](images/paste-7.png)
-
-![](images/paste-6.png)
-
-![](images/paste-10.png)
-
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210802-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2021/20210805-3day.png)
-:::
-
-## Trange: Encounter 11, 2022-02
-
-> E11, C6, Q8, Q9 23–27 February, 2022.
-PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth–
-
-![](images/paste-3.png)
-
-[![](images/paste-4.png)](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)
+##
 
@@
 
-::: {.column-page layout-nrow="1"}
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220225-3day.png)
-
-![](https://www.ngdc.noaa.gov/dscovr/plots/dscovr_3day_plots/2022/20220228-3day.png)
-:::
+![](images/paste-4.png)

### 2024-02-29 notebooks/events/index.qmd
update

@@
 
+[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)
+
 [Orbit Plotter - PSP Science Gateway](https://psp-gateway.jhuapl.edu/website/Tools/OrbitPlotter)
-
-## 2020-01-28 PSP-Earth, E4
-
--   [WHPI - Campaign: 2226](https://whpi.hao.ucar.edu/whpi_campaign-cr2226.php)
-    -   [WHPI - Parker Perihelion 4 Campaign Highlights](https://whpi.hao.ucar.edu/whpi_campaign-cr2226-highlights.php)
--   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)
-
-> The orbit of Parker Solar Probe (Parker) during the 4th encounter with the Sun presented a unique opportunity for a multi-mission and multi-observatory collaboration as the 4th perihelion occurred nearly at the ***Sun-Earth*** line.
-This unprecedented configuration allowed ground-based solar observatories to measure the solar surface that Parker was magnetically connected to while Parker simultaneously measured the near-Sun environment at the closest distance to the Sun recorded to date (27.8 RS).
-Additionally, near-Earth missions (e.g., ACE, ARTEMIS, and MMS) could then measure this solar wind once it reached 1 au to study the evolution of solar wind structures as they propagate radially outward from the Sun.
-Probes within the magnetosphere of Earth, and observatories focused on the ionosphere, could then study how these structures affect the near-Earth environment.
-To take advantage of this great opportunity for large-scale coordinated science, the Parker Project Science team and the Whole Heliosphere and Planetary Interactions (WHPI) group organized a campaign that has brought together observatories and missions from across the world.
-This page is meant to contain information and links relevant to the Parker Solar Probe Encounter 4 campaign.
-For more information, please contact Robert C.
-Allen (Robert.Allen\@jhuapl.edu), the Parker Project Science team coordinator for this effort.
-
-Conjunction with In Situ Observations
-
-> In addition to magnetic footpoint mapping for solar observers, ballistic mappings were performed to estimate when solar wind observed at Parker may reach 1 au at either STEREO-A or near-Earth observers.
-This shows that the footpoints of STEREO-A and Parker may have been near each other from Jan 26th, 2020 to Jan 28th, 2020 (where the red lines cross the black horizontal line at 0), while the footpoints of Earth and Parker may have been close *from Jan 29th, 2020 until Jan 31st, 2020* (where the blue lines cross the zero-line).
-
-::: {.column-page layout-nrow="1"}
-![](images/paste-1.png)
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E4_orbit.png)
-:::
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/Lag_from_PSP_to_STA_and_Earth.png)
-
-Start Date: 20200125
-
-End Date: 20200131
-
-``` txt
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2020-01-20+through+2020-01-31
-file:///Users/zijin/projects/autoplot/psp_mag_sw.vap?timerange=2020-01-27+through+2020-01-31
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/ace.vap?timerange=2019-04-11+through+2019-04-14
-file:///Users/zijin/projects/autoplot/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
-file:///Users/zijin/projects/autoplot/dscovr.vap?timerange=2019-04-08+through+2019-04-10
-```
-
-![](images/paste-2.png)
-
-## ![](images/paste-5.png)![](images/paste-4.png)PSP Encounter Infos
-
-[PSP Science Planning](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters)
 
@@
 
-# Trange: Encounter 8
+## Trange: Encounter 8
 
@@
 2021-05-09
-
-05/09/2021
 

### 2024-02-29 presentations/sparthb.qmd
update

---
title: "Solar Wind Discontinuities: Parker Solar Probe vs ARTEMIS Observations"
subtitle: SPARTHB
author:
  - name: Zijin Zhang
  - name: Anton V. Artemyev
  - name: Vassilis Angelopoulos
  - name: Chen Shi
  - name: Zesen Huang
# format: revealjs
format:
  pptx:
    slide-level: 2
  html: default
  revealjs:
    output-file: 'sparthb.revealjs.html'
slide-number: true
---

## Solar wind discontinuities (SWD)

Discontinuous changes in plasmas parameters and magnetic fields

## Formation of SWD

Turbulent ion heating by reconnection of tangential discontinuities. (a) Current density (color) and magnetic field lines, possible reconnection sites are indicated by crosses. (b) The proton temperature anisotropy (color) that indicates acceleration

Alfven wave steepening results in the discontinuity formation: magnetic energy transport from large scale (Alfven waves generated in the solar corona) to small (ion kinetic) scales of discontinuities, where this energy can be dissipated to particle heating

## Motivation

Studying the radial distribution of occurrence rate, as well as the properties of solar wind discontinuities may help answer the following questions:

- How does the discontinuities change with the radial distance from the Sun?

- How is solar wind discontinuities formed? What is the physical mechanisms?

  - Generated at or near the sun?

  - Locally generated in the interplanetary space by turbulence?

## Evolution with radial distance

## Orbits

:::: {.columns}

::: {.column}
![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E4_orbit.png)
:::

::: {.column}
![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/Lag_from_PSP_to_STA_and_Earth.png)

![](../notebooks/events/images/paste-1.png)
:::

::::

## ENLIL simulation

<!-- ![Normalized solar wind density at the ecliptic and the IMF lines](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4) -->

<!-- ![Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4) -->

## Observation

:::: {.columns}

::: {.column}
![PSP Observation Overvall](../images/paste-19.png)
:::

::: {.column}
![PSP observation](../images/paste-18.png)
:::

::::

## Observation (continued)

:::: {.columns}

::: {.column}
![PSP observation](../images/paste-18.png)
:::

::: {.column}
![ACE observation](../images/paste-16.png)
:::

::: {.column}
![ACE observation (continued)](../images/paste-17.png)
:::

::::

## Examples of discontinuities

![](../figures/examples/psp_e2_example.png)

Solar wind discontinuities examples observed by PSP and ARTEMIS fitted by a logistic function in LMN coordinates.

In general discontinuities observed by PSP is much shorter (1~5 secs) with larger current density.

## Identification/Detection method

## Properties of discontinuities

![](../figures/examples/psp_e2_example.png)

Every discontinuity's L component is fitted by a tanh (logistic) function.

$L$: thickness of the discontinuity

$J_0$: maxium current density

$\Delta v_l$

## Plasma adiabatic evolution

:::: {.columns}
::: {.column}
![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)

![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)

![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
:::

::: {.column}

![](../images/sty3348fig5.jpeg)

@perroneRadialEvolutionSolar2019
:::
::::

<!-- 
The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by

$$
n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
$$

$$
B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
$$

The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation

$$
β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
$$ -->

## Comparison with discontinuities properties

## Comparison with Alfven speed and plasma speed change

## Comparison with anisotropy

## Conclusion

### 2024-02-29 notebooks/utils/__init__.py

@@ -1,10 +1,11 @@
 from datetime import timedelta
 from sunpy.time import TimeRange
-from pydantic import BaseModel
 from typing import Literal
 
 from discontinuitypy.datasets import IDsDataset
 from space_analysis.utils.speasy import Variables
+from space_analysis.ds.meta import Meta, PlasmaMeta, TempMeta
+from discontinuitypy.config import SpeasyIDsConfig
 from beforerr.polars import pl_norm
 import polars as pl
 
@@ -15,26 +16,6 @@ from loguru import logger
 
 import astropy.units as u
 from astropy.constants import m_p, mu0
-
-from typing_extensions import TypedDict
-
-
-# class Meta(TypedDict):
-class Meta(BaseModel):
-    dataset: str = None
-    parameters: list[str] = None
-
-
-class PlasmaMeta(Meta):
-    density_col: str = None
-    velocity_cols: list[str] = None
-    speed_col: str = None
-    temperature_col: str = None
-
-
-class TempMeta(Meta):
-    para_col: str = None
-    perp_cols: list[str] = None
 
 
 def thermal_spd2temp(speed, speed_unit=u.km / u.s):
@@ -69,7 +50,7 @@ def _standardize_plasma_temperature(data: pl.LazyFrame, s_var: SpeasyVariable):
         return data.rename({temperature_col: "plasma_temperature"})
 
 
-def standardize_plasma_data(data: pl.LazyFrame, p_vars: Variables):
+def standardize_plasma_data(data: pl.LazyFrame, p_vars: Variables, meta: Meta = None):
 
     density_col = p_vars.data[0].columns[0]
     vec_cols = p_vars.data[1].columns
@@ -83,59 +64,9 @@ def standardize_plasma_data(data: pl.LazyFrame, p_vars: Variables):
     else:
         return data
 
-
-class IDsConfig(BaseModel):
-
-    tau: timedelta = None
-    ts: timedelta = None
-    timerange: list[str] = None
-
-    mag_meta: Meta = None
-    plasma_meta: PlasmaMeta = None
-    ion_temp_meta: TempMeta = None
-    e_temp_meta: TempMeta = None
+class IDsConfig(SpeasyIDsConfig):
 
     fname: str = "ids_ds"
-    fmt: str = "arrow"
-
-    _cached_vars: dict[str, Variables] = {}
-
-    def get_cached_vars(self, vars: str):
-        if vars not in self._cached_vars:
[…]

### 2024-03-16 notebooks/events/index.qmd
update

@@
 
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png) ![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
+![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png)
+
+![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
 

### 2024-03-16 presentations/sparthb.qmd
update

@@
 format:
+  html: default
   pptx:
     slide-level: 2
-  html: default
   revealjs:
@@
 Discontinuous changes in plasmas parameters and magnetic fields
+
+- Import element of solar wind turbulences
+
+- Very kinetic structure: interact with energetic part of the solar wind ions
 
@@
 
-Studying the radial distribution of occurrence rate, as well as the properties of solar wind discontinuities may help answer the following questions:
+Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
 
@@
 
-## Evolution with radial distance
+## In-situ synergistic observations
+
+**Similar** type of solar wind or **Same** solar solar wind
+
+How to define alignment?
+
+- Trajectory & Orbits (theory): ballistic approximation of Parker spiral
+
+- Plasma properties (observation):
+
+  - Invariants: plasma composition, ionization states, mass flux $n u r^2$
+
+  - Correlation: magnetic field / plasma velocity
+
+- Simulation: Trace plasma parcels evolution
+
+<!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
+-->
 
@@
 
-![](../notebooks/events/images/paste-1.png)
+![Heliographic frame (corotating with Sun)](../notebooks/events/images/paste-1.png)
 :::
@@
 
-<!-- ![Normalized solar wind density at the ecliptic and the IMF lines](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4) -->
+::: {.content-visible when-format="html"}
 
-<!-- ![Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4) -->
+![Normalized solar wind density at the ecliptic and the IMF lines](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4)
+
+![Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4)
+:::
 
@@
 :::
+::::
 
-::::
+---
+
+Time resolution (from high to low): SPC, SPI, SQTN, QTN
+
+Quality (fluctuating, from high to low): SQTN, QTN, SPC/SPI
+
+![Different Density Product ](../figures/examples/psp_density_comparison.png)
 
@@
 
-Solar wind discontinuities examples observed by PSP and ARTEMIS fitted by a logistic function in LMN coordinates.
+In general discontinuities observed by PSP are with
 
-In general discontinuities observed by PSP is much shorter (1~5 secs) with larger current density.
+- shorter duration (1~5 secs)
+
+  compared with 5-10 secs
+
+- large current density (100-1000 nA/m^2)
+
+  compared with 1-10 nA/m^2
 
 ## Identification/Detection method
+
+![](../figures/examples/detection_liu2022.png)
+
+@liuMagneticDiscontinuitiesSolar2022
+
+Compared with adjacent intervals without sampling
 
@@
 
-Every discontinuity's L component is fitted by a tanh (logistic) function.
+Every discontinuity's $l$ component is fitted by a $\tanh$ (logistic) function.
+
+Combined with plasma data ($n$, $v$, $T$)
 
@@
 
-$\Delta v_l$
+---
+
+If we expect the discontinuities to be generated locally, then the thickness of the discontinuities should be related to local plasma parameters:
+
+- Normalize thickness by $d_i$ (ion inertial length) or $r_i$ (ion gyroradius)
+- Normalize current density by $J_A$ (Alfven current density)
 
@@
 
+![](../figures/enc2/thickness_current.spi_n_spi.png)
+
+![](../figures/enc2/density_distribution.spi_n_spi.png)
+
+K1: Normalized discontinuities properties does not vary much with radial distance
+
+---
+
+![](../figures/enc2/thickness_current.spc_n_spc.png)
+
+![](../figures/enc2/density_distribution.spc_n_spc.png)
+
+K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
+
 ## Comparison with Alfven speed and plasma speed change
+
+For rotational discontinuities, the plasma velocity jump across them: the plasma ﬂow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$ [@hudsonDiscontinuitiesAnisotropicPlasma1970].
+
+![](../figures/enc2/dvl.spi_n_spi.png)
 
@@
 
+The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
+
+![](../figures/enc2/anisotropy.spi_n_spi.png)
+
+Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
+
 ## Conclusion
+
+- The properties of the discontinuities is related to the local plasma parameters
+  - Thickness => ion inertial length
+  - Current density => Alfven velocity (current density)
+- Normalized thickness and current density of discontinuities remain constant with radial distance
+- Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
+
+---
+
+## References

### 2024-03-27 notebooks/events/e7.qmd
update

# Encounter 7 (2021-01-17)

-   [WHPI - Campaign: PSP 7th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp7p.php)
-   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)

> The seventh encounter of Parker Solar Probe provides observations down to 0.09 au (20.3 RS). Because of the favorable alignment between Parker and Earth, the Parker mission has teamed with theWhole Heliosphere and Planetary Interactions (WHPI) group to orgnanize another multi-observatory campaign similar to the fourth encounter of Parker. From 2021 January 10 - 20, Parker footpoint predictions will be issued on a daily basis to the community.

https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E7_ParkerSpiral_mapping.png

> During the 7th PSP perihelion passage (January 17, 2021) the Earth and many space observatories were near-radially aligned with PSP, and STEREO A was along the Parker spiral from PSP.

------------------------------------------------------------------------

![](images/paste-6.png)

Start Date: 20210114 End Date: 20210121

``` txt
file:///Users/zijin/projects/autoplot/scripts/psp_mag_sw.vap?timerange=2021-01-14+through+2021-01-21
file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2021-01-15+through+2021-01-22
file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/scripts/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/scripts/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

![](images/paste-7.png)

![](images/paste-9.png)

### 2024-05-08 notebooks/events/e11.qmd
update

# Encounter 11

-   Perihelion: 2022-02-25T15:38

> E11, C6, Q8, Q9 23–27 February, 2022. PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU. There will be clear opportunities here for cross calibration of magnetic ﬁeld measurements, as well as a true stereoscopic reconstruction of the solar corona crossed by PSP, with opportunities for all the PSP–SO objectives.

> The eleventh encounter of Parker Solar Probe provides observations down to 0.062 au (13.3 R~S~). Since the footpoints of Parker will be visible from Earth when it is near perihelion, the Parker team has again partnered with the Whole Heliosphere and Planetary Interactions (WHPI) group to coordinate remote observing during this encounter. The first footpoint prediction will be issued on February 18th followed by daily updates form February 21st through 28th, 2022. For more information, please contact Robert C. Allen ([Robert.Allen\@jhuapl.edu](mailto:Robert.Allen@jhuapl.edu)), the Parker Project Science team coordinator for this effort and visit the[WHPI page for this campaign](https://whpi.hao.ucar.edu/whpi_campaign-psp11p.php).

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)

![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_orbit.png)

![](images/paste-14.png)

``` txt
file:///Users/zijin/projects/autoplot/scripts/psp_mag_sw.vap?timerange=2022-02-22+through+2022-03-01
file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2022-02-23+through+2022-03-02
```

------------------------------------------------------------------------

-   Perihelion: 2021-04-29
-   Start Date: 20210426 End Date: 20210503

-   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)

> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth. Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.

> E8, C2, Q4, Q5, 24 April–1 May, 2021. Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb. In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April. STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude. This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.

![](images/paste-10.png)

Start Date: 20210426 End Date: 20210503

``` txt
file:///Users/zijin/projects/autoplot/scripts/psp_mag_sw.vap?timerange=2021-04-26+through+2021-05-03
file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2021-04-27+through+2021-05-04
```

![](images/paste-11.png)

![](images/paste-12.png)

------------------------------------------------------------------------

```         
file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2019-04-11+through+2019-04-14
file:///Users/zijin/projects/autoplot/scripts/wind_plasma.vap?timerange=2019-04-08+through+2019-04-10
file:///Users/zijin/projects/autoplot/scripts/dscovr.vap?timerange=2019-04-08+through+2019-04-10
```

![](images/paste-7.png)

![](images/paste-9.png)

### 2024-05-08 notebooks/events/e7.qmd
update

@@
 -   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)
+
+> E7 and Q3, 14–18 January, 2021.
+>
+> During this interval, STEREO-A, Earth, and SO will provide 360◦ coverage of the heliosphere, and just before E7, on 14 January, 2021, PSP will be in conjunction with STEREO-A, followed by conjunction with Earth on 16, E7 on 17, and quadrature Q3 on the east limb (trailing) with SO on 18 January, 2021.
+Synergies here arise mostly from potential remote-sensing measurements from SO and STEREO-A and from assets on the PSP–Earth line (SDO, Hinode) and ground-based instrumentation.
 

### 2024-05-08 notebooks/events/e8.qmd
update

--- 2024-05-08 notebooks/events/e11.qmd
@@
-# Encounter 11
-
--   Perihelion: 2022-02-25T15:38
-
-> E11, C6, Q8, Q9 23–27 February, 2022.
-PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU.
-There will be clear opportunities here for cross calibration of magnetic ﬁeld measurements, as well as a true stereoscopic reconstruction of the solar corona crossed by PSP, with opportunities for all the PSP–SO objectives.
-
-> The eleventh encounter of Parker Solar Probe provides observations down to 0.062 au (13.3 R~S~).
-Since the footpoints of Parker will be visible from Earth when it is near perihelion, the Parker team has again partnered with the Whole Heliosphere and Planetary Interactions (WHPI) group to coordinate remote observing during this encounter.
-The first footpoint prediction will be issued on February 18th followed by daily updates form February 21st through 28th, 2022.
-For more information, please contact Robert C.
-Allen ([Robert.Allen\@jhuapl.edu](mailto:Robert.Allen@jhuapl.edu)), the Parker Project Science team coordinator for this effort and visit the[WHPI page for this campaign](https://whpi.hao.ucar.edu/whpi_campaign-psp11p.php).
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_HEE.png)
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E11_orbit.png)
-
-![](images/paste-14.png)
-
-``` txt
-file:///Users/zijin/projects/autoplot/scripts/psp_mag_sw.vap?timerange=2022-02-22+through+2022-03-01
-file:///Users/zijin/projects/autoplot/scripts/ace.vap?timerange=2022-02-23+through+2022-03-02
-```
-
-------------------------------------------------------------------------
+# Encounter 8
 
@@
 -   Start Date: 20210426 End Date: 20210503
+
+![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png)
+
+![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
 

### 2024-05-08 notebooks/events/index.qmd
update

@@
 
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_orbit.png)
-
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E8_HEE.png)
-
-> Using a nominal 400 km/s solar wind velocity, the following figures show the ballistic mapping in a helioprojective and heliographic frame, followed by an ecliptic view of the trajectory in the frame rotating with the Earth.
-Several Parker spirals are drawn, showing the possible magnetic connection to the Earth near May 9th.
-
-> E8, C2, Q4, Q5, 24 April–1 May, 2021.
-Throughout this period SO will be in quadrature with Earth, appearing from Earth on the solar east limb.
-In rapid succession over E8, PSP will appear in quadrature from SO on the east limb (trailing), then in conjunction with SO at perihelion on 28 April, with PSP at a distance of 15.5RS, then in conjunction with STEREO-A on 29 April and with Earth on 30 April.
-STEREO-A will be positioned trailing Earth by 45◦ midway to SO in longitude.
-This PSP encounter is extremely favorable to a potential joint in situ–remote-sensing campaign comprising PSP, SO, STEREOA, SDO, Hinode, and ground-based instrumentation.
-
--   [WHPI - Campaign: PSP 8th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp8p.php)
 -   [WHPI - Campaign: PSP 15th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp15p.php)

### 2024-05-08 notebooks/utils/__init__.py

@@ -79,6 +79,13 @@ def get_timerange(enc: int) -> list[str]:
 
             earth_start = '2020-01-29'
             earth_end = '2020-01-31'
+        
+        case 7:
+            start = '2021-01-14'
+            end = '2021-01-21'
+
+            earth_start = '2021-01-15'
+            earth_end = '2021-01-23'
 
     psp_timerange = [start, end]
     earth_timerange = [earth_start, earth_end]

### 2024-05-09 index.qmd
update

@@
 - [ ] Disagreement between anisotropy observed and predicted by the theory
+  - maybe just too localized anisotropy that is not well measured with available time resolution... 
+  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
+# TODO
+
+- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?
 
@@
 ## 02/20/2024
-
-{{< embed notebooks/02_psp_events.ipynb#fig-data-products >}}
 
@@
 
+# Alignment
+
+Composition and ionization state should remain invariant.
+
+PSP_ISOIS-EPILO_L2-IC:   Info  Metadata
+Parker Solar Probe ISOIS EPI-Lo Level 2 Ion Composition - David McComas (Princeton University)
+
 # References
@@
     ```
+
+## Anistropy
+
+@shenComparingPlasmaAnisotropy2024
+
+pressure anisotropy is defined as $Λ = \mu (P_∥ - P_⊥) / B^2$.

### 2024-05-09 notebooks/utils/config.py

@@ -1,0 +1,302 @@
+from space_analysis.ds.meta import Meta, PlasmaMeta, TempMeta
+from discontinuitypy.config import SpeasyIDsConfig
+from pathlib import Path
+
+from datetime import timedelta
+from sunpy.time import TimeRange
+from typing import Literal
+
+from space_analysis.utils.speasy import Variables
+from beforerr.polars import pl_norm
+import polars as pl
+
+from speasy import SpeasyVariable
+from rich import print
+
+from loguru import logger
+
+import astropy.units as u
+from astropy.constants import m_p, mu0
+
+
+def thermal_spd2temp(speed, speed_unit=u.km / u.s):
+    return (m_p * (speed * speed_unit) ** 2 / 2).to("eV").value
+
+
+def df_thermal_spd2temp(ldf: pl.LazyFrame, speed_col, speed_unit=u.km / u.s):
+    df = ldf.collect()
+    return df.with_columns(
+        plasma_temperature=thermal_spd2temp(df[speed_col].to_numpy(), speed_unit)
+    ).lazy()
+
+
+def df_p2temp(ldf: pl.LazyFrame, p_col, density_col):
+    """converts the pressure to temperature"""
+    return ldf.with_columns(plasma_temperature=pl.col(p_col) * pl.col(density_col))
+
+
+def validate(timerange):
+    if isinstance(timerange, TimeRange):
+        return [timerange.start.to_string(), timerange.end.to_string()]
+
+
+def _standardize_plasma_temperature(data: pl.LazyFrame, s_var: SpeasyVariable):
+    temperature_col = s_var.columns[0]
+
+    if s_var.unit == "km/s":
+        return data.pipe(df_thermal_spd2temp, temperature_col)
+    elif s_var.unit == "eV/cm^3":
+        return data.pipe(df_p2temp, temperature_col, "plasma_density")
+    else:
+        return data.rename({temperature_col: "plasma_temperature"})
+
+
+def standardize_plasma_data(data: pl.LazyFrame, p_vars: Variables, meta: Meta = None):
+
+    density_col = p_vars.data[0].columns[0]
+    vec_cols = p_vars.data[1].columns
+
+    data = data.with_columns(plasma_speed=pl_norm(vec_cols)).rename(
+        {density_col: "plasma_density"}
+    )
+
+    if len(p_vars.data) > 2:
[…]

### 2024-05-09 notebooks/utils/temp.py

@@ -1,0 +1,46 @@
+from astropy.constants import mu0
+import astropy.units as u
+import polars as pl
+from loguru import logger
+
+def calc_pressure_anisotropy(
+    df: pl.DataFrame,
+    density_col: str = "plasma_density",
+    ion_temp_para_col: str = "ion_temp_para",
+    ion_temp_perp_col: str = "ion_temp_perp",
+    e_temp_para_col: str = "e_temp_para",
+    e_temp_perp_col: str = "e_temp_perp",
+):
+    if density_col not in df.columns:
+        logger.warning(f"{density_col} not in dataframe")
+        logger.info("Need plasma density to calculate pressure anisotropy")
+        return df
+    
+    B = (df["B.before"].to_numpy() + df["B.after"].to_numpy()) / 2 * u.nT
+    n = df[density_col].to_numpy() * u.cm**-3
+    
+    if ion_temp_para_col in df.columns and ion_temp_perp_col in df.columns:
+        ion_temp_para = df[ion_temp_para_col].to_numpy() * u.eV
+        ion_temp_perp = df[ion_temp_perp_col].to_numpy() * u.eV
+        Λ_ion = (mu0 * n * (ion_temp_para - ion_temp_perp) / B**2).to(
+            u.dimensionless_unscaled
+        )
+        df = df.with_columns(Λ_ion=Λ_ion)
+    else:
+        Λ_ion = False
+        logger.info("Ion temperature columns not found")
+        
+    if e_temp_para_col in df.columns and e_temp_perp_col in df.columns:
+        e_temp_para = df[e_temp_para_col].to_numpy() * u.eV
+        e_temp_perp = df[e_temp_perp_col].to_numpy() * u.eV
+        Λ_e = (mu0 * n * (e_temp_para - e_temp_perp) / B**2).to(u.dimensionless_unscaled)
+        df = df.with_columns(Λ_e=Λ_e)
+    else:
+        Λ_e = False
+        logger.info("Electron temperature columns not found")
+
+    if Λ_e and Λ_ion:
+        Λ = Λ_ion + Λ_e
+        df = df.with_columns(Λ=Λ)
+
+    return df

### 2024-05-11 index.qmd
chore: remove embed

@@
 - [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?
-
-## 02/22/2024
-
-::: {.column-screen-inset layout-nrow="1"}
-{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}
-
-{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp >}}
-:::
-
-::: {.column-screen-inset layout-nrow="1"}
-{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-2d >}}
-
-{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-i-e >}}
-:::
-
-## 02/20/2024
-
-{{< embed notebooks/10_results.ipynb#fig-dvl >}}
-
-::: {.column-screen-inset layout-nrow="1"}
-{{< embed notebooks/10_results.ipynb#fig-dn-dT >}}
-{{< embed notebooks/10_results.ipynb#fig-dT-dB >}}
-{{< embed notebooks/10_results.ipynb#fig-dn-dB >}}
-:::
 

### 2024-05-11 article.qmd
update

@@
 
-![](figures/density_distribution){#fig-distribution}
+![](figures/density_distribution.png
 
-![](figures/thickness_current){#fig-thickness-current}
+![](figures/enc2/thickness_current.spc_n_spc.png)
 
@@
 
-![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current_spc_n_spc.png){#fig-comp-map}
+![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current.spc_n_spc.png){#fig-comp-map}
 

### 2024-05-12 index.qmd
chore: update dates and move updates to a different file

@@
 
-# Updates
+# Motivation
 
-- [x] Why ARTEMIS electron data and Wind ion data?
-- [ ] Disagreement between anisotropy observed and predicted by the theory
-  - maybe just too localized anisotropy that is not well measured with available time resolution... 
-  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
-# TODO
+Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
 
-- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?
+- How does the discontinuities change with the radial distance from the Sun?
 
-## 02/11/2024 (Encounter 4)
+- How is solar wind discontinuities formed? What is the physical mechanisms?
 
-::: {.column-screen-inset layout-nrow="1"}
+  - Generated at or near the sun?
 
-![](figures/enc4/thickness_current)
+  - Locally generated in the interplanetary space by turbulence?
 
-![](figures/enc4/density_distribution)
+# Methods
 
-![](figures/enc4/dvl)
-:::
+## In-situ synergistic observations (Alignment)
 
-::: {.column-screen-inset layout-nrow="1"}
+**Similar** type of solar wind or **Same** solar solar wind
 
-![](figures/enc4/dn-dT)
+How to define alignment?
 
-![](figures/enc4/dT-dB)
+- Trajectory & Orbits (theory): ballistic approximation of Parker spiral
 
-![](figures/enc4/dn-dB)
-:::
+- Plasma properties (observation):
 
-## 02/09/2024 (Encounter 2)
+  - Invariants: plasma composition, ionization states, mass flux $n u r^2$
 
-::: {.column-screen-inset layout-nrow="1"}
+  - Correlation: magnetic field / plasma velocity
 
-![](figures/enc2/thickness_current)
+- Simulation: Trace plasma parcels evolution
 
-![](figures/enc2/density_distribution)
-
-![](figures/enc2/dvl)
-:::
-
-Pair plot
-
-::: {.column-screen-inset layout-nrow="1"}
-
-![](figures/enc2/dn-dT)
-
-![](figures/enc2/dT-dB)
-
-![](figures/enc2/dn-dB)
-:::
-
-##
-
-![](images/paste-20.png)
-
-Given timeseries $(R_a, \phi_a$, $R_b(t)$,
-
-![](images/paste-11.png)
-
-![](images/paste-12.png)
-
-# Alignment
-
-Composition and ionization state should remain invariant.
-
-PSP_ISOIS-EPILO_L2-IC:   Info  Metadata
-Parker Solar Probe ISOIS EPI-Lo Level 2 Ion Composition - David McComas (Princeton University)
+<!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
+-->
 

### 2024-05-12 notes.qmd
chore: update dates and move updates to a different file

# Updates

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory
  - maybe just too localized anisotropy that is not well measured with available time resolution... 
  - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
# TODO

- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?

## 02/11/2024 (Encounter 4)

::: {.column-screen-inset layout-nrow="1"}

![](figures/enc4/thickness_current)

![](figures/enc4/density_distribution)

![](figures/enc4/dvl)
:::

::: {.column-screen-inset layout-nrow="1"}

![](figures/enc4/dn-dT)

![](figures/enc4/dT-dB)

![](figures/enc4/dn-dB)
:::

## 02/09/2024 (Encounter 2)

::: {.column-screen-inset layout-nrow="1"}

![](figures/enc2/thickness_current)

![](figures/enc2/density_distribution)

![](figures/enc2/dvl)
:::

Pair plot

::: {.column-screen-inset layout-nrow="1"}

![](figures/enc2/dn-dT)

![](figures/enc2/dT-dB)

![](figures/enc2/dn-dB)
:::

##

![](images/paste-20.png)

Given timeseries $(R_a, \phi_a$, $R_b(t)$,

![](images/paste-11.png)

![](images/paste-12.png)

### 2024-05-12 presentations/rMeeting.qmd
chore: update dates and move updates to a different file

--- 2024-03-16 presentations/sparthb.qmd
@@
 ---
-title: "Solar Wind Discontinuities: Parker Solar Probe vs ARTEMIS Observations"
+title: "Current Sheets in the Solar Wind: Parker Solar Probe Observations"
 subtitle: SPARTHB
@@
   - name: Vassilis Angelopoulos
-  - name: Chen Shi
-  - name: Zesen Huang
-# format: revealjs
 format:
@@
     slide-level: 2
-  revealjs:
-    output-file: 'sparthb.revealjs.html'
 slide-number: true
+date: "2024-05"
 ---
 
-## Solar wind discontinuities (SWD)
+<!-- 
+See [share notes](../../beforerr/docs/research/topics/swd/index.qmd) for
+- introduction
+- formation mechanisms
 
-Discontinuous changes in plasmas parameters and magnetic fields
-
-- Import element of solar wind turbulences
-
-- Very kinetic structure: interact with energetic part of the solar wind ions
-
-## Formation of SWD
-
-Turbulent ion heating by reconnection of tangential discontinuities.
-(a) Current density (color) and magnetic field lines, possible reconnection sites are indicated by crosses.
-(b) The proton temperature anisotropy (color) that indicates acceleration
-
-Alfven wave steepening results in the discontinuity formation: magnetic energy transport from large scale (Alfven waves generated in the solar corona) to small (ion kinetic) scales of discontinuities, where this energy can be dissipated to particle heating
-
-## Motivation
-
-Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
-
-- How does the discontinuities change with the radial distance from the Sun?
-
-- How is solar wind discontinuities formed? What is the physical mechanisms?
-
-  - Generated at or near the sun?
-
-  - Locally generated in the interplanetary space by turbulence?
-
-## In-situ synergistic observations
-
-**Similar** type of solar wind or **Same** solar solar wind
-
-How to define alignment?
-
-- Trajectory & Orbits (theory): ballistic approximation of Parker spiral
-
-- Plasma properties (observation):
-
-  - Invariants: plasma composition, ionization states, mass flux $n u r^2$
-
-  - Correlation: magnetic field / plasma velocity
-
-- Simulation: Trace plasma parcels evolution
-
-<!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
+See [sparthrb](./sparthb.qmd) for alignment and observation details
 -->
-
-## Orbits
-
-:::: {.columns}
-
-::: {.column}
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/E4_orbit.png)
-:::
-
-::: {.column}
-![](https://psp-gateway.jhuapl.edu/website/SciencePlanning/Encounters/Lag_from_PSP_to_STA_and_Earth.png)
-
-![Heliographic frame (corotating with Sun)](../notebooks/events/images/paste-1.png)
-:::
-
-::::
-
-## ENLIL simulation
-
-::: {.content-visible when-format="html"}
-
-![Normalized solar wind density at the ecliptic and the IMF lines](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_den1-psp-x15wifs3z1fo_med_201903-201904.mp4)
-
-![Radial solar wind velocity at the ecliptic on the global and detail regions together with the temporal profile at spacecraft](../images/enlil/tuz-a7b1-d4t05x1-d200t1-donki_vel2e1-psp-x15ifs3z1fr_med_201903-201904.mp4)
-:::
-
-## Observation
-
-:::: {.columns}
-
-::: {.column}
-![PSP Observation Overvall](../images/paste-19.png)
-:::
-
-::: {.column}
-![PSP observation](../images/paste-18.png)
-:::
-
-::::
-
-## Observation (continued)
-
-:::: {.columns}
-
-::: {.column}
-![PSP observation](../images/paste-18.png)
-:::
-
-::: {.column}
-![ACE observation](../images/paste-16.png)
-:::
-
-::: {.column}
-![ACE observation (continued)](../images/paste-17.png)
-:::
-::::
-
----
-
-Time resolution (from high to low): SPC, SPI, SQTN, QTN
-
-Quality (fluctuating, from high to low): SQTN, QTN, SPC/SPI
-
-![Different Density Product ](../figures/examples/psp_density_comparison.png)
 

### 2024-05-12 presentations/sparthb.qmd
chore: update dates and move updates to a different file

@@
 slide-number: true
+date: "2024-03"
 ---

### 2024-05-13 index.qmd
chore: move content locations

@@
 
+### High-speed solar wind radial evolution
+
+:::: {.columns}
+::: {.column}
+![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+
+![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
+:::
+
+::: {.column}
+
+![](../images/sty3348fig5.jpeg)
+
+@perroneRadialEvolutionSolar2019
+:::
+::::
+
+::: {.notes}
+The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by
+
+$$
+n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
+\\
+B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
+$$
+
+The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation
+
+$$
+β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
+$$ 
+:::
+
+## Examples of discontinuities
+
+![](../figures/examples/psp_e2_example.png)
+
+In general discontinuities observed by PSP are with
+
+- shorter duration (1~5 secs)
+
+  compared with 5-10 secs
+
+- large current density (100-1000 nA/m^2)
+
+  compared with 1-10 nA/m^2
+
+# Results
+
+## Comparison of Discontinuity Properties
+
+![](../figures/enc2/thickness_current.spi_n_spi.png)
+
+![](../figures/enc2/density_distribution.spi_n_spi.png)
+
+K1: Normalized discontinuities properties does not vary much with radial distance
+
+## Comparison between Alfven speed and plasma speed change
+
+For rotational discontinuities, the plasma velocity jump across them: the plasma flow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$.
+
+![](figures/dvl.spi_n_spi.png)
+
+K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
+
+## Estimated Anisotropy
+
+The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
+
+Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
+
+![](figures/anisotropy_theory.png)
+
+## Comparison between Estimated and Observed Anisotropy
+
+![](figures/anisotropy_comparison_2d.png)
+
+# Conclusion
+
+- The properties of the discontinuities is related to the local plasma parameters
+  - Thickness => ion inertial length
+  - Current density => Alfven velocity (current density)
+- Normalized thickness and current density of discontinuities remain constant with radial distance
+- Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
+
 # References

### 2024-05-13 presentations/rMeeting.qmd
chore: move content locations

@@
 - formation mechanisms
-
 See [sparthrb](./sparthb.qmd) for alignment and observation details
+See [Main Website](../index.qmd) for the results
 -->
-
-## Examples of discontinuities
-
-![](../figures/examples/psp_e2_example.png)
-
-In general discontinuities observed by PSP are with
-
-- shorter duration (1~5 secs)
-
-  compared with 5-10 secs
-
-- large current density (100-1000 nA/m^2)
-
-  compared with 1-10 nA/m^2
-
-## Identification/Detection method
-
-![](../figures/examples/detection_liu2022.png)
-
-@liuMagneticDiscontinuitiesSolar2022
-
-Compared with adjacent intervals without sampling
-
-## Properties of discontinuities
-
-![](../figures/examples/psp_e2_example.png)
-
-Every discontinuity's $l$ component is fitted by a $\tanh$ (logistic) function.
-
-Combined with plasma data ($n$, $v$, $T$)
-
-$L$: thickness of the discontinuity
-
-$J_0$: maxium current density
-
----
-
-If we expect the discontinuities to be generated locally, then the thickness of the discontinuities should be related to local plasma parameters:
-
-- Normalize thickness by $d_i$ (ion inertial length) or $r_i$ (ion gyroradius)
-- Normalize current density by $J_A$ (Alfven current density)
-
-## Plasma adiabatic evolution
-
-:::: {.columns}
-::: {.column}
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
-
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
-
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
-:::
-
-::: {.column}
-
-![](../images/sty3348fig5.jpeg)
-
-@perroneRadialEvolutionSolar2019
-:::
-::::
-
-<!-- 
-The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by
-
-$$
-n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
-$$
-
-$$
-B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
-$$
-
-The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation
-
-$$
-β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
-$$ -->
-
-## Comparison with discontinuities properties
-
-![](../figures/enc2/thickness_current.spi_n_spi.png)
-
-![](../figures/enc2/density_distribution.spi_n_spi.png)
-
-K1: Normalized discontinuities properties does not vary much with radial distance
-
----
-
-![](../figures/enc2/thickness_current.spc_n_spc.png)
-
-![](../figures/enc2/density_distribution.spc_n_spc.png)
-
-K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
-
-## Comparison with Alfven speed and plasma speed change
-
-For rotational discontinuities, the plasma velocity jump across them: the plasma ﬂow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$ [@hudsonDiscontinuitiesAnisotropicPlasma1970].
-
-![](../figures/enc2/dvl.spi_n_spi.png)
-
-## Comparison with anisotropy
-
-The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
-
-![](../figures/enc2/anisotropy.spi_n_spi.png)
-
-Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
-
-## Conclusion
-
-- The properties of the discontinuities is related to the local plasma parameters
-  - Thickness => ion inertial length
-  - Current density => Alfven velocity (current density)
-- Normalized thickness and current density of discontinuities remain constant with radial distance
-- Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
-
----
-
-## References

### 2024-08-24 article.qmd
add agu extensions
update: manuscripts

@@
   - name: Vassilis Angelopoulos
+    email: vassilis@ucla.edu
     orcid: 0000-0001-7024-1561
     affiliation: University of California, Los Angeles
-affiliations:
-  - id: ucla
-    name: University of California, Los Angeles
+  - name: Tai Phan
+    email: phan@ssl.berkeley.edu
+    orcid: 0000-0002-6924-9408
+    affiliation: Space Sciences Laboratory, University of California, Berkeley
 ---
 
-![](figures/density_distribution.png
+# Plain Language Summary
 
-![](figures/enc2/thickness_current.spc_n_spc.png)
+# Introduction
+
+The study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind
+
+Previous statistical studies of solar wind discontinuities in the inner heliosphere @marianiStatisticalStudyMagnetohydrodynamic1983 @liuCharacteristicsInterplanetaryDiscontinuities2021
+
+Alignement study of solar wind discontinuities @artemyevDynamicsIntenseCurrents2018
+
+By indentifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions
+
+@hudsonDiscontinuitiesAnisotropicPlasma1970
+
+# Dataset and method
+
+## Dataset
+
+### PSP
+
+We use the high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments on board the Parker Solar Probe (PSP).
+
+Solar Probe ANalyzer (SPAN) is
+
+We also use dataset from Solar Probe Cup (SPC) and 
+sqtn data from Radio Frequency Spectrometer (RFS) and Low Frequency Reciever (LFR) for density measurements. And in general, we find the results are consistent with the FIELDS and SPAN-i data.
+
+ARTEMIS:
+
+<!-- 
+@shenComparingPlasmaAnisotropy2024
+-->
+
+## Method
+
+TODO: define alignmetn / conjunction
+
+Statistical alignment study ...
+where the solar wind parcels pass through one spacecraft and then the other.
+During this process, the solar wind parcels are expected to evolve due to expansion, heating, and other processes.
+
+@velliUnderstandingOriginsHeliosphere2020
 
@@
 
+@schwartzRadialEvolutionSingle1983
+
+## Identification and characterization of discontinuities
+
+TODO: We use the same process described in @??? to identify and characterize discontinuities in the solar wind.
+
 ::: {#fig-examples .column-page}
@@
 
+# Results
+
+![](figures/density_distribution.png)
+
+## Comparison of Discontinuity Properties
+
 ![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current.spc_n_spc.png){#fig-comp-map}
+
+![](figures/enc2/density_distribution.spi_n_spi.png)
 
@@
 $\Delta v_l$
+
+![](figures/enc2/thickness_current.spi_n_spi.png)
+
+Scale-dependent properties of current sheets in the solar wind
+
+@vaskoKineticscaleCurrentSheets2022
+
+## Comparison between Alfven speed and plasma speed change
+
+For rotational discontinuities, the plasma velocity jump across them: the plasma flow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$.
+
+![](figures/enc7/dvl.png)
+
+K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
+
+## Estimated Anisotropy
+
+The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
+
+Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
+
+![](figures/enc7/anisotropy_theory.png)
+
+## Comparison between Estimated and Observed Anisotropy
+
+![](figures/enc7/anisotropy_comparison_2d.png)
+
+# Discussion
+
+- The properties of the discontinuities is related to the local plasma parameters
+  - Thickness => ion inertial length
+  - Current density => Alfven velocity (current density)
+
+- Normalized thickness and current density of discontinuities remain constant with radial distance.
+In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease  in normalized thickness and increase in normalized current density with radial distance.
+
+Assuming the 
+Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
+
+# Conclusion
+
+# References
+
+---
+
+@marianiStatisticalStudyMagnetohydrodynamic1983
+
+- Statistical study of magnetic field discontinuities in the inner solar system
+- ⭐️ Findings Strong day-to-day variations in occurrence rates of discontinuities
+- ✏️ Morphology Orientation of discontinuities strongly organized by the average magnetic field
+- 💡 Implications Interpretation of evidence of crossing of flux tubes
+
+---

### 2024-08-24 index.qmd
Update image paths for discontinuity properties
update: manuscripts

@@
 ::: {.column}
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
 
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
 
-![](../figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
 :::
@@
 
-![](../images/sty3348fig5.jpeg)
+![](images/sty3348fig5.jpeg)
 
@@
 
-![](../figures/examples/psp_e2_example.png)
+![](figures/examples/psp_e2_example.png)
 
@@
 
-![](../figures/enc2/thickness_current.spi_n_spi.png)
+![](figures/enc2/thickness_current.spi_n_spi.png)
 
-![](../figures/enc2/density_distribution.spi_n_spi.png)
+![](figures/enc2/density_distribution.spi_n_spi.png)
 
@@
 
-![](figures/dvl.spi_n_spi.png)
+![](figures/enc7/dvl.png)
 
@@
 
-![](figures/anisotropy_theory.png)
+![](figures/enc7/anisotropy_theory.png)
 
@@
 
-![](figures/anisotropy_comparison_2d.png)
+![](figures/enc7/anisotropy_comparison_2d.png)
 
@@
     ```         
-    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensiﬁcation of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
+    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensification of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
     ```

### 2024-08-25 article.qmd
update: articles and notebooks

@@
     affiliation: Space Sciences Laboratory, University of California, Berkeley
+code-links:
+  - href: https://www.overleaf.com/project/664f7b472768760cf7d6321c
+    text: Overleaf
+  - href: zotero://select/library/collections/L9JC7XAI
+    text: Zotero
 ---
@@
 
+We use the datasets from PSP and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR and Wind) to study the evolution of solar wind discontinuities in the inner heliosphere, focusing on the periods of conjunctions and alignments between PSP and Earth-orbiting missions.
+
 ## Dataset
 
-### PSP
+<!-- 
+PSP:
+SWEAP consists of four separate sensors that measure the ions and electrons that make up the plasma in the solar wind and solar corona.
+The Solar Probe ANalyzer (SPAN) instruments are electrostatic analyzers (ESAs) that use curved plates to measure the 3-D particle distribution from within the shadow cast by the spacecraft thermal shield.
+Two of the sensors are co-located on the ram side of the spacecraft: SPAN-Ai measures ions, and SPAN-Ae measures electrons.
+SPAN-B measures electrons and is on the anti-ram side of the spacecraft.
+The Solar Probe Cup (SPC) is a Faraday Cup instrument that is directly illuminated by the Sun and measures both ions and electrons.
+-->
 
-We use the high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments on board the Parker Solar Probe (PSP).
-
-Solar Probe ANalyzer (SPAN) is
-
-We also use dataset from Solar Probe Cup (SPC) and 
-sqtn data from Radio Frequency Spectrometer (RFS) and Low Frequency Reciever (LFR) for density measurements. And in general, we find the results are consistent with the FIELDS and SPAN-i data.
-
-ARTEMIS:
+We utilized high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments aboard the Parker Solar Probe (PSP).
+For the plasma data presented in the figures of this paper, we used the dataset from SPAN-i, which measures ions in the solar wind.
+Although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution, making it more suitable for analyzing discontinuities.
+Our analysis confirms that the results obtained from SPC are consistent with those derived from SPAN-i data.
+It is also worth noting that sqtn data from the Radio Frequency Spectrometer (RFS) and Low-Frequency Receiver (LFR) for density measurements is available.
+However, we generally find that the results obtained from RFS/LFR do not differ significantly from those derived from SPAN-i data.
 
 <!-- 
-@shenComparingPlasmaAnisotropy2024
+ARTEMIS:
+We use the following data collected by ARTEMIS P1: magnetic fields with a ∼4s spin resolution (Auster et al.
+2008), the ion bulk velocity v, and the ion (assumed to be proton) temperature (scalar) Tp calculated from velocity distributions measured at spin resolution by the Electrostatic Analyzer (ESA; McFadden et al.
+2008).
+Being designed for measurements of a hot, rarefied plasma in Earth’s magnetosphere, ESA typically overestimates the proton temperature in the solar wind, because the solar wind proton beam is narrower than ESA’s energy and angular resolution.
+TODO: check if the ESA is in solar wind mode
+-->
+
+We utilized data collected by ARTEMIS, including magnetic fields measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity ($v$) and density ($n$), which were derived from velocity distribution data obtained by the Electrostatic Analyzer with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
+It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
+Therefore, any findings related to temperature anisotropy should be interpreted with caution.
+
+<!-- 
+WIND:
+Wind 3dp, PESA LOW 1 spin resolution ion (proton and alpha) moments
+Wind 3D Plasma Analyzer
+Instrument Description
+The Wind 3DP instrument consists of six different sensors.
+There are two electron (EESA) and two ion (PESA) electrostatic analyzers with different geometrical factors and field-of-views covering the energy range from 3 eV to 30 keV.
+There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie
+-->
+
+The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
+
+<!--
+References:
+- @shenComparingPlasmaAnisotropy2024
 -->
@@
 
-TODO: define alignmetn / conjunction
+TODO: define alignment / conjunction
 

### 2024-08-25 src/psp/config/__init__.py

@@ -8,7 +8,6 @@ from datetime import timedelta
 from ..utils import standardize_ion_temp_df, standardize_e_temp_df
 from .. import get_timerange
 
-
 class Config(BaseModel):
     enc: int = 7
     tau: timedelta = timedelta(seconds=30)

### 2024-08-25 src/psp/plot.py

@@ -3,11 +3,8 @@ from datetime import timedelta
 import pytplot
 from pytplot import tplot
 
-from discontinuitypy.utils.plot import ts_mva
 from discontinuitypy.naming import start_col, end_col
-from space_analysis.ds.tplot.formulary import ts_Alfven_speed
-from space_analysis.ds.ts.plot import tsplot
-from xarray import DataArray
+from discontinuitypy.plot import tplot_Alvenicity
 
 from psp.io.psp import PSP_MAG_TNAME, PSP_DEN_TNAME, PSP_VEL_TNAME, PSP_TEMP_TNAME
 
@@ -56,32 +53,6 @@ def plot_event(
 
     return tplot(tnames2plot, return_plot_objects=True)
 
-def set_mva_ts_option(
-    da: DataArray,
-    type="B",
-):
-    options_dict = {
-        "B": {
-            "title": "$B$",
-            "units": "nT",
-            "subtitle": "[nT LMN]",
-            "legend_names": [r"$B_l$", r"$B_m$", r"$B_n$", r"$B_{total}$"],
-        },
-        "V": {
-            "title": "$V$",
-            "subtitle": "[km/s LMN]",
-            "units": "km/s",
-            "legend_names": [r"$V_l$", r"$V_m$", r"$V_n$", r"$V_{total}$"],
-        },
-    }
-
-    da.attrs["long_name"] = options_dict[type]["title"]
-    da.attrs["units"] = options_dict[type]["units"]
-    if "v_dim" in da.dims:
-        da["v_dim"] = options_dict[type]["legend_names"]
-    return da
-
-
 def plot_candidate_tplot(
     event,
     mag_tname: str = PSP_MAG_TNAME,
@@ -91,29 +62,7 @@ def plot_candidate_tplot(
 ):
     """Plot the candidate event with velocity profiles"""
 
-    tstart = event[start_col]
-    tend = event[end_col]
-    trange = slice(tstart - offset, tend + offset)
-
-    mag_da = pytplot.data_quants[mag_tname].sel(time=trange)
-    vec_da = pytplot.data_quants[vec_tname].sel(time=trange)
-    den_da = pytplot.data_quants[den_tname].sel(time=trange)
-
[…]

### 2024-08-26 article.qmd
update: manuscript

@@
 
-We use the datasets from PSP and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR and Wind) to study the evolution of solar wind discontinuities in the inner heliosphere, focusing on the periods of conjunctions and alignments between PSP and Earth-orbiting missions.
+<!-- 
+References:
+- @velliUnderstandingOriginsHeliosphere2020
+- @berriotIdentificationSinglePlasma2024
+- @telloniSpacecraftRadialAlignments2023
+-->
 
-## Dataset
+TODO: define alignment / conjunction
+
+Our study focuses on the evolution of solar wind discontinuities within plasma parcels as they undergo expansion.
+We analyze datasets from the Parker Solar Probe (PSP) and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR, and Wind) at various radial distances in the inner heliosphere, during periods of conjunctions and alignments between PSP and these Earth-orbiting missions.
+
+To achieve this, we utilize a configuration where two spacecraft are radially aligned in the Heliographic (HG) frame, with the longitude fixed on the Sun.
+It is important to note that the plasma parcels observed by the two spacecraft may differ in composition, as solar wind particles propagate at varying velocities.
+For instance, protons often exhibit a beam in their velocity distribution function, while the thermal speed of electrons is much higher than their bulk speed.
+Nonetheless, observing plasma that passes through both spacecraft offers the best opportunity to study the evolution of solar wind discontinuities with minimal influence from other processes during propagation.
+It is also expected that these plasma parcels evolve due to heating and other processes.
+
+<!-- ::: {#fig-plasma-adiabatic-evolution .column-page}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
+Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
+
+@schwartzRadialEvolutionSingle1983
+::: -->
+
+The plasma parcels in question are large-scale structures.
+As the scale size decreases below the mesoscale [@viallMesoscaleStructureSolar2021] (with radial sizes ranging from approximately 5 × 10³ km to 10⁷ km), it becomes increasingly unlikely to identify the same structure, depending on the latitude difference between the two spacecraft.
+Furthermore, although large-scale structures (especially density enhancements) can be identified as passing through both spacecraft [@berriotIdentificationSinglePlasma2024], it is nearly impossible to detect kinetic-scale structures, such as solar wind discontinuities (with time scales on the order of seconds), by both spacecraft simultaneously.
+Therefore, our study focuses on the statistical properties of solar wind discontinuities within the "same" large-scale structures that pass through both spacecraft.
+
+After identifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions, we apply the methodology described in [@???] to identify and characterize solar wind discontinuities.
+Generally, discontinuities observed by PSP are shorter (1-5 seconds) and exhibit higher current density.
+Consequently, we use different time windows for identifying discontinuities: 15 seconds for PSP and 30 seconds for Earth-orbiting missions.
+A example of the discontinuities observed by PSP is shown in @fig-examples.
+
+::: {#fig-examples .column-page}
+
+![](figures/examples/psp_e2_example.png)
+
+Solar wind discontinuities examples observed by PSP fitted by a logistic function in LMN coordinates.
+:::
 
@@
 The Solar Probe Cup (SPC) is a Faraday Cup instrument that is directly illuminated by the Sun and measures both ions and electrons.
+
+"Looking at your intervals, which occurred during the early phase of the mission when PSP was far from the Sun, I realize that the plasma data wasn't good for your purpose because (1) SPAN-ion during at least the first 3-4 orbits did not measure the solar wind well, since a good portion of the solar wind distributions was out of view of that instrument, and (2) data from SPC (Farady Cup) does not give good temperature data.
+I am wondering if you have conjunction events that occurred later, say starting Encounter 7, when data from SPAN would be accurate.
+If not, some parts of Encounters 4-6 might be OK."
 -->
+
+For this study
 
@@
 However, we generally find that the results obtained from RFS/LFR do not differ significantly from those derived from SPAN-i data.
+Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument’s view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.
 
@@
 
-## Method
-
-TODO: define alignment / conjunction
-
-Statistical alignment study ...
-where the solar wind parcels pass through one spacecraft and then the other.
-During this process, the solar wind parcels are expected to evolve due to expansion, heating, and other processes.
-
-@velliUnderstandingOriginsHeliosphere2020
-
-::: {#fig-plasma-adiabatic-evolution .column-page}
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
-
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
-
-<!-- Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
-Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
--->
-:::
-
-@schwartzRadialEvolutionSingle1983
-
-## Identification and characterization of discontinuities
-
-TODO: We use the same process described in @??? to identify and characterize discontinuities in the solar wind.
-
-::: {#fig-examples .column-page}
-
-![](figures/examples/psp_e2_example.png)
-
-Solar wind discontinuities examples observed by PSP and ARTEMIS fitted by a logistic function in LMN coordinates.
-
-In general discontinuities observed by PSP is much shorter (1~5 secs) with larger current density.
-:::
-
 # Results
 
-![](figures/density_distribution.png)
+<!-- ![](figures/density_distribution.png) -->
 
@@
 ---
+
+<!--
+- Citation Key:: @berriotIdentificationSinglePlasma2024
+- Title:: Identification of a single plasma parcel during a radial alignment of the Parker Solar Probe and Solar Orbiter
+- Author(s):: 
+  - Etienne Berriot
+  - Pascal Démoulin
+  - Olga Alexandrova
+- Year:: 2024
+- Publication:: Astronomy & Astrophysics
+- Links:: 
+  - [DOI](https://doi.org/10.1051/0004-6361/202449285)
+  - [Connected Papers](https://connectedpapers.com/api/redirect/doi/10.1051/0004-6361/202449285)
+- Abstract:: Configurations in which two spacecraft, such as the Parker Solar Probe (PSP) and Solar Orbiter, are radially aligned provide opportunities for studying the evolution of a single solar wind parcel during so-called plasma line-ups.
+The most critical part of these studies arguably is the identification of what can be considered the same plasma crossing both spacecraft.
+We present here a method that allowed us to determine what we think to be the same plasma parcel that passed through PSP (∼0.075 au) and Solar Orbiter (∼0.9 au) after their radial alignment on April 29, 2021.
+We started by modeling the plasma propagation in order to obtain a first estimation of the plasma line-up intervals.
+The identification of the same density structure (with a crossing duration ∼1.5 h) that passed through the two spacecraft allowed us to specify and confirm this estimate.
+Our main finding is that the density structure was very stable and remained well recognizable from PSP to Solar Orbiter despite its journey of ∼137 hours in the inner heliosphere.
+We found, moreover, that the slow solar wind plasma parcel was significantly accelerated (from ∼200 to ∼300 km s<sup>−1<sup/>) during its propagation.
+
+- Quotes::
+  - Moreover, the terms “plasma line-up” and “plasma parcel” are somewhat ill-defined, as discussed in Schwartz & Marsch (1983).
+For example, the particle populations of the solar wind tend to propagate with different velocities.
+The protons often exhibit a beam in their velocity distribution function, the thermal speed of the electrons is much higher than their bulk speed, and alpha particles usually have a different bulk speed than protons (see Marsch 2012, and references therein).
+Furthermore, halo electrons are probably governed by nonlocal scattering mechanisms (Zaslavsky et al.
+2024).
+We prefer to keep the general terminology “plasma parcel” and “line-up” throughout this study, however.
+-->

### 2024-08-26 article.qmd
update: figures

@@
 
-<!-- ![](figures/density_distribution.png) -->
+TODO: how does the results depend on the period selected for the conjunctions and alignments?
 
@@
 
-![Comparision map of (normalized) thickness and (normalized) current density](figures/enc2/thickness_current.spc_n_spc.png){#fig-comp-map}
+![](figures/enc7/properties_distribution.svg)
 
-![](figures/enc2/density_distribution.spi_n_spi.png)
+Thickness and current density relationship
+Scale-dependent properties of current sheets in the solar wind
 
-Solar wind properties
-
-L:
-j:
-$\Delta v_l$
-
-![](figures/enc2/thickness_current.spi_n_spi.png)
-
-Scale-dependent properties of current sheets in the solar wind
+![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
 

### 2024-08-26 src/main.jl

@@ -11,11 +11,12 @@ using Beforerr
 using Discontinuity
 using Discontinuity.DefaultMapping
 
+ds_order = ["Parker Solar Probe", "ARTEMIS", "Wind"]
+
 include("io.jl")
 include("plot.jl")
 
 set_aog_theme!()
-
 
 dn_over_n = ("n.change", "n.mean") => (/) => L"\Delta n/n"
 dB_over_B = ("B.change", "b_mag") => (/) => L"\Delta B/B"

### 2024-08-26 src/plot.jl

@@ -6,7 +6,6 @@ include("anisotry.jl")
 # %%
 legend_kwargs = (position=:top, titleposition=:left)
 
-ds_order = ["Parker Solar Probe", "ARTEMIS", "Wind"]
 ds_mapping = :dataset => sorter(ds_order)
 
 log_axis = (yscale=log10, xscale=log10)
@@ -48,7 +47,7 @@ function plot_dvl(
     end
     axislegend("slope", position=:ct)
 
-    easy_save(fname; dir="$fig_dir/$enc")
+    easy_save(fname)
 end
 
 
@@ -68,7 +67,7 @@ function plot_dvl(; legend=legend_kwargs)
     end
     axislegend("slope", position=:ct)
 
-    easy_save(fname; dir="$fig_dir/$enc")
+    easy_save(fname)
 end
 
 function plot_dvl_c()

### 2024-08-26 src/psp/io/psp.py

@@ -32,7 +32,7 @@ def get_psp_data(kind):
     match kind:
         case "mag":
             data = get_data_lf(PSP_MAG_TNAME)
-        case "den": 
+        case "den":
             data = get_data_lf(PSP_DEN_TNAME)
         case "vel":
             data = get_data_lf(PSP_VEL_TNAME)

### 2024-08-26 src/psp/plot.py

@@ -8,12 +8,12 @@ from discontinuitypy.plot import tplot_Alvenicity
 
 from psp.io.psp import PSP_MAG_TNAME, PSP_DEN_TNAME, PSP_VEL_TNAME, PSP_TEMP_TNAME
 
-psp_tnames2plot = [
-    PSP_MAG_TNAME,
-    PSP_DEN_TNAME,
-    PSP_VEL_TNAME,
-    PSP_TEMP_TNAME,
-]
+psp_tnames2plot = [PSP_MAG_TNAME, PSP_DEN_TNAME, PSP_VEL_TNAME, PSP_TEMP_TNAME]
+
+
+def preview_psp_data(tnames=psp_tnames2plot, **kwargs):
+    # TODO: remove spike in time series
+    return tplot(tnames, **kwargs)
 
 
 def tlimit(arg, **kwargs):
@@ -53,6 +53,7 @@ def plot_event(
 
     return tplot(tnames2plot, return_plot_objects=True)
 
+
 def plot_candidate_tplot(
     event,
     mag_tname: str = PSP_MAG_TNAME,
@@ -64,5 +65,5 @@ def plot_candidate_tplot(
 
     start = event[start_col]
     end = event[end_col]
-    
+
     return tplot_Alvenicity(start, end, mag_tname, vec_tname, den_tname, offset)

### 2024-08-28 notebooks/events/e7.qmd
update event 8

@@
 -   [WHPI - Campaign: PSP 7th Perhihelion](https://whpi.hao.ucar.edu/whpi_campaign-psp7p.php)
--   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 04](http://helioweather.net/missions/psp/per04/)
+-   [ENLIL Solar Wind Prediction - Parker Solar Probe - Perihelion 07](http://helioweather.net/missions/psp/per07/)
 

### 2024-08-28 src/io.jl

@@ -72,7 +72,8 @@ function calc_vl_ratio!(df)
     if "Λ_ion" in names(df)
         @chain df begin
             @transform!(
-                :"v.Alfven.change.l.fit.Λ_ion" = @. sqrt(1 - :"Λ_ion") * :"v.Alfven.change.l.fit"
+                :"v.Alfven.change.l.fit.Λ_ion" =
+                    @. ifelse(:Λ_ion > 1, missing, sqrt(max(0, 1 - :Λ_ion)) * :"v.Alfven.change.l.fit")
             )
             @transform!(
                 :"v_l_ratio.fit.Λ_ion" = :"v.ion.change.l" ./ :"v.Alfven.change.l.fit.Λ_ion"

### 2024-08-28 src/main.jl

@@ -11,7 +11,7 @@ using Beforerr
 using Discontinuity
 using Discontinuity.DefaultMapping
 
-ds_order = ["Parker Solar Probe", "ARTEMIS", "Wind"]
+ds_order = ["Parker Solar Probe", "Solar Orbiter", "ARTEMIS", "Wind"]
 
 include("io.jl")
 include("plot.jl")

### 2024-08-28 src/psp/__init__.py

@@ -3,36 +3,34 @@ from datetime import datetime
 td_start_c = "t.d_start"
 td_stop_c = "t.d_end"
 
-def get_timerange(enc: int) -> list[str]:
-    match enc:
-        case 2: # Encounter 2
-            start = "2019-04-07T01:00"
-            end = "2019-04-07T12:00" 
+def get_timerange(enc: int):
+    encounter_map = {
+        2: {
+            "psp": ["2019-04-07T01:00", "2019-04-07T12:00"],
+            "earth": ["2019-04-09", "2019-04-12"]
+        },
+        4: {
+            "psp": ["2020-01-27", "2020-01-29"],
+            "earth": ["2020-01-29", "2020-01-31"]
+        },
+        7: {
+            "psp": ["2021-01-14", "2021-01-21"],
+            "earth": ["2021-01-15", "2021-01-23"]
+        },
+        8: {
+            "psp": ["2021-04-28", "2021-04-30"],
+            "solo": ["2021-05-03", "2021-05-06"],
+            "earth": ["2021-05-03", "2021-05-06"] #TODO: Check
+        }
+    }
 
-            earth_start = "2019-04-09"
-            earth_end = "2019-04-12"
-        case 4: # Encounter 4
-            start = '2020-01-27'
-            end = '2020-01-29'
+    if enc not in encounter_map:
+        raise ValueError("Invalid encounter")
 
-            earth_start = '2020-01-29'
-            earth_end = '2020-01-31'
-        
-        case 7:
-            start = '2021-01-14'
-            end = '2021-01-21'
+    timerange = encounter_map[enc]
 
-            earth_start = '2021-01-15'
-            earth_end = '2021-01-23'
-            
-        case _: # Encounter 1
-            raise ValueError("Invalid encounter")
+    # Convert string times to datetime objects
+    for key, times in timerange.items():
+        timerange[key] = [datetime.fromisoformat(t) for t in times]
 
-    start = datetime.fromisoformat(start)
-    end = datetime.fromisoformat(end)
-    earth_start = datetime.fromisoformat(earth_start)
-    earth_end = datetime.fromisoformat(earth_end)
-
-    psp_timerange = [start, end]
-    earth_timerange = [earth_start, earth_end]
-    return psp_timerange, earth_timerange
+    return timerange

### 2024-08-28 src/psp/config/psp.py

@@ -59,7 +59,7 @@ class PSPConfig(IDsConfig):
     def model_post_init(self, __context):
         super().model_post_init(__context)
 
-        self.timerange = get_timerange(self.enc)[0]
+        self.timerange = get_timerange(self.enc)["psp"]
 
         if self.enc not in TPLOT_ENCS:
             self.plasma_meta = get_psp_plasma_meta(self.instr_p, self.instr_p_den)

### 2024-08-28 src/psp/plot.py

@@ -4,7 +4,7 @@ import pytplot
 from pytplot import tplot
 
 from discontinuitypy.naming import start_col, end_col
-from discontinuitypy.plot import tplot_Alvenicity
+from discontinuitypy.plot.alfvenicity import tplot_Alfvenicity
 
 from psp.io.psp import PSP_MAG_TNAME, PSP_DEN_TNAME, PSP_VEL_TNAME, PSP_TEMP_TNAME
 
@@ -66,4 +66,4 @@ def plot_candidate_tplot(
     start = event[start_col]
     end = event[end_col]
 
-    return tplot_Alvenicity(start, end, mag_tname, vec_tname, den_tname, offset)
+    return tplot_Alfvenicity(start, end, mag_tname, vec_tname, den_tname, offset)

### 2024-08-28 presentations/rMeeting.qmd
chore: update website

@@
 title: "Current Sheets in the Solar Wind: Parker Solar Probe Observations"
-subtitle: SPARTHB
 author:
@@
   - name: Vassilis Angelopoulos
-format:
-  html: default
-  pptx:
-    slide-level: 2
-slide-number: true
 date: "2024-05"

### 2024-09-03 notebooks/events/e11.qmd
feat: encounter 9

@@
 > E11, C6, Q8, Q9 23–27 February, 2022.
-PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihe- lion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU.
+PSP approaches encounter E11 beginning with a trailing quadrature Q8 on 23 February, 2022, appearing on the east limb of the Sun from SO, before rapidly going through conjunction with STEREO-A and then SO and Earth (24 and 25 February, respectively) at perihelion with the Earth–Sun–STEREO-A angle '40◦ and the Earth– Sun–SO angle decreasing from '15◦ to 0◦ on 7 March, 2022, with SO at 0.5 AU.
 There will be clear opportunities here for cross calibration of magnetic ﬁeld measurements, as well as a true stereoscopic reconstruction of the solar corona crossed by PSP, with opportunities for all the PSP–SO objectives.

### 2024-09-03 src/psp/config/__init__.py

@@ -1,7 +1,12 @@
 from pydantic import BaseModel
 from beforerr.project import datadir
 from discontinuitypy.config import SpeasyIDsConfig
-from discontinuitypy.mission import WindConfigBase, ThemisConfigBase, SoloConfigBase
+from discontinuitypy.mission import (
+    WindConfigBase,
+    ThemisConfigBase,
+    SoloConfigBase,
+    StereoConfigBase,
+)
 
 from datetime import timedelta
 
@@ -35,6 +40,12 @@ class SoloConfig(Config, SoloConfigBase, SpeasyIDsConfig):
 class THEMISConfig(Config, ThemisConfigBase, SpeasyIDsConfig):
     ts: timedelta = timedelta(seconds=1)
 
+    def model_post_init(self, __context):
+        super().model_post_init(__context)
+        self.timerange = get_timerange(self.enc)["earth"]
+
+
+class StereoConfig(Config, StereoConfigBase, SpeasyIDsConfig):
     def model_post_init(self, __context):
         super().model_post_init(__context)
         self.timerange = get_timerange(self.enc)["earth"]

### 2024-09-03 src/psp/utils.py

@@ -1,8 +1,6 @@
 from space_analysis.meta import TempDataset
 from space_analysis.utils.speasy import Variables
 
-from sunpy.time import TimeRange
-
 from beforerr.polars import pl_norm
 import polars as pl
 
@@ -29,6 +27,8 @@ def df_p2temp(ldf: pl.LazyFrame, p_col, density_col):
 
 
 def validate(timerange):
+    from sunpy.time import TimeRange
+    
     if isinstance(timerange, TimeRange):
         return [timerange.start.to_string(), timerange.end.to_string()]
 

### 2024-10-10 article.qmd
update event 8
update refs

@@
 
-<!-- 
-References:
-- @velliUnderstandingOriginsHeliosphere2020
-- @berriotIdentificationSinglePlasma2024
-- @telloniSpacecraftRadialAlignments2023
--->
-
 TODO: define alignment / conjunction
@@
 Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
-
-@schwartzRadialEvolutionSingle1983
 ::: -->
@@
 
-@vaskoKineticscaleCurrentSheets2022
-
 ## Comparison between Alfven speed and plasma speed change
@@
 Assuming the 
-Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
+Anisotropy of tAzdhe plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
 
 # Conclusion
-
-# References
-
----
-
-@marianiStatisticalStudyMagnetohydrodynamic1983
-
-- Statistical study of magnetic field discontinuities in the inner solar system
-- ⭐️ Findings Strong day-to-day variations in occurrence rates of discontinuities
-- ✏️ Morphology Orientation of discontinuities strongly organized by the average magnetic field
-- 💡 Implications Interpretation of evidence of crossing of flux tubes
-
----
-
-<!--
-- Citation Key:: @berriotIdentificationSinglePlasma2024
-- Title:: Identification of a single plasma parcel during a radial alignment of the Parker Solar Probe and Solar Orbiter
-- Author(s):: 
-  - Etienne Berriot
-  - Pascal Démoulin
-  - Olga Alexandrova
-- Year:: 2024
-- Publication:: Astronomy & Astrophysics
-- Links:: 
-  - [DOI](https://doi.org/10.1051/0004-6361/202449285)
-  - [Connected Papers](https://connectedpapers.com/api/redirect/doi/10.1051/0004-6361/202449285)
-- Abstract:: Configurations in which two spacecraft, such as the Parker Solar Probe (PSP) and Solar Orbiter, are radially aligned provide opportunities for studying the evolution of a single solar wind parcel during so-called plasma line-ups.
-The most critical part of these studies arguably is the identification of what can be considered the same plasma crossing both spacecraft.
-We present here a method that allowed us to determine what we think to be the same plasma parcel that passed through PSP (∼0.075 au) and Solar Orbiter (∼0.9 au) after their radial alignment on April 29, 2021.
-We started by modeling the plasma propagation in order to obtain a first estimation of the plasma line-up intervals.
-The identification of the same density structure (with a crossing duration ∼1.5 h) that passed through the two spacecraft allowed us to specify and confirm this estimate.
-Our main finding is that the density structure was very stable and remained well recognizable from PSP to Solar Orbiter despite its journey of ∼137 hours in the inner heliosphere.
-We found, moreover, that the slow solar wind plasma parcel was significantly accelerated (from ∼200 to ∼300 km s<sup>−1<sup/>) during its propagation.
-
-- Quotes::
-  - Moreover, the terms “plasma line-up” and “plasma parcel” are somewhat ill-defined, as discussed in Schwartz & Marsch (1983).
-For example, the particle populations of the solar wind tend to propagate with different velocities.
-The protons often exhibit a beam in their velocity distribution function, the thermal speed of the electrons is much higher than their bulk speed, and alpha particles usually have a different bulk speed than protons (see Marsch 2012, and references therein).
-Furthermore, halo electrons are probably governed by nonlocal scattering mechanisms (Zaslavsky et al.
-2024).
-We prefer to keep the general terminology “plasma parcel” and “line-up” throughout this study, however.
--->

### 2024-11-04 article.qmd
update: new section on alignment effects and discontinuity properties

@@
 
+## The effect of alignment on discontinuity properties
+
+![](figures/thickness_current.png)
+
+![](figures/B_angle.png)
+
 # Discussion
@@
 
-- Normalized thickness and current density of discontinuities remain constant with radial distance.
+- Normalized thickness and current density of discontinuities remain constant with radial distance (negligible change compared to their spread).
 In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease in normalized thickness and increase in normalized current density with radial distance.
+
+- Better alignment period has a slightly better agreement of the properties of the discontinuities (normalized thickness, current density, $|\Delta \mathbf{B}/B|$ and rotation angle) between PSP and Earth-orbiting missions.
+- $B_N/B$ and in-plane rotation angle are significantly different between PSP and Earth-orbiting missions independent of the alignment period.
 

### 2024-11-04 notebooks/11_alignment.qmd
update: new section on alignment effects and discontinuity properties

## Effect of alignment on discontinuity properties

```{julia}
include("../src/main.jl")
using CairoMakie
using Beforerr

df_enc_7 = load_all(7);
df_enc_8 = load_all(8);
df_enc_9 = load_all(9);
df = reduce(vcat, [df_enc_7, df_enc_8, df_enc_9], cols=:intersect);
```

```{julia}
layer = data(df) * mapping(color=:dataset, col=enc_m)

function plot_p1()
    maps = [l_log_map, l_norm_log_map, j_log_map, j_norm_log_map]
    figure = (size=(450, 800),)
    f = plot_dist(layer, maps; figure, axis)

    # fine tune the plot
    for i in 1:4
        axs = contents(f[i, 1][:, :])
        ylims!.(axs; low=1e-3)
    end
    axs = contents(f[1, 1][:, :])
    xlims!.(axs; low=-1)
    axs = contents(f[2, 1][:, :])
    xlims!.(axs; low=-1.5)
    axs = contents(f[4, 1][:, :])
    xlims!.(axs; high=1)

    easy_save("thickness_current")
end
```

![](../figures/thickness_current.png)

```{julia}
function plot_B_angle(; figure=(size=(450, 800),), name = "B_angle")
    maps = [M.dB_norm_over_B, M.bn, ω_map, M.ω_in]
    f = plot_dist(layer, maps; figure)

    # fine tune the plot
    gl3_axs = contents(f[3, 1][:, :])
    gl4_axs = contents(f[4, 1][:, :])
    foreach(vcat(gl3_axs, gl4_axs)) do ax
        vlines!(ax, [30]; color=:gray, linestyle=:dash)
    end

    easy_save(name)
end

f = plot_B_angle()
```

![](../figures/B_angle.png)

### 2025-01-24 index.qmd
chore: combine article and index

@@
   - name: Vassilis Angelopoulos
+    email: vassilis@ucla.edu
     orcid: 0000-0001-7024-1561
     affiliation: University of California, Los Angeles
-code-links:
-  - repo
-  - href: https://app.tana.inc?nodeid=PZ6j7iriic2l
-    text: Tana
-  - href: zotero://select/library/collections/L9JC7XAI
-    text: Zotero
+  - name: Tai Phan
+    email: phan@ssl.berkeley.edu
+    orcid: 0000-0002-6924-9408
+    affiliation: Space Sciences Laboratory, University of California, Berkeley
 ---
@@
 
-# Methods
+# Introduction
+
+The study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind
+
+Previous statistical studies of solar wind discontinuities in the inner heliosphere @marianiStatisticalStudyMagnetohydrodynamic1983 @liuCharacteristicsInterplanetaryDiscontinuities2021
+
+Alignement study of solar wind discontinuities @artemyevDynamicsIntenseCurrents2018
+
+By indentifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions
+
+@hudsonDiscontinuitiesAnisotropicPlasma1970
+
+# Dataset and method
+
+TODO: define alignment / conjunction
+
+Our study focuses on the evolution of solar wind discontinuities within plasma parcels as they undergo expansion.
+We analyze datasets from the Parker Solar Probe (PSP) and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR, and Wind) at various radial distances in the inner heliosphere, during periods of conjunctions and alignments between PSP and these Earth-orbiting missions.
+
+To achieve this, we utilize a configuration where two spacecraft are radially aligned in the Heliographic (HG) frame, with the longitude fixed on the Sun.
+It is important to note that the plasma parcels observed by the two spacecraft may differ in composition, as solar wind particles propagate at varying velocities.
+For instance, protons often exhibit a beam in their velocity distribution function, while the thermal speed of electrons is much higher than their bulk speed.
+Nonetheless, observing plasma that passes through both spacecraft offers the best opportunity to study the evolution of solar wind discontinuities with minimal influence from other processes during propagation.
+It is also expected that these plasma parcels evolve due to heating and other processes.
+
+<!-- ::: {#fig-plasma-adiabatic-evolution .column-page}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
+Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
+::: -->
+
+The plasma parcels in question are large-scale structures.
+As the scale size decreases below the mesoscale [@viallMesoscaleStructureSolar2021] (with radial sizes ranging from approximately 5 × 10³ km to 10⁷ km), it becomes increasingly unlikely to identify the same structure, depending on the latitude difference between the two spacecraft.
+Furthermore, although large-scale structures (especially density enhancements) can be identified as passing through both spacecraft [@berriotIdentificationSinglePlasma2024], it is nearly impossible to detect kinetic-scale structures, such as solar wind discontinuities (with time scales on the order of seconds), by both spacecraft simultaneously.
+Therefore, our study focuses on the statistical properties of solar wind discontinuities within the "same" large-scale structures that pass through both spacecraft.
+
+After identifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions, we apply the methodology described in [@???] to identify and characterize solar wind discontinuities.
+Generally, discontinuities observed by PSP are shorter (1-5 seconds) and exhibit higher current density.
+Consequently, we use different time windows for identifying discontinuities: 15 seconds for PSP and 30 seconds for Earth-orbiting missions.
+A example of the discontinuities observed by PSP is shown in @fig-examples.
+
+::: {#fig-examples .column-page}
+
+![](figures/examples/psp_e2_example.png)
+
+Solar wind discontinuities examples observed by PSP fitted by a logistic function in LMN coordinates.
+:::
+
+<!-- 
+PSP:
+SWEAP consists of four separate sensors that measure the ions and electrons that make up the plasma in the solar wind and solar corona.
+The Solar Probe ANalyzer (SPAN) instruments are electrostatic analyzers (ESAs) that use curved plates to measure the 3-D particle distribution from within the shadow cast by the spacecraft thermal shield.
+Two of the sensors are co-located on the ram side of the spacecraft: SPAN-Ai measures ions, and SPAN-Ae measures electrons.
+SPAN-B measures electrons and is on the anti-ram side of the spacecraft.
+The Solar Probe Cup (SPC) is a Faraday Cup instrument that is directly illuminated by the Sun and measures both ions and electrons.
+
+"Looking at your intervals, which occurred during the early phase of the mission when PSP was far from the Sun, I realize that the plasma data wasn't good for your purpose because (1) SPAN-ion during at least the first 3-4 orbits did not measure the solar wind well, since a good portion of the solar wind distributions was out of view of that instrument, and (2) data from SPC (Farady Cup) does not give good temperature data.
+I am wondering if you have conjunction events that occurred later, say starting Encounter 7, when data from SPAN would be accurate.
+If not, some parts of Encounters 4-6 might be OK."
+-->
+
+For this study
+
+We utilized high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments aboard the Parker Solar Probe (PSP).
+For the plasma data presented in the figures of this paper, we used the dataset from SPAN-i, which measures ions in the solar wind.
+Although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution, making it more suitable for analyzing discontinuities.
+Our analysis confirms that the results obtained from SPC are consistent with those derived from SPAN-i data.
+It is also worth noting that sqtn data from the Radio Frequency Spectrometer (RFS) and Low-Frequency Receiver (LFR) for density measurements is available.
+However, we generally find that the results obtained from RFS/LFR do not differ significantly from those derived from SPAN-i data.
+Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument’s view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.
+
+<!-- 
+ARTEMIS:
+We use the following data collected by ARTEMIS P1: magnetic fields with a ∼4s spin resolution (Auster et al.
+2008), the ion bulk velocity v, and the ion (assumed to be proton) temperature (scalar) Tp calculated from velocity distributions measured at spin resolution by the Electrostatic Analyzer (ESA; McFadden et al.
+2008).
+Being designed for measurements of a hot, rarefied plasma in Earth’s magnetosphere, ESA typically overestimates the proton temperature in the solar wind, because the solar wind proton beam is narrower than ESA’s energy and angular resolution.
+TODO: check if the ESA is in solar wind mode
+-->
+
+We utilized data collected by ARTEMIS, including magnetic fields measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity ($v$) and density ($n$), which were derived from velocity distribution data obtained by the Electrostatic Analyzer with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
+It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
+Therefore, any findings related to temperature anisotropy should be interpreted with caution.
+
+<!-- 
+WIND:
+Wind 3dp, PESA LOW 1 spin resolution ion (proton and alpha) moments
+Wind 3D Plasma Analyzer
+Instrument Description
+The Wind 3DP instrument consists of six different sensors.
+There are two electron (EESA) and two ion (PESA) electrostatic analyzers with different geometrical factors and field-of-views covering the energy range from 3 eV to 30 keV.
+There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie
+-->
+
+The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
 
@@
 
+![](figures/enc7/properties_distribution.svg)
+
+Thickness and current density relationship
+Scale-dependent properties of current sheets in the solar wind
+
+![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
+
 ## Comparison between Alfven speed and plasma speed change
@@
 
+## The effect of alignment on discontinuity properties
+
+![](figures/thickness_current.png)
+
+![](figures/B_angle.png)
+
 # Conclusion
@@
 - Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
+
+- Normalized thickness and current density of discontinuities remain constant with radial distance (negligible change compared to their spread).
+In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease in normalized thickness and increase in normalized current density with radial distance.
+
+- Better alignment period has a slightly better agreement of the properties of the discontinuities (normalized thickness, current density, $|\Delta \mathbf{B}/B|$ and rotation angle) between PSP and Earth-orbiting missions.
+- $B_N/B$ and in-plane rotation angle are significantly different between PSP and Earth-orbiting missions independent of the alignment period.
 

### 2025-01-24 index.qmd
chore: cleanup

@@
 
-### High-speed solar wind radial evolution
-
-:::: {.columns}
-::: {.column}
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
-
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
-
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
-:::
-
-::: {.column}
-
-![](images/sty3348fig5.jpeg)
-
-@perroneRadialEvolutionSolar2019
-:::
-::::
-
-::: {.notes}
-The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by
-
-$$
-n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
-\\
-B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
-$$
-
-The faster decrease of the magnetic than kinetic pressure is reﬂected in the radial proton plasma beta variation
-
-$$
-β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
-$$ 
-:::
-
 ## Examples of discontinuities
@@
 
-## Comparison between Alfven speed and plasma speed change
+## Alfvénicity
+
+Comparison between Alfven speed and plasma speed change
 
@@
 
-## Estimated Anisotropy
+### Estimated Anisotropy
 
@@
 pressure anisotropy is defined as $Λ = \mu (P_∥ - P_⊥) / B^2$.
+
+# Appendix

### 2025-01-24 notes.qmd
chore: cleanup

@@
   - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
+
 # TODO
@@
 - [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?
+
+## High-speed solar wind radial evolution
+
+:::: {.columns}
+::: {.column}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-previous.svg)
+:::
+
+::: {.column}
+
+![](images/sty3348fig5.jpeg)
+
+@perroneRadialEvolutionSolar2019
+:::
+::::
+
+::: {.notes}
+The radial dependence of the proton number density, $n_p$ and magnetic ﬁeld magnitude, $B$, is given by
+
+$$
+n_p = (2.4 ± 0.1)(R/R_0)^{−(1.96±0.07)} cm^{−3}
+\\
+B = (5.7 ± 0.2)(R/R_0)^{−(1.59±0.06)} nT
+$$
+
+The faster decrease of the magnetic than kinetic pressure is reflected in the radial proton plasma beta variation
+
+$$
+β_p = P_k/P_B = (0.55 ± 0.04)(R/R_0)^{(0.4±0.1)}
+$$ 
+:::
 

### 2025-02-18 notebooks/00_index.qmd
docs: update

Interactively exploring the quantities of solar wind.

## Data

- [PSP/FIELDS Level 2 and higher data](https://fields.ssl.berkeley.edu/data/), [SPDF - Coordinated Data Analysis Web (CDAWeb)](https://cdaweb.gsfc.nasa.gov/cgi-bin/eval2.cgi?dataset=PSP_FLD_L2_MAG_RTN&index=sp_phys)

```{julia}
using Speasy
using Speasy: DataSet
spz = speasy()

using DimensionalData
using SpaceTools
using GLMakie
using Dates
```

```{julia}
tmin = DateTime("2021-04-29")
tmax = DateTime("2021-04-30")

tvars_psp = [
    "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
    ["cda/PSP_SWP_SPI_SF00_L3_MOM/DENS", "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"],
    "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
    "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
]

tvars_wind = [
    "cda/WI_H2_MFI/BGSE",
    "cda/WI_PM_3DP/P_DENS",
    "cda/WI_PM_3DP/P_VELS",
    "cda/WI_PM_3DP/P_TEMP",
]

f = Figure()
add_title = true
tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
add_labels!()
f
```

### 2025-02-18 notebooks/10_results.qmd
docs: update

---
title: Results
engine: julia
---

```{julia}
using Revise
using DrWatson
@quickactivate
include(srcdir("main.jl"))
import Beforerr: easy_save
```

```{julia}
enc = 8 # event id (encounter id)    
easy_save(fname; enc=enc) = Beforerr.easy_save(fname; dir="$fig_dir/enc$enc", formats=[:svg, :pdf])
```

```{julia}
df_enc_7 = load_all(7);
df_enc_8 = load_all(8);
df_enc_9 = load_all(9);
df = reduce(vcat, [df_enc_7, df_enc_8, df_enc_9], cols=:intersect);
```

```{julia}
function plot_dist_comp(
    df1, df2;
    figure_kwargs=(size=(800, 600),),
    kwargs...
)

    df = reduce(vcat, [df1, df2], cols=:intersect)
    data_layer = data(df) * mapping(color=ds_mapping, marker=ds_mapping)

    maps = [l_log_map j_log_map
        l_norm_log_map j_norm_log_map]

    plot_dist(data_layer; maps, axis=(), visual=mapping(), figure_kwargs=figure_kwargs, kwargs...)
end

function plot_dist_comp(df1, df2, tr1, tr2)
    df1 = subset_timerange(df1, tr1...)
    df2 = subset_timerange(df2, tr2...)
    @info "Number of data points in df1: $(nrow(df1))"
    @info "Number of data points in df2: $(nrow(df2))"
    plot_dist_comp(df1, df2)
end
```

## Distribution comparison

### Enc 7

```{julia}
enc = 7 # event id (encounter id)    
easy_save(fname) = Beforerr.easy_save(fname; dir="$fig_dir/enc$enc", formats=[:svg])
mkpath("$fig_dir/$enc");
```

```{julia}
plot_dist_comp(psp_df, wind_df,
    ["2021-01-15", "2021-01-17"],
    ["2021-01-17", "2021-01-19"]
)
```

```{julia}
plot_dist_comp(psp_df, wind_df,
    ["2021-01-15", "2021-01-17"],
    ["2021-01-21", "2021-01-23"]
)
```

### Enc 8

```{julia}
plot_dist_comp(psp_df, solo_df)
```

```{julia}
DateTime("2021-04-29T00:45") + Hour(145)
DateTime("2021-04-29T00:45") + Hour(-1)
```

```{julia}
#| layout-ncol: 3
#| column: screen
f1 = plot_dist_comp(psp_df, solo_df,
    ["2021-04-29T00:15", "2021-04-29T02:15"],
    ["2021-05-04T17:45:00", "2021-05-04T19:45:00"]
)
f2 = plot_dist_comp(psp_df, solo_df,
    ["2021-04-28T00:15", "2021-04-29T02:15"],
    ["2021-05-03T17:45:00", "2021-05-04T19:45:00"]
)

f3 = plot_dist_comp(psp_df, solo_df,
    ["2021-04-28T00:15", "2021-04-29T02:15"],
    ["2021-05-04T17:45:00", "2021-05-05T19:45:00"]
)
display(f1)
display(f2)
display(f3);
```

```{julia}
begin
    df = reduce(
        vcat,
        [psp_df, thm_df, wind_df, solo_df],
        cols=:intersect
    )
    levels!(df.dataset, ds_order)

    earth_df = reduce(
        vcat,
        [thm_df, wind_df],
        cols=:intersect
    )
end;
```

```{julia}
begin
    # base data layer
    data_layer = data(df) * mapping(color=ds_mapping, marker=ds_mapping)

    # data layer with different alpha
    data_layer_a = (
        (data(thm_df) + data(wind_df)) * visual(alpha=0.3) + data(psp_df) * visual(alpha=1)
    ) * mapping(
        color=ds_mapping, marker=ds_mapping
    )

    # data layer with 1au missions
    data_layer_b = (
        (data(wind_df) + data(thm_df))
    ) * mapping(
        color=:dataset, marker=:dataset
    )
end;
```

## Discontinuities' properties

```{julia}
# velocity v is normalized to $l Ω$, where $l$ represents the width of the RD and $Ω = q B/(mpc)$ is the cyclotron frequency.
function v_norm!(df::AbstractDataFrame)
    df.v_to_norm = df.L_k .* df."B.mean"
end
v_norm!(df);
```

```{julia}
layer = data(df) * mapping(color=:dataset, col=:enc)
axis = (yscale=log10,)
figure = (size=(600, 800),);
```

```{julia}
Bn = :bn_over_b => abs => L"B_N/B";
v_norm = :v_to_norm => log10 => "Log v_gyro";
```

```{julia}
dfplot(layer, args...; axis=(;), kwargs...) = draw(layer * mapping(args...; kwargs...); axis)
dfplot(df::AbstractDataFrame, args...; axis=(;), kwargs...) = draw(data(df) * mapping(args...; kwargs...); axis)
```

```{julia}
using GLMakie
GLMakie.activate!()
axis = (type=Axis3, width=300, height=300)
dfplot(layer, v_norm, ω_in, Bn; axis)
```

```{julia}
maps = [B_log_map, v_norm, ω_in]
plot_dist(layer, maps; figure=figure)
```

```{julia}
function plot_dB_over_B(layer; axis=(yscale=identity,), datalimits=((0, 0.3),))
    plt = layer * mapping(dB_over_B_map) * density(datalimits=datalimits) * visual(Lines)
    draw(plt; axis=axis)
end

# log scale is not good for this parameter
# plot_dB_over_B(layer; axis = (yscale=log10,)) |> display

plot_dB_over_B(layer)
```

```{julia}
# plot the density distribution of the thickness and current density
begin
    fname = "properties_distribution"

    maps = [l_log_map j_log_map
        l_norm_log_map j_norm_log_map]
    figure_kwargs = (size=(800, 600),)

    plot_dist(data_layer; maps, axis=(), visual=mapping(), figure_kwargs=figure_kwargs)
    easy_save(fname)
end
```

```{julia}
function plot_l_j_local_comp(df)
    fig = Figure(size=(1000, 800))

    data_layer = data(df) * mapping(col=:dataset)

    facet = (; linkxaxes=:none, linkyaxes=:none)
    # Thickness Panels
    begin
        plt = data_layer * mapping(di_log_map, l_log_map)
        axis = (;)
        draw!(fig[1, 1:3], plt, axis=axis, facet=facet)
    end

    # Current Density Panels
    begin
        plt = data_layer * mapping(jA_log_map, j_log_map)
        axis = (;)
        draw!(fig[2, 1:3], plt, axis=axis, facet=facet)
    end

    fig
end

df |> plot_l_j_local_comp
```

```{julia}
begin
    fname = "thickness_current"

    plt = data_layer_a * visual(Scatter)

    fig = Figure(size=(1000, 500))
    axis = log_axis

    ga = fig[1, 1]
    gb = fig[1, 2]

    grid1 = plt * mapping(l_map, j_map) |> draw!(ga; axis=axis)
    grid2 = plt * mapping(l_norm_map, j_norm_map) |> draw!(gb; axis=axis)

    pretty_legend!(fig, grid1)
    add_labels!([ga, gb])
    easy_save(fname)
end
```

`ggscatterhist` can not handle log scale well

```{julia}
#| label: fig-dn-dB
#| column: screen
axis = (limits=((-0.5, 0.5), (-0.5, 0.5)),)

begin
    fname = "dn-dB"
    plt = data_layer_a * mapping(dn_over_n, dB_over_B) * (AlgebraOfGraphics.linear() + visual(Scatter))
    fg = draw(plt, axis=axis)
    easy_save(fname)
end
```

```{julia}
#| label: fig-dn-dT
#| column: screen
begin
    fname = "dn-dT"
    plt = data_layer_a * mapping(dT_over_T, dn_over_n) * (mapping())

    fig = Figure(size=(1000, 500))
    grid1 = plt |> draw!(fig[1, 1])
    grid2 = plt |> draw!(fig[1, 2]; axis=(; limits=((-0.5, 0.5), (-0.5, 0.5))))

    pretty_legend!(fig, grid1)
    easy_save(fname)

    fig
end
```

```{julia}
#| label: fig-dT-dB
#| column: screen
begin
    fname = "dT-dB"
    plt = data_layer_a * mapping(dT_over_T, dB_over_B) * (AlgebraOfGraphics.linear() + mapping())

    fig = Figure(size=(1000, 500))
    grid = draw!(fig[1, 1], plt)
    draw!(fig[1, 2], plt, axis=(; limits=((-0.5, 0.5), (-0.5, 0.5))))

    pretty_legend!(fig, grid1)
    easy_save(fname)

    fig
end
```

```{julia}
ω_map = :rotation_angle => "rotation angle (deg)";
v_l_ratio_map = :v_l_ratio => L"Δ V_{ion,l} / Δ V_{A,l}"
plt = data(psp_df) * mapping(ω_map, v_l_ratio_map) * (linear() + visual(Scatter))
draw(plt)
```

## Alfvenicity

Comparison of change in Alfven speed and plasma speed

The distinguishing feature of rotational discontinuities is the plasma velocity jump across them: the plasma ﬂow velocity $v_l$ (the solar wind velocity projected onto l) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$ (Landau & Lifshitz 1960; Hudson 1970).

```{julia}
#| label: fig-dvl
#| column: screen
fig = plot_dvl(psp_df)
```

```{julia}
plot_vl_ratio(df)
```

```{julia}
vl_ratio_label = L"\Delta V_{i,l} / \Delta V_{A,l}"
v_l_fit_ratio_map = "v_l_fit_ratio" => vl_ratio_label

plot_vl_ratio(psp_df; mapping_args=(v_l_fit_ratio_map,), fname=missing)
```

```{julia}
v_l_fit_ratio_map = "v_l_ratio.fit.Λ_ion" => vl_ratio_label

plot_vl_ratio(psp_df; mapping_args=(v_l_fit_ratio_map,), fname=missing)
```

## Anistropy

@shenComparingPlasmaAnisotropy2024

```{julia}
plot_anistropy_comparison_2d(psp_df)
```

```{julia}
psp_df.Λ_ion_r = abs.(psp_df.Λ_ion ./ psp_df.Λ_t .- 1)
first(sort(psp_df, :Λ_ion_r), 4)
```

```{julia}
plot_anistropy(df)
```

```{julia}
#| label: fig-anisotropy
#| column: screen
plot_anistropy_theory(df)
```

```{julia}
function plot_anistropy_comparison()
    fname = "anisotropy_comparison"

    fig = Figure(size=(1000, 800))

    plt_Λ = data(
        stack(earth_df, [:Λ, :Λ_t, :Λ_ion, :Λ_e], [:time, :dataset])
    ) * mapping(:value => L"\Lambda", color=:variable, marker=:variable, col=:dataset)

    grid1 = plt_Λ * density() |> draw!$fig[1, 1:2]
    grid2 = plt_Λ * histogram() |> draw!$fig[2, 1:2]
    # easy_save("$(fname)_$psp_p_instr")
    # legend!(fig[1, 1:2], grid, titleposition=:left, orientation=:horizontal)
    pretty_legend!(fig, grid1)

    fig
end

function plot_anistropy_comparison_i_e()
    fname = "anisotropy_comparison_i_e"

    mapping_layer = mapping(
        Λ_e_map, Λ_ion_map,
    )

    # draw a dashed line with slope 1
    df2 = (Λ_e=[0, 0.3], Λ_ion=[0, 0.3])

    plt = (data(earth_df) * mapping(row=:dataset) + data(df2) * visual(Lines)) * mapping_layer

    fig = draw(plt, facet=(; linkxaxes=:minimal, linkyaxes=:minimal))
    fig
end
```

```{julia}
#| label: fig-anisotropy-comp
#| column: screen
plot_anistropy_comparison()
```

```{julia}
#| label: fig-anisotropy-comp-2d
#| column: screen
plot_anistropy_comparison_2d()
```

```{julia}
#| label: fig-anisotropy-comp-i-e
#| column: screen
plot_anistropy_comparison_i_e()
```

### 2025-02-26 notebooks/00_index.qmd
feat: combine density and temp

@@
 using Speasy
-using Speasy: DataSet
-spz = speasy()
+speasy()
 
@@
 
-tvars_psp = [
-    "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
-    ["cda/PSP_SWP_SPI_SF00_L3_MOM/DENS", "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"],
-    "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
-    "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
+density_tvar = SpaceTools.DataSet(
+    "Density",
+    [
+        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
+        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
+        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
     ]
+)
+
+# tvars_psp = [
+#     "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
+#     density_tvar,
+#     "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
+#     "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
+# ]
 
@@
     "cda/WI_H2_MFI/BGSE",
-    "cda/WI_PM_3DP/P_DENS",
+    ["cda/WI_PM_3DP/P_DENS" "cda/WI_PM_3DP/P_TEMP"],
     "cda/WI_PM_3DP/P_VELS",
-    "cda/WI_PM_3DP/P_TEMP",
 ]
@@
 add_title = true
-tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
+# tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
 tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)

### 2025-02-27 notebooks/00_index.qmd
update

--- 2025-02-18 notebooks/00_index.qmd
@@
 using Speasy
-using Speasy: DataSet
-spz = speasy()
-
+using SpaceTools
 using DimensionalData
-using SpaceTools
 using GLMakie
+# using CairoMakie
 using Dates
@@
 ```{julia}
-tmin = DateTime("2021-04-29")
-tmax = DateTime("2021-04-30")
+
+tmin_psp = DateTime("2021-01-14")
+tmax_psp = DateTime("2021-01-21")
+tmin_wind = DateTime("2021-01-15")
+tmax_wind = DateTime("2021-01-23")
+
+density_tvar = SpaceTools.DataSet(
+    "Density",
+    [
+        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
+        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
+        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
+    ],
+    (title="Density", labels=["SPI", "RFS"])
+)
 
@@
     "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
-    ["cda/PSP_SWP_SPI_SF00_L3_MOM/DENS", "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"],
+    density_tvar,
     "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
@@
     "cda/WI_PM_3DP/P_DENS",
-    "cda/WI_PM_3DP/P_VELS",
+    tnorm_combine ∘ SpeasyProduct("cda/WI_PM_3DP/P_VELS"),
+    tnorm_combine ∘ SpeasyProduct("cda/WI_K0_SWE_RTN/V_RTN"),
     "cda/WI_PM_3DP/P_TEMP",
+    # ("cda/WI_PM_3DP/P_DENS", "cda/WI_PM_3DP/P_TEMP")
 ]
 
-f = Figure()
+f = Figure(; size=(1200, 800))
 add_title = true
-tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
-tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
+tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title)
+# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title)
 add_labels!()

### 2025-04-02 notebooks/00_index.qmd
update

--- 2025-02-18 notebooks/00_index.qmd
@@
 using Speasy
-using Speasy: DataSet
-spz = speasy()
-
+using SPEDAS
 using DimensionalData
-using SpaceTools
 using GLMakie
+# using CairoMakie
 using Dates
+using PartialFunctions
 ```
@@
 ```{julia}
-tmin = DateTime("2021-04-29")
-tmax = DateTime("2021-04-30")
+tmin_psp = DateTime("2021-01-14")
+tmax_psp = DateTime("2021-01-21")
+tmin_wind = DateTime("2021-01-15")
+tmax_wind = DateTime("2021-01-23")
+
+tmin_wind = DateTime("2021-01-17")
+tmax_wind = DateTime("2021-01-19")
+
+density_tvar = SPEDAS.DataSet(
+    "Density",
+    [
+        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
+        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
+        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
+    ],
+    (title="Density", labels=["SPI", "RFS"])
+)
 
@@
 
+wind_B = tnorm_combine ∘ SpeasyProduct(
+    "cda/WI_H2_MFI/BGSE",
+    (; ylabel="B (nT)", labels=["Bx", "By", "Bz", "Magnitude"])
+)
+
+wind_vel = tnorm_combine ∘ SpeasyProduct(
+    "cda/WI_K0_SWE_RTN/V_RTN"
+    # "cda/WI_PM_3DP/P_VELS"
+)
+
 tvars_wind = [
-    "cda/WI_H2_MFI/BGSE",
+    wind_B,
     "cda/WI_PM_3DP/P_DENS",
-    "cda/WI_PM_3DP/P_VELS",
+    "cda/WI_K0_SWE_RTN/V_RTN",
+    wind_vel,
     "cda/WI_PM_3DP/P_TEMP",
@@
 
-f = Figure()
-add_title = true
-tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
-tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
-add_labels!()
+f = Figure(; size=(1200, 800))
+add_title = false
+# tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title)
+tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title)
+add_labels!(; position=Left(), valign=:top, halign=:left, padding=(10, 10, 10, 0));
 f

### 2025-04-03 notebooks/00_index.qmd
feat: overview plot

--- 2025-02-26 notebooks/00_index.qmd
@@
 
+WI_H1_SWE	Proton_W_moment	        Proton thermal speed W (km/s) from isotropic moment analysis
+WI_H1_SWE	Proton_Wperp_moment 	Proton thermal speed Wperpendicular (km/s) from bimax moment analysis
+WI_H1_SWE	Proton_Wpar_moment	    Proton thermal speed Wparallel (km/s) from bimax moment analysis
+
+WI_H1_SWE	Proton_Wperp_nonlin	    Proton thermal speed perpendicular to the magnetic field direction [km/s].
+WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].
+
 ```{julia}
 using Speasy
-speasy()
+using SPEDAS
+using SPEDAS: ulabel
+using DimensionalData
+using GLMakie
+# using CairoMakie
+using Dates
+using PartialFunctions
+using Unitful, Latexify, UnitfulLatexify, LaTeXStrings
+using Beforerr: _theme_legend
 
-using DimensionalData
-using SpaceTools
-using GLMakie
-using Dates
+update_theme!(_theme_legend(; padding=(0, 0, 0, 0)))
 ```
@@
 ```{julia}
-tmin = DateTime("2021-04-29")
-tmax = DateTime("2021-04-30")
+tmin_psp = DateTime("2021-01-14")
+tmax_psp = DateTime("2021-01-21")
+tmin_wind = DateTime("2021-01-15")
+tmax_wind = DateTime("2021-01-23")
 
-density_tvar = SpaceTools.DataSet(
+tmin_psp = DateTime("2021-01-14")
+tmax_psp = DateTime("2021-01-15")
+tmin_wind = DateTime("2021-01-17")
+tmax_wind = DateTime("2021-01-18")
+
+B_ylabel = "B (nT)"
+B_labels = ["Bx", "By", "Bz", "Magnitude"]
+V_ylabel = "Velocity (km/s)"
+V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
+Temp_ylabel = "Temperature (eV)"
+WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
+WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
+
+psp_n = SPEDAS.DataSet(
     "Density",
     [
-        "cda/PSP_SWP_SPI_SF00_L3_MOM/DENS",
-        "cda/PSP_FLD_L3_RFS_LFR_QTN/N_elec",
-        "cda/PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"
-    ]
+        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
+        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
+        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
+    ];
+    ylabel=ulabel("Density", "cm^-3")
 )
 
-# tvars_psp = [
-#     "cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc",
-#     density_tvar,
-#     "cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
-#     "cda/PSP_SWP_SPI_SF00_L3_MOM/TEMP",
-# ]
+psp_temp = SPEDAS.DataSet(
+    "Temperature",
+    [
+        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
+        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
+    ];
+    ylabel=Temp_ylabel
+)
+
+tvars_psp = [
+    tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
+    psp_n,
+    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
+    psp_temp,
+]
+
+wind_n = SPEDAS.DataSet(
+    "Density",
+    [
+        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
+        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
+    ];
+    ylabel=ulabel("Density", "cm^-3")
+)
+
+wind_temp = SPEDAS.DataSet(
+    "Temperature",
+    [
+        SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
+        SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
+    ];
+    ylabel=Temp_ylabel
+)
 
 tvars_wind = [
-    "cda/WI_H2_MFI/BGSE",
-    ["cda/WI_PM_3DP/P_DENS" "cda/WI_PM_3DP/P_TEMP"],
-    "cda/WI_PM_3DP/P_VELS",
+    tnorm_combine ∘ SpeasyProduct("WI_H3-RTN_MFI/BRTN"; ylabel=B_ylabel, labels=B_labels),
+    wind_n,
+    SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
+    wind_temp,
+    SPEDAS.DataSet("Thermal speed", ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]),
+    "WI_ELM2_3DP/MAGT3"
 ]
 
-f = Figure()
-add_title = true
-# tplot(f[1, 1], tvars_psp, tmin, tmax; add_title)
-tplot(f[1, 2], tvars_wind, tmin, tmax; add_title)
-add_labels!()
+tvars_themis = [
+    tnorm_combine ∘ SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ"; ylabel=B_ylabel, labels=B_labels),
+    ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"],
+    SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ"; ylabel=V_ylabel, labels=V_labels),
+    "THB_L2_ESA/thb_peif_avgtempQ",
+    SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
+    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
+]
+
+f = Figure(; size=(1200, 800))
+add_title = false
+legend = (; position=Top())
+tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
+tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
+tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
+add_labels!(f[1, 1]; labels='1':'9', open="(a.")
+add_labels!(f[1, 2]; labels='1':'9', open="(b.")
+add_labels!(f[1, 3]; labels='1':'9', open="(c.")
 f

### 2025-04-04 notebooks/00_index.qmd
fix: Remove unused imports and extract density ylabel to variable

@@
 using PartialFunctions
-using Unitful, Latexify, UnitfulLatexify, LaTeXStrings
 using Beforerr: _theme_legend
@@
 B_labels = ["Bx", "By", "Bz", "Magnitude"]
+n_ylabel = ulabel("Density", "cm^-3")
 V_ylabel = "Velocity (km/s)"
@@
     ];
-    ylabel=ulabel("Density", "cm^-3")
+    ylabel=n_ylabel
 )

### 2025-04-04 notebooks/00_index.qmd
feat: Add smooth function to PSP and THEMIS data processing, update plot labels

@@
 using SPEDAS
-using SPEDAS: ulabel
+using SPEDAS: ulabel, smooth
 using DimensionalData
@@
         SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
-        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
+        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
     ];
@@
 tvars_psp = [
-    tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
+    smooth(30u"s") ∘ tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
     psp_n,
@@
 tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
+add_labels!(f[1, 1]; labels='1':'9', open="(a.")
+
 tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
+add_labels!(f[1, 2]; labels='1':'9', open="(b.")
+
 tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
-add_labels!(f[1, 1]; labels='1':'9', open="(a.")
-add_labels!(f[1, 2]; labels='1':'9', open="(b.")
 add_labels!(f[1, 3]; labels='1':'9', open="(c.")

### 2025-04-04 notebooks/00_index.qmd
feat: Add functions to save/load PSP data to netCDF

@@
 
+Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
+
+## Overview
+
 ```{julia}
@@
 using GLMakie
+using Statistics
 # using CairoMakie
@@
 using PartialFunctions
+using Unitful
 using Beforerr: _theme_legend
+using SPEDAS.SpaceDataModel: set
 
@@
 ```{julia}
+# along time get the temperature from anisotropic temperature
+function tTemp(x; dims=Ti)
+    return mean.(eachslice(x; dims))
+end
+```
+
+```{julia}
+using NCDatasets
+using YAXArrays
+path = "data/psp_e07.nc"
+# ds = NCDataset(path)
+ds = YAXArrays.open_dataset(path)
+```
+
+```{julia}
 tmin_psp = DateTime("2021-01-14")
 tmax_psp = DateTime("2021-01-21")
-tmin_wind = DateTime("2021-01-15")
+tmin_wind = DateTime("2021-01-17")
 tmax_wind = DateTime("2021-01-23")
 
-tmin_psp = DateTime("2021-01-14")
-tmax_psp = DateTime("2021-01-15")
+tmin_psp = DateTime("2021-01-16")
+tmax_psp = DateTime("2021-01-19")
 tmin_wind = DateTime("2021-01-17")
@@
 WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
+```
+
+```{julia}
+psp_B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels)
 
@@
 tvars_psp = [
-    smooth(30u"s") ∘ tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
+    tnorm_combine ∘ psp_B,
     psp_n,
@@
 
+mva_B = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
+mva_V_labels = ["V_L", "V_M", "V_N"]
+```
+
+```{julia}
 wind_n = SPEDAS.DataSet(
@@
     wind_n,
-    SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
-    wind_temp,
-    SPEDAS.DataSet("Thermal speed", ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]),
-    "WI_ELM2_3DP/MAGT3"
+    tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
+    wind_temp
 ]
+```
+
+```{julia}
+thm_temp = SPEDAS.DataSet(
+    "Temperature",
+    [
+        "THB_L2_ESA/thb_peif_avgtempQ",
+        tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label="Electron")
+    ];
+    ylabel=Temp_ylabel
+)
 
@@
     SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ"; ylabel=V_ylabel, labels=V_labels),
-    "THB_L2_ESA/thb_peif_avgtempQ",
-    SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
-    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
+    thm_temp,
 ]
+```
 
+```{julia}
 f = Figure(; size=(1200, 800))
@@
 legend = (; position=Top())
+# plot = (; resample=(; n=Inf))
+labels = '1':'9'
 tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
-add_labels!(f[1, 1]; labels='1':'9', open="(a.")
+add_labels!(f[1, 1]; labels, open="(a.")
 
-tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
-add_labels!(f[1, 2]; labels='1':'9', open="(b.")
+# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
+# add_labels!(f[1, 2]; labels, open="(b.")
 
-tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
-add_labels!(f[1, 3]; labels='1':'9', open="(c.")
+# tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
+# add_labels!(f[1, 3]; labels, open="(c.")
 f
 ```
+
+## Event example (with pressure anisotropy)
+
+```{julia}
+using Discontinuity
+
+tau = Second(30)
+psp_events = detect_variance(psp_B(tmin_psp, tmax_psp), tau)
+```
+
+```{julia}
+function plot_candidate(event, ts)
+    tplot(ts, event["tstart"], event["tstop"])
+end
+
+event = psp_events[2, :]
+# psp_ds(event["tstart"], event["tstop"])
+plot_candidate(event, [tvars_psp; mva_B])
+```
+
+### Plot
+
+```{julia}
+wind_proton_T3 = SPEDAS.DataSet("Thermal speed",
+    ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]
+)
+
+tvars_wind2 = tvars_wind + [
+    wind_proton_T3,
+    "WI_ELM2_3DP/MAGT3"
+]
+
+tvars_themis2 = tvars_themis + [
+    # SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
+    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
+]
+```

### 2025-04-04 scripts/data.py

@@ -2,6 +2,8 @@ from psp.config import WindConfig, THEMISConfig, SoloConfig
 from psp.config.psp import PSPConfig
 from speasy.core.requests_scheduling.request_dispatch import init_cdaweb
 from loguru import logger
+from psp.io.psp import load_psp_data
+from psp.io import save_to_hdf5
 
 init_cdaweb()
 
@@ -16,3 +18,9 @@ for enc in encs:
             logger.warning(
                 f"Failed to produce {cls.__name__} for enc={enc} due to {e} not found in timerange"
             )
+
+
+for enc in encs:
+    # convert .tplot file to hdf5
+    tnames = load_psp_data(enc)
+    save_to_hdf5(["Tp_spani_b", "Tp_spanib_b"], f"data/psp_e{enc:02}.nc")

### 2025-04-04 src/psp/io/__init__.py

@@ -1,5 +1,8 @@
 from pytplot import get_data
 import polars as pl
+from numbers import Number
+import xarray
+import numpy as np
 
 
 def time_stamp(ts):
@@ -15,3 +18,29 @@ def get_data_lf(name):
     return pl.LazyFrame(df).with_columns(
         pl.col("time").dt.cast_time_unit("ns"),
     )
+
+
+def clean_attributes(da):
+    da.attrs = {
+        k: v
+        for k, v in da.attrs.items()
+        if isinstance(v, (str, Number, bool, list, tuple))
+    }
+    return da
+
+
+def save_to_hdf5(tnames, path):
+    data_dict = {
+        tname: convert_time(
+            clean_attributes(get_data(tname, xarray=True))
+        ).drop_duplicates(dim="time")
+        for tname in tnames
+    }
+    ds = xarray.Dataset(data_dict)
+    ds.to_netcdf(path)
+
+
+def convert_time(da: xarray.DataArray, type="ms"):
+    if np.issubdtype(da.time.dtype, np.datetime64):
+        da = da.assign_coords(time=da.time.values.astype(f"datetime64[{type}]"))
+    return da

### 2025-04-04 src/psp/io/psp.py

@@ -34,7 +34,8 @@ def load_psp_data(enc: int = 7):
 def determine_enc(timerange):
     return 7
 
-def drop_duplicates(da: xr.DataArray, dim = "time"):
+
+def drop_duplicates(da: xr.DataArray, dim="time"):
     """Drop duplicates from a DataArray."""
     if not da.get_index(dim).is_unique:
         logger.warning(f"{da.name} {dim} is not unique, dropping duplicates")
@@ -47,6 +48,7 @@ def get_data(product, timerange):
     load_psp_data(enc)
     da = pytplot.get_data(product, xarray=True)
     return drop_duplicates(da.sel(time=slice(*timerange)))
+
 
 def get_psp_data(kind):
     match kind:

### 2025-04-04 src/main.jl
fix: update

@@ -8,7 +8,6 @@ using PartialFunctions
 using LaTeXStrings
 using Beforerr
 using Discontinuity
-using Discontinuity.DefaultMapping
 
 ds_order = ["Parker Solar Probe", "Solar Orbiter", "ARTEMIS", "Wind"]
 

### 2025-04-04 src/psp/config/psp.py

@@ -71,14 +71,14 @@ class PSPConfig(IDsConfig):
             density_col = "n"
             velocity_cols = ["v_R", "v_T", "v_N"]
 
-            mag_data = get_psp_data("mag")
+            mag_data = get_psp_data("mag").collect()
             density_data = get_psp_data("den").rename({"0": density_col})
             velocity_data = get_psp_data("vel").rename(
                 dict(zip(["0", "1", "2"], velocity_cols))
             )
             ion_temp_data = get_psp_data("temp")
 
-            time = mag_data.collect().get_column("time").to_numpy()
+            time = mag_data.get_column("time").to_numpy()
             self.ts = timedelta(
                 microseconds=np.median(np.diff(time)).item() / 1000
             )  # Related: https://github.com/python/cpython/issues/59648

### 2025-04-08 notebooks/00_index.qmd
feat: mva of velocity

@@
 end
+
+_unitify(u) = x -> x * u
+mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
 ```
@@
 WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
+
+mva_V_labels = ["V_L", "V_M", "V_N"]
 ```
@@
         SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
+        _unitify(u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
         SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
@@
 
+psp_V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels)
+
 tvars_psp = [
@@
     psp_n,
-    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
-    psp_temp,
+    psp_V,
+    psp_temp
 ]
-
-mva_B = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
-mva_V_labels = ["V_L", "V_M", "V_N"]
 ```
@@
 
+psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
+psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)
+
 event = psp_events[2, :]
-# psp_ds(event["tstart"], event["tstop"])
-plot_candidate(event, [tvars_psp; mva_B])
+plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
 ```

### 2025-04-09 notebooks/00_index.qmd
feat: data reading

@@
 using SPEDAS.SpaceDataModel: set
+include("../src/psp_temp.jl")
 
@@
 mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
-```
-
-```{julia}
-using NCDatasets
-using YAXArrays
-path = "data/psp_e07.nc"
-# ds = NCDataset(path)
-ds = YAXArrays.open_dataset(path)
 ```
@@
 psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
-psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)
+psp_V_mva = Product((psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)
+psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
+psp_pTemp_ani = Product(read_proton_temperature(), tview; labels=["Proton (parallel)", "Proton (perpendicular)"])
+psp_Temp_ani = [psp_eTemp_ani, psp_pTemp_ani]
 
 event = psp_events[2, :]
-plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
+plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva, psp_Temp_ani]])
 ```
@@
 ```
+
+```{julia}

### 2025-04-09 scripts/data.py

@@ -1,15 +1,18 @@
+# %%
 from psp.config import WindConfig, THEMISConfig, SoloConfig
 from psp.config.psp import PSPConfig
 from speasy.core.requests_scheduling.request_dispatch import init_cdaweb
 from loguru import logger
 from psp.io.psp import load_psp_data
-from psp.io import save_to_hdf5
+from psp.io import save_tnames
 
+# %%
 init_cdaweb()
 
 encs = [7, 8, 9, 11]
 configs = [PSPConfig, THEMISConfig, WindConfig, SoloConfig]
 
+# %%
 for enc in encs:
     for cls in configs:
         try:
@@ -19,8 +22,10 @@ for enc in encs:
                 f"Failed to produce {cls.__name__} for enc={enc} due to {e} not found in timerange"
             )
 
-
+# %%
 for enc in encs:
     # convert .tplot file to hdf5
     tnames = load_psp_data(enc)
-    save_to_hdf5(["Tp_spani_b", "Tp_spanib_b"], f"data/psp_e{enc:02}.nc")
+    save_tnames(["Tp_spani_b", "Tp_spanib_b"], f"../data/psp_e{enc:02}")
+
+# %%

### 2025-04-09 src/psp/io/__init__.py

@@ -3,6 +3,7 @@ import polars as pl
 from numbers import Number
 import xarray
 import numpy as np
+import os
 
 
 def time_stamp(ts):
@@ -29,15 +30,16 @@ def clean_attributes(da):
     return da
 
 
-def save_to_hdf5(tnames, path):
-    data_dict = {
-        tname: convert_time(
-            clean_attributes(get_data(tname, xarray=True))
-        ).drop_duplicates(dim="time")
-        for tname in tnames
-    }
-    ds = xarray.Dataset(data_dict)
-    ds.to_netcdf(path)
+def save_tnames(tnames, path, format="netcdf"):
+    os.makedirs(path, exist_ok=True)
+
+    for tname in tnames:
+        da = get_data(tname, xarray=True)
+        da = convert_time(clean_attributes(da)).drop_duplicates(dim="time").to_dataset()
+        if format == "netcdf":
+            da.to_netcdf(path + "/" + tname + ".nc", group=tname)
+        elif format == "zarr":
+            da.to_zarr(path + "/" + tname + ".zarr", mode="w-")
 
 
 def convert_time(da: xarray.DataArray, type="ms"):

### 2025-04-09 src/psp_temp.jl

@@ -1,0 +1,63 @@
+using CSV
+using DataFrames
+using Dates
+using DimensionalData
+using DrWatson
+using Unitful
+using NetCDF
+using YAXArrays
+
+"""
+    read_electron_temperature(filename; data_dir=datadir())
+
+Read electron temperature data from CSV file into a DimensionalData structure.
+Returns a DimArray with dimensions of time and temperature components (parallel and perpendicular).
+
+# Arguments
+- `filename`: Name of the CSV file in the electron_fit_Halekas directory
+- `data_dir`: Base directory for data, defaults to DrWatson's datadir()
+
+# Returns
+- DimArray with electron temperature data
+"""
+function read_electron_temperature(filename; data_dir=datadir(), unit=u"eV")
+    # Construct full path to the file
+    filepath = joinpath(data_dir, filename)
+
+    # Read CSV file
+    df = CSV.File(filepath; dateformat="yyyy-mm-dd/HH:MM:SS.sss", drop=[3])
+
+    temp_data = hcat(df.coretpar_data, df.coretperp_data) * unit
+
+    # Create DimArray with appropriate dimensions
+    return DimArray(
+        temp_data,
+        (
+            Ti(df.coretpar_time),
+            Dim{:component}([:parallel, :perpendicular])
+        ),
+        name=:electron_temperature
+    )
+end
+
+"""
+    read_all_electron_temperature(; data_dir=datadir())
+
+Read all electron temperature data files.
+"""
+function read_electron_temperature(; data_dir=datadir("electron_fit_Halekas"))
+    # Define the files to read
+    files = [
+        "e7e8_coretemp.csv" => [7, 8],       # Encounters 7-8 (higher resolution)
+        "e9_coretemp.csv" => [9]             # Encounter 9
+    ]
+    mapreduce(vcat, files) do (file, _)
+        read_electron_temperature(file; data_dir=data_dir)
+    end
+end
+
+function read_proton_temperature(; path="data/psp_e07/Tp_spanib_b.nc", unit=u"eV")
+    ds = YAXArrays.open_dataset(path; driver=:netcdf)
+    Tp_spani = readcubedata(ds.Tp_spanib_b)
+    return DimArray(transpose(Tp_spani) * unit)
+end

### 2025-04-09 notebooks/00_index.qmd
feat: event plot

--- 2025-04-08 notebooks/00_index.qmd
@@
 WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].
+WI_PLSP_3DP	Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
+WI_PM_3DP	Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
 
@@
 using SPEDAS.SpaceDataModel: set
+using PSPAnisotropy
+include("../src/psp_temp.jl")
+using PSPAnisotropy: Wind, PSP, THEMIS
 
@@
 Temp_ylabel = "Temperature (eV)"
-WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
-WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 
-mva_V_labels = ["V_L", "V_M", "V_N"]
+V_mva_labels = ["V_L", "V_M", "V_N"]
+B_mva_labels = ["B_L", "B_M", "B_N"]
 ```
@@
 ```{julia}
-psp_B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels)
-
-psp_n = SPEDAS.DataSet(
-    "Density",
-    [
-        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
-        _unitify(u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
-        SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
-        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
-    ];
-    ylabel=n_ylabel
-)
-
-psp_temp = SPEDAS.DataSet(
-    "Temperature",
-    [
-        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
-        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
-    ];
-    ylabel=Temp_ylabel
-)
-
-psp_V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels)
-
 tvars_psp = [
-    tnorm_combine ∘ psp_B,
-    psp_n,
-    psp_V,
-    psp_temp
+    tnorm_combine ∘ PSP.B,
+    PSP.n,
+    PSP.V,
+    PSP.T
 ]
@@
 ```{julia}
-wind_n = SPEDAS.DataSet(
-    "Density",
-    [
-        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
-        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
-    ];
-    ylabel=n_ylabel
-)
-
-wind_temp = SPEDAS.DataSet(
-    "Temperature",
-    [
-        SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
-        SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
-    ];
-    ylabel=Temp_ylabel
-)
-
 tvars_wind = [
-    tnorm_combine ∘ SpeasyProduct("WI_H3-RTN_MFI/BRTN"; ylabel=B_ylabel, labels=B_labels),
-    wind_n,
-    tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
+    tnorm_combine ∘ Wind.B,
+    Wind.n,
+    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
+    tsubtract ∘ Wind.V,
     wind_temp
@@
 ```{julia}
-thm_temp = SPEDAS.DataSet(
-    "Temperature",
-    [
-        "THB_L2_ESA/thb_peif_avgtempQ",
-        tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label="Electron")
-    ];
-    ylabel=Temp_ylabel
-)
-
 tvars_themis = [
-    tnorm_combine ∘ SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ"; ylabel=B_ylabel, labels=B_labels),
-    ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"],
-    SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ"; ylabel=V_ylabel, labels=V_labels),
-    thm_temp,
+    tnorm_combine ∘ THEMIS.B,
+    THEMIS.n,
+    THEMIS.V_GSE,
+    THEMIS.T,
 ]
@@
 tau = Second(30)
-psp_events = detect_variance(psp_B(tmin_psp, tmax_psp), tau)
+psp_events = detect_variance(PSP.B(tmin_psp, tmax_psp), tau)
+wind_events = detect_variance(Wind.B(tmin_wind, tmax_wind), tau)
+thm_events = detect_variance(THEMIS.B_FGL_GSE(tmin_wind, tmax_wind), tau)
 ```
@@
 ```{julia}
-function plot_candidate(event, ts)
-    tplot(ts, event["tstart"], event["tstop"])
+psp_B_mva = set(mva ∘ PSP.B; name="mva_B", labels=B_mva_labels)
+psp_V_mva = Product((PSP.V, PSP.B), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
+psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
+psp_pTemp_ani = Product(read_proton_temperature(), tview; labels=["Proton (parallel)", "Proton (perpendicular)"])
+psp_Temp_ani = [psp_eTemp_ani, psp_pTemp_ani]
+psp_mva_all = [psp_B_mva, psp_V_mva, psp_Temp_ani]
+
+wind_B_mva = set(mva ∘ Wind.B; name="mva_B", labels=B_mva_labels)
+wind_V_mva = Product((Wind.V_GSE, Wind.B_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
+wind_mva_all = [wind_B_mva, wind_V_mva, Wind.Temp_ani]
+
+thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=B_mva_labels)
+thm_V_mva = Product((THEMIS.V_GSE, THEMIS.B_FGL_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
+thm_mva_all = [thm_B_mva, thm_V_mva, THEMIS.T_ani]
+```
+
+```{julia}
+using DataFrames
+
+@kwdef struct Event
+    start
+    stop
+    metadata = Dict()
 end
 
-psp_B_mva = set(mva ∘ psp_B; name="mva_B", labels=["B_L", "B_M", "B_N"])
-psp_V_mva = Product("mva_V", (psp_V, psp_B), mva_transform; ylabel=V_ylabel, labels=mva_V_labels)
+Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict())
 
-event = psp_events[2, :]
-plot_candidate(event, [tvars_psp; [psp_B_mva, psp_V_mva]])
+(P::AbstractProduct)(e::Event) = P(e.start, e.stop)
 ```
 
-### Plot
+```{julia}
+function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
+    tplot(f, ts, event.tstart - toffset, event.tstop + toffset; kwargs...)
+end
 
-```{julia}
-wind_proton_T3 = SPEDAS.DataSet("Thermal speed",
-    ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"]
-)
-
-tvars_wind2 = tvars_wind + [
-    wind_proton_T3,
-    "WI_ELM2_3DP/MAGT3"
+let link_xaxes = false
+    tvars_wind = [
+        tnorm_combine ∘ Wind.B,
+        Wind.n,
+        Wind.V_GSE,
+        Wind.temp,
+        wind_B_mva,
+        wind_V_mva,
+        Wind.Temp_ani
     ]
 
-tvars_themis2 = tvars_themis + [
-    # SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity),
-    SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity),
-]
+    tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]
+
+    f = Figure(; size=(1200, 800))
+    plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
+    wind_plots = plot_candidate(f[1, 2], Event(wind_events, 3), tvars_wind, Minute(1); link_xaxes)
+    themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
+    # hideydecorations!(wind_plots)
+    # hideydecorations!(themis_plots)
+    f
+end
 ```

### 2025-04-09 src/PSPAnisotropy.jl

@@ -1,0 +1,6 @@
+module PSPAnisotropy
+using Speasy
+include("PSP.jl")
+include("Wind.jl")
+include("THEMIS.jl")
+end

### 2025-04-09 src/THEMIS.jl

@@ -1,0 +1,27 @@
+module THEMIS
+using StatsBase
+using DimensionalData
+using SPEDAS: SpeasyProduct, DataSet
+
+function tTemp(x; dims=Ti)
+    return mean.(eachslice(x; dims))
+end
+
+B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
+B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
+
+n = ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"]
+
+V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ")
+
+T = DataSet("Temperature", [
+    "THB_L2_ESA/thb_peif_avgtempQ",
+    tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label="Electron")
+])
+
+pTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity)
+eTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity)
+
+T_ani = DataSet("Temperature anisotropy", [pTemp_ani, eTemp_ani]; yscale=identity)
+
+end

### 2025-04-09 src/Wind.jl

@@ -1,0 +1,45 @@
+module Wind
+using Base: Fix2
+using Unitful
+using SPEDAS: SpeasyProduct, DataSet, ulabel
+
+# WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM] 
+
+B_labels = ["Bx", "By", "Bz", "Magnitude"]
+WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
+WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
+
+B = SpeasyProduct("WI_H4-RTN_MFI/BRTN"; labels=B_labels)
+
+V = SpeasyProduct("WI_K0_SWE_RTN/V_RTN")
+
+V_RTN = SpeasyProduct("WI_H1_SWE_RTN/Proton_V_nonlin")
+# Proton_V_moment
+
+B_GSE = SpeasyProduct("WI_H2_MFI/BGSE")
+V_GSE = SpeasyProduct("WI_PM_3DP/P_VELS")
+
+n = DataSet(
+    "Density",
+    [
+        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
+        SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
+    ]
+)
+
+temp = DataSet(
+    "Temperature",
+    [
+        SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
+        SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
+    ];
+    ylabel="Temperature (eV)"
+)
+
+pTemp_ani = Fix2(*, u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.P.MAGT3")
+alphaTemp_ani = Fix2(*, u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.A.MAGT3"; labels=["Perp_1", "Perp_2", "Parallel"]) # original labels ["BX_GSE", "BY_GSE", "BZ_GSE"] is not right
+eTemp_ani = SpeasyProduct("WI_ELM2_3DP/MAGT3")
[…]

### 2025-04-10 notebooks/00_index.qmd
update

@@
 
-_unitify(u) = x -> x * u
 mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
+
+```
+
+```{julia}
+using SPEDAS: timedim
+
+function tdiff(x; dims=Ti)
+    times = SPEDAS.times(x)
+    return diff(x; dims) ./ diff(times)
+end
+```
+
+```{julia}
+using Unitful: μ0
+using LinearAlgebra: norm
+
+"""
+    current_density(B, V)
+
+Calculate the current density time series from the magnetic field (B) and plasma velocity (V) time series.
+"""
+@views function current_density(B, V)
+    _B_in = tview(B, timerange(V))
+    dBdt = tdiff(_B_in)
+
+    dBxdt = dBdt[:, 1]
+    dBydt = dBdt[:, 2]
+    ts = SPEDAS.times(dBdt)
+    Vn = tinterp(V[:, 3], ts)
+    Jx = @. upreferred(dBydt / (μ0 * Vn))
+    Jy = @. upreferred(-dBxdt / (μ0 * Vn))
+
+    B_in = _B_in[1:end-1, :]
+    Bx = B_in[:, 1]
+    By = B_in[:, 2]
+    Bmag = norm.(eachrow(B_in))
+    Jpara = @. (Jx * Bx + Jy * By) / Bmag
+    Jperp = @. (Jy * Bx - Jx * By) / Bmag
+    return (; Jx, Jy, Jpara, Jperp)
+end
+
+@b current_density(B, V)
 ```
@@
 tmax_psp = DateTime("2021-01-21")
-tmin_wind = DateTime("2021-01-17")
+tmin_wind = DateTime("2021-01-15")
 tmax_wind = DateTime("2021-01-23")
+tmax_wind = DateTime("2021-02-15")
 
@@
 tmax_psp = DateTime("2021-01-19")
-tmin_wind = DateTime("2021-01-17")
-tmax_wind = DateTime("2021-01-18")
+# tmin_wind = DateTime("2021-01-17")
+# tmax_wind = DateTime("2021-01-18")
 
@@
 tau = Second(30)
-psp_events = detect_variance(PSP.B(tmin_psp, tmax_psp), tau)
-wind_events = detect_variance(Wind.B(tmin_wind, tmax_wind), tau)
-thm_events = detect_variance(THEMIS.B_FGL_GSE(tmin_wind, tmax_wind), tau)
+# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
+# wind_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau)
+thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
 ```

### 2025-04-10 src/Wind.jl

@@ -5,11 +5,10 @@ using SPEDAS: SpeasyProduct, DataSet, ulabel
 
 # WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM] 
 
-B_labels = ["Bx", "By", "Bz", "Magnitude"]
 WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
 WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 
-B = SpeasyProduct("WI_H4-RTN_MFI/BRTN"; labels=B_labels)
+B = SpeasyProduct("WI_H4-RTN_MFI/BRTN")
 
 V = SpeasyProduct("WI_K0_SWE_RTN/V_RTN")
 
@@ -31,6 +30,7 @@ temp = DataSet(
     "Temperature",
     [
         SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
+        SpeasyProduct("WI_H0_SWE/Te"),
         SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels=WI_ELM2_3DP_labels),
     ];
     ylabel="Temperature (eV)"
@@ -38,8 +38,9 @@ temp = DataSet(
 
 pTemp_ani = Fix2(*, u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.P.MAGT3")
 alphaTemp_ani = Fix2(*, u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.A.MAGT3"; labels=["Perp_1", "Perp_2", "Parallel"]) # original labels ["BX_GSE", "BY_GSE", "BZ_GSE"] is not right
-eTemp_ani = SpeasyProduct("WI_ELM2_3DP/MAGT3")
+eTemp_T3 = SpeasyProduct("WI_ELM2_3DP/MAGT3")
+eTemp_ani = SpeasyProduct("WI_H0_SWE/Te_anisotropy"; CATDESC="Temperature anisotropy = Te_para / Te_perp")
 pW_ani = DataSet("Thermal speed", ["WI_H1_SWE/Proton_Wperp_nonlin", "WI_H1_SWE/Proton_Wpar_nonlin", "WI_H1_SWE/Proton_Wperp_moment", "WI_H1_SWE/Proton_Wpar_moment"])
 
[…]

### 2025-04-12 notebooks/00_index.qmd
feat: current_density

@@
 mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
-
-```
-
-```{julia}
-using SPEDAS: timedim
-
-function tdiff(x; dims=Ti)
-    times = SPEDAS.times(x)
-    return diff(x; dims) ./ diff(times)
-end
-```
-
-```{julia}
-using Unitful: μ0
-using LinearAlgebra: norm
-
-"""
-    current_density(B, V)
-
-Calculate the current density time series from the magnetic field (B) and plasma velocity (V) time series.
-"""
-@views function current_density(B, V)
-    _B_in = tview(B, timerange(V))
-    dBdt = tdiff(_B_in)
-
-    dBxdt = dBdt[:, 1]
-    dBydt = dBdt[:, 2]
-    ts = SPEDAS.times(dBdt)
-    Vn = tinterp(V[:, 3], ts)
-    Jx = @. upreferred(dBydt / (μ0 * Vn))
-    Jy = @. upreferred(-dBxdt / (μ0 * Vn))
-
-    B_in = _B_in[1:end-1, :]
-    Bx = B_in[:, 1]
-    By = B_in[:, 2]
-    Bmag = norm.(eachrow(B_in))
-    Jpara = @. (Jx * Bx + Jy * By) / Bmag
-    Jperp = @. (Jy * Bx - Jx * By) / Bmag
-    return (; Jx, Jy, Jpara, Jperp)
-end
-
-@b current_density(B, V)
 ```
@@
 B_mva_labels = ["B_L", "B_M", "B_N"]
+```
+
+```{julia}
+B = PSP.B(tmin_psp, tmin_psp + Hour(1))
+V = PSP.V(tmin_psp, tmin_psp + Hour(1))
+current_density(B, V)
 ```

### 2025-04-14 notebooks/00_index.qmd
feat: anisotry plot

@@
 using Beforerr: _theme_legend
-using SPEDAS.SpaceDataModel: set
+using SPEDAS.SpaceDataModel: set, extend, @set
 using PSPAnisotropy
 include("../src/psp_temp.jl")
+include("../src/calc.jl")
 using PSPAnisotropy: Wind, PSP, THEMIS
@@
 
-mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
+mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
+make_mva_transform(tb_min, tb_max) = mva_transform$(; tb_min, tb_max)
+
+j_transform((V, B), tmin, tmax) = current_density(B(tmin, tmax), V(tmin, tmax))
 ```
@@
 tmax_wind = DateTime("2021-01-23")
-tmax_wind = DateTime("2021-02-15")
 
@@
 n_ylabel = ulabel("Density", "cm^-3")
-V_ylabel = "Velocity (km/s)"
+V_ylabel = "V (km/s)"
+ΔV_ylabel = "ΔV (km/s)"
 V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
@@
 B_mva_labels = ["B_L", "B_M", "B_N"]
-```
-
-```{julia}
-B = PSP.B(tmin_psp, tmin_psp + Hour(1))
-V = PSP.V(tmin_psp, tmin_psp + Hour(1))
-current_density(B, V)
 ```
@@
     tsubtract ∘ Wind.V,
-    wind_temp
+    Wind.temp
 ]
@@
 tvars_themis = [
-    tnorm_combine ∘ THEMIS.B,
+    tnorm_combine ∘ THEMIS.B_GSE,
     THEMIS.n,
@@
 using Discontinuity
-
 tau = Second(30)
 # psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
-# wind_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau)
-thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
+wind_events = ids_finder(Wind.B, tmin_wind, tmax_wind, tau)
+# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
 ```
@@
 
-wind_B_mva = set(mva ∘ Wind.B; name="mva_B", labels=B_mva_labels)
-wind_V_mva = Product((Wind.V_GSE, Wind.B_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
-wind_mva_all = [wind_B_mva, wind_V_mva, Wind.Temp_ani]
-
 thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=B_mva_labels)
@@
 ```{julia}
-using DataFrames
-
-@kwdef struct Event
-    start
-    stop
-    metadata = Dict()
+function make_mva_product(event, V, B=V; kwargs...)
+    mva_transform = make_mva_transform(t_us_ds(event)...)
+    return Product((V, B), mva_transform; kwargs...)
 end
 
-Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict())
+function make_mva_products(event, B, V, n=nothing, T3=nothing)
+    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
+    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
+    J = Product((V_mva, B_mva), j_transform)
+    result = [tnorm_combine ∘ B, V, B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
+    isnothing(n) || push!(result, set(
+        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
+        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
+    ))
+    isnothing(T3) || begin
+        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
+        Va_Λ = set(
+            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
+            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
+        )
+        push!(result, Λ, Va_Λ)
+    end
+    return result
+end
+```
 
-(P::AbstractProduct)(e::Event) = P(e.start, e.stop)
+```{julia}
+tvars2_wind = [
+    tnorm_combine ∘ Wind.B,
+    Wind.n,
+    Wind.V_GSE,
+    Wind.temp,
+    Wind.Temp_ani
+]
+
+tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]
 ```
@@
 function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
-    tplot(f, ts, event.tstart - toffset, event.tstop + toffset; kwargs...)
+    tmin, tmax = t_us_ds(event)
+    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
+    tlines!(f, [tmin, tmax])
+    f
 end
 
-let link_xaxes = false
-    tvars_wind = [
-        tnorm_combine ∘ Wind.B,
-        Wind.n,
-        Wind.V_GSE,
-        Wind.temp,
-        wind_B_mva,
-        wind_V_mva,
-        Wind.Temp_ani
-    ]
+f = let
+    f = Figure(; size=(1200, 800))
+    # plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
 
-    tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]
-
-    f = Figure(; size=(1200, 800))
-    plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
-    wind_plots = plot_candidate(f[1, 2], Event(wind_events, 3), tvars_wind, Minute(1); link_xaxes)
-    themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
+    wind_event = Event(wind_events, 9) # 300
+    wind_T3 = extend(Wind.pTemp_ani, Second(20))
+    wind_tvars = make_mva_products(wind_event, Wind.B_GSE, Wind.V_GSE, Wind.n_p, wind_T3)
+    wind_tvars = [wind_tvars[3:end]; Wind.Temp_ani; Wind.n; Wind.Temp]
+    for p in Wind.Temp_ani
+        @info "$p" data = p(wind_event)
+    end
+    wind_plots = plot_candidate(f, wind_event, wind_tvars, tau)
+    # themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
     # hideydecorations!(wind_plots)
     # hideydecorations!(themis_plots)
-    f
 end

### 2025-04-14 src/PSP.jl

@@ -1,15 +1,15 @@
 module PSP
-using Base: Fix2
 using Unitful
 using SPEDAS
-using SPEDAS: SpeasyProduct, DataSet, ulabel
+using Speasy: SpeasyProduct
+using SPEDAS: DataSet, ulabel
 
 
 B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc")
 n = DataSet("Density",
     [
         SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
-        Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
+        Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
         SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
         SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
     ]

### 2025-04-14 src/THEMIS.jl

@@ -1,7 +1,8 @@
 module THEMIS
 using StatsBase
 using DimensionalData
-using SPEDAS: SpeasyProduct, DataSet
+using Speasy: SpeasyProduct
+using SPEDAS: DataSet
 
 function tTemp(x; dims=Ti)
     return mean.(eachslice(x; dims))

### 2025-04-14 src/Wind.jl

@@ -1,9 +1,14 @@
 module Wind
 using Base: Fix2
+using Speasy: SpeasyProduct
+using PartialFunctions
 using Unitful
-using SPEDAS: SpeasyProduct, DataSet, ulabel
+using SPEDAS: DataSet, ulabel
 
+unitify(u) = (*)$u
 # WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM] 
+# WI_PM_3DP : Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
+# WI_PLSP_3DP : Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
 
 WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
 WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
@@ -18,26 +23,29 @@ V_RTN = SpeasyProduct("WI_H1_SWE_RTN/Proton_V_nonlin")
 B_GSE = SpeasyProduct("WI_H2_MFI/BGSE")
 V_GSE = SpeasyProduct("WI_PM_3DP/P_VELS")
 
+n_p = SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels)
+
 n = DataSet(
     "Density",
     [
-        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=WI_PM_3DP_labels),
+        n_p,
+        SpeasyProduct("WI_PLSP_3DP/MOM.P.DENSITY"),
         SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels=WI_ELM2_3DP_labels)
     ]
 )
 
-temp = DataSet(
+Temp = DataSet(
     "Temperature",
     [
         SpeasyProduct("WI_PM_3DP/P_TEMP"; labels=WI_PM_3DP_labels),
-        SpeasyProduct("WI_H0_SWE/Te"),
+        SpeasyProduct("WI_PLSP_3DP/MOM.P.AVGTEMP"),
[…]

### 2025-04-14 src/calc.jl

@@ -1,0 +1,28 @@
+using PlasmaFormulary
+using Discontinuity: anisotropy
+
+function alfven_velocity_ts(B, n)
+    n_mean = mean(parent(n))
+    mass_number = 1
+    return uconvert.(u"km/s", alfven_velocity.(B, n_mean, Ref(mass_number)))
+end
+
+function anisotropy_ts(B, n, T3; kw...)
+    n_mean = mean(parent(n))
+    T3_mean = mean(parent(T3); dims=1)
+    return anisotropy.(eachrow(B), n_mean, Ref(T3_mean); kw...)
+end
+
+function alfven_velocity_ani_ts(B, n, T3; kw...)
+    Va = alfven_velocity_ts(B, n)
+    Λ = anisotropy_ts(B, n, T3; kw...)
+    return @. Va * sqrt(1 - Λ)
+end
+
+for f in (:alfven_velocity_ts, :anisotropy_ts, :alfven_velocity_ani_ts)
+    @eval $f(args::Tuple, tmin, tmax) = $f(map(p -> p(tmin, tmax), args)...)
+end
+
+function tmaterialize(p::AbstractProduct, tmin, tmax)
+    # @set p(tmin, tmax)
+end

### 2025-04-14 src/utils.jl

@@ -13,3 +13,10 @@ function subset_timerange(df, start, stop)
 end
 
 subset_timerange(df, timerange::Tuple) = subset_timerange(df, timerange...)
+
+import SPEDAS: Event
+
+SPEDAS.Event(df::DataFrame) = (i = rand(1:size(df, 1)); @info i; Event(df, i))
+SPEDAS.Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict(:t_us_ds => df.t_us_ds[i]))
+(P::AbstractProduct)(e::Event) = P(e.start, e.stop)
+t_us_ds(e::Event) = e.metadata[:t_us_ds]

### 2025-04-21 notebooks/00_index.qmd
feat: more features processing

@@
 tmax_wind = DateTime("2021-01-23")
+_tmax_wind = DateTime("2021-01-15T02")
 
@@
 ```{julia}
-using Discontinuity
+using Discontinuity: ids_finder
 tau = Second(30)
 # psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
-wind_events = ids_finder(Wind.B, tmin_wind, tmax_wind, tau)
+wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
 # thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
@@
     J = Product((V_mva, B_mva), j_transform)
-    result = [tnorm_combine ∘ B, V, B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
+    result = [tnorm_combine ∘ B, V, tnorm_combine ∘ B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
     isnothing(n) || push!(result, set(
@@
     Wind.V_GSE,
-    Wind.temp,
+    Wind.Temp,
     Wind.Temp_ani
@@
 
-    wind_event = Event(wind_events, 9) # 300
+    wind_event = AniEvent(wind_events, 1) # 300
     wind_T3 = extend(Wind.pTemp_ani, Second(20))

### 2025-04-21 src/calc.jl

@@ -3,8 +3,7 @@ using Discontinuity: anisotropy
 
 function alfven_velocity_ts(B, n)
     n_mean = mean(parent(n))
-    mass_number = 1
-    return uconvert.(u"km/s", alfven_velocity.(B, n_mean, Ref(mass_number)))
+    return alfven_velocity.(B, n_mean)
 end
 
 function anisotropy_ts(B, n, T3; kw...)
@@ -21,8 +20,4 @@ end
 
 for f in (:alfven_velocity_ts, :anisotropy_ts, :alfven_velocity_ani_ts)
     @eval $f(args::Tuple, tmin, tmax) = $f(map(p -> p(tmin, tmax), args)...)
-end
-
-function tmaterialize(p::AbstractProduct, tmin, tmax)
-    # @set p(tmin, tmax)
 end

### 2025-04-21 src/utils.jl

@@ -16,7 +16,7 @@ subset_timerange(df, timerange::Tuple) = subset_timerange(df, timerange...)
 
 import SPEDAS: Event
 
-SPEDAS.Event(df::DataFrame) = (i = rand(1:size(df, 1)); @info i; Event(df, i))
-SPEDAS.Event(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict(:t_us_ds => df.t_us_ds[i]))
+AniEvent(df::DataFrame) = (i = rand(1:size(df, 1)); @info i; Event(df, i))
+AniEvent(df::DataFrame, i) = Event(df.tstart[i], df.tstop[i], Dict(:data => df[i, :]))
 (P::AbstractProduct)(e::Event) = P(e.start, e.stop)
-t_us_ds(e::Event) = e.metadata[:t_us_ds]
+t_us_ds(e::Event) = e.metadata[:data].t_us_ds

### 2025-04-24 notebooks/00_index.qmd
update

@@
 using DimensionalData
+# using CairoMakie
 using GLMakie
 using Statistics
-# using CairoMakie
 using Dates
@@
 using Unitful
-using Beforerr: _theme_legend
+using Beforerr: _theme_legend, easy_save
 using SPEDAS.SpaceDataModel: set, extend, @set
@@
 include("../src/calc.jl")
+include("../src/meta.jl")
 using PSPAnisotropy: Wind, PSP, THEMIS
@@
 tmin_psp = DateTime("2021-01-14")
-tmax_psp = DateTime("2021-01-21")
+tmax_psp = DateTime("2021-01-20")
 tmin_wind = DateTime("2021-01-15")
@@
 # tmax_wind = DateTime("2021-01-18")
-
-B_ylabel = "B (nT)"
-B_labels = ["Bx", "By", "Bz", "Magnitude"]
-n_ylabel = ulabel("Density", "cm^-3")
-V_ylabel = "V (km/s)"
-ΔV_ylabel = "ΔV (km/s)"
-V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
-Temp_ylabel = "Temperature (eV)"
-
-V_mva_labels = ["V_L", "V_M", "V_N"]
-B_mva_labels = ["B_L", "B_M", "B_N"]
 ```
@@
 tvars_psp = [
-    tnorm_combine ∘ PSP.B,
-    PSP.n,
-    PSP.V,
-    PSP.T
+    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
+    set(PSP.n; ylabel=n_ylabel),
+    set(tnorm_combine ∘ PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
+    set(PSP.T; ylabel=T_ylabel)
 ]
@@
 tvars_wind = [
-    tnorm_combine ∘ Wind.B,
-    Wind.n,
-    # tsubtract ∘ SpeasyProduct("WI_K0_SWE_RTN/V_RTN"; ylabel=V_ylabel, labels=V_labels),
-    tsubtract ∘ Wind.V,
-    Wind.temp
+    set(tnorm_combine ∘ Wind.B_RTN_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
+    set(Wind.n; ylabel=n_ylabel),
+    set(Wind.V_RTN; ylabel=V_ylabel, labels=V_RTN_labels),
+    set(Wind.T; ylabel=T_ylabel)
 ]
@@
 ```{julia}
-tvars_themis = [
-    tnorm_combine ∘ THEMIS.B_GSE,
-    THEMIS.n,
-    THEMIS.V_GSE,
-    THEMIS.T,
-]
+using Intervals: Interval
+data = THEMIS.V_GSE(tmin_wind, tmax_wind)
+_times = @views SPEDAS.times(data)[(data[:, 1].>-200u"km/s").|(data[:, 2].<-50u"km/s")]
+dt = Minute(10)
+its = union([Interval(t - dt, t + dt) for t in _times])
+_tmask! = tmask!(its)
 ```
@@
 ```{julia}
-f = Figure(; size=(1200, 800))
-add_title = false
+tvars_themis = [
+    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
+    THEMIS.n,
+    _tmask! ∘ THEMIS.V_GSE,
+    set(THEMIS.T; ylabel=T_ylabel)
+]
+
+```
+
+```{julia}
+tmin_psp = "2021-01-14"
+tmax_psp = "2021-01-20"
+
+f = Figure(; size=(900, 600))
 legend = (; position=Top())
-# plot = (; resample=(; n=Inf))
 labels = '1':'9'
-tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
-add_labels!(f[1, 1]; labels, open="(a.")
+# plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
+# add_labels!(f[1, 1]; labels, open="(a.")
 
-# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
+# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
 # add_labels!(f[1, 2]; labels, open="(b.")
 
-# tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
-# add_labels!(f[1, 3]; labels, open="(c.")
+tplot(f[1, 1], tvars_themis, tmin_wind, tmax_wind; legend)
+add_labels!(f[1, 1]; labels, open="(c.")
 f
+# easy_save("overview")
 ```

### 2025-04-24 src/Wind.jl

@@ -1,24 +1,42 @@
 module Wind
 using Base: Fix2
-using Speasy: SpeasyProduct
+using Speasy: SpeasyProduct, getdimarray
+using DimensionalData: Y
 using PartialFunctions
 using Unitful
-using SPEDAS: DataSet, ulabel
+using SPEDAS: DataSet, ulabel, Product
 
 unitify(u) = (*)$u
 # WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM] 
 # WI_PM_3DP : Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
 # WI_PLSP_3DP : Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
+# WI_H0_SWE : 6 - 12 sec Solar Wind Electron Moments
+# WI_H1_SWE : 92-sec Solar Wind Alpha and Proton Anisotropy Analysis
+# WI_H1_SWE_RTN : Solar wind proton and alpha parameters, including anisotropic temperatures, derived by non-linear fitting of the measurements and with moment techniques
+# WI_H5_SWE : 9 sec solar wind electron moments at 12 sec cadence
 
 WI_PM_3DP_labels = ["Proton"] # "Proton (3DP, PESA Low)"
 WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 
 B = SpeasyProduct("WI_H4-RTN_MFI/BRTN")
+B_RTN_1MIN = SpeasyProduct("WI_H3-RTN_MFI/BRTN")
 
-V = SpeasyProduct("WI_K0_SWE_RTN/V_RTN")
+V = SpeasyProduct("WI_K0_SWE_RTN/V_RTN") # Note: it contains some weird spikes
 
-V_RTN = SpeasyProduct("WI_H1_SWE_RTN/Proton_V_nonlin")
-# Proton_V_moment
+function combine_getdimarrays(ps, args...)
+    das = getdimarray.(ps, args...)
+    cat(das...; dims=Y())
+end
+
+V_RTN = Product(
+    [
+        "cda/WI_H1_SWE_RTN/Proton_VR_nonlin",
[…]

### 2025-04-24 src/meta.jl

@@ -1,0 +1,17 @@
+begin
+    B_ylabel = ulabel("B", "nT")
+    B_labels = ["Bx", "By", "Bz", "Magnitude"]
+    B_RTN_labels = [L"B_R", L"B_T", L"B_N", L"|B\;|"]
+    B_LMN_labels = [L"B_L", L"B_M", L"B_N"]
+    B_XYZ_labels = [L"B_x", L"B_y", L"B_z", L"|B\;|"]
+    n_ylabel = ulabel("n", "cm^-3")
+
+    V_ylabel = ulabel("V", "km/s")
+    V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
+    V_RTN_labels = [L"V_R", L"V_T", L"V_N", L"|V\;|"]
+    V_LMN_labels = [L"V_L", L"V_M", L"V_N"]
+    V_XYZ_labels = [L"V_x", L"V_y", L"V_z", L"|V\;|"]
+    ΔV_ylabel = "ΔV (km/s)"
+
+    T_ylabel = ulabel("T", "eV")
+end

### 2025-06-05 index.qmd
docs: update
chore: clean a little

@@
 # Introduction
+
+@lotekarKineticscaleCurrentSheets2022
 
@@
 
+> We will also present plasma density estimates delivered by the quasi-thermal noise spectroscopy available at about 7 s cadence (Moncuquet et al. 2020).
+> The procedure of CS selection and methodology, briefly described below, is equivalent to those used in the paper
+
 ## In-situ synergistic observations (Alignment)
@@
 
+@telloniSpacecraftRadialAlignments2023
+
 <!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
 -->
+
+# Overview and Example of Current Sheets
+
+> @lotekarKineticscaleCurrentSheets2022 Figure 1 presents an overview of the considered 10 day interval.
+Over this interval, the spacecraft was at radial distances from 0.17 to 0.24 au, that is, from 35 to 50 solar radii, and remained within the inward magnetic field sector without crossing the heliospheric current sheet (Phan et al.
+2020; Szabo et al.
+2020).
+No coronal mass ejections were observed in the considered interval (Phan et al.
+2020; Szabo et al.
+2020).
+The spacecraft was approximately corotating with the Sun and connected to the same coronal hole (Bale et al.
+2019; Badman et al.
+2020).
+Panels (a)–(d) present 1 minute averages of the magnetic field magnitude, proton flow velocity, densities, and temperatures of protons and electrons as well as plasma density estimates provided by the quasi-thermal noise spectroscopy.
+The magnetic field magnitude was about 100 nT at the perihelion on November 6, and around 50 nT as the spacecraft moved to a radial distance of 50 solar radii from the Sun on November 1 and 10.
+The solar wind was typically slow  with a proton flow velocity below 400 km s−1, except for the ≈20 hr period of fast solar wind between November 9 and 10.
+The three plasma density estimates in panel (c) are consistent with each other within a few tens of percent over the entire interval, except for the fast solar wind interval, where the proton densities were about 4 times smaller than the plasma density estimates provided by the quasi-thermal noise spectroscopy.
+We will use the electron density estimates, calibrated to best match proton densities and the results of quasi-thermal noise spectroscopy, as plasma density estimates.
+The proton temperature during the considered interval varied between about 10 and 100 eV, while the electron temperature remained around 30 eV.
+Panel (e) presents 1 minute averages of proton and electron betas and shows that both quantities varied in the range from 0.1 to 5.
+> Figure 2 presents several CSs from our data set.
 
@@
 
-## Comparison of Discontinuity Properties
-
-![](figures/enc2/thickness_current.spi_n_spi.png)
-
-![](figures/enc2/density_distribution.spi_n_spi.png)
-
-K1: Normalized discontinuities properties does not vary much with radial distance
-
-![](figures/enc7/properties_distribution.svg)
-
-Thickness and current density relationship
-Scale-dependent properties of current sheets in the solar wind
-
 ![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
-
-## Alfvénicity
 
@@
 
-### Estimated Anisotropy
+## Estimated Anisotropy
 
@@
 ![](figures/B_angle.png)
+
+# Discussion
+
+K1: Normalized discontinuities properties does not vary much with radial distance
+
+Thickness and current density relationship, scale-dependent properties of current sheets in the solar wind
 

### 2025-06-05 notebooks/10_results.qmd
fix: update
chore: clean a little

@@
 ```{julia}
-using Revise
 using DrWatson
-@quickactivate
-include(srcdir("main.jl"))
+using PSPAnisotropy.Dataset: load_all
+using Discontinuity: var_mapping
 import Beforerr: easy_save
-```
-
-```{julia}
-enc = 8 # event id (encounter id)    
-easy_save(fname; enc=enc) = Beforerr.easy_save(fname; dir="$fig_dir/enc$enc", formats=[:svg, :pdf])
+using GLMakie, AlgebraOfGraphics
+m = var_mapping()
 ```
@@
 
-## Discontinuities' properties
+## Current sheet's properties
 
@@
 
+### Thickness and current density comparison
+
 ```{julia}
 begin
-    fname = "thickness_current"
-
-    plt = data_layer_a * visual(Scatter)
+    fname = "thickness_current_xy_comp"
+    data_layer = data(df)
+    plt = data_layer * visual(Scatter)
 
     fig = Figure(size=(1000, 500))
-    axis = log_axis
+    axis = (; yscale=log10, xscale=log10)
 
@@
 
-    grid1 = plt * mapping(l_map, j_map) |> draw!(ga; axis=axis)
-    grid2 = plt * mapping(l_norm_map, j_norm_map) |> draw!(gb; axis=axis)
+    spec1 = plt * mapping(m.l, m.j)
+    spec2 = plt * mapping(m.l_norm, m.j_norm)
+
+    draw!(ga, spec1; axis)
+    draw!(gb, spec2; axis)
 
@@
 ```
-
-`ggscatterhist` can not handle log scale well
 

### 2025-06-05 src/PSPAnisotropy.jl

@@ -3,4 +3,5 @@ using Speasy
 include("PSP.jl")
 include("Wind.jl")
 include("THEMIS.jl")
+include("dataset.jl")
 end

### 2025-06-05 src/calc.jl

@@ -8,7 +8,7 @@ end
 
 function anisotropy_ts(B, n, T3; kw...)
     n_mean = mean(parent(n))
-    T3_mean = mean(parent(T3); dims=1)
+    T3_mean = mean(parent(T3); dims = 1)
     return anisotropy.(eachrow(B), n_mean, Ref(T3_mean); kw...)
 end
 
@@ -20,4 +20,72 @@ end
 
 for f in (:alfven_velocity_ts, :anisotropy_ts, :alfven_velocity_ani_ts)
     @eval $f(args::Tuple, tmin, tmax) = $f(map(p -> p(tmin, tmax), args)...)
+end
+
+
+DEFAULT_B_UNIT = u"nT"
+DEFAULT_DENSITY_UNIT = u"cm^-3"
+DEFAULT_TEMP_UNIT = u"eV"
+
+function anisotropy(B, density, para_temp, perp_temp)
+    Λ = @. (μ0 * density * (para_temp - perp_temp) / B^2) |> NoUnits
+    return Λ
+end
+
+"""
+Calculate the pressure anisotropy
+"""
+function calc_pressure_anisotropy!(
+        df;
+        B = "B.mean",
+        density = "n.mean",
+        ion_temp_para = "ion_temp_para",
+        ion_temp_perp = "ion_temp_perp",
+        e_temp_para = "e_temp_para",
+        e_temp_perp = "e_temp_perp",
+        B_unit = DEFAULT_B_UNIT,
+        density_unit = DEFAULT_DENSITY_UNIT,
+        temp_unit = DEFAULT_TEMP_UNIT,
+    )
+
+    B = df[:, B] .* B_unit
+    n = df[:, density] .* density_unit
+
+    if ion_temp_para in names(df) && ion_temp_perp in names(df)
+        ion_temp_para_u = df[:, ion_temp_para] .* temp_unit
+        ion_temp_perp_u = df[:, ion_temp_perp] .* temp_unit
+        df[:, :Λ_ion] = anisotropy(B, n, ion_temp_para_u, ion_temp_perp_u)
+    else
+        @info "Ion temperature columns not found"
+    end
+
+    if e_temp_para in names(df) && e_temp_perp in names(df)
+        e_temp_para_u = df[:, e_temp_para] .* temp_unit
+        e_temp_perp_u = df[:, e_temp_perp] .* temp_unit
+        df[:, :Λ_e] = anisotropy(B, n, e_temp_para_u, e_temp_perp_u)
+    else
[…]

### 2025-06-05 src/main.jl

@@ -11,7 +11,6 @@ using Discontinuity
 
 ds_order = ["Parker Solar Probe", "Solar Orbiter", "ARTEMIS", "Wind"]
 
-include("io.jl")
 include("plot.jl")
 include("utils.jl")
 

### 2025-06-05 src/utils.jl

@@ -1,3 +1,4 @@
+using SpaceDataModel: AbstractProduct
 using Dates
 
 # select the time range of interest "2021-04-29T00:45" to "2021-04-29T01:15"

### 2025-06-06 notebooks/00_index.qmd
refactor: update

@@
 
+## Setup
+
+```{julia}
+using Dates
+using DrWatson
+using PSPAnisotropy
+using PSPAnisotropy: Wind, PSP, THEMIS
+using Discontinuity
+```
+
 ## Overview
@@
 using Speasy
-using SPEDAS
-using SPEDAS: ulabel, smooth
+using SPEDAS: ulabel, smooth, tnorm_combine, tplot
 using DimensionalData
@@
 using Statistics
-using Dates
 using PartialFunctions
@@
 using SPEDAS.SpaceDataModel: set, extend, @set
-using PSPAnisotropy
 include("../src/psp_temp.jl")
@@
 include("../src/meta.jl")
-using PSPAnisotropy: Wind, PSP, THEMIS
 
@@
 tau = Second(30)
-# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
+psp_events = ids_finder(PSP.B, tmin_psp, tmax_psp, tau)
 wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
-# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
+thm_events = ids_finder(THEMIS.B_FGL_GSE, tmin_wind, tmax_wind, tau)
 ```
@@
 ```
+
+## Batch processing
+
+Wind Speed, Time to Earth
+300 km/s, ~5.8 days
+400 km/s, ~3.9 days
+500 km/s, ~3.5 days
+700 km/s, ~2.5 days

### 2025-06-06 notebooks/10_results.qmd
refactor: update

@@
 m = var_mapping()
-```
-
-```{julia}
-df_enc_7 = load_all(7);
-df_enc_8 = load_all(8);
-df_enc_9 = load_all(9);
-df = reduce(vcat, [df_enc_7, df_enc_8, df_enc_9], cols=:intersect);
+df = PSPAnisotropy.workload()
 ```

### 2025-06-06 src/THEMIS.jl

@@ -1,28 +1,36 @@
+## THB_L2_MOM
+# `thb_peem_t3_magQ`: Electron Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)
+# `thb_peim_t3_magQ`: Ion Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)
+# `thb_peem_ptens_magQ`: Electron Pressure Tensor, Field Aligned
+# `thb_peim_ptens_magQ`: Ion Pressure Tensor, Field Aligned
+
 module THEMIS
 using StatsBase
 using DimensionalData
-using Speasy: SpeasyProduct
-using SPEDAS: DataSet
+using Speasy: SpeasyProduct, getdimarray
+using SPEDAS: DataSet, tsort
 
-function tTemp(x; dims=Ti)
+function tTemp(x; dims = Ti)
     return mean.(eachslice(x; dims))
 end
 
 B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
-B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
+B_FGL_GSE = tsort ∘ SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
 
 n = ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"]
 
 V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ")
 
-T = DataSet("Temperature", [
-    "THB_L2_ESA/thb_peif_avgtempQ",
-    tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label="Electron")
-])
+T = DataSet(
+    "Temperature", [
+        "THB_L2_ESA/thb_peif_avgtempQ",
+        tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label = "Electron"),
+    ]
+)
 
-pTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale=identity)
-eTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale=identity)
+pTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale = identity)
[…]

### 2025-06-09 notebooks/00_index.qmd
update

@@
 using Discontinuity
+using SPEDAS
 ```
@@
 using DimensionalData
-# using CairoMakie
-using GLMakie
+using CairoMakie
+# using GLMakie
 using Statistics
@@
     set(PSP.n; ylabel=n_ylabel),
-    set(tnorm_combine ∘ PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
+    set(PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
     set(PSP.T; ylabel=T_ylabel)
@@
 tvars_wind = [
-    set(tnorm_combine ∘ Wind.B_RTN_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
+    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel),
     set(Wind.n; ylabel=n_ylabel),
-    set(Wind.V_RTN; ylabel=V_ylabel, labels=V_RTN_labels),
+    # set(Wind.V_GSE_p; ylabel=V_ylabel),
+    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel),
     set(Wind.T; ylabel=T_ylabel)
@@
 ```{julia}
+using GLMakie
+```
+
+```{julia}
 using Intervals: Interval
-data = THEMIS.V_GSE(tmin_wind, tmax_wind)
-_times = @views SPEDAS.times(data)[(data[:, 1].>-200u"km/s").|(data[:, 2].<-50u"km/s")]
+thx_v_gse = THEMIS.V_GSE(tmin_wind, tmax_wind)
+_times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
 dt = Minute(10)
@@
     _tmask! ∘ THEMIS.V_GSE,
-    set(THEMIS.T; ylabel=T_ylabel)
+    set(_tmask! ∘ THEMIS.eTemp; ylabel=T_ylabel)
 ]
@@
 
-tplot(f[1, 1], tvars_themis, tmin_wind, tmax_wind; legend)
-add_labels!(f[1, 1]; labels, open="(c.")
+tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; legend)
+add_labels!(f[1, 3]; labels, open="(c.")
 f

### 2025-06-09 src/PSP.jl

@@ -8,21 +8,19 @@ using SPEDAS: DataSet, ulabel
 B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc")
 B_1MIN = SpeasyProduct("PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min")
 
-n = DataSet("Density",
-    [
-        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels=["SPI Proton"]),
-        Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels=["SPC Proton"]),
-        # SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels=["RFS Electron"]),
-        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels=["SQTN Electron"])
-    ],
-)
+n_spi = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels = ["SPI Proton"])
+n_spc = Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels = ["SPC Proton"])
+n_sqtn = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels = ["SQTN Electron"])
+n_rfs = SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels = ["RFS Electron"])
+n = DataSet("Density", [n_spi, n_spc, n_sqtn])
 
 V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN")
 
-T = DataSet("Temperature",
+T = DataSet(
+    "Temperature",
     [
-        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
-        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
[…]

### 2025-06-09 src/PSPAnisotropy.jl

@@ -26,9 +26,9 @@ end
 
 
 function workload()
-    psp_config = Dict(:id => "PSP", :B => PSP.B, :tau => 30)
-    wind_config = Dict(:id => "Wind", :B => Wind.B_GSE, :tau => 30)
-    thm_config = Dict(:id => "THEMIS", :B => THEMIS.B_FGL_GSE, :tau => 30)
+    psp_config = Dict(:id => "PSP", :B => PSP.B, :V => PSP.V, :n => PSP.n_spi, :tau => 30)
+    wind_config = Dict(:id => "Wind", :B => Wind.B_GSE, :V => Wind.V_GSE_K0, :n => Wind.n_p_K0, :tau => 30)
+    thm_config = Dict(:id => "THEMIS", :B => THEMIS.B_FGL_GSE, :n => THEMIS.n_ion, :V => THEMIS.V_GSE, :tau => 30)
     configs = [psp_config, wind_config, thm_config]
 
     df = mapreduce(vcat, 7:9) do enc
@@ -39,7 +39,7 @@ function workload()
             c[:t0] = Date(timerange[1])
             c[:t1] = Date(timerange[2])
             res, = produce_or_load(c, datadir(); tag = false) do c
-                c[:events] = ids_finder(c[:B], c[:t0], c[:t1], Second(c[:tau]))
+                c[:events] = ids_finder(c[:B], c[:t0], c[:t1], Second(c[:tau]), c[:V], c[:n])
                 c
             end
             @rtransform!(res["events"], :enc = enc, :id = id)

### 2025-06-09 src/THEMIS.jl

@@ -17,16 +17,15 @@ end
 B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
 B_FGL_GSE = tsort ∘ SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
 
-n = ["THB_L2_MOM/thb_peim_densityQ", "THB_L2_MOM/thb_peem_densityQ"]
+n_ion = SpeasyProduct("THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale = identity)
+n_elec = SpeasyProduct("THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
+n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
 
 V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ")
 
-T = DataSet(
-    "Temperature", [
-        "THB_L2_ESA/thb_peif_avgtempQ",
-        tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label = "Electron"),
-    ]
-)
+pTemp = SpeasyProduct("THB_L2_ESA/thb_peif_avgtempQ"; label = "Proton")
+eTemp = tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; label = "Electron")
+T = DataSet("Temperature", [pTemp, eTemp])
 
 pTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale = identity)
 eTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale = identity)

### 2025-06-09 src/Wind.jl

@@ -4,14 +4,14 @@ using Speasy: SpeasyProduct, getdimarray
 using DimensionalData: Y
 using PartialFunctions
 using Unitful
-using SPEDAS: DataSet, ulabel, Product
+using SPEDAS: DataSet, ulabel, Product, replace_outliers!
 
-unitify(u) = (*)$u
-# WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM] 
-# WI_PM_3DP : Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
+unitify(u) = (*) $ u
+# WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM]
+# WI_PM_3DP : Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP (PRIMARY SCIENCE DATA)
 # WI_PLSP_3DP : Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
 # WI_H0_SWE : 6 - 12 sec Solar Wind Electron Moments
-# WI_H1_SWE : 92-sec Solar Wind Alpha and Proton Anisotropy Analysis
+# WI_H1_SWE : 92-sec Solar Wind Alpha and Proton Anisotropy Analysis (PRIMARY SCIENCE DATA)
 # WI_H1_SWE_RTN : Solar wind proton and alpha parameters, including anisotropic temperatures, derived by non-linear fitting of the measurements and with moment techniques
 # WI_H5_SWE : 9 sec solar wind electron moments at 12 sec cadence
 
@@ -21,54 +21,52 @@ WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 B = SpeasyProduct("WI_H4-RTN_MFI/BRTN")
 B_RTN_1MIN = SpeasyProduct("WI_H3-RTN_MFI/BRTN")
 
-V = SpeasyProduct("WI_K0_SWE_RTN/V_RTN") # Note: it contains some weird spikes
[…]

### 2025-06-09 notebooks/00_index.qmd
fig: update overplot

@@
 tvars_wind = [
-    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel),
+    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
     set(Wind.n; ylabel=n_ylabel),
     # set(Wind.V_GSE_p; ylabel=V_ylabel),
-    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel),
+    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel, labels=V_XYZ_labels),
     set(Wind.T; ylabel=T_ylabel)
@@
 ```{julia}
-using GLMakie
+using CairoMakie
+CairoMakie.activate!()
 ```
@@
 using Intervals: Interval
-thx_v_gse = THEMIS.V_GSE(tmin_wind, tmax_wind)
+
+function get_themis_tmask(t0, t1) 
+    thx_v_gse = THEMIS.V_GSE(t0, t1)
     _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
@@
     its = union([Interval(t - dt, t + dt) for t in _times])
-_tmask! = tmask!(its)
+    return tmask!(its)
+end
 ```
@@
 tvars_themis = [
-    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
-    THEMIS.n,
-    _tmask! ∘ THEMIS.V_GSE,
-    set(_tmask! ∘ THEMIS.eTemp; ylabel=T_ylabel)
+    set(tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
+    set(THEMIS.n; ylabel=n_ylabel),
+    replace_outliers! ∘ set(THEMIS.V_GSE; ylabel=V_ylabel, labels=V_XYZ_labels),
+    set(THEMIS.eTemp; ylabel=T_ylabel)
 ]
@@
 ```{julia}
-tmin_psp = "2021-01-14"
-tmax_psp = "2021-01-20"
+for enc in (7, 8, 9)
+    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
 
-f = Figure(; size=(900, 600))
+    _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
+
     legend = (; position=Top())
     labels = '1':'9'
-# plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
-# add_labels!(f[1, 1]; labels, open="(a.")
 
-# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
-# add_labels!(f[1, 2]; labels, open="(b.")
+    f = Figure(; size=(1200, 600))
+    plots = tplot(f[1, 1], tvars_psp[1:3], tmin_psp, tmax_psp; legend)
+    add_labels!(f[1, 1]; labels, open="(a.")
+    tplot(f[1, 2], tvars_wind[1:3], tmin_wind, tmax_wind; legend)
+    add_labels!(f[1, 2]; labels, open="(b.")
+    tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
+    add_labels!(f[1, 3]; labels, open="(c.")
+    easy_save("overview-$enc")
 
-tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; legend)
+    f = Figure(; size=(1200, 600))
+    plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
+    add_labels!(f[1, 1]; labels, open="(a.")
+    tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
+    add_labels!(f[1, 2]; labels, open="(b.")
+    tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
     add_labels!(f[1, 3]; labels, open="(c.")
-f
-# easy_save("overview")
+    easy_save("overview-$enc-all")
+end
 ```

### 2025-06-09 src/PSP.jl

@@ -16,13 +16,9 @@ n = DataSet("Density", [n_spi, n_spc, n_sqtn])
 
 V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN")
 
-T = DataSet(
-    "Temperature",
-    [
-        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels = ["SPI Proton"]),
-        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels = ["SQTN Electron core"]),
-    ]
-)
+pTemp = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels = ["SPI Proton"])
+eTemp = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels = ["SQTN Electron core"])
+T = DataSet("Temperature", [pTemp, eTemp])
 
 
 end

### 2025-06-12 index.qmd
update

@@
 # Dataset and method
-
-TODO: define alignment / conjunction
 
@@
 
-## In-situ synergistic observations (Alignment)
-
-**Similar** type of solar wind or **Same** solar solar wind
-
-How to define alignment?
-
-- Trajectory & Orbits (theory): ballistic approximation of Parker spiral
-
-- Plasma properties (observation):
-
-  - Invariants: plasma composition, ionization states, mass flux $n u r^2$
-
-  - Correlation: magnetic field / plasma velocity
-
-- Simulation: Trace plasma parcels evolution
-
 @telloniSpacecraftRadialAlignments2023
@@
 
-## Estimated Anisotropy
-
-The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
-
-Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
-
-![](figures/enc7/anisotropy_theory.png)
-
-## Comparison between Estimated and Observed Anisotropy
-
-![](figures/enc7/anisotropy_comparison_2d.png)
-
 ## The effect of alignment on discontinuity properties
@@
 
-## Anistropy
-
-@shenComparingPlasmaAnisotropy2024
-
-pressure anisotropy is defined as $Λ = \mu (P_∥ - P_⊥) / B^2$.
-
 # Appendix

### 2025-06-12 notebooks/000_data.qmd
update

--- 2025-06-06 notebooks/00_index.qmd
@@
-Interactively exploring the quantities of solar wind.
-
 ## Data
@@
 - [PSP/FIELDS Level 2 and higher data](https://fields.ssl.berkeley.edu/data/), [SPDF - Coordinated Data Analysis Web (CDAWeb)](https://cdaweb.gsfc.nasa.gov/cgi-bin/eval2.cgi?dataset=PSP_FLD_L2_MAG_RTN&index=sp_phys)
+
+Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
+
+```{julia}
+using Dates
+using PSPAnisotropy
+using PSPAnisotropy: Wind, PSP, THEMIS
+using SPEDAS: tplot
+using GLMakie
+```
+
+### THEMIS
+
+```{julia}
+let tmin = DateTime("2021-01-15")
+    tvars = (
+        THEMIS.B_GSE,
+        THEMIS.B_FGL_GSE,
+        THEMIS.n,
+    )
+    tplot(tvars, tmin, tmin + Day(1))
+end
+```
+
+### Wind
+
+```{julia}
+let tmin = DateTime("2021-01-15")
+    tvars = (
+        [Wind.V_GSE_3DP, Wind.V_GSE_K0],
+        [Wind.n_p_K0, Wind.n_p_3DP, Wind.n_p_nonlin],
+    )
+    tplot(tvars, tmin, tmin + Hour(3))
+end
+```
+
+`Wind.V_GSE_3DP` ("WI_PM_3DP/P_VELS") has higer time resolution than `Wind.V_GSE_K0` ("WI_K0_SWE/V_GSE").
+
+`Wind.n_p_nonlin` and `Wind.n_p_K0` seem to be the same.
+
+![](../figures/others/wind.png)
 
@@
 WI_PM_3DP	Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
-
-Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
-
-## Setup
-
-```{julia}
-using Dates
-using DrWatson
-using PSPAnisotropy
-using PSPAnisotropy: Wind, PSP, THEMIS
-using Discontinuity
-```
-
-## Overview
-
-```{julia}
-using Speasy
-using SPEDAS: ulabel, smooth, tnorm_combine, tplot
-using DimensionalData
-# using CairoMakie
-using GLMakie
-using Statistics
-using PartialFunctions
-using Unitful
-using Beforerr: _theme_legend, easy_save
-using SPEDAS.SpaceDataModel: set, extend, @set
-include("../src/psp_temp.jl")
-include("../src/calc.jl")
-include("../src/meta.jl")
-
-update_theme!(_theme_legend(; padding=(0, 0, 0, 0)))
-```
-
-```{julia}
-# along time get the temperature from anisotropic temperature
-function tTemp(x; dims=Ti)
-    return mean.(eachslice(x; dims))
-end
-
-mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
-make_mva_transform(tb_min, tb_max) = mva_transform$(; tb_min, tb_max)
-
-j_transform((V, B), tmin, tmax) = current_density(B(tmin, tmax), V(tmin, tmax))
-```
-
-```{julia}
-tmin_psp = DateTime("2021-01-14")
-tmax_psp = DateTime("2021-01-20")
-tmin_wind = DateTime("2021-01-15")
-tmax_wind = DateTime("2021-01-23")
-_tmax_wind = DateTime("2021-01-15T02")
-
-tmin_psp = DateTime("2021-01-16")
-tmax_psp = DateTime("2021-01-19")
-# tmin_wind = DateTime("2021-01-17")
-# tmax_wind = DateTime("2021-01-18")
-```
-
-```{julia}
-tvars_psp = [
-    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
-    set(PSP.n; ylabel=n_ylabel),
-    set(tnorm_combine ∘ PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
-    set(PSP.T; ylabel=T_ylabel)
-]
-```
-
-```{julia}
-tvars_wind = [
-    set(tnorm_combine ∘ Wind.B_RTN_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
-    set(Wind.n; ylabel=n_ylabel),
-    set(Wind.V_RTN; ylabel=V_ylabel, labels=V_RTN_labels),
-    set(Wind.T; ylabel=T_ylabel)
-]
-```
-
-```{julia}
-using Intervals: Interval
-data = THEMIS.V_GSE(tmin_wind, tmax_wind)
-_times = @views SPEDAS.times(data)[(data[:, 1].>-200u"km/s").|(data[:, 2].<-50u"km/s")]
-dt = Minute(10)
-its = union([Interval(t - dt, t + dt) for t in _times])
-_tmask! = tmask!(its)
-```
-
-```{julia}
-tvars_themis = [
-    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
-    THEMIS.n,
-    _tmask! ∘ THEMIS.V_GSE,
-    set(THEMIS.T; ylabel=T_ylabel)
-]
-
-```
-
-```{julia}
-tmin_psp = "2021-01-14"
-tmax_psp = "2021-01-20"
-
-f = Figure(; size=(900, 600))
-legend = (; position=Top())
-labels = '1':'9'
-# plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
-# add_labels!(f[1, 1]; labels, open="(a.")
-
-# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
-# add_labels!(f[1, 2]; labels, open="(b.")
-
-tplot(f[1, 1], tvars_themis, tmin_wind, tmax_wind; legend)
-add_labels!(f[1, 1]; labels, open="(c.")
-f
-# easy_save("overview")
-```
-
-## Event example (with pressure anisotropy)
-
-```{julia}
-using Discontinuity: ids_finder
-tau = Second(30)
-psp_events = ids_finder(PSP.B, tmin_psp, tmax_psp, tau)
-wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
-thm_events = ids_finder(THEMIS.B_FGL_GSE, tmin_wind, tmax_wind, tau)
-```
-
-```{julia}
-psp_B_mva = set(mva ∘ PSP.B; name="mva_B", labels=B_mva_labels)
-psp_V_mva = Product((PSP.V, PSP.B), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
-psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
-psp_pTemp_ani = Product(read_proton_temperature(), tview; labels=["Proton (parallel)", "Proton (perpendicular)"])
-psp_Temp_ani = [psp_eTemp_ani, psp_pTemp_ani]
-psp_mva_all = [psp_B_mva, psp_V_mva, psp_Temp_ani]
-
-thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=B_mva_labels)
-thm_V_mva = Product((THEMIS.V_GSE, THEMIS.B_FGL_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
-thm_mva_all = [thm_B_mva, thm_V_mva, THEMIS.T_ani]
-```
-
-```{julia}
-function make_mva_product(event, V, B=V; kwargs...)
-    mva_transform = make_mva_transform(t_us_ds(event)...)
-    return Product((V, B), mva_transform; kwargs...)
-end
-
-function make_mva_products(event, B, V, n=nothing, T3=nothing)
-    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
-    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
-    J = Product((V_mva, B_mva), j_transform)
-    result = [tnorm_combine ∘ B, V, tnorm_combine ∘ B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
-    isnothing(n) || push!(result, set(
-        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
-        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
-    ))
-    isnothing(T3) || begin
-        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
-        Va_Λ = set(
-            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
-            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
-        )
-        push!(result, Λ, Va_Λ)
-    end
-    return result
-end
-```
-
-```{julia}
-tvars2_wind = [
-    tnorm_combine ∘ Wind.B,
-    Wind.n,
-    Wind.V_GSE,
-    Wind.Temp,
-    Wind.Temp_ani
-]
-
-tvars_themis2 = [[THEMIS.B_FGL_GSE, THEMIS.n, THEMIS.V_GSE, THEMIS.T]; thm_mva_all]
-```
-
-```{julia}
-function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
-    tmin, tmax = t_us_ds(event)
-    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
-    tlines!(f, [tmin, tmax])
-    f
-end
-
-f = let
-    f = Figure(; size=(1200, 800))
-    # plot_candidate(f[1, 1], Event(psp_events, 2), [tvars_psp; psp_mva_all]; link_xaxes)
-
-    wind_event = AniEvent(wind_events, 1) # 300
-    wind_T3 = extend(Wind.pTemp_ani, Second(20))
-    wind_tvars = make_mva_products(wind_event, Wind.B_GSE, Wind.V_GSE, Wind.n_p, wind_T3)
-    wind_tvars = [wind_tvars[3:end]; Wind.Temp_ani; Wind.n; Wind.Temp]
-    for p in Wind.Temp_ani
-        @info "$p" data = p(wind_event)
-    end
-    wind_plots = plot_candidate(f, wind_event, wind_tvars, tau)
-    # themis_plots = plot_candidate(f[1, 3], Event(thm_events, 3), tvars_themis2, Minute(1); link_xaxes)
-    # hideydecorations!(wind_plots)
-    # hideydecorations!(themis_plots)
-end
-```
-
-## Batch processing
-
-Wind Speed, Time to Earth
-300 km/s, ~5.8 days
-400 km/s, ~3.9 days
-500 km/s, ~3.5 days
-700 km/s, ~2.5 days

### 2025-06-12 notebooks/00_index.qmd
update

@@
-Interactively exploring the quantities of solar wind.
-
-## Data
-
-- [PSP/FIELDS Level 2 and higher data](https://fields.ssl.berkeley.edu/data/), [SPDF - Coordinated Data Analysis Web (CDAWeb)](https://cdaweb.gsfc.nasa.gov/cgi-bin/eval2.cgi?dataset=PSP_FLD_L2_MAG_RTN&index=sp_phys)
-
-WI_H1_SWE	Proton_W_moment	        Proton thermal speed W (km/s) from isotropic moment analysis
-WI_H1_SWE	Proton_Wperp_moment 	Proton thermal speed Wperpendicular (km/s) from bimax moment analysis
-WI_H1_SWE	Proton_Wpar_moment	    Proton thermal speed Wparallel (km/s) from bimax moment analysis
-
-WI_H1_SWE	Proton_Wperp_nonlin	    Proton thermal speed perpendicular to the magnetic field direction [km/s].
-WI_H1_SWE	Proton_Wpar_nonlin	    Proton thermal speed parallel to the magnetic field direction [km/s].
-WI_PLSP_3DP	Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
-WI_PM_3DP	Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
-
-Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
+Interactively exploring the quantities of solar wind. See [Data](000_data.qmd) for more details about different data products.
 
@@
 using Dates
+using Speasy
 using DrWatson
@@
 using SPEDAS
+using DataFrames, DataFramesMeta
+using GLMakie
+using SPEDAS: set_meta, set_meta!
+using PartialFunctions
+
+import PSPAnisotropy.Labels as 𝑳
+import PSPAnisotropy.YLabel as 𝒀
+
+using Unitful
+Unitful.preferunits(u"nA", u"km")
+unitify(u) = (*)$u
+unitify(u::String) = (*)$uparse(u)
+```
+
+## Event example (simple)
+
+```{julia}
+df, configs = workload()
+
+psp_df = @rsubset(df, :id == "PSP"; view=true)
+psp_config = configs[1]
+wind_df = @rsubset(df, :id == "Wind"; view=true)
+wind_config = configs[2]
+thm_df = @rsubset(df, :id == "THEMIS"; view=true)
+thm_config = configs[3]
+
+thm_config["B"] = unitify("nT") ∘ thm_config["B"]
+```
+
+```{julia}
+function plot_candidate(f, event, config, toffset=Second(0); kwargs...)
+    tmin, tmax = event.t_us_ds
+    t0 = tmin - toffset
+    t1 = tmax + toffset
+
+    B_product = config["B"]
+    V_product = config["V"]
+
+    B = B_product(t0, t1) |> set_meta!(; ylabel="B", labels=𝑳.B_RTN)
+    V = V_product(t0, t1) |> set_meta!(; ylabel="V", labels=𝑳.V_RTN)
+    n = config["n"](t0, t1)
+
+    B_mva = mva(B, B) |> set_meta(; labels=𝑳.B_LMN)
+    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
+    V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)
+    J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")
+
+    result = [tnorm_combine(B_mva), tsubtract(V_mva), n, tsubtract(Va), J]
+
+    f = tplot(f, result; kwargs...)
+    tlines!(f, [tmin, tmax])
+    result
+end
+
+f = Figure(; size=(1200, 800))
+res_psp = plot_candidate(f[1, 1], psp_df[18, :], psp_config, Second(10))
+# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
+# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
+# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
+# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
+f
+
 ```
@@
 using Speasy
-using SPEDAS: ulabel, smooth, tnorm_combine, tplot
+using SPEDAS: tnorm_combine, tplot, DataSet
 using DimensionalData
@@
 include("../src/psp_temp.jl")
-include("../src/calc.jl")
 include("../src/meta.jl")
 
-update_theme!(_theme_legend(; padding=(0, 0, 0, 0)))
+import Discontinuity.AlgebraOfGraphics as AoG
+
+update_theme!(;
+    figure_padding=1,
+    fonts=(; regular=AoG.firasans("Regular"), bold=AoG.firasans("Medium")),
+    Legend=(; framevisible=false, padding=(0, 0, 0, -15)),
+    Axis=(; xlabelfont=:bold, ylabelfont=:bold),
+)
+
 ```
@@
 ```{julia}
-tvars_psp = [
-    set(tnorm_combine ∘ PSP.B_1MIN; ylabel=B_ylabel, labels=B_RTN_labels),
-    set(PSP.n; ylabel=n_ylabel),
-    set(PSP.V; ylabel=V_ylabel, labels=V_RTN_labels),
-    set(PSP.T; ylabel=T_ylabel)
+psp_B = set(tnorm_combine ∘ PSP.B_1MIN; ylabel=𝒀.B, labels=𝑳.B_RTN)
+psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
+psp_n = set(PSP.n_spi; ylabel=𝒀.n, yscale=identity)
+
+tvars_psp = [psp_B, psp_n, psp_V]
+tvars_psp_all = [
+    psp_B,
+    set(PSP.n; ylabel=𝒀.n),
+    psp_V,
+    set(PSP.T; ylabel=𝒀.T)
 ]
@@
 ```{julia}
-tvars_wind = [
-    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
-    set(Wind.n; ylabel=n_ylabel),
-    # set(Wind.V_GSE_p; ylabel=V_ylabel),
-    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel, labels=V_XYZ_labels),
-    set(Wind.T; ylabel=T_ylabel)
+wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
+wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
+
+tvars_wind = [wind_B, set(Wind.n_p_K0; ylabel=𝒀.n), wind_V]
+tvars_wind_all = [
+    wind_B,
+    set(Wind.n; ylabel=𝒀.n),
+    wind_V,
+    set(Wind.T; ylabel=𝒀.T)
 ]
@@
 tvars_themis = [
-    set(tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
-    set(THEMIS.n; ylabel=n_ylabel),
-    replace_outliers! ∘ set(THEMIS.V_GSE; ylabel=V_ylabel, labels=V_XYZ_labels),
-    set(THEMIS.eTemp; ylabel=T_ylabel)
+    set(tnorm_combine ∘ THEMIS.B_GSE; ylabel=𝒀.B, labels=𝑳.B_XYZ),
+    set(THEMIS.n; ylabel=𝒀.n),
+    replace_outliers! ∘ set(THEMIS.V_GSE; ylabel=𝒀.V, labels=𝑳.V_XYZ),
+    set(THEMIS.eTemp; ylabel=𝒀.T)
 ]
-
 ```
@@
 ```{julia}
-for enc in (7, 8, 9)
+update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(0, 0, 0, 15))
+
+for enc in 7:9
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
@@
     labels = '1':'9'
+    padding = (0, 30, 0, -30)
 
-    f = Figure(; size=(1200, 600))
+    f = Figure(; size=(800, 450))
     plots = tplot(f[1, 1], tvars_psp[1:3], tmin_psp, tmax_psp; legend)
-    add_labels!(f[1, 1]; labels, open="(a.")
+    add_labels!(f[1, 1]; labels, open="(a.", padding)
     tplot(f[1, 2], tvars_wind[1:3], tmin_wind, tmax_wind; legend)
-    add_labels!(f[1, 2]; labels, open="(b.")
-    tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
-    add_labels!(f[1, 3]; labels, open="(c.")
+    add_labels!(f[1, 2]; labels, open="(b.", padding)
+    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
+    # add_labels!(f[1, 3]; labels, open="(c.")
     easy_save("overview-$enc")
 
-    f = Figure(; size=(1200, 600))
-    plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
-    add_labels!(f[1, 1]; labels, open="(a.")
-    tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
-    add_labels!(f[1, 2]; labels, open="(b.")
-    tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
-    add_labels!(f[1, 3]; labels, open="(c.")
-    easy_save("overview-$enc-all")
+    # f = Figure(; size=(1200, 600))
+    # plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
+    # add_labels!(f[1, 1]; labels, open="(a.")
+    # tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
+    # add_labels!(f[1, 2]; labels, open="(b.")
+    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
+    # add_labels!(f[1, 3]; labels, open="(c.")
+    # easy_save("overview-$enc-all")
 end
@@
 ```{julia}
-psp_B_mva = set(mva ∘ PSP.B; name="mva_B", labels=B_mva_labels)
-psp_V_mva = Product((PSP.V, PSP.B), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
+psp_B_mva = set(mva ∘ PSP.B; name="mva_B", labels=𝑳.B_LMN)
+psp_V_mva = Product((PSP.V, PSP.B), mva_transform; ylabel=𝒀.V, labels=𝑳.V_LMN)
 psp_eTemp_ani = Product(read_electron_temperature(), tview; labels=["Electron (parallel)", "Electron (perpendicular)"])
@@
 
-thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=B_mva_labels)
-thm_V_mva = Product((THEMIS.V_GSE, THEMIS.B_FGL_GSE), mva_transform; ylabel=V_ylabel, labels=V_mva_labels)
+thm_B_mva = set(mva ∘ THEMIS.B_FGL_GSE; name="mva_B", labels=𝑳.B_LMN)
+thm_V_mva = Product((THEMIS.V_GSE, THEMIS.B_FGL_GSE), mva_transform; ylabel=𝒀.V, labels=𝑳.V_LMN)
 thm_mva_all = [thm_B_mva, thm_V_mva, THEMIS.T_ani]
-```
-
-```{julia}
-function make_mva_product(event, V, B=V; kwargs...)
-    mva_transform = make_mva_transform(t_us_ds(event)...)
-    return Product((V, B), mva_transform; kwargs...)
-end
-
-function make_mva_products(event, B, V, n=nothing, T3=nothing)
-    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=B_ylabel)
-    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=V_ylabel)
-    J = Product((V_mva, B_mva), j_transform)
-    result = [tnorm_combine ∘ B, V, tnorm_combine ∘ B_mva, set(tsubtract ∘ V_mva; ylabel=ΔV_ylabel), J]
-    isnothing(n) || push!(result, set(
-        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
-        ylabel=ΔV_ylabel, labels=["Va_L", "Va_M", "Va_N"]
-    ))
-    isnothing(T3) || begin
-        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
-        Va_Λ = set(
-            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
-            ylabel=ΔV_ylabel, labels=["Va*_L", "Va*_M", "Va*_N"]
-        )
-        push!(result, Λ, Va_Λ)
-    end
-    return result
-end
 ```
@@
 700 km/s, ~2.5 days
+
+## Thickness, current density comparison and Alfvénicity
+
+```{julia}
+using AlgebraOfGraphics
+using Discontinuity: compute_params!, filter_low_mva_quality, compute_Alfvenicity_params!
+using Beforerr
+using Beforerr: add_labels!
+using CairoMakie
+using StatsBase
+CairoMakie.activate!()
+
+set_aog_theme!()
+formats = (:pdf,)
+
+foreach([:log10, :log2, :log]) do f
+    @eval import Base: $f
+    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
+end
+
+df, configs = workload()
+𝐧 = :mva
+𝒎 = var_mapping(; 𝐧)
+
+compute_params!(df)
+
+# AoG fix
+using LaTeXStrings
+import AlgebraOfGraphics: append_unit_string
+append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
+
+subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
+
+function alpha_layer(df, alpha)
+    psp_df = @rsubset(df, :id == "PSP"; view=true)
+    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
+    wind_df = @rsubset(df, :id == "Wind"; view=true)
+    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
+end
+```
+
+```{julia}
+fname = "properties_xy_comp-enc"
+
+for enc in 7:9, 𝐧 in [:mva, :cross]
+    view = true
+    𝒎 = var_mapping(; 𝐧)
+
+    tdf = subset_𝐧(dropmissing(@subset(df, :enc .== enc; view)), 𝐧)
+    compute_Alfvenicity_params!(tdf)
+    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=8, legend=(; alpha=1)) * mapping(color=:id, marker=:id)
+
+    fig = Figure(size=(800, 300))
+    axis = (; yscale=log10, xscale=log10)
+    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))
+
+    ga = fig[1, 1]
+    gb = fig[1, 2]
+    gc = fig[1, 3]
+
+    spec1 = plt * mapping(𝒎.l, 𝒎.j)
+    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
+    spec3 = plt * mapping(𝒎.v_Alfven, 𝒎.v_ion)
+
+    grid1 = draw!(ga, spec1; axis)
+    draw!(gb, spec2; axis)
+    draw!(gc, spec3; axis=v_axis)
+
+    slopes = (1.0, 0.7, 0.4, 0.1)
+    foreach(slopes) do s
+        lines!(1 .. 1000, (*)$s, linestyle=:dash, label="$s")
+    end
+    axislegend("slope", position=:lt)
+
+    pretty_legend!(fig, grid1)
+    add_labels!([ga, gb, gc])
+    easy_save("$fname-$enc-$𝐧"; formats, force=true)
+    display(fig)
+end
+```
+
+![](../figures/properties_xy_comp-enc-7-mva.pdf)
+![](../figures/properties_xy_comp-enc-7-cross.pdf)
+![](../figures/properties_xy_comp-enc-8-mva.pdf)
+![](../figures/properties_xy_comp-enc-8-cross.pdf)
+![](../figures/properties_xy_comp-enc-9-mva.pdf)
+![](../figures/properties_xy_comp-enc-9-cross.pdf)
+
+```{julia}
+fname = "properties_hist-enc"
+
+for enc in 7:9, 𝐧 in [:mva, :cross]
+    view = true
+    𝒎 = var_mapping(; 𝐧)
+    datalimits_f = x -> quantile(x, [0.02, 0.98])
+    # drop missing and NaN
+    tdf = @chain df begin
+        @subset(:enc .== enc, .!isnan.(:L_n_cross_norm); view)
+        dropmissing
+        subset_𝐧(𝐧)
+        compute_Alfvenicity_params!
+        @subset(.!isnan.(:v_l_ratio))
+    end
+
+    spec = data(tdf) *
+           mapping([𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log, 𝒎.v_l_ratio, 𝒎.bn], layout=AoG.dims(1) => renamer(ones(String, 6))) *
+           mapping(color=:id) *
+           AoG.density(datalimits=datalimits_f)
+
+    draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
+    easy_save("$fname-$enc-$𝐧"; formats, force=true)
+end
+```
+
+```{julia}
+for enc in 7:9
+    tdf = filter_low_mva_quality(dropmissing(@subset(df, :enc .== enc; view=true), view=true))
+    data_layer = data(tdf)
+    legend = (; markersize=10, alpha=1)
+    plt = data_layer * visual(Scatter; markersize=4, alpha=0.618, legend) * mapping(color=:id, marker=:id)
+
+    fig = Figure(size=(800, 400))
+    axis = (; yscale=identity, xscale=identity)
+
+    ga = fig[1, 1]
+    gb = fig[1, 2]
+
+    spec1 = plt * mapping(𝒎.bn, 𝒎.ω)
+    spec2 = plt * mapping(𝒎.bn, 𝒎.ω_in)
+
+    grid1 = draw!(ga, spec1; axis)
+    draw!(gb, spec2; axis)
+
+    pretty_legend!(fig, grid1)
+    add_labels!([ga, gb])
+    display(fig)
+end
+```

### 2025-06-12 notebooks/10_results.qmd
update

@@
 
-### Thickness and current density comparison
-
-```{julia}
-begin
-    fname = "thickness_current_xy_comp"
-    data_layer = data(df)
-    plt = data_layer * visual(Scatter)
-
-    fig = Figure(size=(1000, 500))
-    axis = (; yscale=log10, xscale=log10)
-
-    ga = fig[1, 1]
-    gb = fig[1, 2]
-
-    spec1 = plt * mapping(m.l, m.j)
-    spec2 = plt * mapping(m.l_norm, m.j_norm)
-
-    draw!(ga, spec1; axis)
-    draw!(gb, spec2; axis)
-
-    pretty_legend!(fig, grid1)
-    add_labels!([ga, gb])
-    easy_save(fname)
-end
-```
-
 ```{julia}

### 2025-06-12 notes.qmd
update

@@
 ![](images/paste-12.png)
+
+# Research notes
+
+## In-situ synergistic observations (Alignment)
+
+**Similar** type of solar wind or **Same** solar solar wind
+
+How to define alignment?
+
+- Trajectory & Orbits (theory): ballistic approximation of Parker spiral
+
+- Plasma properties (observation):
+
+  - Invariants: plasma composition, ionization states, mass flux $n u r^2$
+
+  - Correlation: magnetic field / plasma velocity
+
+- Simulation: Trace plasma parcels evolution
+
+## Anisotropy
+
+### Estimated Anisotropy
+
+@shenComparingPlasmaAnisotropy2024
+
+The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
+
+Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
+
+![](figures/enc7/anisotropy_theory.png)
+
+### Comparison between Estimated and Observed Anisotropy
+
+![](figures/enc7/anisotropy_comparison_2d.png)

### 2025-06-12 src/PSPAnisotropy.jl

@@ -1,16 +1,24 @@
 module PSPAnisotropy
 using Speasy
-include("PSP.jl")
-include("Wind.jl")
-include("THEMIS.jl")
-include("dataset.jl")
-
 using CSV
 using Dates
 using DataFrames, DataFramesMeta
 using CategoricalArrays
 using DrWatson
-export get_timerange
+using Discontinuity: ids_finder
+using SPEDAS
+
+export get_timerange, workload
+
+include("meta.jl")
+include("mva.jl")
+include("calc.jl")
+
+
+include("PSP.jl")
+include("Wind.jl")
+include("THEMIS.jl")
+include("dataset.jl")
 
 const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat = "yyyy-mm-dd HH:MM")
 
@@ -27,27 +35,27 @@ end
 
 
 function workload()
-    psp_config = Dict(:id => "PSP", :B => PSP.B, :V => PSP.V, :n => PSP.n_spi, :tau => 30)
-    wind_config = Dict(:id => "Wind", :B => Wind.B_GSE, :V => Wind.V_GSE_K0, :n => Wind.n_p_K0, :tau => 30)
-    thm_config = Dict(:id => "THEMIS", :B => THEMIS.B_FGL_GSE, :n => THEMIS.n_ion, :V => THEMIS.V_GSE, :tau => 30)
+    psp_config = @strdict(id = "PSP", B = PSP.B, V = PSP.V, n = PSP.n_spi, tau = 30)
+    wind_config = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, tau = 30)
+    thm_config = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, tau = 30)
     configs = [psp_config, wind_config, thm_config]
 
     df = mapreduce(vcat, 7:9) do enc
         tpsp, tearth = get_timerange(enc)
         mapreduce(vcat, configs) do c
-            id = c[:id]
+            id = c["id"]
             timerange = id == "PSP" ? tpsp : tearth
-            c[:t0] = Date(timerange[1])
-            c[:t1] = Date(timerange[2])
+            c["t0"] = Date(timerange[1])
+            c["t1"] = Date(timerange[2])
             res, = produce_or_load(c, datadir(); tag = false) do c
[…]

### 2025-06-12 src/THEMIS.jl

@@ -21,7 +21,7 @@ n_ion = SpeasyProduct("THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale =
 n_elec = SpeasyProduct("THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
 n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
 
-V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ")
+V_GSE = tsort ∘ SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
 
 pTemp = SpeasyProduct("THB_L2_ESA/thb_peif_avgtempQ"; labels = ["Proton"])
 eTemp = tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; labels = ["Electron"])

### 2025-06-12 src/Wind.jl

@@ -1,5 +1,4 @@
 module Wind
-using Base: Fix2
 using Speasy: SpeasyProduct, getdimarray
 using DimensionalData: Y
 using PartialFunctions
@@ -39,18 +38,20 @@ V_RTN_nonlin = Product(
 )
 
 B_GSE = SpeasyProduct("WI_H2_MFI/BGSE")
-V_GSE_p = SpeasyProduct("WI_PM_3DP/P_VELS")
+B_GSE_1MIN = SpeasyProduct("WI_H0_MFI/BGSE")
+V_GSE_3DP = SpeasyProduct("WI_PM_3DP/P_VELS")
 V_GSE_K0 = SpeasyProduct("WI_K0_SWE/V_GSE")  # Note: it contains some weird spikes
 
 
-n_p_K0 = replace_outliers! ∘ SpeasyProduct("WI_K0_SWE/Np")
-n_p = SpeasyProduct("WI_PM_3DP/P_DENS"; labels = WI_PM_3DP_labels)
+n_p_K0 = replace_outliers! ∘ SpeasyProduct("WI_K0_SWE/Np"; labels = ["Proton"]) # Time resolution is 110 seconds
+n_p_3DP = SpeasyProduct("WI_PM_3DP/P_DENS"; labels = WI_PM_3DP_labels)
 # SpeasyProduct("WI_PLSP_3DP/MOM.P.DENSITY"), # Quite similar to "WI_PM_3DP/P_DENS"
 n_e = SpeasyProduct("WI_ELM2_3DP/DENSITY"; labels = WI_ELM2_3DP_labels)
 # SpeasyProduct("WI_H5_SWE/N_elec") # No data available
 n_p_nonlin = SpeasyProduct("WI_H1_SWE/Proton_Np_nonlin", labels = ["Proton (non-linear fitting)"])
 
-n = DataSet("Density", [n_p_K0, n_p, n_p_nonlin, n_e])
+n = DataSet("Density", [n_p_K0, n_p_3DP, n_p_nonlin, n_e])
+n_p_e = DataSet("Density", (n_p_K0, n_e))
 
 # SpeasyProduct("WI_H0_SWE/Te"), Definition range <DateTimeRange: 1994-12-29T00:00:02+00:00 -> 2001-05-31T23:59:57+00:00>
 

### 2025-06-12 src/calc.jl

@@ -1,10 +1,13 @@
 using PlasmaFormulary
 using Discontinuity: anisotropy
 using DataFramesMeta
+using StatsBase: mean
+using Unitful
+export Alfven_velocity_ts
 
-function alfven_velocity_ts(B, n)
+function Alfven_velocity_ts(B, n)
     n_mean = mean(parent(n))
-    return alfven_velocity.(B, n_mean)
+    return Alfven_velocity.(B, n_mean)
 end
 
 function anisotropy_ts(B, n, T3; kw...)

### 2025-06-12 src/meta.jl

@@ -1,17 +1,28 @@
-begin
-    B_ylabel = ulabel("B", "nT")
-    B_labels = ["Bx", "By", "Bz", "Magnitude"]
-    B_RTN_labels = [L"B_R", L"B_T", L"B_N", L"|B\;|"]
-    B_LMN_labels = [L"B_L", L"B_M", L"B_N"]
-    B_XYZ_labels = [L"B_x", L"B_y", L"B_z", L"|B\;|"]
-    n_ylabel = ulabel("n", "cm^-3")
+# https://github.com/PainterQubits/Unitful.jl/issues/649
 
-    V_ylabel = ulabel("V", "km/s")
-    V_labels = ["Vx", "Vy", "Vz", "Magnitude"]
-    V_RTN_labels = [L"V_R", L"V_T", L"V_N", L"|V\;|"]
-    V_LMN_labels = [L"V_L", L"V_M", L"V_N"]
-    V_XYZ_labels = [L"V_x", L"V_y", L"V_z", L"|V\;|"]
-    ΔV_ylabel = "ΔV (km/s)"
+baremodule YLabel
+    B = "B (nT)"
+    V = "V (km s⁻¹)"
+    n = "n (cm⁻³)"
+    ΔV = "ΔV (km/s)"
+    T = "T (eV)"
+    J = "J (nA m⁻²)"
+end
 
-    T_ylabel = ulabel("T", "eV")
+
+module Labels
+    using LaTeXStrings
+
+    B = ["Bx", "By", "Bz", "Magnitude"]
+    B_RTN = [L"B_R", L"B_T", L"B_N", L"B"]
+    B_LMN = [L"B_L", L"B_M", L"B_N", L"B"]
+    B_XYZ = [L"B_X", L"B_Y", L"B_Z", L"B"]
+
+    V = ["Vx", "Vy", "Vz", "Magnitude"]
+    V_RTN = [L"V_R", L"V_T", L"V_N", L"|V\;|"]
+    V_LMN = [L"V_L", L"V_M", L"V_N"]
+    Va_LMN = [L"V_{A, L}", L"V_{A, M}", L"V_{A, N}"]
+    V_XYZ = [L"V_X", L"V_Y", L"V_Z", L"|V\;|"]
+
+    J = [L"J_X", L"J_Y", L"J_∥", L"J_⊥"]
 end

### 2025-06-12 src/mva.jl

@@ -1,0 +1,29 @@
+using PartialFunctions
+
+mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
+
+
+function make_mva_product(event, V, B=V; kwargs...)
+    tb_min, tb_max = t_us_ds(event)
+    return Product((V, B), mva_transform$(; tb_min, tb_max); kwargs...)
+end
+
+function make_mva_products(event, B, V, n=nothing, T3=nothing)
+    B_mva = make_mva_product(event, B, B; labels=B_mva_labels, ylabel=𝒀.B)
+    V_mva = make_mva_product(event, V, B; labels=V_mva_labels, ylabel=𝒀.V)
+    J = Product((V_mva, B_mva), j_transform)
+    result = [tnorm_combine ∘ B, V, tnorm_combine ∘ B_mva, set(tsubtract ∘ V_mva; ylabel=𝒀.ΔV), J]
+    isnothing(n) || push!(result, set(
+        tsubtract ∘ Product((B_mva, n), alfven_velocity_ts);
+        ylabel=𝒀.ΔV, labels=["Va_L", "Va_M", "Va_N"]
+    ))
+    isnothing(T3) || begin
+        Λ = Product((B_mva, n, T3), anisotropy_ts; ylabel="Λ")
+        Va_Λ = set(
+            tsubtract ∘ Product((B_mva, n, T3), alfven_velocity_ani_ts);
+            ylabel=𝒀.ΔV, labels=["Va*_L", "Va*_M", "Va*_N"]
+        )
+        push!(result, Λ, Va_Λ)
+    end
+    return result
+end

### 2025-06-12 src/plot.jl

@@ -4,106 +4,71 @@ using Statistics
 include("anisotry.jl")
 
 # %%
-legend_kwargs = (position=:top, titleposition=:left)
+legend_kwargs = (position = :top, titleposition = :left)
 
 begin
     ds_mapping = :dataset => sorter(ds_order)
-    enc_m = :enc => x -> "Enc $x" 
+    enc_m = :enc => x -> "Enc $x"
 end
 
-log_axis = (yscale=log10, xscale=log10)
+log_axis = (yscale = log10, xscale = log10)
 
-function draw!(grid; axis=NamedTuple(), palettes=NamedTuple())
-    plt -> draw!(grid, plt; axis=axis, palettes=palettes)
+function draw!(grid; axis = NamedTuple(), palettes = NamedTuple())
+    return plt -> draw!(grid, plt; axis = axis, palettes = palettes)
 end
 
 function plot_vl_ratio(
-    df;
-    datalimits=x -> quantile(x, [0.01, 0.99]),
-    legend=legend_kwargs,
-    fname="vl_ratio",
-    mapping_args=(v_l_ratio_map,),
-    mapping_kwargs=(; color=ds_mapping)
-)
-    plt = data(df) * mapping(mapping_args...; mapping_kwargs...) * density(datalimits=datalimits)
-    draw(plt, legend=legend)
-    easy_save(fname; dir="$fig_dir/$enc")
+        df;
+        datalimits = x -> quantile(x, [0.01, 0.99]),
+        legend = legend_kwargs,
+        fname = "vl_ratio",
+        mapping_args = (v_l_ratio_map,),
+        mapping_kwargs = (; color = ds_mapping)
+    )
+    plt = data(df) * mapping(mapping_args...; mapping_kwargs...) * density(datalimits = datalimits)
+    draw(plt, legend = legend)
+    return easy_save(fname; dir = "$fig_dir/$enc")
 end
 
 function plot_dvl(
-    df;
-    legend=legend_kwargs,
-    fname="dvl",
-    mapping_args=(v_Alfven_map, v_ion_map),
-    mapping_kwargs=(; color=ds_mapping)
-)
+        df;
+        legend = legend_kwargs,
+        fname = "dvl",
+        mapping_args = (v_Alfven_map, v_ion_map),
+        mapping_kwargs = (; color = ds_mapping)
+    )
[…]

### 2025-06-13 notebooks/00_index.qmd
fig: update

@@
 using Discontinuity
+using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
 using SPEDAS
@@
 df, configs = workload()
+compute_params!(df)
+compute_Alfvenicity_params!(df)
 
@@
 ```{julia}
-function plot_candidate(f, event, config, toffset=Second(0); kwargs...)
+function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs...)
     tmin, tmax = event.t_us_ds
@@
     V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)
+
+    result = [tnorm_combine(B_mva), tsubtract(V_mva), tsubtract(Va)]
+
+    if add_J
         J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")
-
-    result = [tnorm_combine(B_mva), tsubtract(V_mva), n, tsubtract(Va), J]
+        push!(result, J)
+    end
 
@@
 f = Figure(; size=(1200, 800))
-res_psp = plot_candidate(f[1, 1], psp_df[18, :], psp_config, Second(10))
+psp_event = filter_low_mva_quality(psp_df)[4, :]
+res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
+@info "v_l_ratio" psp_event.v_l_ratio
 # res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
@@
 ## Overview
+
+<!-- TODO: add Alfvénicity over time -->
 
@@
 using AlgebraOfGraphics
-using Discontinuity: compute_params!, filter_low_mva_quality, compute_Alfvenicity_params!
+using Discontinuity: compute_params!, compute_Alfvenicity_params!
 using Beforerr

### 2025-06-16 notebooks/000_data.qmd
update

@@
 ## Data
-
-- [PSP/FIELDS Level 2 and higher data](https://fields.ssl.berkeley.edu/data/), [SPDF - Coordinated Data Analysis Web (CDAWeb)](https://cdaweb.gsfc.nasa.gov/cgi-bin/eval2.cgi?dataset=PSP_FLD_L2_MAG_RTN&index=sp_phys)
-
-Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
 
@@
 
+### Parker Solar Probe
+
+- [PSP/FIELDS Level 2 and higher data](https://fields.ssl.berkeley.edu/data/), [SPDF - Coordinated Data Analysis Web (CDAWeb)](https://cdaweb.gsfc.nasa.gov/cgi-bin/eval2.cgi?dataset=PSP_FLD_L2_MAG_RTN&index=sp_phys)
+
+The parameters are:
+
+- 'psp_fld_l2_mag_RTN_4_Sa_per_Cyc' (B in RTN, 0.25s resolution)
+- 'psp_swp_spi_sf00_L3_DENS' (Ion density, regular resolution)
+- 'psp_swp_spi_af00_L3_DENS' (Ion density, burst resolution)
+- 'psp_swp_spi_sf00_L3_VEL_RTN_SUN' (velocity in RTN in Sun's frame, regular resolution)
+- 'psp_swp_spi_af00_L3_VEL_RTN_SUN' (velocity in RTN in Sun's frame, burst resolution)
+- 'psp_swp_spi_sf00_L3_VEL_RTN' (velocity in RTN in spacecraft frame, regular resolution, you need this to calculate current sheet thickness)
+- 'psp_swp_spi_af00_L3_VEL_RTN' (velocity in RTN in spacecraft frame, burst resolution, you need this to calculate current sheet thickness)
+- 'Tp_spani_b' (Ion parallel and perpendicular ion temperature, regular resolution. Blue (first element in array): parallel, Red: perp)
+- 'Tp_spanib_b' (Ion parallel and perpendicular ion temperature, burst resolution. Blue (first element in array): parallel, Red: perp)
+
 ### THEMIS
+
+Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
 
@@
 WI_PM_3DP	Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP
+
+### SOLO
+
+"cda/SOLO_L2_MAG-RTN-NORMAL-1-MINUTE/B_RTN",
+"cda/SOLO_L2_SWA-PAS-GRND-MOM/N",
+"cda/SOLO_L2_SWA-PAS-GRND-MOM/V_RTN",
+"cda/SOLO_L2_SWA-PAS-GRND-MOM/T",
+
+### STEREO
+
+"cda/STA_L2_PLA_1DMAX_1MIN/proton_number_density",
+"cda/STA_L2_PLA_1DMAX_1MIN/proton_bulk_speed",
+"cda/STA_L2_PLA_1DMAX_1MIN/proton_n_s_flow_angle_inst",
+"cda/STA_L2_PLA_1DMAX_1MIN/proton_e_w_flow_angle_inst",
+"cda/STA_L2_PLA_1DMAX_1MIN/proton_Vr_RTN",

### 2025-06-16 notebooks/00_index.qmd
update

@@
 thm_config["B"] = unitify("nT") ∘ thm_config["B"]
+```
+
+```{julia}
+using DimensionalData
+Tp = PSP.read_proton_temperature(7:8)
+Te = PSP.read_electron_temperature()
+
+tselect(A, t) = A[Ti(Near(t))]
+function tselect(A, t, δt)
+    tmp = @views A[Ti((t - δt) .. (t + δt))]
+    length(tmp) == 0 ? missing : tmp[Ti(Near(t))]
+end
+
+deunit(x::Quantity, u) = NoUnits(x / u)
+deunit(x, u) = x
+
+function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt=Minute(1))
+    @rtransform! df begin
+        :Tp_para = deunit(tselect(Tp_para, :time, dt), u"eV")
+        :Tp_perp = deunit(tselect(Tp_perp, :time, dt), u"eV")
+        :Te_para = deunit(tselect(Te_para, :time, dt), u"eV")
+        :Te_perp = deunit(tselect(Te_perp, :time, dt), u"eV")
+    end
+end
+
+add_temp_anisotropy!(df, Tp, Te, args...) =
+    add_temp_anisotropy!(df, Tp.para, Tp.perp, Te.para, Te.perp, args...)
+
+add_temp_anisotropy!(psp_df, Tp, Te)
+compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
 ```
@@
 using SPEDAS.SpaceDataModel: set, extend, @set
-include("../src/psp_temp.jl")
-include("../src/meta.jl")
 
@@
 ```{julia}
-# along time get the temperature from anisotropic temperature
-function tTemp(x; dims=Ti)
-    return mean.(eachslice(x; dims))
-end
-
 mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
-make_mva_transform(tb_min, tb_max) = mva_transform$(; tb_min, tb_max)
-
-j_transform((V, B), tmin, tmax) = current_density(B(tmin, tmax), V(tmin, tmax))
 ```
@@
 psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
-psp_n = set(PSP.n_spi; ylabel=𝒀.n, yscale=identity)
+psp_n = PSP.n_spi
 
@@
 wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
+wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)
 
-tvars_wind = [wind_B, set(Wind.n_p_K0; ylabel=𝒀.n), wind_V]
+tvars_wind = [wind_B, wind_n, wind_V]
 tvars_wind_all = [
@@
 ]
-```
-
-```{julia}
-using CairoMakie
-CairoMakie.activate!()
 ```
@@
 
+Alfvén ratio over time
+
 ```{julia}
-update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(0, 0, 0, 15))
+using StatsBase
+using DimensionalData
+using NaNStatistics
+
+function get_vl_ratio_ts(df)
+    vl_ratio_ts1 = DimArray(df.v_l_ratio, Ti(df.time))
+    vl_ratio_ts2 = DimArray(df.v_l_ratio_Λ, Ti(df.time))
+    gfunc = x -> floor(x, Hour(4))
+    vl_ratio_ts = hcat(
+        nanmedian.(disallowmissing.(groupby(vl_ratio_ts1, Ti => gfunc))),
+        nanmedian.(disallowmissing.(filter.(!ismissing, groupby(vl_ratio_ts2, Ti => gfunc))))
+    )
+    set_meta!(vl_ratio_ts; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"])
+    return vl_ratio_ts
+end
+```
+
+```{julia}
+update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))
+
+# for enc in 7:9
+plot_vl_ratio = true
+
+function modify_faxs_base!(faxs)
+    B_ax = faxs.axes[1]
+    B_ax.ylabel[] = 𝒀.B
+    n_ax = faxs.axes[2]
+    n_ax.yscale[] = identity
+    n_ax.ylabel[] = 𝒀.n
+    V_ax = faxs.axes[3]
+    V_ax.ylabel[] = 𝒀.V
+end
+
+function modify_faxs_vl!(faxs)
+    ylims!(faxs.axes[end-1], 0.09, 0.85)
+    faxs.axes[4].ylabel[] = "T (eV)"
+    β_ax = faxs.axes[6]
+    β_ax.yscale[] = log10
+    β_ax.ylabel[] = "β"
+    ylims!(β_ax, 8e-2, 4e1)
+end
 
@@
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
-
-    _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
 
@@
 
-    f = Figure(; size=(800, 450))
-    plots = tplot(f[1, 1], tvars_psp[1:3], tmin_psp, tmax_psp; legend)
+    f = Figure(; size=(800, 600))
+
+    tvars_psp = (psp_B, psp_n, psp_V)
+    tvars_wind = (wind_B, wind_n, wind_V)
+
+    fname = "overview-$enc"
+
+    if plot_vl_ratio
+        fname = "overview-vl-$enc"
+
+        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
+        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
+        n = PSP.n_spi(tmin_psp, tmax_psp)
+        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false)
+
+        B_mag = tnorm(B)
+        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)
+
+        T = rebuild(T; metadata=(; labels=[L"T_p"]))
+
+        psp_v_l_ratio_ts = get_vl_ratio_ts(psp_df)
+        tvars_psp = (tnorm_combine(B), n, V, [T, Tp, Te], psp_v_l_ratio_ts, β)
+
+        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind)
+        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind)
+        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
+        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+
+        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
+        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
+        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind) |> tsort; metadata=(; labels=[L"T_p"]))
+        B_mag = tnorm(B)
+        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)
+
+        wind_v_l_ratio_ts = get_vl_ratio_ts(wind_df)
+        tvars_wind = (tvars_wind..., [T, Wind.Temp_ani[1:2]...], wind_v_l_ratio_ts, β)
+    end
+
+    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
+    modify_faxs_base!(faxs)
+    plot_vl_ratio && modify_faxs_vl!(faxs)
     add_labels!(f[1, 1]; labels, open="(a.", padding)
-    tplot(f[1, 2], tvars_wind[1:3], tmin_wind, tmax_wind; legend)
+    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
+    modify_faxs_base!(faxs)
+    plot_vl_ratio && modify_faxs_vl!(faxs)
     add_labels!(f[1, 2]; labels, open="(b.", padding)
+    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
     # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
     # add_labels!(f[1, 3]; labels, open="(c.")
-    easy_save("overview-$enc")
+    easy_save(fname; formats=(:pdf,))
+    display(f)
 

### 2025-06-16 src/PSP.jl

@@ -2,10 +2,21 @@ module PSP
 using Unitful
 using SPEDAS
 using Speasy: SpeasyProduct
-using SPEDAS: DataSet
+using SPEDAS: DataSet, meta
+
+using CSV
+using DrWatson
+using Unitful
+using NetCDF
+using YAXArrays
+using DimensionalData
+using LaTeXStrings
+
+import ..PSPAnisotropy.Labels as 𝑳
+
 
 B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc")
-B_1MIN = SpeasyProduct("PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min")
+B_1MIN = SpeasyProduct("PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"; labels=𝑳.B_RTN)
 
 n_spi = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels = ["SPI Proton"])
 n_spc = Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels = ["SPC Proton"])
@@ -19,6 +30,70 @@ V = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN")
 pTemp = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels = ["SPI Proton"])
 eTemp = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels = ["SQTN Electron core"])
 T = DataSet("Temperature", [pTemp, eTemp])
+
+
+"""
+    read_electron_temperature(filename; data_dir=datadir())
+
+Read electron temperature data from CSV file into a DimensionalData structure.
+Returns a DimArray with dimensions of time and temperature components (parallel and perpendicular).s
+"""
+function read_electron_temperature(filename; data_dir = datadir("electron_fit_Halekas"))
+    # Construct full path to the file
+    filepath = joinpath(data_dir, filename)
+
+    # Read CSV file
+    df = CSV.File(filepath; dateformat = "yyyy-mm-dd/HH:MM:SS.sss", drop = [3])
+
[…]

### 2025-06-16 src/Wind.jl

@@ -1,9 +1,10 @@
 module Wind
 using Speasy: SpeasyProduct, getdimarray
-using DimensionalData: Y
+using DimensionalData: Y, DimStack, rebuild
 using PartialFunctions
 using Unitful
 using SPEDAS: DataSet, ulabel, Product, replace_outliers!
+using LaTeXStrings
 
 unitify(u) = (*) $ u
 # WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM]
@@ -55,20 +56,38 @@ n_p_e = DataSet("Density", (n_p_K0, n_e))
 
 # SpeasyProduct("WI_H0_SWE/Te"), Definition range <DateTimeRange: 1994-12-29T00:00:02+00:00 -> 2001-05-31T23:59:57+00:00>
 
+T_p_PLSP = SpeasyProduct("WI_PLSP_3DP/MOM.P.AVGTEMP"; labels = [L"T_p"])
+
 T = DataSet(
     "Temperature",
     [
         SpeasyProduct("WI_PM_3DP/P_TEMP"; labels = ["Proton (WI_PM_3DP)"]),
-        SpeasyProduct("WI_PLSP_3DP/MOM.P.AVGTEMP"; labels = ["Proton (WI_PLSP_3DP)"]),
+        T_p_PLSP,
         SpeasyProduct("WI_ELM2_3DP/AVGTEMP"; labels = WI_ELM2_3DP_labels),
     ]
 )
 
-pTemp_ani = unitify(u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.P.MAGT3")
-alphaTemp_ani = unitify(u"eV") ∘ SpeasyProduct("WI_PLSP_3DP/MOM.A.MAGT3"; labels = ["Alpha_MagT3_Perp1", "Alpha_MagT3_Perp2", "Alpha_MagT3_Para"]) # original labels ["BX_GSE", "BY_GSE", "BZ_GSE"] is not right
+pTemp_T3 = SpeasyProduct("WI_PLSP_3DP/MOM.P.MAGT3"; )
+alphaTemp_T3 = SpeasyProduct("WI_PLSP_3DP/MOM.A.MAGT3"; labels = ["Alpha_MagT3_Perp1", "Alpha_MagT3_Perp2", "Alpha_MagT3_Para"]) # original labels ["BX_GSE", "BY_GSE", "BZ_GSE"] is not right
[…]

### 2025-06-20 notebooks/00_index.qmd
fig: update

@@
 Te = PSP.read_electron_temperature()
-
-tselect(A, t) = A[Ti(Near(t))]
-function tselect(A, t, δt)
-    tmp = @views A[Ti((t - δt) .. (t + δt))]
-    length(tmp) == 0 ? missing : tmp[Ti(Near(t))]
-end
 
@@
 f = Figure(; size=(1200, 800))
-psp_event = filter_low_mva_quality(psp_df)[4, :]
+psp_event = filter_low_mva_quality(psp_df)[5, :]
 res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
@@
 )
-
 ```
@@
 
-tvars_psp = [psp_B, psp_n, psp_V]
-tvars_psp_all = [
-    psp_B,
-    set(PSP.n; ylabel=𝒀.n),
-    psp_V,
-    set(PSP.T; ylabel=𝒀.T)
-]
-```
-
-```{julia}
 wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
@@
 wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)
-
-tvars_wind = [wind_B, wind_n, wind_V]
-tvars_wind_all = [
-    wind_B,
-    set(Wind.n; ylabel=𝒀.n),
-    wind_V,
-    set(Wind.T; ylabel=𝒀.T)
-]
-```
-
-```{julia}
-using Intervals: Interval
-
-function get_themis_tmask(t0, t1)
-    thx_v_gse = THEMIS.V_GSE(t0, t1)
-    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
-    dt = Minute(10)
-    its = union([Interval(t - dt, t + dt) for t in _times])
-    return tmask!(its)
-end
 ```
@@
 
-function get_vl_ratio_ts(df)
-    vl_ratio_ts1 = DimArray(df.v_l_ratio, Ti(df.time))
-    vl_ratio_ts2 = DimArray(df.v_l_ratio_Λ, Ti(df.time))
-    gfunc = x -> floor(x, Hour(4))
-    vl_ratio_ts = hcat(
-        nanmedian.(disallowmissing.(groupby(vl_ratio_ts1, Ti => gfunc))),
-        nanmedian.(disallowmissing.(filter.(!ismissing, groupby(vl_ratio_ts2, Ti => gfunc))))
-    )
-    set_meta!(vl_ratio_ts; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"])
-    return vl_ratio_ts
+function get_vl_ratio_ts(df, col, dt::TimePeriod=Hour(4))
+    data = getproperty(df, col)
+    vl_ratio_ts = DimArray(data, Ti(df.time))
+    gfunc = x -> floor(x, dt)
+    gdf = groupby(vl_ratio_ts, Ti => gfunc)
+    vl_ratio_ts_m = nanmedian.(disallowmissing.(filter.(!ismissing, gdf)))
+    n = rebuild(length.(gdf); metadata=(; ylabel="N (#)", plottype=:Stairs))
+    set_meta!(vl_ratio_ts_m; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"], plottype=:Stairs)
+    return vl_ratio_ts_m, n
+end
+
+function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
+    v_l_ratio_ts, n1 = _get_vl_ratio_ts(df, :v_l_ratio, dt)
+    v_l_ratio_Λ_ts, n2 = _get_vl_ratio_ts(df, :v_l_ratio_Λ, dt)
+    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
+    return vl_ratio_ts, n1
 end
@@
 ```{julia}
+using SPEDAS: tvec
+using CairoMakie
+CairoMakie.activate!()
+
 update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))
@@
     B_ax.ylabel[] = 𝒀.B
+    V_ax = faxs.axes[3]
+    V_ax.ylabel[] = 𝒀.V
     n_ax = faxs.axes[2]
@@
     n_ax.ylabel[] = 𝒀.n
-    V_ax = faxs.axes[3]
-    V_ax.ylabel[] = 𝒀.V
 end
@@
 function modify_faxs_vl!(faxs)
-    ylims!(faxs.axes[end-1], 0.09, 0.85)
-    faxs.axes[4].ylabel[] = "T (eV)"
-    β_ax = faxs.axes[6]
+    T_ax = faxs.axes[end-3]
+    T_ax.ylabel[] = "T (eV)"
+
+    R_ax = faxs.axes[end-1]
+    ylims!(R_ax, 0.09, 0.85)
+
+    β_ax = faxs.axes[end]
     β_ax.yscale[] = log10
@@
         V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
-        n = PSP.n_spi(tmin_psp, tmax_psp)
-        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false)
+        n = PSP.n_spi(tmin_psp, tmax_psp) |> tvec
+        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false) |> tvec
 
@@
 
-        psp_v_l_ratio_ts = get_vl_ratio_ts(psp_df)
-        tvars_psp = (tnorm_combine(B), n, V, [T, Tp, Te], psp_v_l_ratio_ts, β)
+        psp_v_l_ratio_ts, psp_count = get_vl_ratio_ts(psp_df)
+        tvars_psp = (B_mag, n, tnorm(V), tmean.((T, Tp, Te), Minute(8)), psp_count, psp_v_l_ratio_ts, β)
 
-        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind)
-        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind)
+        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind; add_unit=false)
+        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind; add_unit=false)
         add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
@@
         B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
+        V = wind_V(tmin_wind, tmax_wind)
         n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
-        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind) |> tsort; metadata=(; labels=[L"T_p"]))
+        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind; add_unit=false) |> tsort; metadata=(; labels=[L"T_p"]))
         B_mag = tnorm(B)
@@
 
-        wind_v_l_ratio_ts = get_vl_ratio_ts(wind_df)
-        tvars_wind = (tvars_wind..., [T, Wind.Temp_ani[1:2]...], wind_v_l_ratio_ts, β)
+        wind_v_l_ratio_ts, wind_count = get_vl_ratio_ts(wind_df)
+        tvars_wind = (B_mag, n, tnorm(tsort(V)), [T, Wind_Tp2, Wind_Te2], wind_count, wind_v_l_ratio_ts, β)
     end
@@
     add_labels!(f[1, 2]; labels, open="(b.", padding)
+
     # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
@@
     # add_labels!(f[1, 3]; labels, open="(c.")
+
     easy_save(fname; formats=(:pdf,))
@@
 700 km/s, ~2.5 days
+
+## The effect of tau
+
+```{julia}
+psp_df_taus = map([8, 16, 32]) do tau
+    psp_config["tau"] = tau
+    df = PSPAnisotropy.produce(psp_config)
+    @transform! df :tau = tau
+    compute_Alfvenicity_params!(df)
+end
+
+wind_df_taus = map([8, 16, 32]) do tau
+    wind_config["tau"] = tau
+    df = PSPAnisotropy.produce(wind_config)
+    @transform! df :tau = tau
+    compute_Alfvenicity_params!(df)
+end
+```
+
+```{julia}
+f = Figure()
+axR1 = Axis(f[1, 1])
+axn1 = Axis(f[2, 1])
+for (i, df) in enumerate(psp_df_taus)
+    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
+    lines!(axR1, v_l_ratio_ts)
+    lines!(axn1, n)
+end
+
+axR2 = Axis(f[1, 2])
+axn2 = Axis(f[2, 2])
+for (i, df) in enumerate(wind_df_taus)
+    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
+    lines!(axR2, v_l_ratio_ts)
+    lines!(axn2, n)
+end
+
+ylims!.((axR1, axR2), 0.2, 0.8)
+ylims!.((axn1, axn2), 11, 121)
+easy_save("vl_ratio-tau")
+f
+```
 

### 2025-06-20 src/PSPAnisotropy.jl

@@ -33,6 +33,9 @@ function get_timerange(enc)
     return (t0_psp, t1_psp), (t0_earth, t1_earth)
 end
 
+function produce(c)
+    ids_finder(c["B"], c["t0"], c["t1"], Second(c["tau"]), c["V"], c["n"])
+end
 
 function workload()
     psp_config = @strdict(id = "PSP", B = PSP.B, V = PSP.V, n = PSP.n_spi, tau = 30)

### 2025-06-20 src/THEMIS.jl

@@ -8,7 +8,11 @@ module THEMIS
 using StatsBase
 using DimensionalData
 using Speasy: SpeasyProduct, getdimarray
-using SPEDAS: DataSet, tsort
+using SPEDAS: DataSet, tsort, times, tmask!
+using Dates
+using Unitful
+
+using Intervals: Interval
 
 function tTemp(x; dims = Ti)
     return mean.(eachslice(x; dims))
@@ -31,5 +35,14 @@ pTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peim_t3_magQ"; yscale = identity)
 eTemp_ani = SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; yscale = identity)
 
 T_ani = DataSet("Temperature anisotropy", [pTemp_ani, eTemp_ani]; yscale = identity)
+
+
+function get_themis_tmask(t0, t1)
+    thx_v_gse = THEMIS.V_GSE(t0, t1)
+    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
+    dt = Minute(10)
+    its = union([Interval(t - dt, t + dt) for t in _times])
+    return tmask!(its)
+end
 
 end

### 2025-06-29 notebooks/01_flux.qmd
feat: flux

```{julia}
using Unitful
using UnitfulAstro
using Unitful.DefaultSymbols
using Speasy

r = get_data("cda/PSP_COHO1HR_MERGED_MAG_PLASMA/radialDistance", "2022-12-11", "2022-12-12")
```

```{julia}
# Constants
using Unitful: k, G, μ0, mp
using UnitfulAstro: Msun
const mp = 1.6726e-27u"kg"

"""
Calculate fluxes given parameters at a spacecraft
"""
function compute_fluxes(n, V, T, B, r, Ω=1)
    Br = B[1]
    Vr = V[1]
    A = Ω * r^2 # flux tube cross-sectional area

    # Mass flux
    F_mass = n * mp * Vr * A

    # Magnetic flux (radial)
    F_mag = Br * A

    # Energy flux components
    E_kin = 0.5 * ρ * V^2 * Vr
    E_th = (5 / 2) * u * n * k * T
    E_grav = -ρ * u * (G * Msun / r)
    E_mag = (B^2 / (2μ₀)) * (u / ρ)

    # Total energy flux
    E_total = (E_kin + E_th + E_grav + E_mag) * A

    return (mass_flux=F_mass, mag_flux=F_mag,
        E_kin=E_kin * A, E_th=E_th * A, E_grav=E_grav * A, E_mag=E_mag * A,
        E_total=E_total)
end
```

### 2025-07-25 notebooks/000_data.qmd
feat: add alpha

@@
 using PSPAnisotropy: Wind, PSP, THEMIS
-using SPEDAS: tplot
+using SPEDAS: tplot, set_meta
 using GLMakie
@@
 - 'Tp_spanib_b' (Ion parallel and perpendicular ion temperature, burst resolution. Blue (first element in array): parallel, Red: perp)
+
+the helium-to-proton abundance ratio ($A_{He} = N_α/N_p × 100\%$, where $N_α$ and $N_p$ are the number densities of helium particles and protons, respectively)
+
+```{julia}
+tmin = DateTime("2021-01-15")
+n_p = PSP.n_spi(tmin, tmin + Day(1))
+n_α = PSP.n_alpha(tmin, tmin + Day(1))
+
+A_He = set_meta(n_α ./ n_p .* 100; ylabel="A_He", units="%", scale=identity)
+
+let tmin = DateTime("2021-01-15")
+    tvars = (
+        PSP.n_spi,
+        PSP.n_alpha,
+        A_He
+    )
+    tplot(tvars, tmin, tmin + Day(1))
+end
+```
 

### 2025-07-25 src/PSP.jl

@@ -19,6 +19,7 @@ B = SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_C
 B_1MIN = SpeasyProduct("PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"; labels=𝑳.B_RTN)
 
 n_spi = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels = ["SPI Proton"])
+n_alpha = SpeasyProduct("PSP_SWP_SPI_SF0A_L3_MOM/DENS"; labels = ["SPI Alpha"])
 n_spc = Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels = ["SPC Proton"])
 n_sqtn = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels = ["SQTN Electron"])
 n_rfs = SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels = ["RFS Electron"])

### 2025-07-27 notebooks/000_data.qmd
update

@@
     tvars = (
-        [Wind.V_GSE_3DP, Wind.V_GSE_K0],
-        [Wind.n_p_K0, Wind.n_p_3DP, Wind.n_p_nonlin],
+    # [Wind.V_GSE_3DP, Wind.V_GSE_K0],
+        [
+        unitify("1/cm^3") ∘ SpeasyProduct("WI_K0_SWE/Np"; labels=["Proton"]),
+        SpeasyProduct("WI_PM_3DP/P_DENS"; labels=["Proton (3DP, PESA Low)"]),
+        SpeasyProduct("WI_H1_SWE/Proton_Np_nonlin", labels=["Proton (non-linear fitting)"]),
+        SpeasyProduct("WI_H1_SWE/Alpha_Na_nonlin", labels=["Alpha (non-linear fitting)"]),
+        Wind.n_e
+    ],
     )

### 2025-07-27 notebooks/00_index.qmd
feat: add alpha
update

@@
 using SPEDAS: set_meta, set_meta!
+using Beforerr: _theme_legend, easy_save
 using PartialFunctions
@@
 using DimensionalData
-Tp = PSP.read_proton_temperature(7:8)
-Te = PSP.read_electron_temperature()
 
@@
 
+function compute_PSP_anisotropy_params!(psp_df)
+    Tp = PSP.read_proton_temperature(7:8)
+    Te = PSP.read_electron_temperature()
     add_temp_anisotropy!(psp_df, Tp, Te)
     compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+end
+
+function compute_Wind_anisotropy_params!(df, tmin, tmax)
+    Wind_Tp2 = Wind.pTemp_T2(tmin, tmax; add_unit=false)
+    Wind_Te2 = Wind.eTemp_T2(tmin, tmax; add_unit=false)
+    add_temp_anisotropy!(df, Wind_Tp2, Wind_Te2, Minute(2))
+    compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+end
 ```
@@
 ```{julia}
-function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs...)
-    tmin, tmax = event.t_us_ds
-    t0 = tmin - toffset
-    t1 = tmax + toffset
-
-    B_product = config["B"]
-    V_product = config["V"]
-
-    B = B_product(t0, t1) |> set_meta!(; ylabel="B", labels=𝑳.B_RTN)
-    V = V_product(t0, t1) |> set_meta!(; ylabel="V", labels=𝑳.V_RTN)
-    n = config["n"](t0, t1)
-
-    B_mva = mva(B, B) |> set_meta(; labels=𝑳.B_LMN)
-    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
-    V_mva = mva(V, B) |> set_meta(; labels=𝑳.V_LMN)
-
-    result = [tnorm_combine(B_mva), tsubtract(V_mva), tsubtract(Va)]
-
-    if add_J
-        J = hcat(current_density(B_mva, V_mva)...) |> set_meta(; labels=𝑳.J, ylabel="J")
-        push!(result, J)
-    end
-
-    f = tplot(f, result; kwargs...)
-    tlines!(f, [tmin, tmax])
-    result
-end
-
 f = Figure(; size=(1200, 800))
 psp_event = filter_low_mva_quality(psp_df)[5, :]
-res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
-@info "v_l_ratio" psp_event.v_l_ratio
+fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
+@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
 # res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
@@
 using Unitful
-using Beforerr: _theme_legend, easy_save
 using SPEDAS.SpaceDataModel: set, extend, @set
 
-import Discontinuity.AlgebraOfGraphics as AoG
+import AlgebraOfGraphics as AoG
 
@@
 function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
-    v_l_ratio_ts, n1 = _get_vl_ratio_ts(df, :v_l_ratio, dt)
-    v_l_ratio_Λ_ts, n2 = _get_vl_ratio_ts(df, :v_l_ratio_Λ, dt)
+    v_l_ratio_ts, n1 = get_vl_ratio_ts(df, :V_l_ratio, dt)
+    v_l_ratio_Λ_ts, n2 = get_vl_ratio_ts(df, :V_l_ratio_Λ, dt)
     vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
     return vl_ratio_ts, n1
+end
+```
+
+```{julia}
+function modify_faxs_base!(faxs)
+    B_ax = faxs.axes[1]
+    B_ax.ylabel[] = 𝒀.B
+    V_ax = faxs.axes[3]
+    V_ax.ylabel[] = 𝒀.V
+    n_ax = faxs.axes[2]
+    n_ax.yscale[] = identity
+    n_ax.ylabel[] = 𝒀.n
+end
+
+function modify_faxs_vl!(faxs)
+    i = 1
+    T_ax = faxs.axes[end-3-i]
+    T_ax.ylabel[] = "T (eV)"
+
+    R_ax = faxs.axes[end-2-i]
+    ylims!(R_ax, 0.09, 0.85)
+
+    β_ax = faxs.axes[end-i]
+    β_ax.yscale[] = log10
+    ylims!(β_ax, 8e-2, 4e1)
+
+    A_He_ax = faxs.axes[end]
+    A_He_ax.yscale[] = identity
+    A_He_ax.ylabel[] = L"A_{\text{He}} (%)"
+    ylims!(A_He_ax, 0, 8)
+end
+
+f = Figure(; size=(800, 600))
+# faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...)
+modify_faxs_vl!(faxs)
+f
+```
+
+```{julia}
+let tmin = tmin_psp, tmax = tmax_psp
+    f = Figure(; size=(800, 600))
+
+    faxs = plot_Wind(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(wind_df)...)
+    f
 end
@@
 
-function modify_faxs_base!(faxs)
-    B_ax = faxs.axes[1]
-    B_ax.ylabel[] = 𝒀.B
-    V_ax = faxs.axes[3]
-    V_ax.ylabel[] = 𝒀.V
-    n_ax = faxs.axes[2]
-    n_ax.yscale[] = identity
-    n_ax.ylabel[] = 𝒀.n
-end
-
-function modify_faxs_vl!(faxs)
-    T_ax = faxs.axes[end-3]
-    T_ax.ylabel[] = "T (eV)"
-
-    R_ax = faxs.axes[end-1]
-    ylims!(R_ax, 0.09, 0.85)
-
-    β_ax = faxs.axes[end]
-    β_ax.yscale[] = log10
-    β_ax.ylabel[] = "β"
-    ylims!(β_ax, 8e-2, 4e1)
-end
-
-for enc in 7:9
+for enc in 7:7
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
@@
 
-    tvars_psp = (psp_B, psp_n, psp_V)
-    tvars_wind = (wind_B, wind_n, wind_V)
-
     fname = "overview-$enc"
@@
         fname = "overview-vl-$enc"
+        faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
+        modify_faxs_base!(faxs)
+        plot_vl_ratio && modify_faxs_vl!(faxs)
 
-        B = set_meta!(PSP.B_1MIN(tmin_psp, tmax_psp); labels=𝑳.B_RTN)
-        V = set_meta!(psp_V(tmin_psp, tmax_psp); labels=𝑳.V_RTN)
-        n = PSP.n_spi(tmin_psp, tmax_psp) |> tvec
-        T = PSP.pTemp(tmin_psp, tmax_psp; add_unit=false) |> tvec
-
-        B_mag = tnorm(B)
-        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)
-
-        T = rebuild(T; metadata=(; labels=[L"T_p"]))
-
-        psp_v_l_ratio_ts, psp_count = get_vl_ratio_ts(psp_df)
-        tvars_psp = (B_mag, n, tnorm(V), tmean.((T, Tp, Te), Minute(8)), psp_count, psp_v_l_ratio_ts, β)
-
-        Wind_Tp2 = Wind.pTemp_T2(tmin_wind, tmax_wind; add_unit=false)
-        Wind_Te2 = Wind.eTemp_T2(tmin_wind, tmax_wind; add_unit=false)
-        add_temp_anisotropy!(wind_df, Wind_Tp2, Wind_Te2, Minute(2))
-        compute_anisotropy_params!(wind_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
-
-        B = Wind.B_GSE_1MIN(tmin_wind, tmax_wind)
-        V = wind_V(tmin_wind, tmax_wind)
-        n = Wind.n_p_K0(tmin_wind, tmax_wind) |> tsort
-        T = rebuild(Wind.T_p_PLSP(tmin_wind, tmax_wind; add_unit=false) |> tsort; metadata=(; labels=[L"T_p"]))
-        B_mag = tnorm(B)
-        β = Discontinuity.plasma_beta.(tsync(T, n, B_mag)...)
-
-        wind_v_l_ratio_ts, wind_count = get_vl_ratio_ts(wind_df)
-        tvars_wind = (B_mag, n, tnorm(tsort(V)), [T, Wind_Tp2, Wind_Te2], wind_count, wind_v_l_ratio_ts, β)
+        compute_Wind_anisotropy_params!(wind_df, tmin_wind, tmax_wind)
+        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind, get_vl_ratio_ts(wind_df)...; legend)
+        modify_faxs_base!(faxs)
+        plot_vl_ratio && modify_faxs_vl!(faxs)
     end
 
-    faxs = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
-    modify_faxs_base!(faxs)
-    plot_vl_ratio && modify_faxs_vl!(faxs)
     add_labels!(f[1, 1]; labels, open="(a.", padding)
-    faxs = tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
-    modify_faxs_base!(faxs)
-    plot_vl_ratio && modify_faxs_vl!(faxs)
     add_labels!(f[1, 2]; labels, open="(b.", padding)
-
-    # _tmask! = get_themis_tmask(tmin_wind, tmax_wind)
-    # tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
-    # add_labels!(f[1, 3]; labels, open="(c.")
 
@@
 
+    # tvars_psp = (psp_B, psp_n, psp_V)
+    # tvars_wind = (wind_B, wind_n, wind_V)
     # f = Figure(; size=(1200, 600))
@@
 ```{julia}
-psp_df_taus = map([8, 16, 32]) do tau
+psp_df_taus = map([2, 4, 8, 16, 32]) do tau
     psp_config["tau"] = tau
@@
 
-wind_df_taus = map([8, 16, 32]) do tau
+wind_df_taus = map([2, 4, 8, 16, 32]) do tau
     wind_config["tau"] = tau
@@
 
+Check examples
+
+```{julia}
+f = Figure(; size=(1200, 800))
+# let df = psp_df_taus[1], config = psp_config
+begin
+    df = @subset(wind_df_taus[1], :index_std .> 4)
+    config = wind_config
+    event = filter_low_mva_quality(df)[5, :]
+    fax, res_psp = plot_candidate(f[1, 1], event, config, Second(10))
+    plot_var_info!(fax, event)
+    @info "v_l_ratio" event.V_l_ratio event.V_l_ratio_max
+end
+f
+```
+
 ```{julia}
@@
 axn1 = Axis(f[2, 1])
+filter_func = df -> @subset(df, :index_std .> 2)
+
 for (i, df) in enumerate(psp_df_taus)
-    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
+    v_l_ratio_ts, n = get_vl_ratio_ts(filter_func(df), :V_l_ratio_max)
     lines!(axR1, v_l_ratio_ts)
@@
 for (i, df) in enumerate(wind_df_taus)
-    v_l_ratio_ts, n = get_vl_ratio_ts(df, :v_l_ratio)
+    v_l_ratio_ts, n = get_vl_ratio_ts(filter_func(df), :V_l_ratio_max)
     lines!(axR2, v_l_ratio_ts)
@@
 
-ylims!.((axR1, axR2), 0.2, 0.8)
-ylims!.((axn1, axn2), 11, 121)
+ylims!.((axR1, axR2), 0, 0.8)
+# ylims!.((axn1, axn2), 0, 121)
 easy_save("vl_ratio-tau")

### 2025-07-27 notebooks/11_spectra.qmd
update

<a href="https://docs.juliadsp.org/stable/periodograms/">Periodograms - periodogram estimation · DSP.jl</a>

<a href="https://github.com/lootie/Multitaper.jl">lootie/Multitaper.jl: A Julia package for frequency domain analysis of time series</a>

[pmtm - Multitaper power spectral density estimate - MATLAB](https://www.mathworks.com/help/signal/ref/pmtm.html)

Example spectra of Ev, Eb, and Er, calculated over a 2 day interval (2007 July 6 00:00:00–2007 July 8 00:00:00) using the kinetic normalization, are shown in Figure 1.

```{julia}
using Dates
using PSPAnisotropy: Wind
tmin = DateTime("2007-07-06")
tmax = DateTime("2007-07-08")
B = Wind.B(tmin, tmax; add_unit=false)
```

```{julia}
using DSP

pxx = periodogram(B[:, 1])

```

```{julia}
# first, add the package if you haven't already:
# import Pkg; Pkg.add("Multitaper")

using Statistics
using LinearAlgebra
using Multitaper

const μ0 = 4π * 1e-7     # vacuum permeability [H/m]

"""
    compute_fluctuations(v, B, rho)

Given
  • v    : N×3 array of velocity (m/s)
  • B    : N×3 array of magnetic field (T)
  • rho  : length‐N vector of mass density (kg/m³)

Returns
  • δv   : N×3 array of velocity fluctuations
  • δb   : N×3 array of magnetic‐field fluctuations in Alfvén units (m/s)
"""
function compute_fluctuations(v::AbstractMatrix, B::AbstractMatrix, rho::AbstractVector)
    @assert size(v) == size(B) "v and B must be the same size"
    @assert size(v, 1) == length(rho) "rho length must match rows of v,B"

    # subtract mean
    v̄ = mean(v, dims=1)
    δv = v .- v̄

    # magnetic field in velocity units: b = B / sqrt(μ0 ρ)
    b = B ./ sqrt.(μ0 .* rho)[:, None]
    b̄ = mean(b, dims=1)
    δb = b .- b̄

    return δv, δb
end

"""
    trace_psd_mt(x, dt; NW=4)

Compute the trace (sum over 3 components) PSD of a 3‐component fluctuation array x via multitaper.

Arguments:
  • x    : N×3 array of fluctuation time series
  • dt   : sampling interval [s]
Keyword:
  • NW   : time–bandwidth product (default 4)

Returns
  • f    : vector of frequency bins [Hz]
  • P    : vector of trace power spectrum P(f) = ∑ᵢ S_ii(f)
"""
function trace_psd_mt(x::AbstractMatrix, dt::Real; NW::Real=4)
    N, nc = size(x)
    @assert nc == 3 "x must be N×3"

    fs = 1 / dt
    # how many tapers? standard choice K = 2NW − 1
    K = Int(2 * NW - 1)

    # accumulate over components
    f = nothing
    P_trace = nothing

    for comp in 1:3
        # multitaper spectrum for this component
        spec = mt_spectrum(x[:, comp];
            NW=NW,
            K=K,
            fs=fs,
            adaptive=false)  # or true for adaptive weighting

        f === nothing && (f = spec.f)
        P_trace === nothing && (P_trace = zeros(length(f)))
        P_trace .+= spec.amp .^ 2           # mt_spectrum.amp is the amplitude spectrum
    end

    return f, P_trace
end

"""
    compute_sigma(v, B, rho, dt; NW=4)

Compute normalized cross‐helicity σ_C(f) and normalized residual energy σ_R(f)
as functions of frequency.

Returns
  • f      : frequency vector [Hz]
  • σ_C    : normalized cross‐helicity at each f
  • σ_R    : normalized residual energy at each f
"""
function compute_sigma(v::AbstractMatrix, B::AbstractMatrix, rho::AbstractVector, dt::Real; NW::Real=4)
    # fluctuations
    δv, δb = compute_fluctuations(v, B, rho)

    # trace PSDs
    f, E_v = trace_psd_mt(δv, dt; NW=NW)
    _, E_b = trace_psd_mt(δb, dt; NW=NW)

    # build z± and get their trace PSD
    zplus = δv .+ δb
    zminus = δv .- δb
    _, E_p = trace_psd_mt(zplus, dt; NW=NW)
    _, E_m = trace_psd_mt(zminus, dt; NW=NW)

    # normalized cross‐helicity σ_C = (E₊ – E₋)/(E₊ + E₋)
    σ_C = (E_p .- E_m) ./ (E_p .+ E_m)

    # normalized residual energy   σ_R = (E_v – E_b)/(E_v + E_b)
    σ_R = (E_v .- E_b) ./ (E_v .+ E_b)

    return f, σ_C, σ_R
end
```

### 2025-07-27 src/PSPAnisotropy.jl

@@ -20,7 +20,9 @@ include("Wind.jl")
 include("THEMIS.jl")
 include("dataset.jl")
 
-const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat = "yyyy-mm-dd HH:MM")
+include("plot.jl")
+
+const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat="yyyy-mm-dd HH:MM")
 
 function get_timerange(enc)
     Δt_min = Day(2)
@@ -38,10 +40,14 @@ function produce(c)
 end
 
 function workload()
-    psp_config = @strdict(id = "PSP", B = PSP.B, V = PSP.V, n = PSP.n_spi, tau = 30)
-    wind_config = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, tau = 30)
-    thm_config = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, tau = 30)
-    configs = [psp_config, wind_config, thm_config]
+    timeranges = get_timerange.(7:9)
+    psp_timeranges = getindex.(timeranges, 1)
+    earth_timeranges = getindex.(timeranges, 2)
+    configs = (;
+        PSP=@strdict(id = "PSP", B = PSP.B, V = PSP.V, n = PSP.n_spi, tau = 30, timeranges = psp_timeranges),
+        Wind=@strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, tau = 30, timeranges = earth_timeranges),
+        THM=@strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, tau = 30, timeranges = earth_timeranges),
+    )
 
     df = mapreduce(vcat, 7:9) do enc
         tpsp, tearth = get_timerange(enc)
@@ -50,14 +56,14 @@ function workload()
             timerange = id == "PSP" ? tpsp : tearth
             c["t0"] = Date(timerange[1])
             c["t1"] = Date(timerange[2])
-            res, = produce_or_load(c, datadir(); tag = false) do c
+            res, = produce_or_load(c, datadir(); tag=false) do c
                 c["events"] = ids_finder(c["B"], c["t0"], c["t1"], Second(c["tau"]), c["V"], c["n"])
                 c
             end
[…]

### 2025-08-13 notebooks/000_data.qmd
update

--- 2025-07-25 notebooks/000_data.qmd
@@
 using SPEDAS: tplot, set_meta
+using Speasy
 using GLMakie
@@
 
+Different coordinate frames
+
+```{julia}
+tmin = DateTime("2021-01-15")
+tvars = [
+    "PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
+    "PSP_SWP_SPI_SF00_L3_MOM/VEL_SC",
+    "PSP_SWP_SPI_SF00_L3_MOM/VEL_INST",
+    "PSP_SWP_SPI_SF00_L3_MOM/MAGF_SC",
+    "PSP_FLD_L2_MAG_SC_4_SA_PER_CYC/psp_fld_l2_mag_SC_4_Sa_per_Cyc"
+]
+tplot(tvars, tmin, tmin + Hour(1))
+```
+
+"PSP_SWP_SPI_SF00_L3_MOM" ~3.5s resolution
+
 ### THEMIS
@@
 ```{julia}
-let tmin = DateTime("2021-01-15")
+let tmin = DateTime("2021-01-15"), add_unit = false
     tvars = (
-        [Wind.V_GSE_3DP, Wind.V_GSE_K0],
-        [Wind.n_p_K0, Wind.n_p_3DP, Wind.n_p_nonlin],
+        Wind.V_GSE_K0,
+        Wind.V_GSE_3DP,
+        [
+            SpeasyProduct("WI_K0_SWE/Np"; labels=["Proton"]),
+            SpeasyProduct("WI_PM_3DP/P_DENS"; labels=["Proton (3DP, PESA Low)"]),
+            SpeasyProduct("WI_H1_SWE/Proton_Np_nonlin", labels=["Proton (non-linear fitting)"]),
+            SpeasyProduct("WI_H1_SWE/Alpha_Na_nonlin", labels=["Alpha (non-linear fitting)"]),
+            Wind.n_e
+        ],
     )

### 2025-08-13 notebooks/11_spectra.qmd
update

@@
 using Dates
+using DSP
+using PSPAnisotropy
 using PSPAnisotropy: Wind
+using SPEDAS
+using Unitful
+
 tmin = DateTime("2007-07-06")
 tmax = DateTime("2007-07-08")
-B = Wind.B(tmin, tmax; add_unit=false)
+B = Wind.B_GSE(tmin, tmax)
+V = Wind.V_GSE_3DP(tmin, tmax) |> dropna
+n = Wind.n_p_3DP(tmin, tmax) |> dropna
 ```
@@
 ```{julia}
-using DSP
+using PlasmaFormulary
 
-pxx = periodogram(B[:, 1])
+V_B = Alfven_velocity.(tsync(B, n)...)
+
+z_pm = PlasmaFormulary.Elsässer.(tsync(V, B, n)...)
+z_plus, z_minus = getindex.(z_pm, 1), getindex.(z_pm, 2)
+```
+
+```{julia}
+"""
+    trace_pgram(f, x; kwargs...)
+
+Compute the trace (sum over components) power spectral density of a multi-component time series. Returns a `Periodogram` object with trace power spectral density
+"""
+function trace_pgram(f, x; fs=nothing, kwargs...)
+    # Compute periodogram for each component and sum
+    fs = something(fs, samplingrate(x) / 1u"Hz")
+    pgrams = map(eachcol(x)) do col
+        f(col; fs, kwargs...)
+    end
+    trace_power = sum(power, pgrams)
+    # Return periodogram with trace power and same frequency grid
+    return DSP.Periodograms.Periodogram(trace_power, freq(pgrams[1]))
+end
 
@@
 ```{julia}
-# first, add the package if you haven't already:
-# import Pkg; Pkg.add("Multitaper")
+V_B_pxx_mt = trace_pgram(mt_pgram, ustrip(V_B))
 
-using Statistics
-using LinearAlgebra
-using Multitaper
+V_pxx = trace_pgram(periodogram, ustrip(V .|> u"m/s"))
+V_pxx_mt = trace_pgram(mt_pgram, ustrip(V .|> u"m/s"))
+z_plus_pxx_mt = trace_pgram(mt_pgram, ustrip(z_plus))
+z_minus_pxx_mt = trace_pgram(mt_pgram, ustrip(z_minus))
+```
 
-const μ0 = 4π * 1e-7     # vacuum permeability [H/m]
+```{julia}
+using CairoMakie
 
+function plot_pxx_pxx_mt!(ax, pxx, pxx_mt; step=10, linewidth=2, alpha=0.8)
+    # Get frequency and power data
+    freqs_pxx = freq(pxx)
+    powers_pxx = power(pxx)
+    freqs_mt = freq(pxx_mt)
+    powers_mt = power(pxx_mt)
+
+    p1 = lines!(ax, freqs_pxx[2:step:end], powers_pxx[2:step:end]; label="Periodogram", linewidth, alpha)
+    p2 = lines!(ax, freqs_mt[2:step:end], powers_mt[2:step:end]; label="Multitaper", linewidth, alpha)
+    axislegend(ax, position=:lt)
+    return p1, p2
+end
+
+function plot_pxx_pxx_mt(pxx, pxx_mt; kw...)
+    f = Figure(size=(800, 600))
+    ax = Axis(f[1, 1],
+        xlabel="Frequency (Hz)",
+        ylabel="Power Spectral Density",
+        xscale=log10,
+        yscale=log10,
+        title="Comparison of Power Spectral Density Methods"
+    )
+    plot_pxx_pxx_mt!(ax, pxx, pxx_mt; kw...)
+    return f
+end
+
+plot_pxx_pxx_mt(V_pxx, V_pxx_mt)
+```
+
+```{julia}
 """
-    compute_fluctuations(v, B, rho)
+    parker_spiral_direction(r_au; Ω=2.87e-6, V_sw=400e3)
 
-Given
-  • v    : N×3 array of velocity (m/s)
-  • B    : N×3 array of magnetic field (T)
-  • rho  : length‐N vector of mass density (kg/m³)
+Compute the expected Parker spiral magnetic field direction at distance r_au from the Sun.
 
-Returns
-  • δv   : N×3 array of velocity fluctuations
-  • δb   : N×3 array of magnetic‐field fluctuations in Alfvén units (m/s)
+Arguments:
+- `r_au`: distance from Sun in AU
+- `Ω`: solar rotation rate [rad/s] (default: 2.87e-6 rad/s)
+- `V_sw`: solar wind speed [m/s] (default: 400 km/s)
+
+Returns:
+- Unit vector in Parker spiral direction (radial, tangential, normal components)
 """
-function compute_fluctuations(v::AbstractMatrix, B::AbstractMatrix, rho::AbstractVector)
-    @assert size(v) == size(B) "v and B must be the same size"
-    @assert size(v, 1) == length(rho) "rho length must match rows of v,B"
+function parker_spiral_direction(r_au; Ω=2.87e-6, V_sw=400e3)
+    r = r_au * 1.496e11  # convert AU to meters
 
-    # subtract mean
-    v̄ = mean(v, dims=1)
-    δv = v .- v̄
+    # Parker spiral angle
+    φ = atan(Ω * r / V_sw)
 
-    # magnetic field in velocity units: b = B / sqrt(μ0 ρ)
-    b = B ./ sqrt.(μ0 .* rho)[:, None]
-    b̄ = mean(b, dims=1)
-    δb = b .- b̄
-
-    return δv, δb
+    # Unit vector: (radial, tangential, normal)
+    B_parker = [cos(φ), -sin(φ), 0.0]
+    return B_parker / norm(B_parker)
 end
@@
 """
-    trace_psd_mt(x, dt; NW=4)
+    rectify_magnetic_field(B, r_au=1.0)
 
-Compute the trace (sum over 3 components) PSD of a 3‐component fluctuation array x via multitaper.
+Rectify magnetic field direction based on Parker spiral to ensure consistent
+z+ (outward) and z- (inward) Alfvén wave identification.
 
 Arguments:
-  • x    : N×3 array of fluctuation time series
-  • dt   : sampling interval [s]
-Keyword:
-  • NW   : time–bandwidth product (default 4)
+- `B`: N×3 magnetic field array
+- `r_au`: distance from Sun in AU (default: 1.0)
 
-Returns
-  • f    : vector of frequency bins [Hz]
-  • P    : vector of trace power spectrum P(f) = ∑ᵢ S_ii(f)
+Returns:
+- `B_rect`: rectified magnetic field with consistent Parker spiral alignment
 """
-function trace_psd_mt(x::AbstractMatrix, dt::Real; NW::Real=4)
-    N, nc = size(x)
-    @assert nc == 3 "x must be N×3"
+function rectify_magnetic_field(B, r_au=1.0)
+    B_parker = parker_spiral_direction(r_au)
+    B_rect = copy(B)
 
-    fs = 1 / dt
-    # how many tapers? standard choice K = 2NW − 1
-    K = Int(2 * NW - 1)
-
-    # accumulate over components
-    f = nothing
-    P_trace = nothing
-
-    for comp in 1:3
-        # multitaper spectrum for this component
-        spec = mt_spectrum(x[:, comp];
-            NW=NW,
-            K=K,
-            fs=fs,
-            adaptive=false)  # or true for adaptive weighting
-
-        f === nothing && (f = spec.f)
-        P_trace === nothing && (P_trace = zeros(length(f)))
-        P_trace .+= spec.amp .^ 2           # mt_spectrum.amp is the amplitude spectrum
+    for i in 1:size(B, 1)
+        B_vec = B[i, :]
+        # Check if B is aligned with Parker spiral (dot product > 0)
+        if dot(B_vec, B_parker) < 0
+            # Flip B direction if anti-aligned with Parker spiral
+            B_rect[i, :] = -B_vec
+        end
     end
 
-    return f, P_trace
+    return B_rect
 end
+```
 
+```{julia}
+# Plot comparison of Elsasser variable spectra
+f = Figure(size=(1200, 800))
+
+step = 10
+
+ax3 = Axis(f[1, 1],
+    xlabel="Frequency (Hz)",
+    ylabel="Power Spectral Density",
+    xscale=log10,
+    yscale=log10
+)
+
+ax4 = Axis(f[1, 2],
+    xlabel="Frequency (Hz)",
+    ylabel="Power Spectral Density",
+    xscale=log10,
+    yscale=log10
+)
+
+plot_spectras!(ax3, V_B_pxx_mt, V_pxx_mt; labels=["B", "V"], step=step, linewidth=2, alpha=0.8)
+axislegend(ax3, position=:lt)
+xlims!(ax3, (1e-4, 5e-1))
+ylims!(ax3, (1e6, 1e13))
+
+plot_spectras!(ax4, z_plus_pxx_mt, z_minus_pxx_mt; labels=["z+ (Outward)", "z- (Inward)"], step=step, linewidth=2, alpha=0.8)
+axislegend(ax4, position=:lt)
+xlims!(ax4, (1e-4, 5e-1))
+ylims!(ax4, (1e6, 1e13))
+
+f
+```
+
+The spectra of residual energy Er, cross helicity Ec, total energy Et, normalized residual energy σr, normalized cross helicity σc, Alfv ́en ratio rA, and Elsasser ratio rE were then calculated,
+
+$$
+\begin{gathered}
+E_{\mathrm{r}}=E_{\mathrm{v}}-E_{\mathrm{b}}, \\
+E_{\mathrm{c}}=E_{+}-E_{-}, \\
+E_{\mathrm{t}}=E_{\mathrm{v}}+E_{\mathrm{b}}, \\
+\sigma_{\mathrm{r}}=\frac{E_{\mathrm{v}}-E_{\mathrm{b}}}{E_{\mathrm{v}}+E_{\mathrm{b}}}=\frac{r_{\mathrm{A}}-1}{r_{\mathrm{A}}+1}, \\
+\sigma_{\mathrm{c}}=\frac{E_{+}-E_{-}}{E_{+}+E_{-}}=\frac{r_{\mathrm{E}}-1}{r_{\mathrm{E}}+1}, \\
+r_{\mathrm{A}}=\frac{E_{\mathrm{v}}}{E_{\mathrm{b}}}=\frac{1+\sigma_{\mathrm{r}}}{1-\sigma_{\mathrm{r}}}, \\
+r_{\mathrm{E}}=\frac{E_{+}}{E_{-}}=\frac{1+\sigma_{\mathrm{c}}}{1-\sigma_{\mathrm{c}}} .
+\end{gathered}
+$$
+
+```{julia}
 """

### 2025-08-13 src/Wind.jl

@@ -21,7 +21,6 @@ WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 B = SpeasyProduct("WI_H4-RTN_MFI/BRTN")
 B_RTN_1MIN = SpeasyProduct("WI_H3-RTN_MFI/BRTN")
 
-V_RTN = SpeasyProduct("WI_K0_SWE_RTN/V_RTN") # Note: it contains some weird spikes
 
 function combine_getdimarrays(ps, args...)
     das = getdimarray.(ps, args...)
@@ -40,8 +39,9 @@ V_RTN_nonlin = Product(
 
 B_GSE = SpeasyProduct("WI_H2_MFI/BGSE")
 B_GSE_1MIN = SpeasyProduct("WI_H0_MFI/BGSE")
-V_GSE_3DP = SpeasyProduct("WI_PM_3DP/P_VELS")
-V_GSE_K0 = SpeasyProduct("WI_K0_SWE/V_GSE")  # Note: it contains some weird spikes
+V_GSE_3DP = SpeasyProduct("WI_PM_3DP/P_VELS") #about 3.1s/Sample
+V_GSE_K0 = SpeasyProduct("WI_K0_SWE/V_GSE")  # Note: it contains some weird spikes, about 100s/Sample
+V_RTN = SpeasyProduct("WI_K0_SWE_RTN/V_RTN") # Note: it contains some weird spikes
 
 
 n_p_K0 = replace_outliers! ∘ SpeasyProduct("WI_K0_SWE/Np"; labels=["Proton"]) # Time resolution is 110 seconds

### 2025-08-13 src/plot.jl

@@ -2,6 +2,7 @@ import AlgebraOfGraphics: draw!
 import Discontinuity
 using SPEDAS: tvec, set_meta, set_meta!
 using Statistics
+using CairoMakie
 
 include("anisotry.jl")
 
@@ -156,4 +157,15 @@ function plot_dvl(; legend=legend_kwargs)
     axislegend("slope", position=:ct)
 
     return easy_save(fname)
+end
+
+
+using DSP
+export plot_spectras!
+
+function plot_spectras!(ax, specs...; labels = nothing, step=10, kw...)
+    map(enumerate(specs)) do (i, spec)
+        label = get(labels, i, nothing)
+        lines!(ax, freq(spec)[2:step:end], power(spec)[2:step:end]; label=label, kw...)
+    end
 end

### 2025-08-27 notebooks/000_data.qmd
refactor: clean a bit

@@
 using PSPAnisotropy: Wind, PSP, THEMIS
-using SPEDAS: tplot, set_meta
+using SpacePhysicsMakie: tplot
+import SpaceDataModel
+using SpaceDataModel: setmeta, times
+using TimeseriesUtilities
 using Speasy
 using GLMakie
+using DataFrames, DimensionalData
 ```
@@
 tvars = [
-    "PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN",
-    "PSP_SWP_SPI_SF00_L3_MOM/VEL_SC",
-    "PSP_SWP_SPI_SF00_L3_MOM/VEL_INST",
-    "PSP_SWP_SPI_SF00_L3_MOM/MAGF_SC",
-    "PSP_FLD_L2_MAG_SC_4_SA_PER_CYC/psp_fld_l2_mag_SC_4_Sa_per_Cyc"
+    spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN, VEL_SC, VEL_INST, MAGF_SC"...,
+    spz"PSP_FLD_L2_MAG_SC_4_SA_PER_CYC/psp_fld_l2_mag_SC_4_Sa_per_Cyc"
 ]
@@
 "PSP_SWP_SPI_SF00_L3_MOM" ~3.5s resolution
+
+```{julia}
+using Discontinuity
+
+tmin = DateTime("2021-01-15")
+
+# Get results from both methods
+function get_discontinuity_results(tmin, tmax, B, V)
+    @info resolution(B)
+    @info resolution(V)
+    df_pvi = Discontinuity.ids_finder_PVI(B, V; every=Hour(2))
+    df_cvi = Discontinuity.ids_finder_CVI(B, V; every=Hour(2), std_threshold=2)
+    df_variance = Discontinuity.ids_finder(B, V; tau=Second(2))
+    CVI_ts = CVI(B)
+    PVI_ts = PVI(B)
+    return (; df_pvi, df_cvi, df_variance, CVI_ts, PVI_ts)
+end
+
+function get_discontinuity_results(tmin, tmax, B_prod::Product, V_prod::Product)
+    B = DimArray(B_prod(tmin, tmax))
+    V = DimArray(V_prod(tmin, tmax))
+    return get_discontinuity_results(tmin, tmax, B, V)
+end
+
+psp_results = get_discontinuity_results(tmin, tmin + Day(1), PSP.B, PSP.V)
+wind_results = get_discontinuity_results(tmin, tmin + Day(1), Wind.B_GSE, Wind.V_GSE_3DP)
+
+# info the number of events
+@info "Number of events for PSP" nrow.(getproperty.(Ref(psp_results), (:df_pvi, :df_cvi, :df_variance)))
+@info "Number of events for Wind" nrow.(getproperty.(Ref(wind_results), (:df_pvi, :df_cvi, :df_variance)))
+```
+
+Test if the CVI and PVI could capture the discontinuities
+
+```{julia}
+t0 = DateTime("2021-01-15T09:11")
+t1 = DateTime("2021-01-15T09:14")
+B_subset = tview(B, t0, t1)
+V_subset = tview(V, t0, t1)
+df_pvi = Discontinuity.ids_finder_PVI(B_subset, V_subset)
+df_cvi = Discontinuity.ids_finder_CVI(B_subset, V_subset)
+df_variance = Discontinuity.ids_finder(B_subset; tau=Second(30))
+
+CVI_ts = CVI(B_subset)
+PVI_ts = PVI(B_subset)
+
+f = Figure(size=(1400, 1000))
+
+tplot(f[1, 1], [B_subset, [CVI_ts, PVI_ts]])
+
+# Plot 3 candidates from PVI method
+for i in 1:min(3, nrow(df_pvi))
+    plot_candidate(f[2, 1][i, 1], df_pvi[i, :], [PSP.B,])
+end
+for i in 1:min(3, nrow(df_cvi))
+    plot_candidate(f[2, 2][i, 1], df_cvi[i, :], [PSP.B,])
+end
+for i in 1:min(3, nrow(df_variance))
+    plot_candidate(f[2, 3][i, 1], df_variance[i, :], [PSP.B,])
+end
+f
+
+```
+
+```{julia}
+using Random
+
+f = Figure(size=(1400, 1000))
+# Plot 3 candidates from PVI method
+for i in 1:min(3, nrow(df_pvi))
+    plot_candidate(f[i, 1], df_pvi[i, :], [PSP.B, [CVI_ts, PVI_ts]])
+end
+random_indices = randperm(nrow(df_cvi))[1:min(3, nrow(df_cvi))]
+for (plot_idx, i) in enumerate(random_indices)
+    plot_candidate(f[plot_idx, 2], df_cvi[i, :], [PSP.B, [CVI_ts, PVI_ts]])
+end
+random_indices = randperm(nrow(df_variance))[1:min(3, nrow(df_variance))]
+for (plot_idx, i) in enumerate(random_indices)
+    plot_candidate(f[plot_idx, 3], df_variance[i, :], [PSP.B, [CVI_ts, PVI_ts]])
+end
+
+# Add method labels on the left
+Label(f[0, 1], "PVI\nMethod", fontsize=14, tellwidth=false)
+Label(f[0, 2], "CVI\nMethod", fontsize=14, tellwidth=false)
+Label(f[0, 3], "Variance\nMethod", fontsize=14, tellwidth=false)
+resize_to_layout!()
+f
+```
+
+#### The effect of n / τ on the detection
+
+```{julia}
+n_events = 6
+n = 16
+figsize = (n_events * 300, 400)
+f = Figure(; size=figsize)
+df = Discontinuity.ids_finder_CVI(B, V; std_threshold=2, n=n)
+CVI_tmp = CVI(B; n=n)
+# rows = rand(eachrow(df), n_events)
+
+# sort by duration
+df = sort(dropmissing(df), :duration; rev=true)
+rows = eachrow(df)[1:n_events]
+@info rows.duration
+for (i, row) in enumerate(rows)
+    @info getindex.(Ref(row), (:I_max, :index_std, :index_stability, :index_consistency))
+    plot_candidate(f[1, i], row, [PSP.B, CVI_tmp])
+end
+resize_to_layout!()
+f
+```
+
+```{julia}
+n_events = 6
+n = 16
+figsize = (n_events * 300, 400)
+f = Figure(; size=figsize)
+df = Discontinuity.ids_finder(B, V; std_threshold=2, tau=Second(n))
+
+# sort by duration
+df = sort(dropmissing(df), :duration; rev=true)
+rows = eachrow(df)[1:n_events]
+@info rows.duration
+for (i, row) in enumerate(rows)
+    @info getindex.(Ref(row), (:index_std))
+    plot_candidate(f[1, i], row, PSP.B)
+end
+resize_to_layout!()
+f
+```
+
+```{julia}
+f = Figure(size=(1400, 1000))
+
+for (i, n) in enumerate([1, 2, 4, 32])
+    df_cvi = Discontinuity.ids_finder_CVI(B, V; std_threshold=2, n=n)
+    CVI_tmp = CVI(B; n=n)
+    row = rand(eachrow(df_cvi))
+    @info getindex.(Ref(row), (:I_max, :index_std, :index_stability, :index_consistency))
+    plot_candidate(f[1, i], row, [PSP.B, CVI_tmp])
+    f
+end
+f
+```
+
+```{julia}
+f = Figure(size=(1400, 1000))
+
+for (i, n) in enumerate([2, 4, 8, 32])
+    df = Discontinuity.ids_finder(B, V; std_threshold=2, tau=Second(n))
+    row = rand(eachrow(df))
+    @info getindex.(Ref(row), (:index_std, :index_stability))
+    plot_candidate(f[1, i], row, [PSP.B])
+    f
+end
+f
+```
 

### 2025-08-27 notebooks/00_index.qmd
refactor: clean a bit

@@
 using GLMakie
-using SPEDAS: set_meta, set_meta!
+using SPEDAS: setmeta, setmeta!
 using Beforerr: _theme_legend, easy_save
@@
 ```{julia}
-using StatsBase
-using DimensionalData
-using NaNStatistics
-
-function get_vl_ratio_ts(df, col, dt::TimePeriod=Hour(4))
-    data = getproperty(df, col)
-    vl_ratio_ts = DimArray(data, Ti(df.time))
-    gfunc = x -> floor(x, dt)
-    gdf = groupby(vl_ratio_ts, Ti => gfunc)
-    vl_ratio_ts_m = nanmedian.(disallowmissing.(filter.(!ismissing, gdf)))
-    n = rebuild(length.(gdf); metadata=(; ylabel="N (#)", plottype=:Stairs))
-    set_meta!(vl_ratio_ts_m; ylabel=L"R_{VB}", labels=["Isotropy", "Anisotropy"], plottype=:Stairs)
-    return vl_ratio_ts_m, n
-end
-
-function get_vl_ratio_ts(df, dt::TimePeriod=Hour(4))
-    v_l_ratio_ts, n1 = get_vl_ratio_ts(df, :V_l_ratio, dt)
-    v_l_ratio_Λ_ts, n2 = get_vl_ratio_ts(df, :V_l_ratio_Λ, dt)
-    vl_ratio_ts = hcat(v_l_ratio_ts, v_l_ratio_Λ_ts)
-    return vl_ratio_ts, n1
-end
-```
-
-```{julia}
 function modify_faxs_base!(faxs)
@@
 ```{julia}
-function plot_candidate(f, event, ts, toffset=Second(0); kwargs...)
-    tmin, tmax = t_us_ds(event)
-    f = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
-    tlines!(f, [tmin, tmax])
-    f
-end
-
 f = let
@@
     psp_config["tau"] = tau
-    df = PSPAnisotropy.produce(psp_config)
+    df = PSPAnisotropy.produce(psp_config, psp_config["timeranges"][1]...)
     @transform! df :tau = tau
@@
     wind_config["tau"] = tau
-    df = PSPAnisotropy.produce(wind_config)
+    df = PSPAnisotropy.produce(wind_config, wind_config["timeranges"][1]...)
     @transform! df :tau = tau

### 2025-08-27 lib/PSP/src/PSP.jl

@@ -1,0 +1,95 @@
+module PSP
+using Unitful
+using Speasy: SpeasyProduct, @spz_str
+using SPEDAS: DataSet, meta
+
+import CSV
+using YAXArrays, NetCDF
+using DataFrames, DimensionalData
+using LaTeXStrings
+
+const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat="yyyy-mm-dd HH:MM")
+
+B = spz"PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"
+B_1MIN = spz"PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"
+
+n_spi = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels = ["SPI Proton"])
+n_alpha = SpeasyProduct("PSP_SWP_SPI_SF0A_L3_MOM/DENS"; labels = ["SPI Alpha"])
+n_spc = Base.Fix2(*, u"cm^-3") ∘ SpeasyProduct("PSP_SWP_SPC_L3I/np_moment"; labels = ["SPC Proton"])
+n_sqtn = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels = ["SQTN Electron"])
+n_rfs = SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels = ["RFS Electron"])
+n = DataSet("Density", [n_spi, n_spc, n_sqtn])
+n_spi_sqtn = DataSet("Density", [n_spi, n_sqtn])
+
+V = spz"PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"
+
+pTemp = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels = ["SPI Proton"])
+eTemp = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels = ["SQTN Electron core"])
+T = DataSet("Temperature", [pTemp, eTemp])
+
+
+"""
+    read_electron_temperature(filename; data_dir=datadir())
+
+Read electron temperature data from CSV file into a DimensionalData structure.
+Returns a DimArray with dimensions of time and temperature components (parallel and perpendicular).s
+"""
[…]

### 2025-08-27 src/PSPAnisotropy.jl

@@ -1,6 +1,6 @@
 module PSPAnisotropy
 using Speasy
-using CSV
+using SpacePhysicsMakie: tplot, tlines!
 using Dates
 using DataFrames, DataFramesMeta
 using CategoricalArrays
@@ -8,21 +8,18 @@ using DrWatson
 using Discontinuity: ids_finder
 using SPEDAS
 
-export get_timerange, workload
+export get_timerange, workload, get_vl_ratio_ts
 
 include("meta.jl")
 include("mva.jl")
 include("calc.jl")
 
-
-include("PSP.jl")
+using PSP
+using PSP: psp_events
 include("Wind.jl")
 include("THEMIS.jl")
-include("dataset.jl")
 
 include("plot.jl")
-
-const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat="yyyy-mm-dd HH:MM")
 
 function get_timerange(enc)
     Δt_min = Day(2)
@@ -35,8 +32,10 @@ function get_timerange(enc)
     return (t0_psp, t1_psp), (t0_earth, t1_earth)
 end
 
-function produce(c)
-    ids_finder(c["B"], c["t0"], c["t1"], Second(c["tau"]), c["V"], c["n"])
+function produce(c, t0 = nothing, t1 = nothing)
+    t0 = something(t0, c["t0"])
+    t1 = something(t1, c["t1"])
+    ids_finder(c["B"], t0, t1, c["V"], c["n"]; tau = Second(c["tau"]))
 end
 
 function workload()
@@ -57,7 +56,7 @@ function workload()
             c["t0"] = Date(timerange[1])
             c["t1"] = Date(timerange[2])
             res, = produce_or_load(c, datadir(); tag=false) do c
-                c["events"] = ids_finder(c["B"], c["t0"], c["t1"], Second(c["tau"]), c["V"], c["n"])
+                c["events"] = ids_finder(c["B"], c["t0"], c["t1"], c["V"], c["n"]; tau=Second(c["tau"]))
                 c
             end
             @rtransform!(res["events"], :enc = enc, :id = id)

### 2025-08-27 src/THEMIS.jl

@@ -19,13 +19,13 @@ function tTemp(x; dims = Ti)
 end
 
 B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
-B_FGL_GSE = tsort ∘ SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
+B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
 
 n_ion = SpeasyProduct("THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale = identity)
 n_elec = SpeasyProduct("THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
 n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
 
-V_GSE = tsort ∘ SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
+V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
 
 pTemp = SpeasyProduct("THB_L2_ESA/thb_peif_avgtempQ"; labels = ["Proton"])
 eTemp = tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; labels = ["Electron"])

### 2025-08-27 src/dataset.jl

@@ -5,23 +5,6 @@ using Unitful
 using Unitful: μ0
 using Logging
 
-DEFAULT_ENC = 8
-
-function load(enc, name; dataset = missing, dir = "./data")
-    dir = "$dir/enc$enc"
-    filename = filter(contains(Regex("updated_events_$name")), readdir(dir, join = true))[1]
-    @info "Loading $filename"
-    df = Discontinuity.load(filename)
-    @info "Loaded $(size(df, 1)) data points"
-    # add dataset column with the name of the dataset
-    dataset = ismissing(dataset) ? name : dataset
-    df.dataset .= dataset
-    df.dataset = categorical(df.dataset)
-    df.enc .= enc
-    df.enc = categorical(df.enc)
-    return df
-end
-
 load_psp(enc = DEFAULT_ENC) = load(enc, "PSP"; dataset = "Parker Solar Probe")
 
 function load_all(enc)

### 2025-08-27 src/plot.jl

@@ -1,6 +1,6 @@
 import AlgebraOfGraphics: draw!
 import Discontinuity
-using SPEDAS: tvec, set_meta, set_meta!
+using SPEDAS: tvec, setmeta, setmeta!
 using Statistics
 using CairoMakie
 
@@ -30,7 +30,18 @@ end
 
 # ---
 # Example plot
-function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs...)
+function plot_candidate(f, event, ts, toffset=nothing; kwargs...)
+    tmin, tmax = event.t_us, event.t_ds
+    tstart, tstop = event.tstart, event.tstop
+    toffset = something(toffset, tstop - tstart)
+    fax = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
+    tlines!(fax, [tmin, tmax])
+    tlines!(fax, [tstart, tstop])
+    fax
+end
+
+
+function plot_candidate(f, event, config::AbstractDict, toffset=Second(0); add_J=false, kwargs...)
     tmin, tmax = event.t_us, event.t_ds
     t0 = tmin - toffset
     t1 = tmax + toffset
@@ -38,20 +49,20 @@ function plot_candidate(f, event, config, toffset=Second(0); add_J=false, kwargs
     B_product = config["B"]
     V_product = config["V"]
 
-    B = B_product(t0, t1) |> set_meta!(; ylabel="B", labels=𝑳.B_RTN)
-    V = V_product(t0, t1) |> set_meta!(; ylabel="V", labels=𝑳.V_RTN)
+    B = B_product(t0, t1) |> setmeta!(; ylabel="B", labels=𝑳.B_RTN)
+    V = V_product(t0, t1) |> setmeta!(; ylabel="V", labels=𝑳.V_RTN)
     n = config["n"](t0, t1)
 
     B_subset = tview(B, tmin, tmax)
 
-    B_mva = mva(B, B_subset) |> set_meta(; labels=𝑳.B_LMN)
-    Va = Alfven_velocity_ts(B_mva, n) .|> u"km/s" |> set_meta(; labels=𝑳.Va_LMN, ylabel="V")
-    V_mva = mva(V, B_subset) |> set_meta(; labels=𝑳.V_LMN)
[…]

### 2025-08-27 notebooks/000_data.qmd
feat: new visualization with all enc in one panel

@@
 using Dates
+using Speasy
 using PSPAnisotropy
+using PSP
 using PSPAnisotropy: Wind, PSP, THEMIS
@@
 import SpaceDataModel
-using SpaceDataModel: setmeta, times
+using SpaceDataModel: setmeta, times, Product
 using TimeseriesUtilities
-using Speasy
 using GLMakie
@@
 ```{julia}
+tmin = DateTime("2021-01-15")
+tmax = DateTime("2021-01-16")
+B = DimArray(PSP.B(tmin, tmax))
+V = DimArray(PSP.V(tmin, tmax))
+```
+
+```{julia}
 t0 = DateTime("2021-01-15T09:11")
@@
 df_cvi = Discontinuity.ids_finder_CVI(B_subset, V_subset)
-df_variance = Discontinuity.ids_finder(B_subset; tau=Second(30))
+df_variance = Discontinuity.ids_finder(B_subset; tau=Second(16))
 
@@
 f
-
 ```

### 2025-08-27 notebooks/00_index.qmd
feat: new visualization with all enc in one panel

@@
 using Discontinuity
-using Discontinuity: compute_params!, compute_Alfvenicity_params!, filter_low_mva_quality
+using Discontinuity: compute_params!, filter_low_mva_quality
+using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
 using SPEDAS
+using DimensionalData
 using DataFrames, DataFramesMeta
-using GLMakie
+using SpacePhysicsMakie, GLMakie
 using SPEDAS: setmeta, setmeta!
@@
 import PSPAnisotropy.YLabel as 𝒀
+
+𝐧 = :mva
+𝒎 = var_mapping(; 𝐧)
 
@@
 
-Alfvén ratio over time
+### Alfvén ratio over time
 
@@
 using Beforerr: add_labels!
-using CairoMakie
+# using CairoMakie
 using StatsBase
-CairoMakie.activate!()
+# CairoMakie.activate!()
 
-set_aog_theme!()
+set_AoG_theme!()
 formats = (:pdf,)
@@
 
-df, configs = workload()
-𝐧 = :mva
-𝒎 = var_mapping(; 𝐧)
-
+# df, configs = workload()
 compute_params!(df)
@@
 append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
-
-subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
 
@@
 ```{julia}
-fname = "properties_hist-enc"
-
-for enc in 7:9, 𝐧 in [:mva, :cross]
-    view = true
-    𝒎 = var_mapping(; 𝐧)
-    datalimits_f = x -> quantile(x, [0.02, 0.98])
-    # drop missing and NaN
-    tdf = @chain df begin
-        @subset(:enc .== enc, .!isnan.(:L_n_cross_norm); view)
-        dropmissing
-        subset_𝐧(𝐧)
-        compute_Alfvenicity_params!
-        @subset(.!isnan.(:v_l_ratio))
-    end
-
-    spec = data(tdf) *
-           mapping([𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log, 𝒎.v_l_ratio, 𝒎.bn], layout=AoG.dims(1) => renamer(ones(String, 6))) *
-           mapping(color=:id) *
-           AoG.density(datalimits=datalimits_f)
-
-    draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
-    easy_save("$fname-$enc-$𝐧"; formats, force=true)
-end
-```
-
-```{julia}
 for enc in 7:9

### 2025-08-27 notebooks/01_demo.qmd
feat: new visualization with all enc in one panel

## Producing the dataset for one timerange

```{julia}
Speasy.init_cdaweb()
timeranges = get_timerange(7)
tmin, tmax = timeranges[1]
taus = Second.(2 .^ (1:6))
B_p = DimArray ∘ PSP.B_SC
```

```{julia}
timeranges = get_timerange(7)
tmin, tmax = timeranges[1]
tmax = tmin + Day(1)
tau = taus[6]
df = ids_finder(tmin, tmax, PSP.B_SC; tau)
# df= produce(psp_conf, taus, timeranges[1])
```

<!-- 464.596 ms (72275 allocs: 238.104 MiB, 3.73% gc time, without a warmup) -->

Check failed events

```{julia}
# B = PSP.B_SC(tmin, tmax) |> DimArray

time_interval = (DateTime("2021-01-14T11:41:42.440"), DateTime("2021-01-14T11:41:43.430"))
time_interval = (DateTime("2021-01-15T07:27:39.754"), DateTime("2021-01-15T07:28:22.667"))
time_interval = (DateTime("2021-01-14T09:34:44.300"), DateTime("2021-01-14T09:34:51.994"))
time_interval = (DateTime("2021-01-15T12:37:14.741"), DateTime("2021-01-15T12:37:18.008"))
time_interval = (DateTime("2021-01-15T17:19:52.777"), DateTime("2021-01-15T17:19:58.521"))
B_mva_prod = Product(B_p, mva_transform)
tplot([tnorm_combine ∘ B_p, B_mva_prod], time_interval...)
```

Here we randomly check the events to see if we can find any issues. Looks fine for most events.

TODO: Check Wind examples

```{julia}
using Random

f = Figure(size=(1800, 1000))

rows = rand(eachrow(df), min(5, nrow(df)))
for (plot_idx, i) in enumerate(rows)
    plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
end
f
```

## Check events with duration larger than 30 seconds

```{julia}
let df = dropmissing(psp_df, :duration)
    long_events = df[df.duration.> Second(30), :]
    println("Found $(nrow(long_events)) events with duration > 30 seconds")

    if nrow(long_events) > 0
        println("Long duration events:")
        for row in eachrow(long_events)
            println("Time: $(row.time), Duration: $(row.duration), (Fitting duration: $(row.duration_fit))")
        end
    else
        println("No events found with duration > 30 seconds")
    end

    f = Figure(size=(1800, 1000))
    rows = rand(eachrow(long_events), min(5, nrow(long_events)))
    for (plot_idx, i) in enumerate(rows)
    @info "plotting event" i.time i.duration i.duration_fit
        plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
    end
    f
end
```

We can see that the duration is best defined as the minimum of fitting duration `duration` (which sometimes overestimates the duration when the upstream or downstream over-shoots), or the duration between `t_us` and `t_ds` (which sometimes overestimates the duration when the upstream or downstream is is quite stable).

## Check events with duration shorter than 3 seconds

```{julia}
dt = Second(50)
map((psp_df, wind_df), timeranges) do _df, _tr
    df = dropmissing(_df, :duration)
    short_events = df[df.duration.< dt, :]
    n = nrow(short_events)
    occurence_rate = n / Float64(uconvert(u"d", _tr[2] - _tr[1]))
    println("Found $n events with duration < $dt")
    println("Occurence rate: $occurence_rate")
end

### 2025-08-27 notebooks/02_stats.qmd
feat: new visualization with all enc in one panel

# Current sheet statistics

```{julia}
using StatsBase, Statistics
using PSPAnisotropy
using Discontinuity: compute_params!, filter_low_mva_quality
using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
using DimensionalData
using DataFrames, DataFramesMeta
using GLMakie
using Beforerr: _theme_legend, easy_save
using AlgebraOfGraphics
import AlgebraOfGraphics as AoG

𝐧 = :mva
𝒎 = var_mapping(; 𝐧)

using Unitful
Unitful.preferunits(u"nA", u"km")
unitify(u) = (*)$u
unitify(u::String) = (*)$uparse(u)

taus = Second.(2 .^ (1:6))
df = workload(taus)
Discontinuity.assign_accuracy!(df)
@chain df begin
    compute_Alfvenicity_params!()
    compute_params!()
end
```

## Thickness and current density

```{julia}
subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
fname = "properties_hist-enc"

fs = map([:mva]) do 𝐧
    𝒎 = var_mapping(; 𝐧)

    datalimits = x -> quantile(x, [0.01, 0.99])

    tdf = @chain df begin
        @subset(.!isnan.(:L_n_mva_norm); view=true)
        subset_𝐧(𝐧)
        dropmissing(:L_n_mva_norm)
        # compute_Alfvenicity_params!
    end

    vars = [𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log]
    # , 𝒎.bn
    labels = ["Thickness", "Current density", "Normalized thickness", "Normalized current density"]

    plt = data(tdf) *
          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
          mapping(color=:id, linestyle=:enc) *
          AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))

    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
end
fs[1]
```

## Alfvenicity

```{julia}

fs = map([:mva]) do 𝐧
    𝒎 = var_mapping(; 𝐧)

    datalimits = x -> quantile(x, [0.01, 0.99])

    tdf = @chain df begin
        @subset(.!isnan.(:V_l_ratio); view=true)
        subset_𝐧(𝐧)
        dropmissing(:V_l_ratio)
        # compute_Alfvenicity_params!
    end

    vars = [:Q_sonnerup, 𝒎.v_l_ratio, :V_l_ratio_max]
    # 𝒎.v_l_ratio, 𝒎.bn
    labels = ["Alfvénicity", "Velocity ratio", "Max velocity ratio"]

    plt = data(tdf) *
          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
          mapping(color=:id, linestyle=:enc) *
          AoG.density(; datalimits) * visual(Lines)
    draw(plt, axis=(; yscale=log10))

    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
end
fs[1]

```

## Duration (temporal thickness)

Now we analyze what is the distribution of the duration of the current sheet, and how does it vary with the different tau we use.

Plot duration distributions for different missions and time periods.

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines) * mapping(linestyle=:id)
    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
    plt = data(df) * mapping(:duration, color=:enc) * layer
    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
    # scales(Col=(; legend=false))
    draw(plt, axis=(; yscale=log10))
end
```

Plot duration distributions faceted by different taus:

```{julia}
let df = dropmissing(df, :duration)
    df.duration = ustrip.(df.duration .|> u"s")
    plt = data(df) * mapping(:duration, linestyle=:id, color=:enc) * AoG.density(; datalimits=x -> quantile(x, [0.02, 0.98])) * visual(Lines)
    plt *= mapping(col=:tau)
    draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
end
```

### 2025-08-27 lib/PSP/src/PSP.jl

@@ -1,7 +1,7 @@
 module PSP
 using Unitful
 using Speasy: SpeasyProduct, @spz_str
-using SPEDAS: DataSet, meta
+using SpaceDataModel: DataSet
 
 import CSV
 using YAXArrays, NetCDF
@@ -11,6 +11,7 @@ using LaTeXStrings
 const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat="yyyy-mm-dd HH:MM")
 
 B = spz"PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"
+const B_SC = spz"cda/PSP_FLD_L2_MAG_SC/psp_fld_l2_mag_SC"
 B_1MIN = spz"PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"
 
 n_spi = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/DENS"; labels = ["SPI Proton"])
@@ -21,7 +22,8 @@ n_rfs = SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels = ["RFS Electron"]
 n = DataSet("Density", [n_spi, n_spc, n_sqtn])
 n_spi_sqtn = DataSet("Density", [n_spi, n_sqtn])
 
-V = spz"PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"
+V = spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"
+const V_SC = spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_SC"
 
 pTemp = SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels = ["SPI Proton"])
 eTemp = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels = ["SQTN Electron core"])

### 2025-08-27 notebooks/.vdoc.a763f47c-8901-4bd3-9df6-8349fe894beb.jl

@@ -1,0 +1,49 @@
+#
+#
+#
+#
+timeranges = get_timerange(7)
+tmin, tmax = timeranges[1]
+taus = Second.(2 .^ (1:6))
+#
+#
+#
+timeranges = get_timerange(7)
+tmin, tmax = timeranges[1]
+tmax = tmin + Day(1)
+tau = taus[6]
+df = ids_finder(tmin, tmax, PSP.B_SC; tau)
+# df= produce(psp_conf, taus, timeranges[1])
+```
+#
+#
+#
+#
+#
+    # B = PSP.B_SC(tmin, tmax) |> DimArray
+
+time_interval = (DateTime("2021-01-14T11:41:42.440"), DateTime("2021-01-14T11:41:43.430"))
+time_interval = (DateTime("2021-01-15T07:27:39.754"), DateTime("2021-01-15T07:28:22.667"))
+time_interval = (DateTime("2021-01-14T09:34:44.300"), DateTime("2021-01-14T09:34:51.994"))
+time_interval = (DateTime("2021-01-15T12:37:14.741"), DateTime("2021-01-15T12:37:18.008"))
+time_interval = (DateTime("2021-01-15T17:19:52.777"), DateTime("2021-01-15T17:19:58.521"))
+B_p = DimArray ∘ PSP.B_SC
+B_mva_prod = Product(B_p, mva_transform)
+tplot([tnorm_combine ∘ B_p, B_mva_prod], time_interval...)
+#
+#
+#
+#
+#
+using Random
+
+f = Figure(size=(1800, 1000))
+
+rows = rand(eachrow(df), min(5, nrow(df)))
+for (plot_idx, i) in enumerate(rows)
+    plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
+end
+f
+#
+#
+#

### 2025-08-27 src/PSPAnisotropy.jl

@@ -7,6 +7,8 @@ using CategoricalArrays
 using DrWatson
 using Discontinuity: ids_finder
 using SPEDAS
+using LaTeXStrings
+using TimeseriesUtilities: tsplit
 
 export get_timerange, workload, get_vl_ratio_ts
 
@@ -32,22 +34,64 @@ function get_timerange(enc)
     return (t0_psp, t1_psp), (t0_earth, t1_earth)
 end
 
-function produce(c, t0 = nothing, t1 = nothing)
-    t0 = something(t0, c["t0"])
-    t1 = something(t1, c["t1"])
-    ids_finder(c["B"], t0, t1, c["V"], c["n"]; tau = Second(c["tau"]))
+export produce
+
+# Complete specification of the configuration
+function produce(conf)
+    conf["tau"] = Second(conf["tau"]) / Second(1) # convert to float to save in the file name
+    conf, _ = produce_or_load(conf, datadir(); tag = false) do c
+        @unpack t0, t1, B, V, n, tau = c
+        c["events"] = ids_finder(t0, t1, B, V, n; tau = Second(tau))
+        c
+    end
+    return conf["events"]
 end
 
-function workload()
-    timeranges = get_timerange.(7:9)
-    psp_timeranges = getindex.(timeranges, 1)
-    earth_timeranges = getindex.(timeranges, 2)
-    configs = (;
-        PSP=@strdict(id = "PSP", B = PSP.B, V = PSP.V, n = PSP.n_spi, tau = 30, timeranges = psp_timeranges),
-        Wind=@strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, tau = 30, timeranges = earth_timeranges),
-        THM=@strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, tau = 30, timeranges = earth_timeranges),
-    )
+"""
+# Example
+```julia
+produce(psp_conf, timerange, taus)
+```
+"""
+function produce(conf, timerange, taus; split = Day(1))
+    tranges = tsplit(timerange..., split)
+    return mapreduce(vcat, tranges) do trange
+        new_conf = merge(conf, Dict("t0" => Date(trange[1]), "t1" => Date(trange[2])))
+        df_taus = mapreduce(vcat, taus) do tau
+            new_tau_conf = merge(new_conf, Dict("tau" => tau))
+            df = produce(new_tau_conf)
[…]

### 2025-08-27 src/Wind.jl

@@ -3,7 +3,7 @@ using Speasy: SpeasyProduct, getdimarray, @spz_str
 using DimensionalData: Y, DimStack, rebuild
 using PartialFunctions
 using Unitful
-using SPEDAS: DataSet, ulabel, Product, replace_outliers!
+using SPEDAS: DataSet, Product, replace_outliers!
 using LaTeXStrings
 
 unitify(u) = (*)$u

### 2025-08-27 src/mva.jl

@@ -1,6 +1,13 @@
 using PartialFunctions
 
+export mva_transform
+
 mva_transform((V, B), tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(V(tmin, tmax), B(tb_min, tb_max))
+mva_transform(B::AbstractArray{<:Number}, tmin, tmax; tb_min=tmin, tb_max=tmax) = mva(tview(B, tmin, tmax), tview(B, tb_min, tb_max))
+function mva_transform(Bp::Product, tmin, tmax; tb_min=tmin, tb_max=tmax)
+    B = Bp(tmin, tmax)
+    return mva(B, tview(B, tb_min, tb_max))
+end
 
 
 function make_mva_product(event, V, B=V; kwargs...)

### 2025-08-27 src/plot.jl

@@ -3,6 +3,7 @@ import Discontinuity
 using SPEDAS: tvec, setmeta, setmeta!
 using Statistics
 using CairoMakie
+using TimeseriesUtilities: times
 
 include("anisotry.jl")
 
@@ -30,11 +31,37 @@ end
 
 # ---
 # Example plot
-function plot_candidate(f, event, ts, toffset=nothing; kwargs...)
+function plot_candidate(f, event, ts::AbstractArray, toffset=nothing; kwargs...)
     tmin, tmax = event.t_us, event.t_ds
     tstart, tstop = event.tstart, event.tstop
     toffset = something(toffset, tstop - tstart)
     fax = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
+    tlines!(fax, [tmin, tmax])
+    tlines!(fax, [tstart, tstop])
+    fax
+end
+
+get_data(B::AbstractArray, tmin, tmax) = tview(B, tmin, tmax)
+get_data(B::Product, tmin, tmax) = B(tmin, tmax)
+
+function plot_candidate(f, event, B::Union{AbstractArray, Product}, toffset=nothing; add_B_mva=false, add_fit=false, kwargs...)
+    tmin, tmax = event.t_us, event.t_ds
+    tstart, tstop = event.tstart, event.tstop
+    toffset = something(toffset, tstop - tstart)
+    B_subset = get_data(B, tmin - toffset, tmax + toffset)
+    ts = times(B_subset)
+    tvars2plot = Any[tnorm_combine(B_subset)]
+    if add_B_mva
+        B_mva = mva(B_subset, tview(B_subset, tmin, tmax))
+        push!(tvars2plot, B_mva)
+    end
+    if add_fit
+        model = event.model
+        Bl_model = DimArray(model.(ts), Ti(ts))
+        push!(tvars2plot, Bl_model)
+    end
+
+    fax = tplot(f, tvars2plot; kwargs...)
     tlines!(fax, [tmin, tmax])
     tlines!(fax, [tstart, tstop])
     fax

### 2025-09-03 index.qmd
feat: add alpha
feat: add cross_helicity and residual energy

@@
 @lotekarKineticscaleCurrentSheets2022
+@perroneCoherentEventsIon2020
 
@@
 @hudsonDiscontinuitiesAnisotropicPlasma1970
+
+“Knetter [2005] extended this work to intervals in 2002 and 2003 which also included fast wind intervals.
+He obtained similar results to above and amassed a final total collection of 366 discontinuities.
+All of the discontinuities had normal field components consistent with zero.
+He concluded that the discontinuities are best explained as TDs regardless of the amount of dB/B.” ([Vasquez et al., 2007, p.
+2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))
 

### 2025-09-03 notebooks/00_index.qmd
feat: add cross_helicity and residual energy

@@
 
-update_theme!(;
-    figure_padding=1,
-    fonts=(; regular=AoG.firasans("Regular"), bold=AoG.firasans("Medium")),
-    Legend=(; framevisible=false, padding=(0, 0, 0, -15)),
-    Axis=(; xlabelfont=:bold, ylabelfont=:bold),
-)
+set_Z_theme!()
 ```
@@
 
-foreach([:log10, :log2, :log]) do f
-    @eval import Base: $f
-    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
-end
-
 # df, configs = workload()

### 2025-09-03 notebooks/02_stats.qmd
feat: add cross_helicity and residual energy

@@
 ```{julia}
+using Dates
 using StatsBase, Statistics
 using PSPAnisotropy
-using Discontinuity: compute_params!, filter_low_mva_quality
+import Discontinuity as DC
+using Discontinuity: var_mapping, compute_params!, filter_low_mva_quality
 using Discontinuity: compute_Alfvenicity_params!, Alfven_velocity
@@
 using DataFrames, DataFramesMeta
-using GLMakie
+using CairoMakie
 using Beforerr: _theme_legend, easy_save
@@
 import AlgebraOfGraphics as AoG
+using Unitful
+Unitful.preferunits(u"nA", u"km")
 
+# https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
+foreach([:log10, :log2, :log]) do f
+    @eval import Base: $f
+    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
+end
+set_Z_theme!()
+formats = (:pdf,)
+```
+
+```{julia}
 𝐧 = :mva
@@
 
-using Unitful
-Unitful.preferunits(u"nA", u"km")
-unitify(u) = (*)$u
-unitify(u::String) = (*)$uparse(u)
+taus = Second.(2 .^ (1:6))
+# taus = Second.(2 .^ (0:6))
+df = workload(taus)
+@chain df begin
+    DC.compute_Alfvenicity_params!()
+    DC.compute_params!()
+    @transform!(:B_n_mva_norm = abs.(:B_n_mva ./ :B_mag))
+    DC.classify!(:B_n_mva_norm)
+end
 
-taus = Second.(2 .^ (1:6))
-df = workload(taus)
-Discontinuity.assign_accuracy!(df)
-@chain df begin
-    compute_Alfvenicity_params!()
-    compute_params!()
+# Count the number of events for each type
+df_event_counts = @chain df begin
+    groupby(:type)
+    combine(nrow)
 end
@@
 
+Density distributions of (normalized) thickness and current density
+
 ```{julia}
 subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
-fname = "properties_hist-enc"
+fname = "properties_hist"
 
@@
         @subset(.!isnan.(:L_n_mva_norm); view=true)
+        # @rsubset(((:id == "PSP") && :tau <= Second(2)) || (:id != "PSP" && :tau > Second(2))) # select current sheet events with tau <= 2s for PSP and tau > 2s for Earth
         subset_𝐧(𝐧)
         dropmissing(:L_n_mva_norm)
-        # compute_Alfvenicity_params!
     end
@@
 
-    plt = data(tdf) *
+    plt =
+        data(tdf) *
         mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
+        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
         mapping(color=:id, linestyle=:enc) *
@@
     draw(plt, axis=(; yscale=log10))
-
-    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
-    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
+    easy_save("$fname-$𝐧"; formats, force=true)
 end
 fs[1]
-```
-
-## Alfvenicity
-
-```{julia}
-
-fs = map([:mva]) do 𝐧
-    𝒎 = var_mapping(; 𝐧)
-
-    datalimits = x -> quantile(x, [0.01, 0.99])
-
-    tdf = @chain df begin
-        @subset(.!isnan.(:V_l_ratio); view=true)
-        subset_𝐧(𝐧)
-        dropmissing(:V_l_ratio)
-        # compute_Alfvenicity_params!
-    end
-
-    vars = [:Q_sonnerup, 𝒎.v_l_ratio, :V_l_ratio_max]
-    # 𝒎.v_l_ratio, 𝒎.bn
-    labels = ["Alfvénicity", "Velocity ratio", "Max velocity ratio"]
-
-    plt = data(tdf) *
-          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
-          mapping(color=:id, linestyle=:enc) *
-          AoG.density(; datalimits) * visual(Lines)
-    draw(plt, axis=(; yscale=log10))
-
-    # draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
-    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
-end
-fs[1]
-
 ```
@@
     df.duration = ustrip.(df.duration .|> u"s")
-    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines) * mapping(linestyle=:id)
+    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
     # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
-    plt = data(df) * mapping(:duration, color=:enc) * layer
+    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
     plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
@@
     draw(plt, axis=(; yscale=log10))
+    easy_save("duration_dist"; formats, force=true)
 end
@@
     df.duration = ustrip.(df.duration .|> u"s")
-    plt = data(df) * mapping(:duration, linestyle=:id, color=:enc) * AoG.density(; datalimits=x -> quantile(x, [0.02, 0.98])) * visual(Lines)
-    plt *= mapping(col=:tau)
+    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
+    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
+    plt *= mapping(layout=:tau)
     draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
+    easy_save("duration_dist_tau"; formats, force=true)
 end
 ```
+
+## Alfvenicity
+
+```{julia}
+𝒎 = var_mapping(; 𝐧)
+
+datalimits = x -> quantile(x, [0.01, 0.99])
+
+tdf = @chain df begin
+    @subset(.!isnan.(:V_l_ratio); view=true)
+    subset_𝐧(𝐧)
+    dropmissing(:V_l_ratio)
+end
+
+vars = [:Q_sonnerup => abs => "", :ΔV_ratio => identity => "", :V_l_ratio => identity => "", :V_l_ratio_max => identity => ""]
+# 𝒎.v_l_ratio, 𝒎.bn
+labels = ["Q_sonnerup", "Δ V ratio", "ΔV_l ratio", "Max ΔV_l ratio"]
+
+plt =
+    data(tdf) *
+    mapping(vars, row=AoG.dims(1) => renamer(labels)) *
+    #   mapping(vars, col=:tau, row=AoG.dims(1) => renamer(labels)) *
+    mapping(color=:id, linestyle=:enc) *
+    AoG.density(; datalimits) * visual(Lines)
+draw(plt, axis=(; yscale=identity), facet=(; linkyaxes=:minimal))
+# easy_save("Alfvenicities"; formats, force=true)
+# draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
+```
+
+##
+
+Joint distributions of thickness and current density
+
+```{julia}
+for 𝐧 in [:mva]
+    view = true
+    𝒎 = var_mapping(; 𝐧)
+
+    tdf = @chain df begin
+        # @subset(:enc .== enc)
+        dropmissing()
+        @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
+        subset_𝐧(𝐧)
+    end
+
+    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id)
+
+    fig = Figure(size=(800, 300))
+    axis = (; yscale=log10, xscale=log10)
+    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))
+
+    ga = fig[1, 1]
+    gb = fig[1, 2]
+    gc = fig[2, 1]
+    gd = fig[2, 2]
+
+    spec1 = plt * mapping(𝒎.l, 𝒎.j)
+    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
+    spec3 = plt * mapping(:B_n_mva_norm, :ω)
+    spec4 = plt * mapping(:ΔV_ratio, :ΔV_cosθ)
+
+    grid1 = draw!(ga, spec1; axis)
+    draw!(gb, spec2; axis)
+    draw!(gc, spec3)
+    draw!(gd, spec4; axis=(; limits=((0, 2), (-1, 1),)))
+
+    # pretty_legend!(fig, grid1)
+    # add_labels!([ga, gb, gc])
+    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
+    display(fig)
+end
+```
+
+```{julia}
+for 𝐧 in [:mva]
+    view = true
+    𝒎 = var_mapping(; 𝐧)
+
+    tdf = @chain df begin
+        @subset(.!isnan.(:B_n_mva_norm) .& .!isnan.(:σ_c); view=true)
+        dropmissing([:B_n_mva_norm, :duration, :σ_c])
+        @transform!(:duration = Float64.(ustrip.(:duration .|> u"s")))
+        subset_𝐧(𝐧)
+    end
+
+    plt = data(tdf) * mapping(row=:id, col=:enc)
+    vis = visual(Scatter; markersize=6)
+    fig = Figure(; size=(1200, 800))
+    axis = (;)
+
+    ΔV_cosθ_group = :ΔV_cosθ => >(0)
+    ΔV_cosθ_map = mapping(group=ΔV_cosθ_group, color=ΔV_cosθ_group)
+
+    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * vis
+    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.smooth() * ΔV_cosθ_map)
+    σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))
+
+    draw!(fig[1, 1], B_n_spec; axis)
+    draw!(fig[1, 2], ΔV_spec; axis=(; limits=((0, 2), (-1, 1),)))
+    draw!(fig[2, 1], σc_σr_spec)
+
+    # pretty_legend!(fig, grid1)
+    # add_labels!([ga, gb, gc])
+    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
+    display(fig)
+end
+```
+
+Joint distributions of Q_sonnerup and other variables
+
+```{julia}
+CairoMakie.activate!()
+
+view = true
+𝒎 = var_mapping(; 𝐧)
+
+vars = [:B_n_mva_norm, :Q_sonnerup, :duration, :σ_c]
+
+tdf = @chain df begin
+    dropmissing(vars)
+    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
+    @transform!(
+        :duration = Float64.(ustrip.(:duration .|> u"s")),
+        :B_n_mva_norm = Float64.(:B_n_mva_norm),
+    )
+end
+
+A_He_df = @chain tdf begin
+    dropmissing(:A_He)
+    @transform!(:A_He = Float64.(only.(:A_He)))
+    @rsubset(:A_He < 10)
+end
+
+Bn_df = subset_𝐧(tdf, 𝐧)
+
+fig = Figure(; size=(1200, 800))
+axis = (;)
+
+layout = mapping(row=:id, col=:enc)
+plt = data(tdf) * layout
+vis = visual(Scatter; markersize=6)
+
+Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
+A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
+line_vis = visual(linewidth=3)
+
+Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup) * layout * (vis + AoG.linear() * Q_group * line_vis)
+duration_Q_spec = plt * mapping(:duration, :Q_sonnerup) * (vis + AoG.smooth() * Q_group * line_vis)
+σc_Q_spec = plt * mapping(:σ_c, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
+σr_Q_spec = plt * mapping(:σ_r, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
+A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup => abs) * layout * (vis + AoG.smooth() * A_He_group * line_vis)
+
+draw!(fig[1, 1], Bn_Q_spec)
+draw!(fig[1, 2], duration_Q_spec; axis=(; xscale=log10))
+draw!(fig[2, 1], σc_Q_spec)
+draw!(fig[2, 2], σr_Q_spec)
+draw!(fig[3, 1], A_He_Q_spec)
+
+# add_labels!([ga, gb, gc])
+# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
+display(fig)
+```
+
+## Duration vs Alfvénicity Correlation
+
+Let's analyze the relationship between duration and Alfvénicity to see if they are correlated.
+
+```{julia}
+using HypothesisTests
+using NaNStatistics
+using PairPlots
+
+# Filter for clean data with both duration and Alfvénicity measures
+vars = [:duration, :Q_sonnerup, :V_l_ratio, :B_n_mva_norm]
+
+df_corr = @chain df begin
+    filter_low_mva_quality()
+    dropmissing(vars)
+    @transform!(:duration = Float64.(ustrip.(:duration .|> u"s")))
+    @rsubset(all(!isnan, (:Q_sonnerup, :V_l_ratio, :duration, :σ_c)))
+end
+
+# Overall correlation matrix
+println("Overall correlation matrix:")
+cor_vars = [:Q_sonnerup, :duration, :B_n_mva_norm, :σ_c, :σ_r, :L_n_mva_norm, :J_m_max_mva_norm]
+overall_corr = nancor(Matrix(df_corr[!, cor_vars]))
+display(overall_corr)
+# heatmap(cor_vars, cor_vars, overall_corr)
+# pairplot(df_corr[!, cor_vars])
+
+# Group by different missions and compute correlations
+println("\nCorrelation analysis by mission:")
+mission_stats = @chain df_corr begin
+    groupby(:id)
+    @combine(
+        :count = nrow,
+        :corr_Q_duration = nancor(:Q_sonnerup, :duration),
+        :corr_Bn_duration = nancor(:B_n_mva_norm, :duration),
+        :corr_Q_Bn = nancor(:Q_sonnerup, :B_n_mva_norm),
+        :mean_Q = nanmean(abs.(:Q_sonnerup)),
+        :mean_duration = nanmean(:duration),
+        :mean_Bn = nanmean(:B_n_mva_norm)
+    )
+end
+
+display(mission_stats)
+
+# # Statistical significance tests
+# test_q = CorrelationTest(df_corr.duration_s, df_corr.Q_sonnerup)
+# test_vl = CorrelationTest(df_corr.duration_s, collect(skipmissing(df_corr.V_l_ratio)))
+
+# println("Statistical significance:")
+# println("Duration vs Q_sonnerup: p-value = $(round(pvalue(test_q), digits=6))")
+# println("Duration vs V_l_ratio: p-value = $(round(pvalue(test_vl), digits=6))")
+```
+
+Correlation Strength:
+- Duration vs Q_sonnerup: r = -0.0253 (very weak negative correlation)
+- Duration vs V_l_ratio: r = -0.0134 (very weak negative correlation)
+
+Statistical Significance:
+- Duration vs Q_sonnerup: p = 0.009 (statistically significant, p < 0.05)
+- Duration vs V_l_ratio: p = 0.166 (not statistically significant, p > 0.05)
+
+Interpretation:
+1. There is a very weak negative correlation between duration and Alfvénicity - meaning longer events tend to be slightly less Alfvénic
+2. The effect size is tiny (correlations ~-0.02 to -0.03) - practically negligible
+3. Only Q_sonnerup shows statistical significance due to the large sample size (10,684 events)
+4. The large sample size makes even tiny correlations statistically detectable, but they're not practically meaningful
+
+Conclusion: While there's a statistically significant but extremely weak tendency for longer-duration current sheets to be slightly less Alfvénic, the correlation is so small it's essentially negligible in practical terms.
+Duration and Alfvénicity are largely independent of each other in this dataset.
+
+## Unused Code
+
+```{julia}
+# Visualization: Scatter plot with trend line
+f_corr = Figure(size=(1400, 600))
+
+attrs = (alpha=0.6, markersize=6)
+
+# Duration vs Q_sonnerup
+ax1 = Axis(f_corr[1, 1],
+    xscale=log10,
+    xlabel="Duration (seconds)",
+    ylabel="Q_sonnerup (Alfvénicity)",
+    title="Duration vs Alfvénicity")
+
+scatter!(ax1, df_corr.duration_s, abs.(df_corr.Q_sonnerup); color=:blue, attrs...)
+
+# Add trend line (remove any remaining NaNs)
+valid_idx = .!isnan.(df_corr.duration_s) .& .!isnan.(df_corr.Q_sonnerup)
+if sum(valid_idx) > 0
+    x_valid = df_corr.duration_s[valid_idx]
+    y_valid = abs.(df_corr.Q_sonnerup[valid_idx])
+    x_range = range(minimum(x_valid), maximum(x_valid), length=100)
+    X = hcat(ones(length(x_valid)), x_valid)
+    β = X \ y_valid
+    trend_y = β[1] .+ β[2] .* x_range
+    lines!(ax1, x_range, trend_y, color=:red, linewidth=2, linestyle=:dash)
+end
+
+# text!(ax1, 0.05, 0.95, "r = $(round(corr_duration_q, digits=4))", space=:relative, fontsize=12, color=:black)
+
+# Duration vs V_l_ratio  
+df_vl = dropmissing(df_corr, :V_l_ratio)
+ax2 = Axis(f_corr[1, 2],
+    xscale=log10,
+    xlabel="Duration (seconds)",
+    ylabel="V_l_ratio",
+    title="Duration vs Velocity Ratio")
+
+scatter!(ax2, df_vl.duration_s, df_vl.V_l_ratio,
+    color=:green, alpha=0.6, markersize=6)
+
+# Add trend line for V_l_ratio (remove any remaining NaNs)
+valid_idx2 = .!isnan.(df_vl.duration_s) .& .!isnan.(df_vl.V_l_ratio)
+if sum(valid_idx2) > 0
+    x_valid2 = df_vl.duration_s[valid_idx2]
+    y_valid2 = df_vl.V_l_ratio[valid_idx2]
+    x_range2 = range(minimum(x_valid2), maximum(x_valid2), length=100)
+    X2 = hcat(ones(length(x_valid2)), x_valid2)
+    β2 = X2 \ y_valid2
+    trend_y2 = β2[1] .+ β2[2] .* x_range2
+    lines!(ax2, x_range2, trend_y2, color=:red, linewidth=2, linestyle=:dash)
+end
+ylims!(ax2, 0, 1)
+# text!(ax2, 0.05, 0.95, "r = $(round(corr_duration_vl, digits=4))", space=:relative, fontsize=12, color=:black)
+
+f_corr
+```
+
+```{julia}
+using CategoricalArrays
+using NaNStatistics
+# Binned analysis
+duration_bins = [0, 2, 5, 10, 20, 50, maximum(df_corr.duration_s)]
+df_binned = @transform(df_corr,
+    :duration_bin = cut(:duration_s, duration_bins, labels=["0-2s", "2-5s", "5-10s", "10-20s", "20-50s", ">50s"]))
+
+binned_stats = @chain df_binned begin
+    dropmissing([:Q_sonnerup, :V_l_ratio])
+    groupby(:duration_bin)
+    @combine(
+        :count = length(:duration_s),
+        :mean_duration = nanmean(:duration_s),
+        :mean_Q_sonnerup = nanmean(abs.(:Q_sonnerup)),
+        :std_Q_sonnerup = nanstd(abs.(:Q_sonnerup)),
+        :mean_V_l_ratio = nanmean(:V_l_ratio),
+        :std_V_l_ratio = nanstd(:V_l_ratio)
+    )
+end
+
+println("Mean Alfvénicity by Duration Bins:")
+select(binned_stats, :duration_bin, :count, :mean_Q_sonnerup, :mean_V_l_ratio)
+```
+
+```{julia}
+# Add binned averages to the scatter plots
+for (i, row) in enumerate(eachrow(binned_stats))
+    if i < nrow(binned_stats)
+        # Get bin boundaries
+        bin_start = duration_bins[i]
+        bin_end = duration_bins[i+1]
+        bin_center = (bin_start + bin_end) / 2
+
+        # Add mean points with error bars to Q_sonnerup plot
+        scatter!(ax1, [bin_center], [row.mean_Q_sonnerup],
+            color=:red, markersize=12, marker=:diamond)
+        errorbars!(ax1, [bin_center], [row.mean_Q_sonnerup], [row.std_Q_sonnerup],
+            color=:red, whiskerwidth=8, linewidth=2)
+
+        # Add mean points with error bars to V_l_ratio plot  
+        scatter!(ax2, [bin_center], [row.mean_V_l_ratio],
+            color=:red, markersize=12, marker=:diamond)
+        errorbars!(ax2, [bin_center], [row.mean_V_l_ratio], [row.std_V_l_ratio],
+            color=:red, whiskerwidth=8, linewidth=2)
+    else
+        # Handle the last bin (>50s) - use a representative position
+        bin_center = 60  # Approximate position for >50s bin
+
+        scatter!(ax1, [bin_center], [row.mean_Q_sonnerup],
+            color=:red, markersize=12, marker=:diamond)
+        errorbars!(ax1, [bin_center], [row.mean_Q_sonnerup], [row.std_Q_sonnerup],
+            color=:red, whiskerwidth=8, linewidth=2)
+
+        scatter!(ax2, [bin_center], [row.mean_V_l_ratio],
+            color=:red, markersize=12, marker=:diamond)
+        errorbars!(ax2, [bin_center], [row.mean_V_l_ratio], [row.std_V_l_ratio],
+            color=:red, whiskerwidth=8, linewidth=2)
+    end
+end
+
+# Add legend explaining the red diamonds
+Legend(f_corr[2, :], [MarkerElement(color=:red, marker=:diamond, markersize=12)],
+    ["Binned Averages ± Std"], orientation=:horizontal, tellwidth=false, tellheight=true)
+
+f_corr
+```

### 2025-09-03 notebooks/10_results.qmd
update
feat: add cross_helicity and residual energy

@@
 using DrWatson
-using PSPAnisotropy.Dataset: load_all
-using Discontinuity: var_mapping
 import Beforerr: easy_save
 using GLMakie, AlgebraOfGraphics
-m = var_mapping()
 df = PSPAnisotropy.workload()
@@
     )
-    levels!(df.dataset, ds_order)
 
@@
 plot_dB_over_B(layer)
-```
-
-```{julia}
-# plot the density distribution of the thickness and current density
-begin
-    fname = "properties_distribution"
-
-    maps = [l_log_map j_log_map
-        l_norm_log_map j_norm_log_map]
-    figure_kwargs = (size=(800, 600),)
-
-    plot_dist(data_layer; maps, axis=(), visual=mapping(), figure_kwargs=figure_kwargs)
-    easy_save(fname)
-end
 ```

### 2025-09-03 notebooks/11_alignment.qmd
feat: add cross_helicity and residual energy

@@
 ```
-
-```{julia}
-layer = data(df) * mapping(color=:dataset, col=enc_m)
-
-function plot_p1()
-    maps = [l_log_map, l_norm_log_map, j_log_map, j_norm_log_map]
-    figure = (size=(450, 800),)
-    f = plot_dist(layer, maps; figure, axis)
-
-    # fine tune the plot
-    for i in 1:4
-        axs = contents(f[i, 1][:, :])
-        ylims!.(axs; low=1e-3)
-    end
-    axs = contents(f[1, 1][:, :])
-    xlims!.(axs; low=-1)
-    axs = contents(f[2, 1][:, :])
-    xlims!.(axs; low=-1.5)
-    axs = contents(f[4, 1][:, :])
-    xlims!.(axs; high=1)
-
-    easy_save("thickness_current")
-end
-```
-
-![](../figures/thickness_current.png)
 

### 2025-09-03 notebooks/11_spectra.qmd
feat: add cross_helicity and residual energy

@@
+# Cross helicity and residual energy
+
+```{julia}
+using Dates
+using PSPAnisotropy
+using PSPAnisotropy: Wind
+using SPEDAS
+using DimensionalData
+using Unitful
+using PlasmaFormulary
+using TimeseriesUtilities
+Unitful.preferunits(u"nA", u"km")
+```
+
+## Global (whole interval) average
+
+```{julia}
+
+tmin = DateTime("2007-07-06")
+tmax = tmin + Hour(1)
+B = DimArray(Wind.B_GSE(tmin, tmax); add_unit=true)
+V = DimArray(Wind.V_GSE_3DP(tmin, tmax); add_unit=true) |> dropna
+n = DimArray(Wind.n_p_3DP(tmin, tmax); add_unit=true) |> dropna
+# B, V, n = SPEDAS.tsync(B, V, n)
+```
+
+```{julia}
+using LinearAlgebra
+using Statistics
+using SPEDAS.Tullio
+using TimeseriesUtilities.VectorizedStatistics
+
+function fast_cross_helicity(B, V, n)
+    N = size(B, 1)
+    @tullio V_B[i, j] := Alfven_velocity(B[i, j], n[i], 1)
+    @tullio B̄[j] := V_B[i, j]
+    @tullio V̄[j] := V[i, j]
+    B̄ .= B̄ ./ N
+    V̄ .= V̄ ./ N
+    @tullio num := (V_B[i, j] - B̄[j]) * (V[i, j] - V̄[j])
+    @tullio den := (V_B[i, j] - B̄[j]) * (V_B[i, j] - B̄[j]) + (V[i, j] - V̄[j]) * (V[i, j] - V̄[j])
+    return 2 * num / den
+end
+
+@b fast_cross_helicity(B, V, n), cross_helicity(B, V, n)
+```
+
+## Cross helicity and residual energy spectra
+
 <a href="https://docs.juliadsp.org/stable/periodograms/">Periodograms - periodogram estimation · DSP.jl</a>
@@
 ```{julia}
-using PlasmaFormulary
 

### 2025-09-03 lib/PSP/src/PSP.jl

@@ -8,7 +8,7 @@ using YAXArrays, NetCDF
 using DataFrames, DimensionalData
 using LaTeXStrings
 
-const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat="yyyy-mm-dd HH:MM")
+const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat = "yyyy-mm-dd HH:MM")
 
 B = spz"PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"
 const B_SC = spz"cda/PSP_FLD_L2_MAG_SC/psp_fld_l2_mag_SC"
@@ -21,6 +21,12 @@ n_sqtn = SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_density"; labels = ["S
 n_rfs = SpeasyProduct("PSP_FLD_L3_RFS_LFR_QTN/N_elec"; labels = ["RFS Electron"])
 n = DataSet("Density", [n_spi, n_spc, n_sqtn])
 n_spi_sqtn = DataSet("Density", [n_spi, n_sqtn])
+
+function A_He(tmin, tmax; n_p = nothing)
+    n_p = DimArray(@something n_p n_spi(tmin, tmax); standardize = true)
+    n_α = DimArray(n_alpha(tmin, tmax); standardize = true)
+    return n_α ./ n_p .* 100
+end
 
 V = spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"
 const V_SC = spz"cda/PSP_SWP_SPI_SF00_L3_MOM/VEL_SC"
@@ -43,10 +49,12 @@ function read_electron_temperature(filename; data_dir = datadir("electron_fit_Ha
     # Read CSV file
     df = CSV.File(filepath; dateformat = "yyyy-mm-dd/HH:MM:SS.sss", drop = [3])
 
-    para = DimArray(df.coretpar_data, Ti(df.coretpar_time);
+    para = DimArray(
+        df.coretpar_data, Ti(df.coretpar_time);
         metadata = Dict(:ylabel => "T (eV)", :units => "eV", :label => L"T_{e,\parallel}")
     )
-    perp = DimArray(df.coretperp_data, Ti(df.coretpar_time);
+    perp = DimArray(
+        df.coretperp_data, Ti(df.coretpar_time);
[…]

### 2025-09-03 src/PSPAnisotropy.jl

@@ -27,8 +27,8 @@ function get_timerange(enc)
     Δt_min = Day(2)
     Δt_max = Day(6)
     time = psp_events[enc, :Time]
-    t0_psp = floor(time - Day(3), Day(1))
-    t1_psp = ceil(time + Day(3), Day(1))
+    t0_psp = floor(time - Day(2), Day)
+    t1_psp = ceil(time + Day(2), Day)
     t0_earth = t0_psp + Δt_min
     t1_earth = t1_psp + Δt_max
     return (t0_psp, t1_psp), (t0_earth, t1_earth)
@@ -40,8 +40,8 @@ export produce
 function produce(conf)
     conf["tau"] = Second(conf["tau"]) / Second(1) # convert to float to save in the file name
     conf, _ = produce_or_load(conf, datadir(); tag = false) do c
-        @unpack t0, t1, B, V, n, tau = c
-        c["events"] = ids_finder(t0, t1, B, V, n; tau = Second(tau))
+        @unpack t0, t1, B, V, n, tau, extra = c
+        c["events"] = ids_finder(t0, t1, B, V, n, extra...; tau = Second(tau))
         c
     end
     return conf["events"]
@@ -87,9 +87,9 @@ end
 
 export psp_conf, wind_conf, thm_conf
 
-psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi)
-wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP)
-thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE)
+psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He,))
+wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, extra = (:A_He => Wind.A_He,))
+thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, extra = ())
 
 function workload()
     df = mapreduce(vcat, 7:9) do enc

### 2025-09-03 src/dataset.jl

@@ -1,22 +1,0 @@
-module Dataset
-using CategoricalArrays
-import Discontinuity
-using Unitful
-using Unitful: μ0
-using Logging
-
-load_psp(enc = DEFAULT_ENC) = load(enc, "PSP"; dataset = "Parker Solar Probe")
-
-function load_all(enc)
-    dfs = [
-        load_psp(enc),
-        load(enc, "THEMIS"; dataset = "ARTEMIS"),
-        load(enc, "Wind"),
-        # load(enc, "Solo"; dataset="Solar Orbiter")
-    ]
-    df = reduce(vcat, dfs, cols = :intersect)
-    levels!(df.dataset, ["Parker Solar Probe", "ARTEMIS", "Wind"])
-    return df
-end
-
-end

### 2025-09-03 src/plot.jl

@@ -1,3 +1,4 @@
+import AlgebraOfGraphics as AoG
 import AlgebraOfGraphics: draw!
 import Discontinuity
 using SPEDAS: tvec, setmeta, setmeta!
@@ -11,40 +12,52 @@ export plot_candidate, plot_var_info!, plot_PSP, plot_Wind
 
 import .Labels as 𝑳
 
+export set_Z_theme!
+
+set_Z_theme!() = begin
+    AoG.set_aog_theme!()
+    update_theme!(;
+        figure_padding = 1,
+        fonts = (; regular = AoG.firasans("Regular"), bold = AoG.firasans("Medium")),
+        Legend = (; framevisible = false, padding = (0, 0, 0, -15)),
+        Axis = (; xlabelfont = :bold, ylabelfont = :bold),
+    )
+end
+
 
 # %%
-legend_kwargs = (position=:top, titleposition=:left)
+legend_kwargs = (position = :top, titleposition = :left)
 
 begin
     enc_m = :enc => x -> "Enc $x"
 end
 
-log_axis = (yscale=log10, xscale=log10)
+log_axis = (yscale = log10, xscale = log10)
 
-function draw!(grid; axis=NamedTuple(), palettes=NamedTuple())
-    return plt -> draw!(grid, plt; axis=axis, palettes=palettes)
+function draw!(grid; axis = NamedTuple(), palettes = NamedTuple())
+    return plt -> draw!(grid, plt; axis = axis, palettes = palettes)
 end
 
 function plot_var_info!(f, event)
-    tlines!(f, [event.tstart, event.tstop])
+    return tlines!(f, [event.tstart, event.tstop])
 end
 
 # ---
 # Example plot
-function plot_candidate(f, event, ts::AbstractArray, toffset=nothing; kwargs...)
+function plot_candidate(f, event, ts::AbstractArray, toffset = nothing; kwargs...)
     tmin, tmax = event.t_us, event.t_ds
     tstart, tstop = event.tstart, event.tstop
     toffset = something(toffset, tstop - tstart)
     fax = tplot(f, ts, tmin - toffset, tmax + toffset; kwargs...)
     tlines!(fax, [tmin, tmax])
     tlines!(fax, [tstart, tstop])
-    fax
+    return fax
 end
 
[…]

### 2025-09-03 notebooks/02_stats.qmd
feat: add plasma beta parameters

@@
 df = workload(taus)
+
+_float64(x) = Float64(x)
+_float64(::Missing) = missing
+
 @chain df begin
@@
     DC.compute_params!()
-    @transform!(:B_n_mva_norm = abs.(:B_n_mva ./ :B_mag))
+    @transform!(
+        :B_n_mva_norm = abs.(:B_n_mva ./ :B_mag),
+        :duration = _float64.(ustrip.(:duration .|> u"s"))
+    )
     DC.classify!(:B_n_mva_norm)
@@
 end
+
+subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
 ```
+
+## Associations and independence test
+
+```{julia}
+
+println("\n" * "="^60)
+println("ASSOCIATION ANALYSIS FOR ALFVÉNICITY")
+println("="^60)
+
+# Define the variable pairs you want to analyze with transformations embedded
+alfvenicity_pairs = [
+    (:duration, :Q_sonnerup => abs, "Duration vs Alfvénicity (Q_sonnerup)"),
+    (:duration, :V_l_ratio, "Duration vs Velocity Ratio (V_l_ratio)"),
+    (:B_n_mva_norm, :Q_sonnerup => abs, "Magnetic Field Normal vs Alfvénicity"),
+    (:σ_c, :Q_sonnerup, "Cross helicity vs Alfvénicity"),
+    (:σ_r, :Q_sonnerup),
+    (:β, :Q_sonnerup => abs),
+    (:A_He => x -> ismissing(x) ? missing : only(x), :Q_sonnerup => abs, "Helium Abundance vs Alfvénicity"),
+    (:J_m_max_mva_norm, :Q_sonnerup => abs, "Current density vs Alfvénicity"),
+    (:L_n_mva_norm, :Q_sonnerup => abs, "Thickness vs Alfvénicity"),
+    (:A_He => x -> ismissing(x) ? missing : only(x), :J_m_max_mva_norm),
+    (:A_He => x -> ismissing(x) ? missing : only(x), :L_n_mva_norm),
+    (:β, :J_m_max_mva_norm),
+    (:β, :L_n_mva_norm),
+    (:β, :A_He),
+]
+
+# Run overall analysis
+println("OVERALL ASSOCIATION ANALYSIS")
+println("="^50)
+analyze_associations(df, alfvenicity_pairs)
+
+# Grouped analysis
+# println("GROUPED ASSOCIATION ANALYSIS (by $(group_by))")
+println("="^50)
+analyze_associations(df, alfvenicity_pairs; group_by=:id)
+```
+
+```md
+Association Measure Interpretation:
+Values range from 0 (no association) to 1 (perfect association):
+- 0.0 - 0.1: Very weak association
+- 0.1 - 0.3: Weak association  
+- 0.3 - 0.5: Moderate association
+- 0.5 - 0.7: Strong association
+- 0.7 - 1.0: Very strong association
+
+Association Methods Used:
+1. Distance Correlation: Non-parametric measure detecting linear & nonlinear dependencies
+2. Pearson Correlation: Standard linear correlation coefficient  
+3. Spearman Correlation: Rank-based correlation (monotonic relationships)
+4. Chatterjee Correlation: New robust measure for general dependencies
+5. Mutual Information: Information-theoretic measure of shared information
+
+Note: These are association strengths, not statistical significance tests.
+For independence testing, use with caution - consider both effect size and sample size.
+```
+
+[](../association_results.txt)
+
+```md
+
+🔎 Step 1. General observations
+	•	Cross helicity vs Alfvénicity absolutely dominates:
+	•	Pearson = 0.84 overall (0.92 in PSP, 0.76 in Wind).
+	•	Chatterjee = 0.47–0.53.
+	•	MI = 0.58–0.97.
+→ This is a very strong dependence by any metric, which is expected since Alfvénicity is conceptually related to cross helicity.
+	•	Magnetic field normal vs Alfvénicity shows weak-to-moderate positive linear correlation (~0.17–0.19), but Chatterjee and MI stay low.
+Suggests a weak linear trend, not a strong monotonic or nonlinear relationship.
+	•	Σ_r vs Q_sonnerup:
+	•	Small negative Pearson (~ -0.1).
+	•	But Chatterjee 0.09–0.15 and MI up to 0.24 in PSP → weak, possibly nonlinear dependence.
+	•	This might indicate subtle structure missed by linear correlation.
+	•	Duration, velocity ratio, thickness, helium abundance, current density:
+	•	All show weak or negligible correlations (|Pearson| < 0.25, Chatterjee mostly < 0.06, MI close to 0).
+	•	Suggests near independence, with only minor dataset-specific effects (e.g., PSP helium abundance at -0.24).
+
+⸻
+
+🔎 Step 2. Dataset comparison (PSP vs Wind)
+	•	Cross helicity vs Alfvénicity is strong in both spacecraft, but even stronger in PSP (r ~ 0.92 vs 0.76).
+	•	Magnetic field normal vs Alfvénicity is similar across PSP/Wind (r ~ 0.17–0.18).
+	•	Σ_r vs Q_sonnerup is stronger in PSP (MI ~0.24 vs 0.05 in Wind).
+	•	Helium abundance vs Alfvénicity:
+	•	PSP: moderate negative Pearson (-0.24).
+	•	Wind: near zero.
+→ Suggests PSP-specific dependence (possibly tied to solar wind composition closer to the Sun).
+	•	The rest (duration, velocity ratio, thickness, current density) are consistently weak in both datasets.
+
+⸻
+
+🔎 Step 3. Practical interpretation
+	1.	Cross helicity is the defining feature of Alfvénicity.
+The high correlations confirm that your Alfvénicity measure (Q_sonnerup) essentially tracks cross helicity.
+This is expected, but the strength of correlation (0.8–0.9) validates consistency across datasets.
+	2.	Other plasma/structural properties are only weakly linked.
+Magnetic field orientation (normal) shows a weak positive association, but not much more.
+	3.	Σ_r (residual energy measure?) has a modest but interesting nonlinear association with Alfvénicity, especially in PSP.
+Could hint at a subtle dependence worth exploring with scatter plots or conditional analysis.
+	4.	Helium abundance only matters in PSP.
+The -0.24 Pearson suggests Alfvénicity tends to be lower in He-rich regions, but this trend does not appear in Wind. That could reflect heliocentric distance effects.
+
+⸻
+
+✅ Summary of main findings:
+	•	Strong dependence: Cross helicity ↔ Alfvénicity (core relationship).
+	•	Weak but consistent: Magnetic field normal, Σ_r (especially in PSP).
+	•	Dataset-specific: Helium abundance (negative in PSP, absent in Wind).
+	•	Effectively independent: Duration, velocity ratio, thickness, current density.
+
+⸻
+```
+
+Would you like me to help you visualize these dependencies (scatter plots, density plots, MI heatmaps) to confirm the weak vs strong associations, or do you just need a written interpretation for now?
 
@@
 ```{julia}
-subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
 fname = "properties_hist"
@@
 
-##
+## Joint distributions
 
-Joint distributions of thickness and current density
+### Thickness and current density
 
@@
     tdf = @chain df begin
-        @subset(.!isnan.(:B_n_mva_norm) .& .!isnan.(:σ_c); view=true)
+        @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c, :ΔV_ratio, :ΔV_cosθ)); view=true)
         dropmissing([:B_n_mva_norm, :duration, :σ_c])
-        @transform!(:duration = Float64.(ustrip.(:duration .|> u"s")))
+        @transform!(:duration = Float64.(:duration))
         subset_𝐧(𝐧)
@@
 
-    plt = data(tdf) * mapping(row=:id, col=:enc)
+    β_A_He_df = @chain df begin
+        @rsubset(all(!isnan, (:β, :A_He)); view=true)
+        dropmissing([:β, :A_He])
+        @transform!(:log_β = log10.(:β))
+        @rsubset(:A_He < 20, :log_β > -1.5)
+    end
+
+    layout = mapping(row=:id, col=:enc)
+
+    plt = data(tdf) * layout
     vis = visual(Scatter; markersize=6)
@@
     B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * vis
-    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.smooth() * ΔV_cosθ_map)
+    ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
     σc_σr_spec = plt * mapping(:σ_c, :σ_r) * (vis + AoG.smooth() * visual(color=:red))
+
+    A_He_group = mapping(group=:A_He => >(1.5), color=:A_He => >(1.5))
+
+    β_A_He_spec = data(β_A_He_df) * layout * mapping(:log_β, :A_He) * (vis + AoG.smooth(; degree=1) * A_He_group)
 
@@
     draw!(fig[2, 1], σc_σr_spec)
+    draw!(fig[2, 2], β_A_He_spec)
 
@@
 
-Joint distributions of Q_sonnerup and other variables
+### Q_sonnerup and other variables
 
 ```{julia}
-CairoMakie.activate!()
-
 view = true
@@
     @transform!(
-        :duration = Float64.(ustrip.(:duration .|> u"s")),
+        :duration = Float64.(:duration),
         :B_n_mva_norm = Float64.(:B_n_mva_norm),
@@
 
+β_df = @chain df begin
+    @rsubset(all(!isnan, [:β, :Q_sonnerup]); view=true)
+    dropmissing([:β, :Q_sonnerup])
+    @transform!(:log_β = log10.(:β))
+end
+
 Bn_df = subset_𝐧(tdf, 𝐧)
@@
 plt = data(tdf) * layout
-vis = visual(Scatter; markersize=6)
+vis = visual(Scatter; markersize=5)
 
@@
 
-Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup) * layout * (vis + AoG.linear() * Q_group * line_vis)
+Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup => abs) * layout * (vis + AoG.linear() * line_vis * mapping(color=:id))
 duration_Q_spec = plt * mapping(:duration, :Q_sonnerup) * (vis + AoG.smooth() * Q_group * line_vis)
@@
 A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup => abs) * layout * (vis + AoG.smooth() * A_He_group * line_vis)
+β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * (vis + AoG.smooth(; degree=4) * line_vis * mapping(color=:id))
 
@@
 draw!(fig[3, 1], A_He_Q_spec)
+draw!(fig[3, 2], β_Q_spec)
 
 # add_labels!([ga, gb, gc])
-# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
+easy_save("Q_sonnerup_joint_dist"; formats, force=true)
 display(fig)
@@
 cor_vars = [:Q_sonnerup, :duration, :B_n_mva_norm, :σ_c, :σ_r, :L_n_mva_norm, :J_m_max_mva_norm]
-overall_corr = nancor(Matrix(df_corr[!, cor_vars]))
+_cor_func = df -> nancor(Matrix(df[!, cor_vars]))
+overall_corr = _cor_func(df_corr)
 display(overall_corr)
-# heatmap(cor_vars, cor_vars, overall_corr)
-# pairplot(df_corr[!, cor_vars])
-
-# Group by different missions and compute correlations
-println("\nCorrelation analysis by mission:")
-mission_stats = @chain df_corr begin
-    groupby(:id)
-    @combine(
-        :count = nrow,
-        :corr_Q_duration = nancor(:Q_sonnerup, :duration),
-        :corr_Bn_duration = nancor(:B_n_mva_norm, :duration),
-        :corr_Q_Bn = nancor(:Q_sonnerup, :B_n_mva_norm),
-        :mean_Q = nanmean(abs.(:Q_sonnerup)),
-        :mean_duration = nanmean(:duration),
-        :mean_Bn = nanmean(:B_n_mva_norm)
-    )
-end
-
-display(mission_stats)
-
 # # Statistical significance tests

### 2025-09-03 src/PSPAnisotropy.jl

@@ -12,6 +12,7 @@ using TimeseriesUtilities: tsplit
 
 export get_timerange, workload, get_vl_ratio_ts
 
+include("associations.jl")
 include("meta.jl")
 include("mva.jl")
 include("calc.jl")
@@ -87,8 +88,8 @@ end
 
 export psp_conf, wind_conf, thm_conf
 
-psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He,))
-wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, extra = (:A_He => Wind.A_He,))
+psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He, :T => PSP.pTemp))
+wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, extra = (:A_He => Wind.A_He, :T => Wind.T_p_PLSP))
 thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, extra = ())
 
 function workload()

### 2025-09-03 src/associations.jl

@@ -1,0 +1,94 @@
+
+using Associations
+
+export analyze_associations
+
+# Association calculation function (much faster than independence tests)
+function calculate_associations(x, y)
+    # Remove missing values
+    valid_idx = .!ismissing.(x) .& .!ismissing.(y) .& .!isnan.(x) .& .!isnan.(y)
+    x_clean = x[valid_idx] .|> Float64
+    y_clean = y[valid_idx] .|> Float64
+
+    if length(x_clean) < 10
+        return [(measure_name="Insufficient data", association=NaN, n=length(x_clean))]
+    end
+
+    # Multiple association measures
+    measures = [
+        # ("Distance Correlation", DistanceCorrelation()),
+        ("Pearson Correlation", PearsonCorrelation()),
+        ("Chatterjee Correlation", AzadkiaChatterjeeCoefficient()),
+        ("Mutual Information", KSG1(MIShannon()))
+    ]
+
+    results = []
+    for (name, measure) in measures
+        try
+            assoc_value = association(measure, x_clean, y_clean)
+            push!(results, (
+                measure_name=name,
+                association=assoc_value,
+                n=length(x_clean)
+            ))
+        catch e
+            @warn "Failed to calculate association for $(name): $(e)"
+            # Some measures might fail with certain data
+            push!(results, (
+                measure_name=name,
+                association=NaN,
+                n=length(x_clean)
+            ))
+        end
+    end
+
+    return results
+end
+
+function parse_column(df, col_spec::Pair)
+    col, transform_func = col_spec.first, col_spec.second
+    return transform_func.(df[!, col])
+end
+
+parse_column(df, col_spec) = df[!, col_spec]
+
+"""
+Analyze associations between variable pairs, optionally grouped by a column.
+
+Args:
+    data: DataFrame to analyze
+    variable_pairs: Vector of tuples with flexible syntax:
+        - (col1, col2, "Description")
+        - (col1, col2 => transform_func, "Description") 
+        - (col1 => transform_func, col2, "Description")
+        - (col1 => transform_func, col2 => transform_func, "Description")
+    group_by: Column name to group by (e.g., :id for missions), or nothing
+    io: IOStream to write results to (default: stdout)
+"""
+function analyze_associations(data, variable_pairs; group_by=nothing, io = stdout)
+    # Overall analysis (if not grouping)
+    if group_by === nothing
+        for (i, pair) in enumerate(variable_pairs)
+            col1_spec, col2_spec = pair[1], pair[2]
[…]

### 2025-09-29 notebooks/00_index.qmd
feat: plotting figures

@@
 
-import PSPAnisotropy.Labels as 𝑳
-import PSPAnisotropy.YLabel as 𝒀
-
 𝐧 = :mva
@@
 unitify(u::String) = (*)$uparse(u)
+includet("../src/plot.jl")
+```
+
+```{julia}
+df = workload()
+compute_params!(df)
+compute_Alfvenicity_params!(df)
+
+psp_df = @rsubset(df, :id == "PSP"; view=true)
+wind_df = @rsubset(df, :id == "Wind"; view=true)
+thm_df = @rsubset(df, :id == "THEMIS"; view=true)p -
+         thm_conf["B"] = unitify("nT") ∘ thm_conf["B"]
+```
+
+```{julia}
+compute_PSP_anisotropy_params!(psp_df)
+for enc in 7:9
+    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
+    wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
+    compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)
+end
 ```
@@
 ```{julia}
-df, configs = workload()
-compute_params!(df)
-compute_Alfvenicity_params!(df)
-
-psp_df = @rsubset(df, :id == "PSP"; view=true)
-psp_config = configs[1]
-wind_df = @rsubset(df, :id == "Wind"; view=true)
-wind_config = configs[2]
-thm_df = @rsubset(df, :id == "THEMIS"; view=true)
-thm_config = configs[3]
-
-thm_config["B"] = unitify("nT") ∘ thm_config["B"]
-```
-
-```{julia}
-using DimensionalData
-
-deunit(x::Quantity, u) = NoUnits(x / u)
-deunit(x, u) = x
-
-function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt=Minute(1))
-    @rtransform! df begin
-        :Tp_para = deunit(tselect(Tp_para, :time, dt), u"eV")
-        :Tp_perp = deunit(tselect(Tp_perp, :time, dt), u"eV")
-        :Te_para = deunit(tselect(Te_para, :time, dt), u"eV")
-        :Te_perp = deunit(tselect(Te_perp, :time, dt), u"eV")
-    end
-end
-
-add_temp_anisotropy!(df, Tp, Te, args...) =
-    add_temp_anisotropy!(df, Tp.para, Tp.perp, Te.para, Te.perp, args...)
-
-function compute_PSP_anisotropy_params!(psp_df)
-    Tp = PSP.read_proton_temperature(7:8)
-    Te = PSP.read_electron_temperature()
-    add_temp_anisotropy!(psp_df, Tp, Te)
-    compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
-end
-
-function compute_Wind_anisotropy_params!(df, tmin, tmax)
-    Wind_Tp2 = Wind.pTemp_T2(tmin, tmax; add_unit=false)
-    Wind_Te2 = Wind.eTemp_T2(tmin, tmax; add_unit=false)
-    add_temp_anisotropy!(df, Wind_Tp2, Wind_Te2, Minute(2))
-    compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
-end
-```
-
-```{julia}
 f = Figure(; size=(1200, 800))
 psp_event = filter_low_mva_quality(psp_df)[5, :]
-fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_config, Second(10))
+fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_conf, Second(10))
 @info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
-# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_config)
-# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_config)
-# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_config)
-# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_config, Second(10))
+# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_conf)
+# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_conf)
+# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_conf)
+# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_conf, Second(10))
 f
@@
 using Speasy
-using SPEDAS: tnorm_combine, tplot, DataSet
+using SPEDAS: tnorm_combine, DataSet
 using DimensionalData
-using CairoMakie
-# using GLMakie
+# using CairoMakie
+using GLMakie
 using Statistics
@@
 ```{julia}
-tmin_psp = DateTime("2021-01-14")
+tmin_psp = DateTime("2021-01-15")
 tmax_psp = DateTime("2021-01-20")
-tmin_wind = DateTime("2021-01-15")
+tmin_wind = DateTime("2021-01-17")
 tmax_wind = DateTime("2021-01-23")
@@
 
-tmin_psp = DateTime("2021-01-16")
-tmax_psp = DateTime("2021-01-19")
+# tmin_psp = DateTime("2021-01-16")
+# tmax_psp = DateTime("2021-01-19")
 # tmin_wind = DateTime("2021-01-17")
@@
 ```{julia}
-function modify_faxs_base!(faxs)
-    B_ax = faxs.axes[1]
-    B_ax.ylabel[] = 𝒀.B
-    V_ax = faxs.axes[3]
-    V_ax.ylabel[] = 𝒀.V
-    n_ax = faxs.axes[2]
-    n_ax.yscale[] = identity
-    n_ax.ylabel[] = 𝒀.n
-end
-
-function modify_faxs_vl!(faxs)
-    i = 1
-    T_ax = faxs.axes[end-3-i]
-    T_ax.ylabel[] = "T (eV)"
-
-    R_ax = faxs.axes[end-2-i]
-    ylims!(R_ax, 0.09, 0.85)
-
-    β_ax = faxs.axes[end-i]
-    β_ax.yscale[] = log10
-    ylims!(β_ax, 8e-2, 4e1)
-
-    A_He_ax = faxs.axes[end]
-    A_He_ax.yscale[] = identity
-    A_He_ax.ylabel[] = L"A_{\text{He}} (%)"
-    ylims!(A_He_ax, 0, 8)
-end
-
 f = Figure(; size=(800, 600))
-# faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...)
-modify_faxs_vl!(faxs)
+faxs = plot_PSP(f[1, 1], tmin_psp + Day(2), tmin_psp + Day(3), get_vl_ratio_ts(psp_df)...)
+modify_faxs_base!(faxs)
+# modify_faxs_vl!(faxs)
 f
@@
 ```{julia}
-let tmin = tmin_psp, tmax = tmax_psp
+let tmin = tmin_wind, tmax = tmin_wind + Day(3)
     f = Figure(; size=(800, 600))
-
-    faxs = plot_Wind(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(wind_df)...)
+    faxs = plot_Wind(f[1, 1], tmin, tmax, get_vl_ratio_ts(wind_df)...)
+    modify_faxs_base!(faxs)
     f
@@
 ```{julia}
-using SPEDAS: tvec
-using CairoMakie
-CairoMakie.activate!()
+# using CairoMakie
+# CairoMakie.activate!()
 
@@
 
-# for enc in 7:9
-plot_vl_ratio = true
+add_vl_ratio = true
 
@@
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
-
     legend = (; position=Top())
@@
     padding = (0, 30, 0, -30)
-
-    f = Figure(; size=(800, 600))
-
+    f = Figure(; size=(1000, 800))
     fname = "overview-$enc"
-
-    if plot_vl_ratio
+    if add_vl_ratio
         fname = "overview-vl-$enc"
@@
         modify_faxs_base!(faxs)
-        plot_vl_ratio && modify_faxs_vl!(faxs)
-
-        compute_Wind_anisotropy_params!(wind_df, tmin_wind, tmax_wind)
-        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind, get_vl_ratio_ts(wind_df)...; legend)
+        faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
         modify_faxs_base!(faxs)
-        plot_vl_ratio && modify_faxs_vl!(faxs)
     end
@@
     add_labels!(f[1, 2]; labels, open="(b.", padding)
+    display(f)
+    easy_save("overview-$enc-all")
 
-    easy_save(fname; formats=(:pdf,))
-    display(f)
-
-    # tvars_psp = (psp_B, psp_n, psp_V)
-    # tvars_wind = (wind_B, wind_n, wind_V)
-    # f = Figure(; size=(1200, 600))
-    # plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
-    # add_labels!(f[1, 1]; labels, open="(a.")
-    # tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
-    # add_labels!(f[1, 2]; labels, open="(b.")
     # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
     # add_labels!(f[1, 3]; labels, open="(c.")
-    # easy_save("overview-$enc-all")
 end
@@
 psp_df_taus = map([2, 4, 8, 16, 32]) do tau
-    psp_config["tau"] = tau
-    df = PSPAnisotropy.produce(psp_config, psp_config["timeranges"][1]...)
+    psp_conf["tau"] = tau
+    df = PSPAnisotropy.produce(psp_conf, psp_conf["timeranges"][1]...)
     @transform! df :tau = tau
@@
 wind_df_taus = map([2, 4, 8, 16, 32]) do tau
-    wind_config["tau"] = tau
-    df = PSPAnisotropy.produce(wind_config, wind_config["timeranges"][1]...)
+    wind_conf["tau"] = tau
+    df = PSPAnisotropy.produce(wind_conf, wind_conf["timeranges"][1]...)
     @transform! df :tau = tau
@@
 f = Figure(; size=(1200, 800))
-# let df = psp_df_taus[1], config = psp_config
+# let df = psp_df_taus[1], config = psp_conf
 begin
     df = @subset(wind_df_taus[1], :index_std .> 4)
-    config = wind_config
+    config = wind_conf
     event = filter_low_mva_quality(df)[5, :]
@@
 append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
-
-function alpha_layer(df, alpha)
-    psp_df = @rsubset(df, :id == "PSP"; view=true)
-    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
-    wind_df = @rsubset(df, :id == "Wind"; view=true)
-    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
-end
 ```

### 2025-09-29 notebooks/02_stats.qmd
feat: plotting figures

@@
 import AlgebraOfGraphics as AoG
+using LinearAlgebra
+using Accessors
 using Unitful
@@
 set_Z_theme!()
-formats = (:pdf,)
+formats = (:pdf,:png)
 ```
@@
 
+A_lens = @optic _.model.A
+
 @chain df begin
@@
     DC.compute_params!()
-    @transform!(
-        :B_n_mva_norm = abs.(:B_n_mva ./ :B_mag),
+    @transform! @astable begin
+        :Δ𝐁 = @. norm(:B_us - :B_ds)
+        :Δ𝐁_fit = @. 2 * passmissing(A_lens)(:model) |> abs
+        :Δ𝐁_norm = :Δ𝐁 ./ :B_mag
+        :Δ𝐁_fit_norm = :Δ𝐁_fit ./ :B_mag
+        :B_n_mva_norm = abs.(:B_n_mva ./ :B_mag)
         :duration = _float64.(ustrip.(:duration .|> u"s"))
-    )
+    end
     DC.classify!(:B_n_mva_norm)
@@
 fs = map([:mva]) do 𝐧
+    figure = (; size=(650, 400))
     𝒎 = var_mapping(; 𝐧)
@@
 
-    vars = [𝒎.l_log, 𝒎.j_log, 𝒎.l_norm_log, 𝒎.j_norm_log]
-    # , 𝒎.bn
-    labels = ["Thickness", "Current density", "Normalized thickness", "Normalized current density"]
+    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, :Δ𝐁 => log10 => L"\text{Log }|Δ𝐁|", :Δ𝐁_norm => log10 => L"\text{Log } |Δ𝐁|/B",]
+    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/B"]
+    # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
+    # append!(labels, ["Δ𝐁_fit", "Δ𝐁_fit_norm"])
 
@@
         AoG.density(; datalimits) * visual(Lines)
-    draw(plt, axis=(; yscale=log10))
+    draw(plt, scales(Layout=(; palette=wrapped(cols=4, by_col=true))); axis=(; yscale=log10), figure)
     easy_save("$fname-$𝐧"; formats, force=true)
@@
 let df = dropmissing(df, :duration)
-    df.duration = ustrip.(df.duration .|> u"s")
     layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
@@
     draw(plt, axis=(; yscale=log10))
-    easy_save("duration_dist"; formats, force=true)
+    easy_save("duration_dist"; formats)
 end
@@
     draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
-    easy_save("duration_dist_tau"; formats, force=true)
+    easy_save("duration_dist_tau"; formats)
 end
@@
 ```{julia}
+function alpha_layer(df, alpha)
+    psp_df = @rsubset(df, :id == "PSP"; view=true)
+    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
+    wind_df = @rsubset(df, :id == "Wind"; view=true)
+    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
+end
+
+```
+
+```{julia}
 for 𝐧 in [:mva]
@@
 
-    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id)
+    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id, layout=:id)
 
-    fig = Figure(size=(800, 300))
+    fig = Figure(size=(800, 400))
     axis = (; yscale=log10, xscale=log10)
@@
 
+    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
+    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
     spec1 = plt * mapping(𝒎.l, 𝒎.j)
     spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
-    spec3 = plt * mapping(:B_n_mva_norm, :ω)
-    spec4 = plt * mapping(:ΔV_ratio, :ΔV_cosθ)
+    spec3 = plt * mapping(:B_n_mva_norm => L"B_{n}/ B", :ω_in => L"ω_{in}")
+    spec4 = plt * mapping(:ΔV_ratio => L"|Δ𝐕| / |Δ𝐕_A|", :ΔV_cosθ => L"\cos \theta")
 
@@
     # add_labels!([ga, gb, gc])
-    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
+    easy_save("joint_properties-$𝐧"; formats, force=true)
     display(fig)
@@
 
-    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * vis
+    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * AoG.density(npoints=50)
     ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
@@
     # add_labels!([ga, gb, gc])
-    # easy_save("$fname-$enc-$𝐧"; formats, force=true)
     display(fig)
@@
     @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
-    @transform!(
-        :duration = Float64.(:duration),
-        :B_n_mva_norm = Float64.(:B_n_mva_norm),
-    )
+    @transform!(:B_n_mva_norm = Float64.(:B_n_mva_norm))
 end
+
+Bn_df = subset_𝐧(tdf, 𝐧)
+
+fig = Figure(; size=(800, 400))
+axis = (;)
+
+# layout = mapping(row=:id, col=:enc)
+layout = mapping(col=:id)
+plt = data(tdf) * layout
+den_vis = AoG.density(npoints=50)
+
+# vis = visual(Scatter; markersize=5)
+# line_vis = visual(linewidth=3)
+# Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
+# (vis + AoG.linear() * Q_group * line_vis)
+# (vis + AoG.smooth() * A_He_group * line_vis)
+
+Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm => L"B_n/B", :Q_sonnerup => abs  => L"Q") * layout * den_vis
+duration_Q_spec = plt * mapping(:duration => log10, :Q_sonnerup => L"Q") * den_vis
+σc_Q_spec = plt * mapping(:σ_c => L"σ_c", :Q_sonnerup => L"Q") * den_vis
+σr_Q_spec = plt * mapping(:σ_r => L"σ_r", :Q_sonnerup => L"Q") * den_vis
+
+draw!(fig[1, 1], Bn_Q_spec)
+draw!(fig[1, 2], duration_Q_spec)
+draw!(fig[2, 1], σc_Q_spec)
+draw!(fig[2, 2], σr_Q_spec)
+
+# add_labels!([ga, gb, gc])
+easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
+display(fig)
+```
+
+```{julia}
+view = true
+𝒎 = var_mapping(; 𝐧)
 
@@
 
-Bn_df = subset_𝐧(tdf, 𝐧)
-
 fig = Figure(; size=(1200, 800))
@@
 A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
-line_vis = visual(linewidth=3)
+den_vis = AoG.density(npoints=50)
 
-Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm, :Q_sonnerup => abs) * layout * (vis + AoG.linear() * line_vis * mapping(color=:id))
-duration_Q_spec = plt * mapping(:duration, :Q_sonnerup) * (vis + AoG.smooth() * Q_group * line_vis)
-σc_Q_spec = plt * mapping(:σ_c, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
-σr_Q_spec = plt * mapping(:σ_r, :Q_sonnerup) * (vis + AoG.linear() * Q_group * line_vis)
-A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup => abs) * layout * (vis + AoG.smooth() * A_He_group * line_vis)
-β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * (vis + AoG.smooth(; degree=4) * line_vis * mapping(color=:id))
+A_He_Q_spec = data(A_He_df) * mapping(:A_He => log10, :Q_sonnerup => abs) * layout * AoG.density(; npoints=50, datalimits=((-1, 1), (0, 1)))
+β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * AoG.histogram(; bins=50, datalimits=((-1, 1), (0, 1)))
 
-draw!(fig[1, 1], Bn_Q_spec)
-draw!(fig[1, 2], duration_Q_spec; axis=(; xscale=log10))
-draw!(fig[2, 1], σc_Q_spec)
-draw!(fig[2, 2], σr_Q_spec)
+# draw!(fig[1, 1], Bn_Q_spec)
 draw!(fig[3, 1], A_He_Q_spec)
@@
 # add_labels!([ga, gb, gc])
-easy_save("Q_sonnerup_joint_dist"; formats, force=true)
+# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
 display(fig)
@@
 2. The effect size is tiny (correlations ~-0.02 to -0.03) - practically negligible
-3. Only Q_sonnerup shows statistical significance due to the large sample size (10,684 events)
-4. The large sample size makes even tiny correlations statistically detectable, but they're not practically meaningful
 

### 2025-09-29 lib/PSP/src/PSP.jl

@@ -1,61 +1,105 @@
 module PSP
 using Unitful
+import CDAWeb
 using Speasy: SpeasyProduct, @spz_str
 using SpaceDataModel: DataSet
 
 import CSV
-using YAXArrays, NetCDF
+using NCDatasets
 using DataFrames, DimensionalData
+using DimensionalData: TimeDim, Ti
 using LaTeXStrings
+
+struct CDADimArray{N}
+    dataset::String
+    variable::String
+    kwargs::N
+end
+
+CDADimArray(dataset, variable) = CDADimArray(dataset, variable, (;))
+
+function (cdadim::CDADimArray)(tmin, tmax; kw...)
+    A = DimArray(CDAWeb.get_data(cdadim.dataset, cdadim.variable, tmin, tmax; orig = true, cdadim.kwargs..., kw...))
+    dim = dims(A, TimeDim)
+    T = eltype(dim)
+    return @view A[Ti(T(tmin) .. T(tmax))]
+end
+
+function (cdadim::CDADimArray)(trange; kw...)
+    return cdadim(trange[1], trange[2]; kw...)
+end
+
+function cda_DimArray(dataset, variable)
+    return (t0, t1; kw...) -> begin
+        A = DimArray(CDAWeb.get_data(dataset, variable, t0, t1; orig = true, kw...))
+        dim = dims(A, TimeDim)
+        T = eltype(dim)
+        return @view A[Ti(T(t0) .. T(t1))]
+    end
+end
 
 const psp_events = CSV.read("data/psp_events.csv", DataFrame; dateformat = "yyyy-mm-dd HH:MM")
 
 const B = spz"cda/PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"
-const B_SC = spz"cda/PSP_FLD_L2_MAG_SC/psp_fld_l2_mag_SC"
-const B_1MIN = spz"cda/PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"
+# const B_SC = spz"cda/PSP_FLD_L2_MAG_SC/psp_fld_l2_mag_SC"
+const B_SC = CDADimArray("PSP_FLD_L2_MAG_SC", "psp_fld_l2_mag_SC")
+# const B_1MIN = spz"cda/PSP_FLD_L2_MAG_RTN_1MIN/psp_fld_l2_mag_RTN_1min"
[…]

### 2025-09-29 src/PSPAnisotropy.jl

@@ -1,6 +1,5 @@
 module PSPAnisotropy
 using Speasy
-using SpacePhysicsMakie: tplot, tlines!
 using Dates
 using DataFrames, DataFramesMeta
 using CategoricalArrays
@@ -8,6 +7,7 @@ using DrWatson
 using Discontinuity: ids_finder
 using SPEDAS
 using LaTeXStrings
+using Discontinuity
 using TimeseriesUtilities: tsplit
 
 export get_timerange, workload, get_vl_ratio_ts
@@ -16,13 +16,14 @@ include("associations.jl")
 include("meta.jl")
 include("mva.jl")
 include("calc.jl")
+include("anisotropy.jl")
 
 using PSP
 using PSP: psp_events
 include("Wind.jl")
 include("THEMIS.jl")
 
-include("plot.jl")
+# include("plot.jl")
 
 function get_timerange(enc)
     Δt_min = Day(2)
@@ -76,7 +77,7 @@ function produce(conf_tr_pairs, taus; kw...)
     return df
 end
 
-function workload(taus, encs = 7:9; kw...)
+function workload(taus = Second.(2 .^ (1:6)), encs = 7:9; kw...)
     df = mapreduce(vcat, encs) do enc
         timeranges = get_timerange(enc)
         pairs = [psp_conf, wind_conf] .=> timeranges
@@ -91,24 +92,5 @@ export psp_conf, wind_conf, thm_conf
 psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He, :T => PSP.pTemp))
 wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, extra = (:A_He => Wind.A_He, :T => Wind.T_p_PLSP))
 thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, extra = ())
-
-function workload()
-    df = mapreduce(vcat, 7:9) do enc
-        tpsp, tearth = get_timerange(enc)
-        mapreduce(vcat, configs) do c
-            id = c["id"]
-            timerange = id == "PSP" ? tpsp : tearth
-            c["t0"] = Date(timerange[1])
-            c["t1"] = Date(timerange[2])
-            res, = produce_or_load(c, datadir(); tag = false) do c
[…]

### 2025-09-29 src/Wind.jl

@@ -1,12 +1,38 @@
 module Wind
 using Speasy: SpeasyProduct, getdimarray, @spz_str
-using DimensionalData: Y, DimStack, rebuild, DimArray
+import Speasy
+using DimensionalData
+using DimensionalData: X, Y, DimStack, rebuild, DimArray, TimeDim, Ti
 using PartialFunctions
 using Unitful
 using SPEDAS: DataSet, Product, replace_outliers!
 using LaTeXStrings
+import CDAWeb
 
-unitify(u) = (*)$u
+struct CDADimArray{N}
+    dataset::String
+    variable::String
+    kwargs::N
+end
+
+CDADimArray(dataset, variable; kw...) = CDADimArray(dataset, variable, (; kw...))
+
+function (cdadim::CDADimArray)(tmin, tmax; kw...)
+    A = DimArray(CDAWeb.get_data(cdadim.dataset, cdadim.variable, tmin, tmax; cdadim.kwargs..., kw...); replace_invalid = true)
+    dim = dims(A, TimeDim)
+    T = eltype(dim)
+    return @view A[Ti(T(tmin) .. T(tmax))]
+end
+
+function (cdadim::CDADimArray)(trange; kw...)
+    return cdadim(trange[1], trange[2]; kw...)
+end
+
+function spz_DimArray(dataset, variable; kw...)
+    return (t0, t1; _kw...) -> DimArray(SpeasyProduct("cda/$dataset/$variable")(t0, t1); kw..., _kw...)
+end
+
+unitify(u) = (*) $ u
 # WI_K0_SWE_RTN : Wind Solar Wind Experiment, Key Parameters in RTN [PRELIM]
 # WI_PM_3DP : Ion moments (computed on-board) @ 3 second (spin) resolution, PESA LOW, Wind 3DP (PRIMARY SCIENCE DATA)
 # WI_PLSP_3DP : Ion omnidirectional fluxes 0.4-3 keV and moments, often at ~24 second resolution, PESA Low, Wind 3DP
@@ -20,35 +46,37 @@ WI_ELM2_3DP_labels = ["Electron"] # "Electron (3DP, EESA Low)"
 
[…]

### 2025-09-29 src/associations.jl

@@ -77,8 +77,9 @@ function analyze_associations(data, variable_pairs; group_by=nothing, io = stdou
             y = parse_column(data, col2_spec)
 
             assoc_results = calculate_associations(x, y)
+            flag = any(a -> a.association > 0.1, assoc_results)
             for result in assoc_results
-                if !isnan(result.association)
+                if !isnan(result.association) && flag
                     println(io, "  $(result.measure_name): $(round(result.association, digits=4)) (n = $(result.n))")
                 end
             end

### 2025-09-29 src/plot.jl

@@ -5,12 +5,15 @@ using SPEDAS: tvec, setmeta, setmeta!
 using Statistics
 using CairoMakie
 using TimeseriesUtilities: times
-
-include("anisotry.jl")
+using SpacePhysicsMakie: tplot, tlines!
 
 export plot_candidate, plot_var_info!, plot_PSP, plot_Wind
 
+
+include("meta.jl")
+
 import .Labels as 𝑳
+import .YLabel as 𝒀
 
 export set_Z_theme!
 
@@ -24,15 +27,8 @@ set_Z_theme!() = begin
     )
 end
 
-
-# %%
-legend_kwargs = (position = :top, titleposition = :left)
-
-begin
-    enc_m = :enc => x -> "Enc $x"
-end
-
-log_axis = (yscale = log10, xscale = log10)
+const legend_kwargs = (position = :top, titleposition = :left)
+const log_axis = (yscale = log10, xscale = log10)
 
 function draw!(grid; axis = NamedTuple(), palettes = NamedTuple())
     return plt -> draw!(grid, plt; axis = axis, palettes = palettes)
@@ -89,20 +85,21 @@ function plot_candidate(f, event, config::AbstractDict, toffset = Second(0); add
     B_product = config["B"]
     V_product = config["V"]
 
-    B = B_product(t0, t1) |> setmeta!(; ylabel = "B", labels = 𝑳.B_RTN)
-    V = V_product(t0, t1) |> setmeta!(; ylabel = "V", labels = 𝑳.V_RTN)
-    n = config["n"](t0, t1)
+    B = setmeta!(DimArray(B_product(t0, t1); add_unit = true); ylabel = "B", labels = 𝑳.B_RTN)
+    V = setmeta!(DimArray(V_product(t0, t1); add_unit = true); ylabel = "V", labels = 𝑳.V_RTN)
+    n = DimArray(config["n"](t0, t1); add_unit = true)
 
     B_subset = tview(B, tmin, tmax)
 
-    B_mva = mva(B, B_subset) |> setmeta(; labels = 𝑳.B_LMN)
[…]

### 2025-10-04 index.qmd
update stats figures with new plots and visualizations

@@
 
-![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
+![](figures/overview-7-all.pdf){#fig-overview}
+
+![](figures/properties_hist-mva.pdf){#fig-properties-hist}
+
+![](figures/joint_properties-mva.pdf){#fig-joint-properties}
+
+![](figures/Alfvenicities.pdf)
+
+![](figures/Q_sonnerup_joint_dist_den.pdf)
+
+![](figures/B_n_ω_subset=true.pdf)
 

### 2025-10-04 notebooks/00_index.qmd
update stats figures with new plots and visualizations

@@
 wind_df = @rsubset(df, :id == "Wind"; view=true)
-thm_df = @rsubset(df, :id == "THEMIS"; view=true)p -
-         thm_conf["B"] = unitify("nT") ∘ thm_conf["B"]
+thm_df = @rsubset(df, :id == "THEMIS"; view=true)
 ```
@@
 for enc in 7:9
-    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
+    tmin_wind, tmax_wind = get_timerange(enc)[2]
     wind_df_enc = @rsubset(wind_df, :enc == enc; view=true)
     compute_Wind_anisotropy_params!(wind_df_enc, tmin_wind, tmax_wind)
+
+    thm_df_enc = @rsubset(thm_df, :enc == enc; view=true)
+    compute_THM_anisotropy_params!(thm_df_enc, tmin_wind, tmax_wind)
 end
@@
 ```{julia}
-psp_B = set(tnorm_combine ∘ PSP.B_1MIN; ylabel=𝒀.B, labels=𝑳.B_RTN)
-psp_V = set(PSP.V; ylabel=𝒀.V, labels=𝑳.V_RTN)
-psp_n = PSP.n_spi
-
-wind_B = set(tnorm_combine ∘ Wind.B_GSE_1MIN; ylabel=𝒀.B, labels=𝑳.B_XYZ)
-wind_V = replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=𝒀.V, labels=𝑳.V_XYZ)
-wind_n = set(Wind.n_p_K0; ylabel=𝒀.n, yscale=identity)
-```
-
-```{julia}
 tvars_themis = [
@@
 ```{julia}
-# using CairoMakie
-# CairoMakie.activate!()
-
 update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))
 
-add_vl_ratio = true
-
-for enc in 7:7
+for enc in 7:9
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
@@
     f = Figure(; size=(1000, 800))
-    fname = "overview-$enc"
-    if add_vl_ratio
-        fname = "overview-vl-$enc"
     faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
@@
     modify_faxs_base!(faxs)
-    end
 
@@
     easy_save("overview-$enc-all")
-
-    # tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
-    # add_labels!(f[1, 3]; labels, open="(c.")
 end
@@
 ```{julia}
+using Dates
 using Discontinuity: ids_finder

### 2025-10-04 notebooks/02_stats.qmd
update stats figures with new plots and visualizations

@@
 using AlgebraOfGraphics
+using AlgebraOfGraphics: data
 import AlgebraOfGraphics as AoG
@@
 set_Z_theme!()
-formats = (:pdf,:png)
+formats = (:pdf, :png)
 ```
@@
 fs = map([:mva]) do 𝐧
-    figure = (; size=(650, 400))
+    figure = (; size=(450, 600))
     𝒎 = var_mapping(; 𝐧)
@@
         @subset(.!isnan.(:L_n_mva_norm); view=true)
-        # @rsubset(((:id == "PSP") && :tau <= Second(2)) || (:id != "PSP" && :tau > Second(2))) # select current sheet events with tau <= 2s for PSP and tau > 2s for Earth
         subset_𝐧(𝐧)
@@
 
-    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, :Δ𝐁 => log10 => L"\text{Log }|Δ𝐁|", :Δ𝐁_norm => log10 => L"\text{Log } |Δ𝐁|/B",]
-    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/B"]
+    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, 𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
+    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]
     # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
@@
 
-    plt =
-        data(tdf) *
+    plt = AoG.data(tdf) *
           mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
-        # mapping(vars, row=AoG.dims(1) => renamer(labels), col=:type) *
           mapping(color=:id, linestyle=:enc) *
           AoG.density(; datalimits) * visual(Lines)
-    draw(plt, scales(Layout=(; palette=wrapped(cols=4, by_col=true))); axis=(; yscale=log10), figure)
+    f = draw(plt, scales(Layout=(; palette=wrapped(cols=2))); axis=(; yscale=log10), figure, legend=(; position=:top))
+    hide_facet_labels!(f)
+    rowgap!(f.figure.layout, 1)
     easy_save("$fname-$𝐧"; formats, force=true)
@@
 
+Notes: `V_l_ratio_max` and `ΔV_ratio` are pretty much similar
+
+![](../figures/Alfvenicities.png)
+
 ```{julia}
+update_theme!(;
+    Legend=(; framevisible=false, padding=(0, 0, -16, 0)),
+)
+let
     𝒎 = var_mapping(; 𝐧)
-
     datalimits = x -> quantile(x, [0.01, 0.99])
-
     tdf = @chain df begin
-    @subset(.!isnan.(:V_l_ratio); view=true)
+        dropmissing(:V_l_ratio)
+        @subset(.!isnan.(:V_l_ratio) .&& .!isnan.(:ΔV_cosθ); view=true)
         subset_𝐧(𝐧)
-    dropmissing(:V_l_ratio)
     end
 
-vars = [:Q_sonnerup => abs => "", :ΔV_ratio => identity => "", :V_l_ratio => identity => "", :V_l_ratio_max => identity => ""]
-# 𝒎.v_l_ratio, 𝒎.bn
-labels = ["Q_sonnerup", "Δ V ratio", "ΔV_l ratio", "Max ΔV_l ratio"]
+    ΔV_cosθ = :ΔV_cosθ => identity => L"\cos\;θ"
+    ΔV_ratio = :ΔV_ratio => identity => L"|Δ𝐕| / |Δ𝐕_A|"
+    dB_over_B = :dB_over_B => log10 => L"\text{Log } ΔB / ⟨B\;⟩"
+    dB_max_over_B = :dB_max_over_B => log10 => L"\text{Log } ΔB_{\text{max}} / ⟨B\;⟩"
+    Q_sonnerup = :Q_sonnerup => abs => ""
 
-plt =
-    data(tdf) *
-    mapping(vars, row=AoG.dims(1) => renamer(labels)) *
-    #   mapping(vars, col=:tau, row=AoG.dims(1) => renamer(labels)) *
-    mapping(color=:id, linestyle=:enc) *
+    spec = AoG.data(tdf) * mapping(color=:id) *
            AoG.density(; datalimits) * visual(Lines)
-draw(plt, axis=(; yscale=identity), facet=(; linkyaxes=:minimal))
-# easy_save("Alfvenicities"; formats, force=true)
-# draw(spec, scales(Layout=(; palette=wrapped(cols=2))); facet=(; linkyaxes=:none))
+
+    fig = Figure()
+    ga = draw!(fig[1, 1], spec * mapping(ΔV_ratio))
+    gb = draw!(fig[1, 2], spec * mapping(ΔV_cosθ))
+    gc = draw!(fig[2, 1], spec * mapping(dB_over_B))
+    gd = draw!(fig[2, 2], spec * mapping(dB_max_over_B))
+    add_labels!(fig; valign=:top, position=Left(), padding=(0, 37, 0, 0))
+    display(fig)
+    pretty_legend!(fig, ga)
+    easy_save("Alfvenicities"; formats, force=true)
+    # vars = [ΔV_cosθ, ΔV_ratio, dB_over_B, dB_max_over_B]
+    # plt = spec * mapping(vars, layout=AoG.dims(1) => renamer(labels))
+    # draw(plt, axis=(; yscale=log10), facet=(; linkyaxes=:minimal))
+end
 ```
@@
 
+![](../figures/joint_properties-mva.png)
+
 ```{julia}
@@
     wind_df = @rsubset(df, :id == "Wind"; view=true)
-    (data(thm_df) + data(wind_df)) * visual(; alpha) + data(psp_df)
+    (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha)) + AoG.data(psp_df)
 end
-
 ```
@@
 ```{julia}
+layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
+
 for 𝐧 in [:mva]
@@
     𝒎 = var_mapping(; 𝐧)
-
     tdf = @chain df begin
-        # @subset(:enc .== enc)
-        dropmissing()
+        dropmissing(:L_n_mva)
         @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
@@
 
-    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=6, legend=(; alpha=0.6)) * mapping(color=:id, marker=:id, layout=:id)
+    plt = alpha_layer(tdf, 0.3) *
+          visual(Scatter; markersize=6, legend=(; alpha=0.6)) *
+          mapping(color=:id, marker=:id, layout=:id => layout_func)
 
-    fig = Figure(size=(800, 400))
+    fig = Figure(; size=(400, 800))
     axis = (; yscale=log10, xscale=log10)
-    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))
 
-    ga = fig[1, 1]
-    gb = fig[1, 2]
-    gc = fig[2, 1]
-    gd = fig[2, 2]
-
-    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
-    # spec1 = plt * mapping(:Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
     spec1 = plt * mapping(𝒎.l, 𝒎.j)
     spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
-    spec3 = plt * mapping(:B_n_mva_norm => L"B_{n}/ B", :ω_in => L"ω_{in}")
-    spec4 = plt * mapping(:ΔV_ratio => L"|Δ𝐕| / |Δ𝐕_A|", :ΔV_cosθ => L"\cos \theta")
+    B_l_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
+    B_j_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
 
-    grid1 = draw!(ga, spec1; axis)
-    draw!(gb, spec2; axis)
-    draw!(gc, spec3)
-    draw!(gd, spec4; axis=(; limits=((0, 2), (-1, 1),)))
+    grid1 = draw!(fig[1, 1], spec1; axis)
+    grid2 = draw!(fig[2, 1], spec2; axis)
+    grid3 = draw!(fig[3, 1], B_l_spec; axis)
+    grid4 = draw!(fig[4, 1], B_j_spec; axis)
 
-    # pretty_legend!(fig, grid1)
-    # add_labels!([ga, gb, gc])
+    hide_facet_labels!.((grid2, grid3, grid4))
+
+    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 37, 0, 0))
+    display(fig)
     easy_save("joint_properties-$𝐧"; formats, force=true)
-    display(fig)
 end
 ```
+
+### In-plane rotation angle, Bn
+
+![](../figures/B_n_ω_subset=true.png) and ![](../figures/B_n_ω_subset=false.png)
+
+```{julia}
+layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
+
+for 𝐧 in [:mva], subset in (true, false)
+    normalization = :column
+    𝒎 = var_mapping(; 𝐧)
+    tdf = dropmissing(df, :B_n_mva_norm)
+    tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
+    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
+    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
+    f = draw(B_n_ω_spec)
+    colgap!(f.figure.layout, 10)
+
+    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
+    ff = f.figure[0, 1:3]
+    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
+    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
+    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
+    rowgap!(f.figure.layout, 4)
+    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
+    easy_save("B_n_ω_subset=$subset"; formats, force=true)
+end
+```
+
+### β vs A_He
+
+There are two populations for beta and alpha particles abundance, corresponding to different sources of solubility. Correlation exist.
 
@@
 
-    B_n_spec = plt * mapping(:B_n_mva_norm, :ω_in) * AoG.density(npoints=50)
     ΔV_spec = plt * mapping(:ΔV_ratio, :ΔV_cosθ) * (vis + AoG.linear() * ΔV_cosθ_map)
@@
 
-    draw!(fig[1, 1], B_n_spec; axis)
     draw!(fig[1, 2], ΔV_spec; axis=(; limits=((0, 2), (-1, 1),)))
@@
 
+![](../figures/Q_sonnerup_joint_dist_den.png)
+
 ```{julia}
-view = true
 𝒎 = var_mapping(; 𝐧)
 
-vars = [:B_n_mva_norm, :Q_sonnerup, :duration, :σ_c]
-
+let vars = [:Q_sonnerup, :duration, :σ_c]
     tdf = @chain df begin
         dropmissing(vars)
-    @rsubset(all(!isnan, (:B_n_mva_norm, :Q_sonnerup, :σ_c)); view=true)
-    @transform!(:B_n_mva_norm = Float64.(:B_n_mva_norm))
+        @rsubset(all(!isnan, (:ΔV_cosθ, :Q_sonnerup, :σ_c)); view=true)
     end
 
-Bn_df = subset_𝐧(tdf, 𝐧)
+    fig = Figure(; size=(500, 800))
+    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
 
-fig = Figure(; size=(800, 400))
-axis = (;)
+    Q_limit = (-0.992, 0.992) # mainly for plotting so not show (-1, 1) in ticks
+    ΔV_spec = plt * mapping(𝒎.ΔV_ratio, 𝒎.ΔV_cosθ) * AoG.density(; datalimits=((0, 1.1), (-1, 1)))
+    duration_Q_spec = plt * mapping(:duration, 𝒎.Q) * AoG.density(; datalimits=((0, 3.1), Q_limit))
+    σc_Q_spec = plt * mapping(:σ_c => L"σ_c", 𝒎.Q) * AoG.density()
+    σr_Q_spec = plt * mapping(:σ_r => L"σ_r", 𝒎.Q) * AoG.density(; datalimits=(Q_limit, Q_limit))
 
-# layout = mapping(row=:id, col=:enc)
-layout = mapping(col=:id)
-plt = data(tdf) * layout
-den_vis = AoG.density(npoints=50)
+    ff11, ff12, ff21, ff22 = fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]
+    grid1 = cdraw!(ff11, ΔV_spec)
+    grid3 = cdraw!(ff12, σc_Q_spec)
+    grid4 = cdraw!(ff21, σr_Q_spec)
+    grid2 = cdraw!(ff22, duration_Q_spec)
 
-# vis = visual(Scatter; markersize=5)
-# line_vis = visual(linewidth=3)
-# Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
-# (vis + AoG.linear() * Q_group * line_vis)
-# (vis + AoG.smooth() * A_He_group * line_vis)
+    for f in (ff11, ff12, ff21, ff22)
+        colgap!(Makie.content(f[1, 1]), 6)
+    end
 
-Bn_Q_spec = data(Bn_df) * mapping(:B_n_mva_norm => L"B_n/B", :Q_sonnerup => abs  => L"Q") * layout * den_vis
-duration_Q_spec = plt * mapping(:duration => log10, :Q_sonnerup => L"Q") * den_vis
-σc_Q_spec = plt * mapping(:σ_c => L"σ_c", :Q_sonnerup => L"Q") * den_vis
-σr_Q_spec = plt * mapping(:σ_r => L"σ_r", :Q_sonnerup => L"Q") * den_vis
-
-draw!(fig[1, 1], Bn_Q_spec)
-draw!(fig[1, 2], duration_Q_spec)
-draw!(fig[2, 1], σc_Q_spec)
-draw!(fig[2, 2], σr_Q_spec)
-
-# add_labels!([ga, gb, gc])
+    rowgap!(fig.layout, 4)
+    for g in (grid3, grid4)
+        ax = g[1].axis
+        ax.xlabelpadding[] = 1
+        ax.xlabelsize[] = 16
+    end
+    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 0, 0, -5))
+    hide_facet_labels!.((grid2, grid3, grid4))
     easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
     display(fig)
+end
 ```
 
+#### Q_sonnerup vs B_n
+
+Two populations for Q_sonnerup vs B_n: large B_n has larger Q_sonnerup. No strong correlation for small B_n groups.
+
 ```{julia}
-view = true
+let 𝐧 = :mva
     𝒎 = var_mapping(; 𝐧)
+    Bn_df = @chain df begin
+        @rsubset(all(isfinite, (:B_n_mva_norm, :Q_sonnerup)); view=true)
+        subset_𝐧(𝐧)
+    end
+    Bn_Q_spec = data(Bn_df) * mapping(𝒎.bn, :Q_sonnerup => L"Q", col=:id => layout_func) * AoG.density()
+    draw(Bn_Q_spec)
+end
+```
 
-A_He_df = @chain tdf begin
-    dropmissing(:A_He)
-    @transform!(:A_He = Float64.(only.(:A_He)))
-    @rsubset(:A_He < 10)
+#### Q_sonnerup vs A_He
+
+We observe very weak correlation for PSP when $A_{He}<1$, and no correlation for Wind. ![](../figures/A_He_Q_sonnerup.png)
+
+```{julia}
+let
+    𝒎 = var_mapping()
+    A_He_df = @rsubset(df, :A_He > 0, isfinite(:Q_sonnerup))
+    A_He_Q_spec = data(A_He_df) * mapping(:A_He, :Q_sonnerup, col=:id => layout_func) * AoG.density(; datalimits=((0, 5), (-1, 1)))
+    draw(A_He_Q_spec)
+    easy_save("A_He_Q_sonnerup")
 end
+```
 
-β_df = @chain df begin
-    @rsubset(all(!isnan, [:β, :Q_sonnerup]); view=true)
-    dropmissing([:β, :Q_sonnerup])
-    @transform!(:log_β = log10.(:β))
+#### Q_sonnerup vs β
+
+No obvious correlation for PSP and Wind ![](../figures/β_Q_sonnerup.png).
+
+```{julia}
+let
+    β_df = @rsubset(df, all(isfinite, (:β, :Q_sonnerup)); view=true)
+    layout = mapping(row=:id)
+    β_Q_spec = data(β_df) * mapping(:β => log10, :Q_sonnerup) * layout * AoG.density(; datalimits=((-1, 1), (-1, 1)))
+    draw(β_Q_spec)
+    easy_save("β_Q_sonnerup")
 end
-
-fig = Figure(; size=(1200, 800))
-axis = (;)
-
-layout = mapping(row=:id, col=:enc)
-plt = data(tdf) * layout
-vis = visual(Scatter; markersize=5)
-
-Q_group = mapping(group=:Q_sonnerup => >(0), color=:Q_sonnerup => >(0))
-A_He_group = mapping(group=:A_He => >(0), color=:A_He => >(0))
-den_vis = AoG.density(npoints=50)
-
-A_He_Q_spec = data(A_He_df) * mapping(:A_He => log10, :Q_sonnerup => abs) * layout * AoG.density(; npoints=50, datalimits=((-1, 1), (0, 1)))
-β_Q_spec = data(β_df) * mapping(:log_β, :Q_sonnerup => abs) * layout * AoG.histogram(; bins=50, datalimits=((-1, 1), (0, 1)))
-
-# draw!(fig[1, 1], Bn_Q_spec)
-draw!(fig[3, 1], A_He_Q_spec)
-draw!(fig[3, 2], β_Q_spec)
-
-# add_labels!([ga, gb, gc])
-# easy_save("Q_sonnerup_joint_dist"; formats, force=true)
-display(fig)
 ```

### 2025-10-04 notebooks/10_results.qmd
update stats figures with new plots and visualizations

@@
 ```{julia}
-ω_map = :rotation_angle => "rotation angle (deg)";
 v_l_ratio_map = :v_l_ratio => L"Δ V_{ion,l} / Δ V_{A,l}"

### 2025-10-04 src/PSPAnisotropy.jl

@@ -9,6 +9,9 @@ using SPEDAS
 using LaTeXStrings
 using Discontinuity
 using TimeseriesUtilities: tsplit
+using PartialFunctions
+
+include("data.jl")
 
 export get_timerange, workload, get_vl_ratio_ts
 
@@ -27,13 +30,13 @@ include("THEMIS.jl")
 
 function get_timerange(enc)
     Δt_min = Day(2)
-    Δt_max = Day(6)
+    Δt_max = Day(5)
     time = psp_events[enc, :Time]
     t0_psp = floor(time - Day(2), Day)
     t1_psp = ceil(time + Day(2), Day)
     t0_earth = t0_psp + Δt_min
     t1_earth = t1_psp + Δt_max
-    return (t0_psp, t1_psp), (t0_earth, t1_earth)
+    return (t0_psp, t1_psp), (t0_earth, t1_earth), (t0_earth, t1_earth)
 end
 
 export produce
@@ -70,7 +73,7 @@ function produce(conf, timerange, taus; split = Day(1))
 end
 
 function produce(conf_tr_pairs, taus; kw...)
-    df = mapreduce(vcat, conf_tr_pairs) do (conf, tr)
+    df = mapreduce(vcat $ (; cols = :union), conf_tr_pairs) do (conf, tr)
         @rtransform!(produce(conf, tr, taus; kw...), :id = conf["id"])
     end
     df.id = categorical(df.id; compress = true)
@@ -80,7 +83,7 @@ end
 function workload(taus = Second.(2 .^ (1:6)), encs = 7:9; kw...)
     df = mapreduce(vcat, encs) do enc
         timeranges = get_timerange(enc)
-        pairs = [psp_conf, wind_conf] .=> timeranges
+        pairs = [psp_conf, wind_conf, thm_conf] .=> timeranges
         @rtransform!(produce(pairs, taus; kw...), :enc = enc)
     end
     df.enc = categorical(df.enc; compress = true)
@@ -91,6 +94,6 @@ export psp_conf, wind_conf, thm_conf
 
 psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He, :T => PSP.pTemp))
[…]

### 2025-10-04 src/THEMIS.jl

@@ -11,6 +11,8 @@ using Speasy: SpeasyProduct, getdimarray
 using SPEDAS: DataSet, tsort, times, tmask!
 using Dates
 using Unitful
+using LaTeXStrings
+using ..PSPAnisotropy: CDADimArray
 
 using Intervals: Interval
 
@@ -18,23 +20,32 @@ function tTemp(x; dims = Ti)
     return mean.(eachslice(x; dims))
 end
 
-B_GSE = SpeasyProduct("THB_L2_FGM/thb_fgs_gseQ")
-B_FGL_GSE = SpeasyProduct("THB_L2_FGM/thb_fgl_gseQ")
+const B_GSE = SpeasyProduct("cda/THB_L2_FGM/thb_fgs_gseQ")
+const B_FGL_GSE = SpeasyProduct("cda/THB_L2_FGM/thb_fgl_gseQ")
 
-n_ion = SpeasyProduct("THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale = identity)
-n_elec = SpeasyProduct("THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
-n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
+const n_ion = SpeasyProduct("cda/THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale = identity)
+const n_elec = SpeasyProduct("cda/THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
+const n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
 
-V_GSE = SpeasyProduct("THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
+const V_GSE = SpeasyProduct("cda/THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
 
-pTemp = SpeasyProduct("THB_L2_ESA/thb_peif_avgtempQ"; labels = ["Proton"])
-eTemp = tTemp ∘ SpeasyProduct("THB_L2_MOM/thb_peem_t3_magQ"; labels = ["Electron"])
-T = DataSet("Temperature", (pTemp, eTemp))
+const pTemp = SpeasyProduct("cda/THB_L2_ESA/thb_peif_avgtempQ"; labels = ["Proton"])
[…]

### 2025-10-04 src/Wind.jl

@@ -21,7 +21,11 @@ function (cdadim::CDADimArray)(tmin, tmax; kw...)
     A = DimArray(CDAWeb.get_data(cdadim.dataset, cdadim.variable, tmin, tmax; cdadim.kwargs..., kw...); replace_invalid = true)
     dim = dims(A, TimeDim)
     T = eltype(dim)
-    return @view A[Ti(T(tmin) .. T(tmax))]
+    return if isempty(A)
+        A
+    else
+        @view A[Ti(T(tmin) .. T(tmax))]
+    end
 end
 
 function (cdadim::CDADimArray)(trange; kw...)
@@ -79,8 +83,8 @@ const n_p_e = DataSet("Density", (n_p_K0, n_e))
 const T_p_PLSP = CDADimArray("WI_PLSP_3DP", "MOM.P.AVGTEMP")
 
 function A_He(tmin, tmax; n_p = nothing)
-    n_p = DimArray(@something n_p n_p_nonlin(tmin, tmax); standardize = true)
-    n_α = DimArray(n_α_nonlin(tmin, tmax); standardize = true)
+    n_p = @something n_p n_p_nonlin(tmin, tmax)
+    n_α = n_α_nonlin(tmin, tmax)
     return n_α ./ n_p .* 100
 end
 

### 2025-10-04 src/anisotropy.jl

@@ -1,8 +1,8 @@
 using Discontinuity: compute_anisotropy_params!
-export compute_PSP_anisotropy_params!, compute_Wind_anisotropy_params!
+export compute_PSP_anisotropy_params!, compute_Wind_anisotropy_params!, compute_THM_anisotropy_params!
 
-function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt=Minute(1))
-    @rtransform! df begin
+function add_temp_anisotropy!(df, Tp_para, Tp_perp, Te_para, Te_perp, dt = Minute(1))
+    return @rtransform! df begin
         :Tp_para = tselect(Tp_para, :time, dt)
         :Tp_perp = tselect(Tp_perp, :time, dt)
         :Te_para = tselect(Te_para, :time, dt)
@@ -16,14 +16,24 @@ add_temp_anisotropy!(df, Tp, Te, args...) =
 
 function compute_PSP_anisotropy_params!(psp_df)
     Tp = PSP.read_proton_temperature(7:8)
-    Te = PSP.read_electron_temperature(; dir=datadir("electron_fit_Halekas"))
+    Te = PSP.read_electron_temperature(; dir = datadir("electron_fit_Halekas"))
     add_temp_anisotropy!(psp_df, Tp, Te)
-    compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+    return compute_anisotropy_params!(psp_df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
 end
 
 function compute_Wind_anisotropy_params!(df, tmin, tmax)
     Wind_Tp2 = Wind.pTemp_T2(tmin, tmax)
     Wind_Te2 = Wind.eTemp_T2(tmin, tmax)
     add_temp_anisotropy!(df, Wind_Tp2, Wind_Te2, Minute(2))
-    compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+    return compute_anisotropy_params!(df, :ion => (:Tp_para, :Tp_perp), :electron => (:Te_para, :Te_perp))
+end
+
+# ignore proton temperature anisotropy as it is not reliable
+function compute_THM_anisotropy_params!(df, tmin, tmax; dt = Second(10))
+    Te2 = THEMIS.eTemp_T2(tmin, tmax)
[…]

### 2025-10-04 src/data.jl

@@ -1,0 +1,23 @@
+using CDAWeb
+using DimensionalData
+using DimensionalData: TimeDim, Ti
+
+struct CDADimArray{N}
+    dataset::String
+    variable::String
+    kwargs::N
+end
+
+CDADimArray(dataset, variable; kw...) = CDADimArray(dataset, variable, (; kw...))
+
+function (cdadim::CDADimArray)(tmin, tmax; kw...)
+    A = DimArray(CDAWeb.get_data(cdadim.dataset, cdadim.variable, tmin, tmax; cdadim.kwargs..., kw...); replace_invalid = true)
+    dim = dims(A, TimeDim)
+    T = eltype(dim)
+    A_sorted = tsort(A)
+    return @view A_sorted[Ti(T(tmin) .. T(tmax))]
+end
+
+function (cdadim::CDADimArray)(trange; kw...)
+    return cdadim(trange[1], trange[2]; kw...)
+end

### 2025-10-04 src/plot.jl

@@ -115,7 +115,7 @@ _plasma_beta(T, n, B_mag) = setmeta(
     Discontinuity.plasma_beta.(tsync(T, n, B_mag)...); label = "β", units = ""
 )
 
-_tmean(x::AbstractArray{<:Number}) = tmean(x, Minute(8))
+_tmean(x::AbstractArray{<:Number}) = isempty(x) ? x : tmean(x, Minute(8))
 _tmean(x::AbstractArray) = map(_tmean, x)
 _tmean(x::DimStack) = tmean(x, Minute(8))
 _tmean(tuple) = map(_tmean, tuple)
@@ -204,6 +204,10 @@ function modify_faxs_base!(faxs)
 
     modify_A_He_ax!(faxs.axes[end - 1])
     modify_β_ax!(faxs.axes[end])
+
+    R_ax = faxs.axes[5]
+    ylims!(R_ax, 0.09, 0.85)
+    
     modify_N_ax!(faxs.axes[6])
     return
 end

### 2025-10-06 index.qmd
feat: reorganize paper structure with new abstract and discussion sections

@@
 
-# Motivation
+# Abstract
 
-Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
+In this study, we analyze three time intervals during which the Parker Solar Probe (PSP) was in close proximity to the Sun.
+We investigate current sheets (magnetic discontinuities) observed by PSP, as well as by the ARTEMIS and Wind missions.
 
-- How does the discontinuities change with the radial distance from the Sun?
+Using an automated detection method, we identify current sheets in the magnetic field data and examine their properties in conjunction with plasma parameters such as velocity, density, and temperature.
 
-- How is solar wind discontinuities formed? What is the physical mechanisms?
+We identified more than 45,000 current sheets across the three selected time intervals, including approximately 17,000 events from the Parker Solar Probe (PSP).
+Our analysis shows that the absolute current density decreases with increasing radial distance from the Sun, while the normalized current density—defined as the current density divided by the Alfvén current density—remains relatively constant across different heliocentric distances.
+In contrast, the current sheet thickness increases with radial distance, indicating that current sheets broaden as the solar wind expands.
+When normalized by the ion inertial length, however, the thickness shows a slight decrease.
+We also observe distinct distributions in the amplitudes of magnetic field jumps among the different missions.
+Furthermore, the current sheet thickness and current density are found to be strongly correlated, suggesting that thinner current sheets are associated with stronger current densities.
 
-  - Generated at or near the sun?
+Most current sheets exhibit only small variations in magnetic field magnitude, suggesting a predominantly force-free, rotational-discontinuity (RD)–like nature.
+However, significant deviations from the Walén relation are observed, even when pressure anisotropy is taken into account, indicating that anisotropy alone cannot explain the discrepancies expected for ideal RDs.
+Finally, we find that the Alfvénicity of the current sheets is strongly correlated with the cross helicity and residual energy of the ambient plasma, suggesting that the local current sheet dynamics are largely governed by the surrounding turbulent environment.
 
-  - Locally generated in the interplanetary space by turbulence?
+<!-- 
+In addition, we analyze the Alfvénicity of the current sheets and find that both Parker Solar Probe and Wind observations consistently show that the velocity-jump ratio is often smaller than unity.
+While the two missions reveal similar statistical trends, the alignment of the magnetic field and velocity jump directions differs, with Parker Solar Probe exhibiting a larger degree of angular misalignment.
+
+In contrast, other parameters such as plasma beta and the alpha-particle abundance do not show a significant influence, and no strong correlations are observed.
+-->
 
@@
 
-@lotekarKineticscaleCurrentSheets2022
-@perroneCoherentEventsIon2020
+Current sheets are ubiquitous mesoscale structures in the solar wind, where the magnetic field changes direction abruptly over ion-scale thicknesses, while their lateral extents can exceed typical magnetohydrodynamic (MHD) scales.
+These current sheets most readily identified from sharp magnetic-field rotations but can also be evident in simultaneous changes of plasma density, bulk velocity, and temperature.
 
-The study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind
+In turbulent solar wind plasmas, current sheets are widely recognized as signatures of intermittency, contributing to the non-Gaussian nature of magnetic field fluctuations and localized energy dissipation [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They play a crucial role in mediating the transfer of energy across scales, from large-scale MHD fluctuations down to ion and electron kinetic scales, and are believed to be important sites of plasma heating and particle acceleration [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
 
-Previous statistical studies of solar wind discontinuities in the inner heliosphere @marianiStatisticalStudyMagnetohydrodynamic1983 @liuCharacteristicsInterplanetaryDiscontinuities2021
+<!-- Because they concentrate gradients and localized dissipation, current sheets are central features of solar-wind intermittency and non-Gaussian magnetic fluctuations [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They are therefore important for understanding how energy cascades from large MHD scales to ion and electron kinetic scales, and for identifying sites of plasma heating and particle energization [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
+-->
 
-Alignement study of solar wind discontinuities @artemyevDynamicsIntenseCurrents2018
+Understanding the formation, structure, and evolution of current sheets at different heliocentric distances is therefore essential for elucidating the mechanisms that govern solar wind turbulence and heating.
+A number of statistical studies have investigated current sheet properties across a broad range of radial distances [@marianiStatisticalStudyMagnetohydrodynamic1983; @artemyevDynamicsIntenseCurrents2018; @perroneCoherentEventsIon2020; @liuCharacteristicsInterplanetaryDiscontinuities2021; @lotekarKineticscaleCurrentSheets2022; @vaskoKineticscaleCurrentSheets2022; @vaskoKineticScaleCurrentSheets2024].
+Despite this progress, several important gaps remain.
+First, many earlier studies rely on datasets obtained at different times and with instruments of varying temporal resolution, which complicates consistent comparisons across heliocentric distances.
+Few investigations have examined simultaneous observations from multiple radial positions [@velliUnderstandingOriginsHeliosphere2020, @telloniSpacecraftRadialAlignments2023], limiting our understanding of how current sheet properties evolve as the solar wind expands.
+Second, existing identification methods often depend on fixed thresholds—such as absolute magnetic-field jumps—or are highly sensitive to data resolution, as in the case of partial variance increment techniques.
+To enable meaningful cross-mission comparisons, more robust approaches based on normalized, resolution-independent criteria are needed.
+Finally, most prior work has classified discontinuities within the ideal MHD framework—for instance, distinguishing tangential from rotational discontinuities.
+While useful in some contexts and extensively studied, these categories become inadequate at ion scales, where kinetic and multi-fluid effects play a central role.
+In this study, we therefore move beyond strict MHD classifications and instead emphasize the Alfvénic character of current sheets—that is, the extent to which plasma and magnetic-field variations follow Alfvénic correlations [@shenComparingPlasmaAnisotropy2024].
+Although this perspective is fundamental for understanding the origin and evolution of current sheets, it has received relatively limited systematic attention.
 
-By indentifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions
+The Parker Solar Probe (PSP) mission offers an unprecedented opportunity to probe current sheets in the near-Sun environment with high cadence and to compare those observations with near-Earth measurements.
+In this study, we focus on three PSP perihelion intervals (Encounters 7–9) selected for their differing geometric alignments with the near-Earth spacecraft ARTEMIS and Wind.
+Encounter 8 features strong radial alignment, enabling sampling of similar solar wind streams while Encounter 7 exhibits weaker alignment and Encounter 9 places PSP roughly 180° away in longitude.
+These contrasting configurations enable a controlled examination of current sheet properties and, more broadly, provide insight into how those properties depend on the solar wind's source region.
+
+Using a robust automated detection algorithm, we identify and analyze more than 45,000 current sheets across the three intervals (≈17,000 from PSP).
+We systematically characterize their thickness, current density, magnetic-field jump, and Alfvénicity.
+The remainder of the paper is organized as follows: Section 2 describes datasets and methods; Section 3 presents results; and Section 4 discusses physical implications and conclusions.
+
+<!-- References
 
@@
 2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))
+-->
 
 # Dataset and method
+
+In this study, we utilize magnetic field and plasma measurements from multiple spacecraft.
+For the Parker Solar Probe (PSP), we use magnetic field data from the FIELDS instrument and plasma data from the Solar Probe ANalyzer (SPAN) suite.
+The proton and electron anisotropies are derived from the corresponding SPAN-Ion and SPAN-Electron measurements.
+For the Wind and ARTEMIS missions, magnetic field data are obtained from the onboard magnetometers, while plasma parameters are taken from the Faraday cup instrument on Wind and the corresponding plasma instrument on ARTEMIS.
 
@@
 
+## Methodology
+
+To identify current sheets, we employ an automated detection algorithm similar to that used in our previous study (Zhang et al., 2024).
+The magnetic field data are divided into consecutive time intervals, and the standard deviation within each interval is calculated and compared with those of adjacent intervals.
+A current sheet is identified when the standard deviation within an interval significantly exceeds that of its neighboring intervals, indicating a sharp magnetic field variation.
+
+Once the current sheets are identified, we apply minimum variance analysis (MVA) to transform the magnetic field and plasma data into the local LMN coordinate system, where L, M, and N correspond to the maximum, intermediate, and minimum variance directions, respectively.
+The spatial thickness of each current sheet is estimated by multiplying its temporal duration by the plasma velocity projected along the normal (N) direction.
+The current density is then derived accordingly.
+
+For each identified event, we select time steps immediately before and after the current sheet as the upstream and downstream intervals, respectively.
+The mean plasma density and temperature from these intervals are used to estimate the plasma pressure and pressure anisotropy factors.
+Using these parameters, we derive both the Alfvén velocity and a modified Alfvén velocity that accounts for the pressure anisotropy.
+Finally, we compute the cross helicity and residual energy within the same intervals to characterize the local solar wind conditions surrounding each current sheet.
+
 # Overview and Example of Current Sheets
@@
 
-![](figures/examples/psp_e2_example.png)
+![](figures/event-example.pdf){#fig-event-example}
+
+<!-- ![](figures/examples/psp_e2_example.png) -->
 
@@
 
+We analyze the Alfvénicity of the current sheets and find that both Parker Solar Probe and Wind observations consistently show that the velocity-jump ratio is often smaller than unity.
+While the two missions reveal similar statistical trends, the alignment of the magnetic field and velocity jump directions differs, with Parker Solar Probe exhibiting a larger degree of angular misalignment.
+
+Figure 1 presents the statistical distributions of current density, current sheet scale (or cycle length), and magnetic field jumps derived from different missions and time intervals.
+Despite the varying observation conditions, the normalized current density exhibits similar magnitudes across the Parker Solar Probe (PSP), Wind, and ARTEMIS datasets.
+In contrast, the current sheet scale increases systematically from PSP to ARTEMIS, suggesting a radial evolution as the solar wind expands.
+However, after normalization by local parameters, the current sheet scale shows a slight decrease.
+
+The magnetic field jump displays more complex behavior among the missions, with PSP, Wind, and ARTEMIS showing distinct distributions.
+This diversity may indicate the presence of two populations of current sheets in the near-Sun environment, possibly reflecting different formation mechanisms or solar wind regimes.
+
+Figure 2 shows the joint distributions between (a) current density and current sheet scale, (b) current density and magnetic field jump, and (c) current sheet scale and magnetic field jump.
+A clear negative correlation is observed between current density and current sheet scale, indicating that stronger current densities are generally associated with thinner current sheets.
+
 ![](figures/overview-7-all.pdf){#fig-overview}
@@
 ![](figures/properties_hist-mva.pdf){#fig-properties-hist}
+
+Figure 3 illustrates the parameters used to characterize the Alfvénicity of the current sheets.
+Two key quantities are considered: (1) the velocity jump across the current sheet, and (2) the variation in magnetic field magnitude across the same interval.
+The first panel presents the ratio of magnetic field magnitude before and after the current sheet, while the second panel shows the angular difference between the Alfvén velocity and the plasma velocity.
+
+In general, the magnetic field magnitude ratio is less than unity, with mean values of approximately 0.6 for the Parker Solar Probe and 0.5 for the Wind observations.
+The velocity angle distribution is concentrated near 0° and 180°, indicating that the plasma and Alfvén velocities are typically aligned or anti-aligned.
+The Wind data exhibit a somewhat broader angular distribution compared to PSP, suggesting a larger degree of deviation from ideal Alfvénic alignment.
+The variation in magnetic field magnitude across the current sheets is relatively small, implying that the magnetic field strength remains nearly constant while its direction rotates—consistent with the rotational nature of many observed current sheets.
 
@@
 
+To further investigate how the Alfvénicity of current sheets relates to other parameters, we combine the velocity jump ratio and the velocity jump angle into a single scalar parameter, Q, following the formulation introduced by Sonnerup (2016).
+The parameter Q, bounded between –1 and 1, quantifies the deviation from ideal Alfvénic behavior expected for a rotational discontinuity.
+
+We examine the relationship between Q and various plasma properties and find that most parameters show little or no correlation.
+However, two parameters exhibit strong correlations with Q: the cross helicity and the residual energy of the surrounding solar wind.
+Both quantities describe the Alfvénicity of the background solar wind rather than that of individual current sheets.
+Our results show that current sheet Alfvénicity increases with solar wind cross helicity and decreases with residual energy.
+
+Additionally, for the Parker Solar Probe observations, we find a weak positive correlation between the temporal duration of the current sheets and their Alfvénicity, with longer-duration current sheets tending to display slightly higher Alfvénicity.
+However, this trend may partly arise from instrumental limitations, as longer-duration events provide better temporal resolution for plasma measurements.
+
 ![](figures/Q_sonnerup_joint_dist_den.pdf)
+
+We also analyze the rotational characteristics of the current sheets and their relationship with the normal component of the magnetic field.
+The rotational profile provides insights into how the magnetic field vector changes direction across each current sheet.
+Our results show that the Parker Solar Probe observes a distinctly different distribution of rotation angles compared to the Wind and ARTEMIS missions.
+This discrepancy suggests that the orientation and rotational structure of current sheets evolve significantly as the solar wind propagates from the near-Sun environment to near-Earth distances.
 
@@
 Thickness and current density relationship, scale-dependent properties of current sheets in the solar wind
+
+Discussion
+
+Our analysis reveals several robust, physically meaningful trends that illuminate how current sheets evolve from the near-Sun environment sampled by Parker Solar Probe (PSP) to the near-Earth environment sampled by Wind and ARTEMIS.
+Below I synthesize the principal findings, interpret their physical significance, identify methodological caveats, and suggest targeted follow-ups.
+
+1. Alfvénicity is controlled by the background turbulence, not only by local sheet properties.
+The strong positive correlation between current-sheet Alfvénicity and the ambient cross-helicity, together with the negative correlation with residual energy, indicates that the degree to which a current sheet behaves like an ideal rotational discontinuity is largely set by the surrounding turbulence state.
+High cross-helicity (more Alfvénic background fluctuations) promotes velocity–magnetic-field alignment at the sheet and hence higher sheet Alfvénicity; conversely, large (negative) residual energy — a relative excess of magnetic over kinetic fluctuation energy — corresponds to less Alfvénic sheets.
+This pattern is consistent with a picture in which current sheets are embedded, and shaped, by the local turbulent cascade rather than being isolated structures created by a single local process.
+In other words, the macroscopic turbulence environment biases whether a boundary will appear Alfvénic or non-Alfvénic when sampled by a spacecraft.
+
+2. Stronger currents ↔ thinner sheets: intermittency and cascade interpretation.
+The pronounced anti-correlation between current density and sheet scale (cycle length) — stronger current density associated with smaller spatial thickness — is a hallmark of intermittency in MHD turbulence.
+In a turbulent cascade, gradients steepen locally and concentrate current into thin, intense sheets.
+That we observe similar normalized current densities across radial distances suggests the cascade produces structures that are, after normalization by local parameters (e.g., Alfvén speed), roughly self-similar.
+The increase of absolute cycle length with heliocentric distance (and the slight decrease after normalization) can be interpreted as geometric expansion and evolution of structures during propagation combined with changes in local plasma conditions.
+
+3. Two populations and the predominance of rotational behavior.
+The magnetic magnitude change across many sheets is small while the direction rotates, consistent with a predominance of rotational discontinuities (RDs).
+Yet the mission-dependent diversity in magnetic jump distributions and the suggestion of two populations (one with small |ΔB| and one with larger |ΔB|) point to coexisting RD-like and more tangential/discontinuous (TD-like) structures near the Sun.
+PSP’s distinct rotation-angle distribution relative to Wind/ARTEMIS indicates evolution: as the solar wind propagates, some RD-like structures may transform (via interactions, steepening, or merging) into structures with different jump statistics, or different source populations (e.g., switchback boundaries versus streamer-belt tangential discontinuities) could dominate at different radii.
+
+4. Why pressure anisotropy alone fails to explain the velocity vs. magnetic jumps.
+Our finding that pressure anisotropy does not reconcile the observed discrepancy between the magnetic-field-derived Alfvén velocity jump and the measured plasma velocity jump suggests that single-fluid MHD (even with scalar anisotropy corrections) is insufficient.
+Possible contributors include: multi-fluid effects (e.g., decoupling of alpha particles or beams from the proton bulk), Hall and finite-Larmor-radius physics at ion scales, kinetic pressure tensor terms, or wave/beam populations that modify the bulk velocity without a matching magnetic signature.
+This motivates direct inspection of ion distribution functions (alpha particles, proton beams), search for Hall or reconnection signatures, and targeted kinetic modeling (hybrid/PIC) to quantify non-MHD contributions.
+
+5. Temporal-duration effect: physical or instrumental?
+The weak positive relation between current-sheet duration and Alfvénicity (longer events appearing more Alfvénic) must be interpreted cautiously.
+Longer durations provide more plasma samples and therefore better statistical estimates of upstream/downstream velocities; thus part of the trend may be instrumental or sampling bias.
+Nevertheless, if a residual physical trend remains after accounting for resolution effects, it could indicate that more spatially extended sheets preserve the Alfvénic coupling between flows and fields more effectively than shorter, more transient sheets — again pointing to an intimate connection between sheet morphology and the ambient turbulence.
+
+6. Radial evolution, rotation profiles, and implications for solar-wind dynamics.
+The systematic differences in rotation-angle distributions (PSP versus Wind/ARTEMIS) suggest that current sheets do not simply convect unchanged: they undergo reconfiguration.
+Processes that can drive this evolution include differential expansion, interactions with other structures (compressive regions, shocks, stream interactions), and nonlinear turbulent evolution (coalescence, steepening).
+This evolution has practical implications: the dynamical role of current sheets in particle energization, wave generation, and transport will depend on location and on how their topology and Alfvénicity change with distance.
+
+7. Methodological caveats and uncertainties.
+Several limitations could affect quantitative interpretation and should guide follow-up analyses: (i) single-spacecraft MVA and thickness estimates carry uncertainties in the normal direction and the projection of velocity; (ii) current density estimated from ΔB/Δl assumes a 1D geometry and neglects possible multi-dimensional structure; (iii) time-resolution differences between magnetometers and plasma instruments (SPAN, Faraday cup) can bias velocity-jump estimates; and (iv) detection thresholds and interval selection in the automated algorithm can preferentially select certain sheet types.
+We therefore recommend sensitivity tests varying detection thresholds, bootstrapping MVA normals, and quantifying the effect of cadence by sub-sampling or synthetic down-sampling tests.
+
+8. Specific, actionable follow-ups.
+To strengthen the physical interpretation and disentangle competing hypotheses, we recommend:
+	•	Cross-checking events with high-cadence particle moments and full distribution functions (to examine alpha/beams and non-Maxwellian features).
+	•	Searching for localized signatures of Hall physics or reconnection (bipolar electron jets, outflow pairs, Hall magnetic-field patterns) in high-resolution fields and particle data.
+	•	Conditioning the statistics on solar-wind type (fast vs. slow, presence of switchbacks, stream origin) to see whether the two inferred populations map to flow regimes.
+	•	Running hybrid or kinetic simulations initialized with observed upstream parameters to test whether pressure-tensor or multi-species effects reproduce the velocity–field jump mismatch.
+	•	Expanding the radial coverage (include Solar Orbiter, STEREO where possible) or employing multi-point analysis to reduce geometric ambiguities.
+
+9. Concluding synthesis.
+Taken together, our results support a picture in which current sheets are predominantly turbulence-embedded, dynamically evolving structures whose Alfvénic character is governed more by the ambient solar-wind turbulence state (cross-helicity and residual energy) than by simple local pressure anisotropy.
+The tight coupling between sheet intensity and spatial scale, the presence of (at least) two structural populations, and the radial evolution of rotation profiles together point to a complex interplay of cascade intermittency, expansion effects, and kinetic physics.
+Resolving the remaining discrepancies will require higher-resolution particle data, multi-spacecraft constraints, and targeted kinetic modeling.
 

### 2025-10-06 notes.qmd
feat: reorganize paper structure with new abstract and discussion sections

@@
   - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
+
+# Motivation
+
+Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
+
+- How does the discontinuities change with the radial distance from the Sun?
+
+- How is solar wind discontinuities formed? What is the physical mechanisms?
+
+  - Generated at or near the sun?
+
+  - Locally generated in the interplanetary space by turbulence?
 

### 2025-10-06 notebooks/00_index.qmd
feat: finalize paper figures

@@
 using SPEDAS: setmeta, setmeta!
-using Beforerr: _theme_legend, easy_save
+using Beforerr: _theme_legend, easy_save, hideylabel!
 using PartialFunctions
@@
 df = workload()
-compute_params!(df)
-compute_Alfvenicity_params!(df)
 
@@
 ```{julia}
+compute_params!(df)
+compute_Alfvenicity_params!(df)
+
 compute_PSP_anisotropy_params!(psp_df)
@@
 ```{julia}
-f = Figure(; size=(1200, 800))
-psp_event = filter_low_mva_quality(psp_df)[5, :]
-fax, res_psp = plot_candidate(f[1, 1], psp_event, psp_conf, Second(10))
-@info "v_l_ratio" psp_event.V_l_ratio psp_event.V_l_ratio_max
-# res_thm = plot_candidate(f[1, 2], thm_df[10, :], thm_conf)
-# res_thm = plot_candidate(f[1, 2], thm_df[14, :], thm_conf)
-# res_thm = plot_candidate(f[1, 2], thm_df[17, :], thm_conf)
-# res_wind = plot_candidate(f[1, 3], wind_df[1, :], wind_conf, Second(10))
+let add_fit = true, add_Va = true
+    f = Figure(; size=(450, 400))
+    faxs, = plot_candidate(f[1, 1], filter_low_mva_quality(psp_df)[20, :], psp_conf, Second(4); add_fit, legend=nothing, add_Va)
+    faxs, = plot_candidate(f[1, 2], filter_low_mva_quality(thm_df)[12, :], thm_conf, Second(2); add_fit, add_Va)
+    hideylabel!.(faxs.axes)
+    add_labels!(f[1, 1]; position=Left(), padding=(30, -30, 0, 0), labels=1:3, open="(a.")
+    add_labels!(f[1, 2]; position=Left(), padding=(30, -30, 0, 0), labels=1:3, open="(b.")
+    # faxs, = plot_candidate(f[1, 3], filter_low_mva_quality(wind_df)[2, :], wind_conf, Second(6); add_fit)
+    # hideylabel!.(faxs.axes)
+    colgap!(f.layout, 1)
+    resize_to_layout!(f)
+    easy_save("event-example")
     f
+end
+```
+
+```txt
+  :t_us              => 2021-01-15T04:05:04.549
+  :t_ds              => 2021-01-15T04:05:17.957
+  :tstart            => 2021-01-15T04:05:04
 ```
@@
 ```
-
-## Thickness, current density comparison and Alfvénicity
-
-```{julia}
-using AlgebraOfGraphics
-using Discontinuity: compute_params!, compute_Alfvenicity_params!
-using Beforerr
-using Beforerr: add_labels!
-# using CairoMakie
-using StatsBase
-# CairoMakie.activate!()
-
-set_AoG_theme!()
-formats = (:pdf,)
-
-# df, configs = workload()
-compute_params!(df)
-
-# AoG fix
-using LaTeXStrings
-import AlgebraOfGraphics: append_unit_string
-append_unit_string(s::LaTeXStrings.LaTeXString, u::String) = s
-```
-
-```{julia}
-fname = "properties_xy_comp-enc"
-
-for enc in 7:9, 𝐧 in [:mva, :cross]
-    view = true
-    𝒎 = var_mapping(; 𝐧)
-
-    tdf = subset_𝐧(dropmissing(@subset(df, :enc .== enc; view)), 𝐧)
-    compute_Alfvenicity_params!(tdf)
-    plt = alpha_layer(tdf, 0.618) * visual(Scatter; markersize=8, legend=(; alpha=1)) * mapping(color=:id, marker=:id)
-
-    fig = Figure(size=(800, 300))
-    axis = (; yscale=log10, xscale=log10)
-    v_axis = (; yscale=log10, xscale=log10, limits=((2, 400), (2, 400)))
-
-    ga = fig[1, 1]
-    gb = fig[1, 2]
-    gc = fig[1, 3]
-
-    spec1 = plt * mapping(𝒎.l, 𝒎.j)
-    spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
-    spec3 = plt * mapping(𝒎.v_Alfven, 𝒎.v_ion)
-
-    grid1 = draw!(ga, spec1; axis)
-    draw!(gb, spec2; axis)
-    draw!(gc, spec3; axis=v_axis)
-
-    slopes = (1.0, 0.7, 0.4, 0.1)
-    foreach(slopes) do s
-        lines!(1 .. 1000, (*)$s, linestyle=:dash, label="$s")
-    end
-    axislegend("slope", position=:lt)
-
-    pretty_legend!(fig, grid1)
-    add_labels!([ga, gb, gc])
-    easy_save("$fname-$enc-$𝐧"; formats, force=true)
-    display(fig)
-end
-```
-
-![](../figures/properties_xy_comp-enc-7-mva.pdf)
-![](../figures/properties_xy_comp-enc-7-cross.pdf)
-![](../figures/properties_xy_comp-enc-8-mva.pdf)
-![](../figures/properties_xy_comp-enc-8-cross.pdf)
-![](../figures/properties_xy_comp-enc-9-mva.pdf)
-![](../figures/properties_xy_comp-enc-9-cross.pdf)
-
-```{julia}
-for enc in 7:9
-    tdf = filter_low_mva_quality(dropmissing(@subset(df, :enc .== enc; view=true), view=true))
-    data_layer = data(tdf)
-    legend = (; markersize=10, alpha=1)
-    plt = data_layer * visual(Scatter; markersize=4, alpha=0.618, legend) * mapping(color=:id, marker=:id)
-
-    fig = Figure(size=(800, 400))
-    axis = (; yscale=identity, xscale=identity)
-
-    ga = fig[1, 1]
-    gb = fig[1, 2]
-
-    spec1 = plt * mapping(𝒎.bn, 𝒎.ω)
-    spec2 = plt * mapping(𝒎.bn, 𝒎.ω_in)
-
-    grid1 = draw!(ga, spec1; axis)
-    draw!(gb, spec2; axis)
-
-    pretty_legend!(fig, grid1)
-    add_labels!([ga, gb])
-    display(fig)
-end
-```

### 2025-10-06 notebooks/.vdoc.a763f47c-8901-4bd3-9df6-8349fe894beb.jl

@@ -1,49 +1,0 @@
-#
-#
-#
-#
-timeranges = get_timerange(7)
-tmin, tmax = timeranges[1]
-taus = Second.(2 .^ (1:6))
-#
-#
-#
-timeranges = get_timerange(7)
-tmin, tmax = timeranges[1]
-tmax = tmin + Day(1)
-tau = taus[6]
-df = ids_finder(tmin, tmax, PSP.B_SC; tau)
-# df= produce(psp_conf, taus, timeranges[1])
-```
-#
-#
-#
-#
-#
-    # B = PSP.B_SC(tmin, tmax) |> DimArray
-
-time_interval = (DateTime("2021-01-14T11:41:42.440"), DateTime("2021-01-14T11:41:43.430"))
-time_interval = (DateTime("2021-01-15T07:27:39.754"), DateTime("2021-01-15T07:28:22.667"))
-time_interval = (DateTime("2021-01-14T09:34:44.300"), DateTime("2021-01-14T09:34:51.994"))
-time_interval = (DateTime("2021-01-15T12:37:14.741"), DateTime("2021-01-15T12:37:18.008"))
-time_interval = (DateTime("2021-01-15T17:19:52.777"), DateTime("2021-01-15T17:19:58.521"))
-B_p = DimArray ∘ PSP.B_SC
-B_mva_prod = Product(B_p, mva_transform)
-tplot([tnorm_combine ∘ B_p, B_mva_prod], time_interval...)
-#
-#
-#
-#
-#
-using Random
-
-f = Figure(size=(1800, 1000))
-
-rows = rand(eachrow(df), min(5, nrow(df)))
-for (plot_idx, i) in enumerate(rows)
-    plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
-end
-f
-#
-#
-#

### 2025-10-06 src/PSPAnisotropy.jl

@@ -94,6 +94,6 @@ export psp_conf, wind_conf, thm_conf
 
 psp_conf = @strdict(id = "PSP", B = PSP.B_SC, V = PSP.V_SC, n = PSP.n_spi, extra = (:A_He => PSP.A_He, :T => PSP.pTemp))
 wind_conf = @strdict(id = "Wind", B = Wind.B_GSE, V = Wind.V_GSE_3DP, n = Wind.n_p_3DP, extra = (:A_He => Wind.A_He, :T => Wind.T_p_PLSP))
-thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, extra = (:T => THEMIS.pTemp,))
+thm_conf = @strdict(id = "THEMIS", B = THEMIS.B_FGL_GSE, n = THEMIS.n_ion, V = THEMIS.V_GSE, extra = (:T => THEMIS.pTemp))
 
 end

### 2025-10-06 src/THEMIS.jl

@@ -21,13 +21,13 @@ function tTemp(x; dims = Ti)
 end
 
 const B_GSE = SpeasyProduct("cda/THB_L2_FGM/thb_fgs_gseQ")
-const B_FGL_GSE = SpeasyProduct("cda/THB_L2_FGM/thb_fgl_gseQ")
+const B_FGL_GSE = DimArray ∘ SpeasyProduct("cda/THB_L2_FGM/thb_fgl_gseQ")
 
 const n_ion = SpeasyProduct("cda/THB_L2_MOM/thb_peim_densityQ"; labels = ["Ion"], yscale = identity)
 const n_elec = SpeasyProduct("cda/THB_L2_MOM/thb_peem_densityQ"; labels = ["Electron"], yscale = identity)
 const n = DataSet("Density", [n_ion, n_elec]; yscale = identity)
 
-const V_GSE = SpeasyProduct("cda/THB_L2_MOM/thb_peim_velocity_gseQ") # 4.25 s time resolution
+const V_GSE = CDADimArray("THB_L2_MOM", "thb_peim_velocity_gseQ") # 4.25 s time resolution
 
 const pTemp = SpeasyProduct("cda/THB_L2_ESA/thb_peif_avgtempQ"; labels = ["Proton"])
 const eTemp = tTemp ∘ SpeasyProduct("cda/THB_L2_MOM/thb_peem_t3_magQ"; labels = ["Electron"])
@@ -50,7 +50,7 @@ const eTemp_T2 = para_perp_avg("e") ∘ eTemp_ani
 
 function get_themis_tmask(t0, t1)
     thx_v_gse = THEMIS.V_GSE(t0, t1)
-    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
+    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1] .> -200u"km/s") .| (thx_v_gse[:, 2] .< -50u"km/s")]
     dt = Minute(10)
     its = union([Interval(t - dt, t + dt) for t in _times])
     return tmask!(its)

### 2025-10-06 src/calc.jl

@@ -1,4 +1,5 @@
 using PlasmaFormulary
+import Discontinuity
 using Discontinuity: anisotropy
 using DataFramesMeta
 using StatsBase: mean
@@ -7,7 +8,7 @@ export Alfven_velocity_ts
 
 function Alfven_velocity_ts(B, n)
     n_mean = mean(parent(n))
-    return Alfven_velocity.(B, n_mean)
+    return Discontinuity.Alfven_velocity.(B, n_mean)
 end
 
 function anisotropy_ts(B, n, T3; kw...)
@@ -31,48 +32,6 @@ DEFAULT_B_UNIT = u"nT"
 DEFAULT_DENSITY_UNIT = u"cm^-3"
 DEFAULT_TEMP_UNIT = u"eV"
 
-"""
-Calculate the pressure anisotropy
-"""
-function calc_pressure_anisotropy!(
-        df;
-        B = "B.mean",
-        density = "n.mean",
-        ion_temp_para = "ion_temp_para",
-        ion_temp_perp = "ion_temp_perp",
-        e_temp_para = "e_temp_para",
-        e_temp_perp = "e_temp_perp",
-        B_unit = DEFAULT_B_UNIT,
-        density_unit = DEFAULT_DENSITY_UNIT,
-        temp_unit = DEFAULT_TEMP_UNIT,
-    )
-
-    B = df[:, B] .* B_unit
-    n = df[:, density] .* density_unit
-
-    if ion_temp_para in names(df) && ion_temp_perp in names(df)
-        ion_temp_para_u = df[:, ion_temp_para] .* temp_unit
-        ion_temp_perp_u = df[:, ion_temp_perp] .* temp_unit
-        df[:, :Λ_ion] = anisotropy(B, n, ion_temp_para_u, ion_temp_perp_u)
-    else
-        @info "Ion temperature columns not found"
-    end
-
-    if e_temp_para in names(df) && e_temp_perp in names(df)
-        e_temp_para_u = df[:, e_temp_para] .* temp_unit
-        e_temp_perp_u = df[:, e_temp_perp] .* temp_unit
-        df[:, :Λ_e] = anisotropy(B, n, e_temp_para_u, e_temp_perp_u)
-    else
-        @info "Electron temperature columns not found"
-    end
-
[…]

### 2025-10-06 index.qmd
feat: add citations and expand dataset descriptions for PSP, Wind and ARTEMIS missions

@@
 
+@huangTemperatureAnisotropyHelium2025 : alfvénic slow solar wind 
+@larosaSwitchbacksStatisticalProperties2021 : Switchbacks: statistical properties and deviations from Alfvénicity
+
 # Dataset and method
 
-In this study, we utilize magnetic field and plasma measurements from multiple spacecraft.
-For the Parker Solar Probe (PSP), we use magnetic field data from the FIELDS instrument and plasma data from the Solar Probe ANalyzer (SPAN) suite.
-The proton and electron anisotropies are derived from the corresponding SPAN-Ion and SPAN-Electron measurements.
+We utilize magnetic field and plasma measurements from the Parker Solar Probe (PSP) mission [@foxSolarProbeMission2016], ARTEMIS mission [@angelopoulosARTEMISMission2011], and Wind mission [@acunaGlobalGeospaceScience1995].
+For PSP, we utilized high-resolution magnetic field from the FIELDS instrument [@baleFIELDSInstrumentSuite2016] and proton, electron and alpha measurements from the FIELDS and SWEAP instruments [@kasperSolarWindElectrons2016].
+More specifically, the proton and electron temperature anisotropies are derived from the corresponding SPAN-Ion and SPAN-Electron measurements [@whittleseySolarProbeANalyzers2020; @liviSolarProbeANalyzer2022].
 For the Wind and ARTEMIS missions, magnetic field data are obtained from the onboard magnetometers, while plasma parameters are taken from the Faraday cup instrument on Wind and the corresponding plasma instrument on ARTEMIS.
@@
 
-For this study
-
 We utilized high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments aboard the Parker Solar Probe (PSP).
@@
 There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie
+ -->
+
+<!-- For the Wind data used in this work, the Solar Wind  Experiment Faraday cup measures the reduced VDFs of solar wind protons and helium along 40 angles every 92 s (K.
+Ogilvie  et al.
+1995), and the Magnetic Field Investigation provides the  magnetic field data (R.
+Lepping et al.
+1995; A.
+Koval & A.
+Szabo 2013).
+The proton temperature anisotropies are derived by fitting  the spectra with a convected bi-Maxwellian function (J.
+C.
+Kasper  et al.
+2007).
  -->

### 2025-10-22 article.qmd
docs: methods

--- 2024-10-10 article.qmd
@@
     affiliation: Space Sciences Laboratory, University of California, Berkeley
-code-links:
-  - href: https://www.overleaf.com/project/664f7b472768760cf7d6321c
-    text: Overleaf
-  - href: zotero://select/library/collections/L9JC7XAI
-    text: Zotero
+format:
+  html: default
+  latex: 
+    cite-method: natbib
+  typst: default
 ---
 
-# Plain Language Summary
+# Abstract
+
+We analyze three time intervals during which the Parker Solar Probe (PSP) was in close proximity to the Sun and investigate current sheets (magnetic discontinuities) observed by PSP, ARTEMIS, and Wind.
+Using an automated detection algorithm, we identify and examine the statistical properties of over 45,000 current sheets across the three intervals, including approximately 17,000 from PSP.
+The results show that current sheets broaden with increasing heliocentric distance, while their characteristic current density remains largely unchanged.
+The thickness and current density are strongly anti-correlated, indicating that thinner current sheets carry stronger currents, consistent with turbulent intermittency.
+Distinct distributions of magnetic field jumps and rotation angles are also observed among the different missions, suggesting structural evolution of current sheets as the solar wind expands.
+Most current sheets display small variations in magnetic field magnitude, indicating a predominantly force-free character.
+Significant deviations from the Walén relation persist even when pressure anisotropy is included, implying that anisotropy alone cannot explain the observed departures from ideal rotational discontinuities.
+Finally, the Alfvénicity of the current sheets correlates strongly with the cross helicity and residual energy of the surrounding solar wind, demonstrating that current sheet dynamics are largely governed by the ambient turbulent environment.
 
@@
 
-The study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind
+Current sheets are ubiquitous mesoscale structures in the solar wind, where the magnetic field changes direction abruptly over ion-scale thicknesses, while their lateral extents can exceed typical magnetohydrodynamic (MHD) scales.
+These current sheets most readily identified from sharp magnetic-field rotations but can also be evident in simultaneous changes of plasma density, bulk velocity, and temperature.
 
-Previous statistical studies of solar wind discontinuities in the inner heliosphere @marianiStatisticalStudyMagnetohydrodynamic1983 @liuCharacteristicsInterplanetaryDiscontinuities2021
+In turbulent solar wind plasmas, current sheets are widely recognized as signatures of intermittency, contributing to the non-Gaussian nature of magnetic field fluctuations and localized energy dissipation [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They play a crucial role in mediating the transfer of energy across scales, from large-scale MHD fluctuations down to ion and electron kinetic scales, and are believed to be important sites of plasma heating and particle acceleration [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
 
-Alignement study of solar wind discontinuities @artemyevDynamicsIntenseCurrents2018
+<!-- Because they concentrate gradients and localized dissipation, current sheets are central features of solar-wind intermittency and non-Gaussian magnetic fluctuations [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They are therefore important for understanding how energy cascades from large MHD scales to ion and electron kinetic scales, and for identifying sites of plasma heating and particle energization [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
+-->
 
-By indentifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions
+Understanding the formation, structure, and evolution of current sheets at different heliocentric distances is therefore essential for elucidating the mechanisms that govern solar wind turbulence and heating.
+A number of statistical studies have investigated current sheet properties across a broad range of radial distances [@marianiStatisticalStudyMagnetohydrodynamic1983; @artemyevDynamicsIntenseCurrents2018; @perroneCoherentEventsIon2020; @liuCharacteristicsInterplanetaryDiscontinuities2021; @lotekarKineticscaleCurrentSheets2022; @vaskoKineticscaleCurrentSheets2022; @vaskoKineticScaleCurrentSheets2024].
+Despite this progress, several important gaps remain.
+First, many earlier studies rely on datasets obtained at different times and with instruments of varying temporal resolution, which complicates consistent comparisons across heliocentric distances.
+Few investigations have examined simultaneous observations from multiple radial positions [@velliUnderstandingOriginsHeliosphere2020; @telloniSpacecraftRadialAlignments2023], limiting our understanding of how current sheet properties evolve as the solar wind expands.
+Second, existing identification methods often depend on fixed thresholds—such as absolute magnetic-field jumps—or are highly sensitive to data resolution, as in the case of partial variance increment techniques.
+To enable meaningful cross-mission comparisons, more robust approaches based on normalized, resolution-independent criteria are needed.
+Finally, most prior work has classified discontinuities within the ideal MHD framework—for instance, distinguishing tangential from rotational discontinuities.
+While useful in some contexts and extensively studied, these categories become inadequate at ion scales, where kinetic and multi-fluid effects play a central role.
+In this study, we therefore move beyond strict MHD classifications and instead emphasize the Alfvénic character of current sheets—that is, the extent to which plasma and magnetic-field variations follow Alfvénic correlations [@shenComparingPlasmaAnisotropy2024].
+Although this perspective is fundamental for understanding the origin and evolution of current sheets, it has received relatively limited attention.
+
+The Parker Solar Probe (PSP) mission offers an unprecedented opportunity to probe current sheets in the near-Sun environment with high cadence and to compare those observations with near-Earth measurements.
+In this study, we focus on three PSP perihelion intervals (Encounters 7–9) selected for their differing geometric alignments with the near-Earth spacecraft ARTEMIS and Wind.
+Encounter 7 features strong radial alignment, enabling sampling of similar solar wind streams while Encounter 8 exhibits weaker alignment and Encounter 9 places PSP roughly 180° away in longitude.
+These contrasting configurations enable a controlled examination of current sheet properties and, more broadly, provide insight into how those properties depend on the solar wind's source region.
+
+Using a robust automated detection algorithm, we identify and analyze more than 45,000 current sheets across the three selected intervals (approximately 17,000 from PSP).
+We systematically characterize their rotation profiles, thicknesses, current densities, magnetic field jumps, and Alfvénic properties.
+The remainder of this paper is organized as follows: Section 2 describes the datasets and analysis methods; Section 3 presents the results and discusses their physical implications; and Section 4 summarizes the main conclusions.
+
+<!-- References
 
@@
 
+“Knetter [2005] extended this work to intervals in 2002 and 2003 which also included fast wind intervals.
+He obtained similar results to above and amassed a final total collection of 366 discontinuities.
+All of the discontinuities had normal field components consistent with zero.
+He concluded that the discontinuities are best explained as TDs regardless of the amount of dB/B.” ([Vasquez et al., 2007, p.
+2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))
+-->
+
 # Dataset and method
 
-TODO: define alignment / conjunction
+In this study, we utilize magnetic field and plasma measurements from Parker Solar Probe (PSP) [@foxSolarProbeMission2016], ARTEMIS [@angelopoulosARTEMISMission2011] and Wind missions [@acunaGlobalGeospaceScience1995].
+For PSP, we use high-resolution magnetic field data from the FIELDS instrument [@baleFIELDSInstrumentSuite2016] and plasma data from the Solar Wind Electrons Alphas and Protons (SWEAP) suite [@kasperSolarWindElectrons2016].
+The proton and electron anisotropies are derived from the corresponding electrostatic analyzers' measurements: Solar Probe ANalyzer for Ions (SPAN-I) and Electrons (SPAN-E) [@liviSolarProbeANalyzer2022; @whittleseySolarProbeANalyzers2020].
+For ARTEMIS, we use magnetic field data measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity and density from the electrostatic analyzer instrument with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
+The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
 
-Our study focuses on the evolution of solar wind discontinuities within plasma parcels as they undergo expansion.
-We analyze datasets from the Parker Solar Probe (PSP) and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR, and Wind) at various radial distances in the inner heliosphere, during periods of conjunctions and alignments between PSP and these Earth-orbiting missions.
-
-To achieve this, we utilize a configuration where two spacecraft are radially aligned in the Heliographic (HG) frame, with the longitude fixed on the Sun.
-It is important to note that the plasma parcels observed by the two spacecraft may differ in composition, as solar wind particles propagate at varying velocities.
-For instance, protons often exhibit a beam in their velocity distribution function, while the thermal speed of electrons is much higher than their bulk speed.
-Nonetheless, observing plasma that passes through both spacecraft offers the best opportunity to study the evolution of solar wind discontinuities with minimal influence from other processes during propagation.
-It is also expected that these plasma parcels evolve due to heating and other processes.
-
-<!-- ::: {#fig-plasma-adiabatic-evolution .column-page}
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
-
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
-
-Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
-Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
-::: -->
-
-The plasma parcels in question are large-scale structures.
-As the scale size decreases below the mesoscale [@viallMesoscaleStructureSolar2021] (with radial sizes ranging from approximately 5 × 10³ km to 10⁷ km), it becomes increasingly unlikely to identify the same structure, depending on the latitude difference between the two spacecraft.
-Furthermore, although large-scale structures (especially density enhancements) can be identified as passing through both spacecraft [@berriotIdentificationSinglePlasma2024], it is nearly impossible to detect kinetic-scale structures, such as solar wind discontinuities (with time scales on the order of seconds), by both spacecraft simultaneously.
-Therefore, our study focuses on the statistical properties of solar wind discontinuities within the "same" large-scale structures that pass through both spacecraft.
-
-After identifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions, we apply the methodology described in [@???] to identify and characterize solar wind discontinuities.
-Generally, discontinuities observed by PSP are shorter (1-5 seconds) and exhibit higher current density.
-Consequently, we use different time windows for identifying discontinuities: 15 seconds for PSP and 30 seconds for Earth-orbiting missions.
-A example of the discontinuities observed by PSP is shown in @fig-examples.
-
-::: {#fig-examples .column-page}
-
-![](figures/examples/psp_e2_example.png)
-
-Solar wind discontinuities examples observed by PSP fitted by a logistic function in LMN coordinates.
-:::
-
-<!-- 
-PSP:
-SWEAP consists of four separate sensors that measure the ions and electrons that make up the plasma in the solar wind and solar corona.
-The Solar Probe ANalyzer (SPAN) instruments are electrostatic analyzers (ESAs) that use curved plates to measure the 3-D particle distribution from within the shadow cast by the spacecraft thermal shield.
-Two of the sensors are co-located on the ram side of the spacecraft: SPAN-Ai measures ions, and SPAN-Ae measures electrons.
-SPAN-B measures electrons and is on the anti-ram side of the spacecraft.
-The Solar Probe Cup (SPC) is a Faraday Cup instrument that is directly illuminated by the Sun and measures both ions and electrons.
-
-"Looking at your intervals, which occurred during the early phase of the mission when PSP was far from the Sun, I realize that the plasma data wasn't good for your purpose because (1) SPAN-ion during at least the first 3-4 orbits did not measure the solar wind well, since a good portion of the solar wind distributions was out of view of that instrument, and (2) data from SPC (Farady Cup) does not give good temperature data.
-I am wondering if you have conjunction events that occurred later, say starting Encounter 7, when data from SPAN would be accurate.
-If not, some parts of Encounters 4-6 might be OK."
+<!-- It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
+Therefore, any findings related to temperature anisotropy should be interpreted with caution.
 -->
 
-For this study
-
-We utilized high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments aboard the Parker Solar Probe (PSP).
-For the plasma data presented in the figures of this paper, we used the dataset from SPAN-i, which measures ions in the solar wind.
-Although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution, making it more suitable for analyzing discontinuities.
-Our analysis confirms that the results obtained from SPC are consistent with those derived from SPAN-i data.
-It is also worth noting that sqtn data from the Radio Frequency Spectrometer (RFS) and Low-Frequency Receiver (LFR) for density measurements is available.
-However, we generally find that the results obtained from RFS/LFR do not differ significantly from those derived from SPAN-i data.
+It is worth noting that for PSP, although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution.
+Plasma density estimates delivered by the quasi-thermal noise spectroscopy (QTN) is also available [@moncuquetFirstSituMeasurements2020].
+We generally find that the results using QTN data do not differ significantly from those derived from SPAN-i data.
 Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument’s view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.
@@
 <!-- 
-ARTEMIS:
-We use the following data collected by ARTEMIS P1: magnetic fields with a ∼4s spin resolution (Auster et al.
-2008), the ion bulk velocity v, and the ion (assumed to be proton) temperature (scalar) Tp calculated from velocity distributions measured at spin resolution by the Electrostatic Analyzer (ESA; McFadden et al.
-2008).
-Being designed for measurements of a hot, rarefied plasma in Earth’s magnetosphere, ESA typically overestimates the proton temperature in the solar wind, because the solar wind proton beam is narrower than ESA’s energy and angular resolution.
-TODO: check if the ESA is in solar wind mode
+E7,20.3,2021-01-17 17:40,Perihelion
+E8,15.9,2021-04-29 08:48,Perihelion
+E9,15.9,2021-08-09 19:11,Perihelion
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E7_orbit.png
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E8_orbit.png
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E9_orbit.png
 -->
 
-We utilized data collected by ARTEMIS, including magnetic fields measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity ($v$) and density ($n$), which were derived from velocity distribution data obtained by the Electrostatic Analyzer with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
-It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
-Therefore, any findings related to temperature anisotropy should be interpreted with caution.
+Our study investigates the evolution of current sheet properties during the radial expansion of the solar wind.
+To distinguish spatial variations from temporal effects, we analyze three distinct time intervals corresponding to Parker Solar Probe (PSP) Encounters 7 through 9, each characterized by different PSP–Earth alignments [@telloniSpacecraftRadialAlignments2023; @velliUnderstandingOriginsHeliosphere2020].
+Encounter 7 features a favorable alignment between PSP and Earth, enabling nearly simultaneous multi-point observations (PSP approached perihelion on 2021-01-17 17:40; data intervals are 2021-01-15 – 2021-01-20 for PSP and 2021-01-17 – 2021-01-25 for ARTEMIS and Wind).
+Encounter 8 exhibits moderate alignment (PSP perihelion at 2021-04-29 08:48; data intervals 2021-04-27 – 2021-05-02 for PSP and 2021-04-29 – 2021-05-04 for ARTEMIS and Wind).
+In Encounter 9, PSP and Earth are located at substantially different heliolongitudes, with most PSP footpoints lying on the far side of the Sun (PSP perihelion at 2021-08-09 19:11; data intervals 2021-08-07 – 2021-08-12 for PSP and 2021-08-09 – 2021-08-14 for ARTEMIS and Wind).
+By comparing these intervals, we assess how the derived current sheet properties depend on the relative geometry and temporal context of the observations.
+Our results show that although certain plasma parameters vary slightly among intervals, the overall statistical characteristics of the current sheets remain largely consistent.
+This suggests that the observed statistics are not strongly sensitive to either the relative geometry or the temporal context of the measurements.
+
+@fig-overview provides an overview of the selected time interval from Encounter 7, comparing measurements from the PSP (left panels) and Wind (right panels) missions.
+From top to bottom, the panels display 8-minute averages of the magnetic field magnitude, proton number density, and proton bulk flow speed, followed by ion and electron temperatures resolved in the parallel and perpendicular directions.
+To facilitate comparison, Wind data are scaled to $20 R_\odot$ using the empirical relations $B_{\text{scaled}}/B = ( 20 R_\odot / 1\ \text{AU} )^{-1.59}$, $n_{\text{scaled}}/n = ( 20 R_\odot / 1\ \text{AU} )^{-1.96}$ [@perroneRadialEvolutionSolar2019].
+The fifth and sixth panels show the median Alfvén ratio, $R_{VB} = |Δ 𝐕| / |Δ 𝐕_A|$, of the current sheets and the total number of current sheets identified within each four-hour window.
+Including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$ does not significantly affect the Alfvén ratio $R_{VB}^* = R_{VB} / \sqrt{1 - Λ}$; its average value is approximately 0.5 for PSP and 0.4 for Wind over the entire time interval.
+The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
+Panel (a.7) and (b.7) present the cross helicity and residual energy, which describe the Alfvénic nature and energetic balance of the ambient plasma, respectively, calculated every 8 minutes.
+The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind.
+These parameters offer critical insights into identifying the source regions of different solar wind streams [@altermanCrossHelicityHelium2025].
+
+::: {#fig-overview}
+
+![](figures/overview-7-all.png)
+
+Overview of Encounter 7 comparing PSP (left) and Wind (right) observations.
+Panels show 8-minute averages of (a.1, b.1) magnetic field magnitude, (a.2, b.2) proton density, (a.3, b.3) flow speed, (a.4, b.4) ion and electron temperatures, (a.5, b.5) Alfvén ratio, (a.6, b.6) current-sheet counts, (a.7, b.7) cross helicity and residual energy, (a.8, b.8) helium abundance, and (a.9, b.9) plasma beta.
+Wind measurements are radially scaled to $20 R_\odot$ for comparison.
+:::
+
+<!-- Reference
+> @lotekarKineticscaleCurrentSheets2022 Figure 1 presents an overview of the considered 10 day interval.
+Over this interval, the spacecraft was at radial distances from 0.17 to 0.24 au, that is, from 35 to 50 solar radii, and remained within the inward magnetic field sector without crossing the heliospheric current sheet (Phan et al.
+2020; Szabo et al.
+2020).
+No coronal mass ejections were observed in the considered interval (Phan et al.
+2020; Szabo et al.
+2020).
+The spacecraft was approximately corotating with the Sun and connected to the same coronal hole (Bale et al.
+2019; Badman et al.
+2020).
+Panels (a)–(d) present 1 minute averages of the magnetic field magnitude, proton flow velocity, densities, and temperatures of protons and electrons as well as plasma density estimates provided by the quasi-thermal noise spectroscopy.
+The magnetic field magnitude was about 100 nT at the perihelion on November 6, and around 50 nT as the spacecraft moved to a radial distance of 50 solar radii from the Sun on November 1 and 10.
+The solar wind was typically slow  with a proton flow velocity below 400 km s−1, except for the ≈20 hr period of fast solar wind between November 9 and 10.
+The three plasma density estimates in panel (c) are consistent with each other within a few tens of percent over the entire interval, except for the fast solar wind interval, where the proton densities were about 4 times smaller than the plasma density estimates provided by the quasi-thermal noise spectroscopy.
+We will use the electron density estimates, calibrated to best match proton densities and the results of quasi-thermal noise spectroscopy, as plasma density estimates.
+The proton temperature during the considered interval varied between about 10 and 100 eV, while the electron temperature remained around 30 eV.
+Panel (e) presents 1 minute averages of proton and electron betas and shows that both quantities varied in the range from 0.1 to 5.
+-->
+
+## Methodology
+
+To identify current sheets, we employ an improved automated detection algorithm adapted from previous studies [@zhangSolarWindDiscontinuities2025b; @liuMagneticDiscontinuitiesSolar2022].
+The magnetic field data are divided into consecutive time intervals, each lagged by a time $T$.
+For each interval, we compute the standard deviation of the vector magnetic field, $σ(𝐁)$, and compare it with those of the adjacent intervals, $σ(𝐁_{-} )$ and $σ(𝐁_{+})$.
+An interval is flagged as a potential current sheet when its standard deviation significantly exceeds those of its neighbors, indicating a sharp magnetic field variation: $σ(𝐁) > 2 \max(σ(𝐁_{-} ), σ(𝐁_{+}))$.
+For each candidate interval, we refine the boundaries of the potential current sheet by computing the distance between two magnetic field vectors, $d(t_a, t_b) = \|𝐁(t_a) - 𝐁(t_b)\|$.
+The leading and trailing edges, $t_a$ and $t_b$ ($t_a < t_b$), are defined such that $d(t_a, t_b)$ attains its maximum value within the interval.
+To minimize false detections—particularly those caused by wave-like or hole-like structures that may mimic current sheet signatures—we impose the additional requirement $|Δ𝐁| / \bar{B} \ge 1/10$.
+We also evaluate the magnetic field orientation across each candidate structure by computing the angles between magnetic field vectors at the leading and trailing edges and comparing them with the angles between each edge and the interval midpoint.
+Only intervals in which the edge-to-edge angle exceeds all interior angles are retained as valid current sheet candidates.
+Because current sheets span a range of spatial and temporal scales, we performed the identification procedure using multiple time lags ($T = 2, 4, 8, 16, 32, 64\ \mathrm{s}$).
+The resulting event lists from each search were merged into a comprehensive catalog after removing duplicates.
+A subset of automatically detected intervals was visually inspected.
+All verified cases exhibit clear current sheet–like signatures, confirming the robustness and reliability of the automated procedure.
+
+We also evaluated the Partial Variance of Increments (PVI) method for current sheet identification [@grecoPartialVarianceIncrements2017].
+Although the PVI technique is effective for detecting short-duration, kinetic-scale current sheets characterized by sharp gradients, it often fails to capture larger-scale structures that display smoother yet coherent magnetic field variations.
+In addition, the PVI method is highly sensitive to data resolution, complicating cross-mission comparisons where instruments have differing temporal cadences.
+For these reasons, we do not report PVI-based results here.
+
+Once the current sheets are identified, we apply a minimum variance analysis (MVA) to transform the magnetic field and plasma data into the local LMN coordinate system, where $L$, $M$, and $N$ correspond to the directions of maximum, intermediate, and minimum variance, respectively.
+The maximum variance component, $B_L$, is then fitted with a hyperbolic tangent profile to extract parameters characterizing each current sheet, following the standard Harris current sheet model [@harrisPlasmaSheathSeparating1962]: $B_L(t) = B_{L,i} \tanh (\frac{t-t_i}{Δt_i/2} ) + c_i$ where $B_{L,i}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_i$ is the detection time, $Δt_i$ is the temporal duration, and $c_i$ is a magnetic field offset.
+
+Assuming that the current sheets are one-dimensional, planar structures, their spatial scale (thickness) can be estimated once the normal direction is determined.
+The normal vector can be obtained either from the minimum variance direction given by MVA or from the cross product of the magnetic field vectors at the current sheet boundaries.
+However, previous studies have shown that the MVA-derived normal direction can often be unreliable [@knetterFourpointDiscontinuityObservations2004; @wangSolarWindCurrent2024].
+The accuracy can be improved by imposing additional constraints such as $Δ|B|/ |B| > 0.05$ or $ω > 60°$ [@liuFailuresMinimumVariance2023], where $Δ|B|$ denotes the change in magnetic field magnitude and $ω$ is the field rotation angle across the discontinuity.
+The cross-product method, on the other hand, requires that the magnetic field component along the normal direction ($B_n$) be small, making it unsuitable when $B_n$ is large.
+In this study, we apply both methods and report results based on the subset of events satisfying $Δ|B|/ |B| > 0.05$ or $ω > 60°$.
+The results derived using the cross-product method are presented in the Appendix.
+
+The spatial thickness of each current sheet is estimated as $δ = V_n \Delta t$, where $V_n$ is the plasma velocity projected along the normal direction.
+The current density associated with the main magnetic field reversal is calculated from $J_m = - \frac{1}{\mu_0 V_n} \frac{d B_l}{d t}$.
+Within our fitting framework, the magnetic field derivative can be approximated as $\max(dB_L/ dt) = 2 B_{L,i}/ Δt_i$.
+This approach provides a more robust estimate than direct differentiation, as it is less sensitive to measurement noise and limited temporal resolution.Mean proton density, temperature, and alpha-particle density values from each interval are used to compute the Alfvén velocity, pressure anisotropy factor, plasma beta, and alpha-particle abundance, thereby providing a comprehensive characterization of the plasma environment associated with each current sheet.
+the upstream and downstream conditions are defined using timestamps immediately before and after the current sheet boundaries, respectively, such that $Δ𝐕 = 𝐕_{downstream} - 𝐕_{upstream}$. 
+The cosine of the angle between the velocity jump $Δ𝐕$ and the Alfvén velocity jump $Δ𝐕_A$ is then calculated as $\cos θ = \frac{Δ𝐕 \cdot Δ𝐕_A}{\|Δ𝐕\| \|𝐕_A\|}$, serving as a measure of Alfvénic alignment.
+Finally, the cross helicity $σ_c = \frac{2 ⟨ δ 𝐕 \cdot δ 𝐁 ⟩}{ ⟨δ𝐕^2⟩ + ⟨δ𝐁^2⟩ }$ and residual energy $σ_r = \frac{⟨δ 𝐕^2⟩-⟨δ 𝐁^2⟩}{⟨δ 𝐕^2⟩+⟨δ 𝐁^2⟩}$ are computed within intervals extending from each current sheet edge to eight times the current sheet duration (or at least 30 s on either side).
+These parameters quantify the degree of Alfvénicity and the relative contributions of kinetic and magnetic energy fluctuations in the ambient solar wind.
 
 <!-- 
-WIND:
-Wind 3dp, PESA LOW 1 spin resolution ion (proton and alpha) moments
-Wind 3D Plasma Analyzer
-Instrument Description
-The Wind 3DP instrument consists of six different sensors.
-There are two electron (EESA) and two ion (PESA) electrostatic analyzers with different geometrical factors and field-of-views covering the energy range from 3 eV to 30 keV.
-There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie
+$$
+\begin{aligned} & \frac{E^{+}-E^{-}}{E^{+}+E^{-}}=\frac{2\langle\delta \boldsymbol{v} \cdot \delta \boldsymbol{b}\rangle}{\left\langle\delta \boldsymbol{v}^2\right\rangle+\left\langle\delta \boldsymbol{b}^2\right\rangle} \\ & \frac{E^v-E^b}{E^v+E^b}=\frac{\left\langle\delta \boldsymbol{v}^2\right\rangle-\left\langle\delta \boldsymbol{b}^2\right\rangle}{\left\langle\delta \boldsymbol{v}^2\right\rangle+\left\langle\delta \boldsymbol{b}^2\right\rangle}\end{aligned}
+$$
 -->
 
-The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
+@fig-event-example presents two representative current sheet examples observed by PSP (left panels) and ARTEMIS (right panels).
+From top to bottom, the panels display, in LMN coordinates, the magnetic field, proton velocity, and the shifted Alfvén velocity $𝐕_A = \frac{𝐁}{\sqrt{\mu_0 \rho}} - 𝐕_{A,0}$, where $𝐕_{A,0}$ is the Alfvén velocity at the center of the current sheet.
+The cosine of the angle between the velocity jump $Δ𝐕$ and the Alfvén velocity jump $Δ𝐕_A$ is approximately -0.82 for PSP and -0.95 for ARTEMIS, indicating strong anti-correlation.
+The corresponding Alfvén ratio $R_{VB}$ is approximately 0.32 for both PSP and ARTEMIS.
+
+::: {#fig-event-example}
+
+![](figures/event-example.png)
+
+Representative examples of current sheets observed by the Parker Solar Probe (PSP; panels a.1–a.3) and ARTEMIS (panels b.1–b.3) in the local LMN coordinate system.
+Panels (a.1) and (b.1) show the magnetic field components $B_L$, $B_M$, and $B_N$, together with the magnetic field magnitude $B$.
+The red dashed lines indicate the hyperbolic tangent fits used to derive current sheet parameters.
+Panels (a.2) and (b.2) display the corresponding proton bulk velocity components $V_L$, $V_M$, and $V_N$.
+Panels (a.3) and (b.3) show the shifted Alfvén velocity components $V_{A,L}$, $V_{A,M}$, and $V_{A,N}$.
+The vertical gray dashed lines mark the leading and trailing edges of each identified current sheet.
+
+:::
+
+<!-- Reference: 
+Assuming that the SWD structures are planar, the normal direction can be obtained by minimizing the variance of the magnetic field{\textquoteright}s normal component in MVA.
+However, previous studies have indicated that the normal direction obtained through MVA is frequently unreliable \cite<see discussion in>{knetterFourpointDiscontinuityObservations2004,wangSolarWindCurrent2024}.
+Improved accuracy can be achieved by either using the cross product of the magnetic field measured at the boundaries as the normal direction \cite{knetterFourpointDiscontinuityObservations2004} or by enforcing conditions such as $\ensuremath{\Delta}|{\bf B}|/|{\bf B}| > 0.05$ or $\ensuremath{\omega} > 60{\degree}$ \cite{liuFailuresMinimumVariance2023}, where $\ensuremath{\Delta}|{\bf B}|$ is the change in the magnitude of the magnetic field and $\ensuremath{\omega}$ is the field rotation angle across the discontinuity.
+The former approach requires a small magnetic field component ($B_n$) along the discontinuity normal, while the latter approach limits the dataset to a subset that satisfies these conditions.
+These two methods yield closely aligned normal directions when $B_n$ is small and either $\ensuremath{\Delta}|{\bf B}|/|{\bf B}| > 0.05$ or $\ensuremath{\omega} > 60{\degree}$ is satisfied.
+In our analysis, we applied both techniques and found that they yielded statistically consistent results.
+\rev{A direct comparison of the discontinuity properties obtained from these two methods is presented in panels (e-j) of Figure~\ref{fig-juno_sw_comparison} in the Appendix, using intervals from Juno's approach to Jupiter when solar wind parameters were available.}
+-->
+
+# Results and Discussion
+
+@fig-properties-hist presents the statistical distributions of current sheet thickness $δ$, current density $J$, and magnetic field jump magnitude $|Δ𝐁|$ derived from different missions and time intervals.
+For thickness and current density, we display here a subset of the all dataset where MVA normals are trustable.
+The result of using cross product for the current sheet normals are displayed in the appendix @fig-properties-hist-cross and do not show any significant difference.
+Note that we do not need to subset the dataset for magnetic field jump magnitude since it does not depend on the normal direction.
+To better understand how these properties relate to the local plasma environment, we normalize the current sheet thickness by the ion (proton) inertial length, $d_i=c/\omega_{pi}$, and the current density by the Alfvén current density, $J_A = e N V_A = B / \mu_0 d_i$.
+Both parameters represent natural plasma scales: the ion inertial length characterizes the spatial scale where ions decouple from the magnetic field, while the Alfvén current density corresponds to the characteristic current generated by the relative drift of electrons and ions moving at the local Alfvén speed $V_A$.
+These quantities are particularly relevant in studies of MHD turbulence and magnetic reconnection [@zhdankinStatisticalAnalysisCurrent2013; @franciMagneticReconnectionDriver2017].
+
+Despite differing heliocentric distances and instrumental conditions, the normalized current density $J_m / J_A$ shows remarkably similar distributions across the PSP, Wind, and ARTEMIS datasets.
+This suggests that the relative strength of current sheets, when expressed in local plasma units, is largely independent of radial distance from the Sun.
+In contrast, the absolute thickness $δ$ increases from PSP to ARTEMIS and Wind, indicating a broadening of current sheets with solar wind expansion.
+After normalization by the ion inertial length, however, the characteristic scale $δ / d_i$ decreases slightly with increasing distance.
+This trend is consistent with previous analyses using Juno observations between 1 and 5 AU [@zhangSolarWindDiscontinuities2025b] and Maven observations between 1 and 1.5 AU [@artemyevDynamicsIntenseCurrents2018], which found that normalized current density remains nearly constant while normalized thickness gradually decreases with heliocentric distance.
+Similar behavior has been reported by @madarDirectionalDiscontinuitiesInner2024 using Parker Solar Probe and Solar Orbiter data, where the thickness of rotational discontinuities in ion inertial length units decreases rapidly until approximately 0.3 AU.
+
+The distributions of magnetic field jumps ($|Δ𝐁|$ and $|Δ𝐁|/\langle|𝐁|\rangle$) exhibit pronounced differences across the missions.
+In particular, the PSP data display a markedly distinct distribution compared with Wind and ARTEMIS, characterized by substantially larger magnetic field jumps—even after normalization—and a relatively flatter tail in the probability density function.
+These large jumps indicate stronger magnetic field reversals in the near-Sun environment, likely associated with the frequent occurrence of switchbacks.
+Such switchbacks, especially those embedded within switchback patches, have been observed to dissipate with increasing heliocentric distance [@soniSwitchbackPatchesEvolve2024; @shiPatchesMagneticSwitchbacks2022].
+The difference in the shape of the probability density functions thus suggests the coexistence of multiple populations of current sheets in the near-Sun region, potentially generated by distinct physical mechanisms or linked to different solar wind source regions.
+As the solar wind expands and the turbulence undergoes nonlinear evolution [@telloniObservationModelingSolar2022; @telloniEvolutionSolarWind2021], these separate populations likely interact and merge, resulting in the smoother and more homogeneous distributions observed at 1 AU.
+
+::: {#fig-properties-hist}
+![](figures/properties_hist-mva.png)
+
+Probability density functions (PDFs) of current sheet properties obtained from different missions (color-coded) and encounters (distinguished by line styles).
+The left column shows unnormalized quantities, while the right column presents values normalized by characteristic plasma scales.
+From top to bottom, panels display the distributions of (a) current sheet thickness $δ$ and its normalized form $δ / d_i$; (b) current density $J_m$ and normalized current density $J_m / J_A$; and (c) magnetic field jump magnitude $|Δ𝐁|$ and its normalized value $|Δ𝐁| / \langle |𝐁| \rangle$.
+The ion inertial length is $d_i = c / \omega_{pi}$, and the Alfvén current density is $J_A = e N V_A = B / \mu_0 d_i$.
+:::
+
+@fig-joint-properties presents the joint distributions between (a) current density and current sheet thickness, (b) normalized current density and normalized thickness, (c) normalized thickness and normalized magnetic field jump, and (d) normalized current density and normalized magnetic field jump.
+A clear inverse correlation is evident between the (normalized) current density and (normalized) current sheet thickness, indicating that stronger currents are generally associated with thinner sheets—that is, smaller-scale current sheets tend to be more intense.
+After normalization, the scatter distributions of current density versus thickness are highly similar across different missions, both in overall shape and in the range of values.
+This similarity suggests that the statistical relationship between current density and scale is largely independent of heliocentric distance.
+In contrast, the relationship between the magnetic field jump and current sheet thickness, shown in Panel (c), is relatively weak.
+For a given range of magnetic field jump amplitudes, the corresponding spatial scales exhibit a broad distribution, spanning up to two orders of magnitude.
+Moreover, as seen in Panel (d), there is no clear one-to-one correspondence between the magnetic field jump amplitude and the current density.
+Scale-dependent properties of current sheets have been reported by several previous studies using PSP, Wind, and Ulysses observations [@lotekarKineticscaleCurrentSheets2022; @vaskoKineticscaleCurrentSheets2022; @vaskoKineticScaleCurrentSheets2024].
+However, whereas earlier studies primarily focused on kinetic-scale current sheets, our analysis extends this investigation to a broader range of spatial scales—covering nearly two additional orders of magnitude in the logarithmic space of normalized current density and normalized current sheet thickness.
+Similar trends are found when the current sheet normal is determined using the magnetic field cross-product method rather than the minimum variance analysis.
+This consistency across methods confirms that the observed correlations are not strongly affected by the specific approach used to estimate the current sheet geometry.
+
+::: {#fig-joint-properties}
+![](figures/joint_properties-mva.png)
+
+Joint probability distributions of (a) current density versus current sheet thickness, (b) normalized current density versus normalized current sheet thickness, (c) normalized current sheet thickness versus magnetic field jump magnitude, and (d) normalized current density versus normalized magnetic field jump magnitude.
+:::
+
+For an ideal MHD rotational discontinuity (RD), the plasma velocity and magnetic field variations satisfy the Walén relation, $Δ 𝐕 = \pm Δ 𝐕_A$, and the force-free condition ( $Δ B \approx 0$) holds across the current sheet.
+The Walén relation requires agreement in both magnitude and direction between the plasma velocity change and the corresponding Alfvén velocity change.
+However, most observed current sheets deviate from these ideal conditions.
+
+To quantify the degree of Alfvénicity and the deviations from ideal RD behavior, we examine both the magnitude and angular differences between $Δ 𝐕$ and $Δ 𝐕_A$, as well as the variation in magnetic field strength across each current sheet.
+@fig-Alfvenicities summarizes the statistical results.
+Panel (a) shows the ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude.
+Across all missions, the ratio is generally less than unity, with mean values of approximately 0.6 for PSP and 0.5 for the combined Wind and ARTEMIS datasets.
+Panel (b) displays the cosine of the angle between the velocity and Alfvén velocity jumps.
+All missions show clustering near 0° and 180°, corresponding to correlated and anti-correlated states, respectively.
+PSP observations exhibit stronger alignment (cosine values closer to ±1), whereas Wind and ARTEMIS data show a broader angular spread.
+Panels (c) and (d) present the fractional change in magnetic field magnitude across current sheets.
+These variations are small (about 0.1 on average) for all missions, with PSP showing slightly smaller changes than Wind and ARTEMIS.
+This indicates that most current sheets are nearly incompressible, consistent with an approximately force-free magnetic structure.
+
+We also calculate the Alfvén velocity including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$, for PSP and Wind observations when the necessary plasma data are available.
+In most cases, including this anisotropy correction does not significantly alter the velocity-jump ratio.
+The persistent discrepancy between the observed ratios ($R < 1$) and the predictions of anisotropic MHD theory may have several explanations.
+First, the limited temporal resolution of the plasma anisotropy measurements—typically much lower than that of the magnetic field data—may cause underestimation of instantaneous variations at current sheet crossings [@huangProtonTemperatureAnisotropy2020; @shenComparingPlasmaAnisotropy2024].
+Second, kinetic-scale magnetic discontinuities often deviate from the assumptions of MHD theory: their non-Maxwellian particle velocity distributions, including plasma agyrotropies and field-aligned beams [@artemyevIonNongyrotropySolar2020; @neukirchKineticModelsTangential2020], are not accounted for in the fluid equations but can strongly influence the measured velocity ratios.
+Finally, uncertainties in deriving the parallel and perpendicular temperatures—typically obtained from nonlinear fits to complex velocity distribution functions—may introduce additional errors, especially when multiple particle populations are present [@huangProtonTemperatureAnisotropy2020; @halekasElectronsYoungSolar2020].
+
+::: {#fig-Alfvenicities}
+
+![](figures/Alfvenicities.png)
+
+Statistical distributions of parameters used to characterize the Alfvénicity of current sheets: (a) ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude, (b) cosine of the angle between the two vectors, (c) the variation in magnetic field magnitude between the leading and trailing edges of each current sheet; and
+(d) the maximum variation in magnetic field magnitude observed within each current sheet.
+
+:::
+
+To further investigate the physical origins of the observed deviations from Alfvénic behavior, we use a single scalar parameter, $Q^{ \pm}$, introduced by [@sonnerupQualityMeasureWalen2018], to quantify the Alfvénicity of current sheets and examine how $Q^{ \pm}$ correlates with key current sheet and plasma parameters.
+
+The parameter $Q^{\pm}$ is defined as $Q^{\pm} = \pm \left(1 - \frac{|\Delta 𝐕 \mp \Delta 𝐕_A|}{|\Delta 𝐕| + |\Delta 𝐕_A|}\right)$, which combines both magnitude and directional discrepancies between the velocity and Alfvén velocity jumps, and satisfies $-1 < Q^{\pm} < 1$.
+The upper sign is used for cases where $\cos \theta > 0$ and the lower sign for $\cos \theta < 0$.
+Values of $Q^{\pm}$ approaching ±1 correspond to highly Alfvénic behavior.
+The joint distribution of $|\Delta 𝐕| / |\Delta 𝐕_A|$ and $\cos \theta$ is shown in the first panel of @fig-Q_sonnerup_joint_dist_den.
+
+::: {#fig-Q_sonnerup_joint_dist_den}
+
+![](figures/Q_sonnerup_joint_dist_den.png)
+
+(a) Joint distribution of the velocity-jump ratio ($|\Delta 𝐕| / |\Delta 𝐕_A|$) and the cosine of the alignment angle ($\cos \theta$), used in computing the Sonnerup ($Q^{\pm}$) parameter.
+(b) Joint distribution of cross helicity ($\sigma_c$) and ($Q^{\pm}$).
+(c) Joint distribution of residual energy ($\sigma_r$) and ($Q^{\pm}$).
+(d) Joint distribution of temporal duration and ($Q^{\pm}$).
+
+:::
+
+We examine the relationship between $Q^{\pm}$ and various current sheet and ambient solar wind properties.
+Most parameters show little or no correlation with $Q^{\pm}$; however, two quantities exhibit strong correlations: the cross helicity $\sigma_c$ and residual energy $\sigma_r$ of the surrounding solar wind.
+These parameters describe, respectively, the degree of velocity–magnetic field correlation and the partition of energy between velocity and magnetic field fluctuations.
+Both serve as indicators of the Alfvénic character of the background solar wind rather than of individual current sheets.
+
+Panels (b) and (c) of @fig-Q_sonnerup_joint_dist_den show that the Alfvénicity of current sheets, represented by $Q^{+}$, increases with higher cross helicity and larger (more positive) residual energy, while $Q^{-}$ increases with higher cross helicity and smaller (more negative) residual energy.
+This trend suggests that current sheets embedded within highly Alfvénic solar wind streams tend to preserve stronger velocity–magnetic field alignment, whereas those located in more turbulent or energy-imbalanced regions—where magnetic energy $(E_B)$ exceeds kinetic energy $(E_V)$—exhibit greater departures from Alfvénic expectations.
+
+Additionally, observations reveal a weak positive correlation between $Q^{\pm}$ and the temporal duration of current sheets, as shown in Panel (d) of @fig-Q_sonnerup_joint_dist_den.
+Longer-duration current sheets tend to exhibit slightly higher $Q^{\pm}$ values, suggesting a more coherent Alfvénic structure.
+However, this correlation may be partially influenced by instrumental limitations, since longer events are more reliably resolved in plasma velocity measurements.
+Other plasma parameters, such as plasma beta and alpha-particle abundance, show no significant correlation with $Q^{\pm}$, implying that the Alfvénic nature of current sheets is primarily governed by the local turbulent environment rather than by large-scale plasma conditions.
+
+Since the normal component of the magnetic field plays a key role in determining both the spatial scale and the associated current density, we next examine the rotational characteristics of the current sheets and their relationship with the normalized normal magnetic field component, $B_N/B$.
+@fig-B_n_ω shows the distributions of the in-plane rotation angle (also referred to as the shear angle) and the normalized normal component $B_N/B$, along with their joint distributions for different missions.
+Panel (a) reveals that PSP observes a distinctly different distribution of rotation angles compared to the Wind and ARTEMIS missions, while the distributions of $B_N/B$ are largely similar, as shown in Panel (b).
+This discrepancy suggests that the rotational structure of current sheets evolves significantly as the solar wind propagates from the near-Sun environment to 1 AU.
+The multiple peaks in PSP’s in-plane rotation angle distribution likely reflect the coexistence of several current sheet populations, possibly formed through different mechanisms or originating from different solar wind sources.
+As the solar wind expands and mixes, this structured distribution becomes smoother, as observed by Wind and ARTEMIS near Earth.
+The distribution of $B_N / B$ is clearly bimodal, with one population corresponding to nearly field-aligned normals and another to nearly perpendicular ones.
+Only a small fraction of events fall in the intermediate range.
+Such bimodal distributions are consistent with the coexistence of different types of discontinuities—most notably rotational and tangential discontinuities [@madarDirectionalDiscontinuitiesInner2024].
+Panel (c) shows the joint distribution of the in-plane rotation angle and $B_N / B$, where each column has been normalized to highlight how the rotation angle varies with $B_N / B$.
+The distinct distribution observed by PSP again indicates an evolutionary trend: current sheets closer to the Sun exhibit a more structured and varied rotational behavior, which gradually transitions to smoother and more uniform configurations at 1 AU.
+
+::: {#fig-B_n_ω}
+
+![](figures/B_n_ω_-mva-subset=true.png)
+
+(a) Probability density functions of the in-plane rotation angle ($\omega_{\text{in}}$) for Parker Solar Probe (PSP) and Wind + THEMIS.
+(b) Probability density functions of the normalized normal magnetic field component ($B_N / B$).
+(c) Joint distributions of $\omega_{\text{in}}$ and $B_N / B$ for PSP (left) and Wind + THEMIS (right).
+:::
+
+Finally, @fig-duration presents the probability density functions of current sheet temporal durations observed by different missions.
+The distributions differ noticeably in shape, reflecting variations in the relative occurrence of short- and long-duration events among the datasets.
+The gradual change in slope with increasing duration suggests the presence of at least two, and possibly three, distinct regimes contributing to the overall range of current sheet durations.
+The shortest-duration events are likely associated with kinetic-scale current sheets, while the longer-duration events may correspond to flux-tube boundaries, large-scale magnetic structures, or heliospheric current sheets.
+The similar slopes observed at longer durations across missions indicate that large-scale structures are relatively stable with heliocentric distance, whereas the short-duration population evolves more rapidly as the solar wind expands.
+Assuming that current sheets propagate radially without significant distortion or dissipation, the measured temporal duration can be interpreted as a proxy for the spatial thickness of the structure, modulated by the magnetic field orientation.
+To account for geometric effects, we apply a correction based on the Parker spiral model, multiplying the PSP durations by the factor $\sin(\Theta_{\text{Earth}}) / \sin(\Theta_{\text{PSP}})$, where $\Theta \approx \arctan(B_T / B_R)$ is the angle between the magnetic field and the radial direction, with $B_R$ and $B_T$ denoting the radial and transverse magnetic field components, respectively.
+Although this correction is a simplified approximation and not physically rigorous, it provides a useful scaling comparison: after adjustment, the PSP duration distribution aligns closely with those of Wind and ARTEMIS near 1 AU for short-duration current sheets.
+This agreement suggests that the shortest-duration (kinetic-scale) current sheets are predominantly oriented perpendicular to the mean magnetic field and evolve substantially with distance from the Sun.
+
+::: {#fig-duration}
+
+![](figures/duration_dist.png)
+
+Probability density functions of current sheet durations observed by different missions. Grey vertical dashed lines indicate durations of 1, 2, 4, 8, 16, and 32 s (from left to right).
+
+:::
+
+# Conclusion
+
+1.
+We investigated three Parker Solar Probe (PSP) encounters, complemented by ARTEMIS and Wind measurements, to identify and characterize current sheets across different heliocentric distances.
+The results indicate that variations in the selected time intervals exert only a minor influence on key current sheet properties such as thickness, current density, and Alfvénicity.
+This suggests that the observed evolution of current sheet characteristics primarily reflects spatial effects associated with radial expansion rather than temporal variability.
+
+2.
+Our analysis confirms that current sheet properties are closely linked to local plasma conditions and extends previously reported scale-dependent relationships between current sheet thickness and current density by more than two orders of magnitude, encompassing structures from kinetic to large MHD scales.
+Both the normalized current density and normalized thickness remain nearly constant across radial distances, with only a slight decrease in normalized thickness farther from the Sun.
+The pronounced anti-correlation between current density and spatial scale—stronger current densities corresponding to thinner sheets—and the similarity of normalized current densities across radial distances indicate a close connection between current sheets and MHD turbulence, since localized, non-Gaussian current density enhancements are a hallmark of intermittency in turbulent plasmas.
+
+3.
+The Alfvénicity of most current sheets, quantified by the parameter $Q$, remains below unity for the majority of events.
+The magnitude ratios reported by PSP and Wind are broadly consistent, while PSP observations show smaller angular deviations than those from Wind and ARTEMIS.
+Pressure anisotropy alone does not account for the observed velocity and magnetic field jumps.
+Instead, the degree of Alfvénicity appears to be primarily controlled by the surrounding turbulent plasma state—specifically, by cross helicity and residual energy.
+Most current sheets are nearly force-free, exhibiting low compressibility (typically <0.1).
+These findings support a picture in which current sheets are embedded within, and shaped by, the local turbulent cascade rather than being isolated structures produced by single local processes.
+In other words, the macroscopic turbulence environment determines whether a boundary appears Alfvénic or non-Alfvénic when sampled in situ.
 
 <!-- 
-References:
-- @shenComparingPlasmaAnisotropy2024
+The strong positive correlation between current-sheet Alfvénicity and the ambient cross-helicity, together with the negative correlation with residual energy, indicates that the degree to which a current sheet behaves like an ideal rotational discontinuity is largely set by the surrounding turbulence state.
+High cross-helicity (more Alfvénic background fluctuations) promotes velocity–magnetic-field alignment at the sheet and hence higher sheet Alfvénicity; conversely, large (negative) residual energy — a relative excess of magnetic over kinetic fluctuation energy — corresponds to less Alfvénic sheets.
 -->
 
-# Results
+4.
+A comparison between PSP and near-Earth missions reveals that the statistical properties of solar wind current sheets undergo systematic evolution with heliocentric distance.
+Clear differences are observed in the distributions of unnormalized current density, thickness, magnetic field jump, rotation angle, and temporal duration.
+Processes that may drive this evolution include global solar wind expansion [@matteiniIonKineticsSolar2012], nonlinear dynamics of Alfvén waves and Alfvénic turbulence [@medvedevDissipativeDynamicsCollisionless1997], and interactions with other coherent structures.
+This evolution has important implications for the role of current sheets in plasma heating [@sioulasStatisticalAnalysisIntermittency2022], particle energization and transport [@zhangQuantificationIonScattering2025], which are expected to depend strongly on radial distance.
 
-TODO: how does the results depend on the period selected for the conjunctions and alignments?
+Taken together, our results support a picture in which current sheets are predominantly turbulence-embedded, dynamically evolving structures whose Alfvénic character is governed by the ambient solar wind turbulence—through cross helicity and residual energy.
+The tight coupling between current sheet intensity and spatial scale, the coexistence of at least two structural regimes, and the systematic radial evolution of their properties collectively point to a complex interplay between turbulent intermittency, solar wind expansion, and kinetic processes.
+Resolving these remaining discrepancies will require higher-resolution particle measurements, multi-spacecraft observations, and dedicated kinetic modeling.
 
-## Comparison of Discontinuity Properties
+<!-- 7. Methodological caveats and uncertainties.
+Several limitations could affect quantitative interpretation and should guide follow-up analyses: (i) single-spacecraft MVA and thickness estimates carry uncertainties in the normal direction and the projection of velocity; (ii) current density estimated from ΔB/Δl assumes a 1D geometry and neglects possible multi-dimensional structure; (iii) time-resolution differences between magnetometers and plasma instruments (SPAN, Faraday cup) can bias velocity-jump estimates; and (iv) detection thresholds and interval selection in the automated algorithm can preferentially select certain sheet types.
+-->
 
-![](figures/enc7/properties_distribution.svg)
+<!-- 5. Temporal-duration effect: physical or instrumental?
+The weak positive relation between current-sheet duration and Alfvénicity (longer events appearing more Alfvénic) must be interpreted cautiously.
+Longer durations provide more plasma samples and therefore better statistical estimates of upstream/downstream velocities; thus part of the trend may be instrumental or sampling bias.
+Nevertheless, if a residual physical trend remains after accounting for resolution effects, it could indicate that more spatially extended sheets preserve the Alfvénic coupling between flows and fields more effectively than shorter, more transient sheets — again pointing to an intimate connection between sheet morphology and the ambient turbulence.
+-->
 
-Thickness and current density relationship
-Scale-dependent properties of current sheets in the solar wind
+<!-- 
+8. Specific, actionable follow-ups.
+To strengthen the physical interpretation and disentangle competing hypotheses, we recommend:
+	•	Cross-checking events with high-cadence particle moments and full distribution functions (to examine alpha/beams and non-Maxwellian features).
+	•	Searching for localized signatures of Hall physics or reconnection (bipolar electron jets, outflow pairs, Hall magnetic-field patterns) in high-resolution fields and particle data.
+	•	Conditioning the statistics on solar-wind type (fast vs. slow, presence of switchbacks, stream origin) to see whether the two inferred populations map to flow regimes.
+	•	Running hybrid or kinetic simulations initialized with observed upstream parameters to test whether pressure-tensor or multi-species effects reproduce the velocity–field jump mismatch.
+	•	Expanding the radial coverage (include Solar Orbiter, STEREO where possible) or employing multi-point analysis to reduce geometric ambiguities. 
+-->
 
-![Comparision map of (normalized) thickness and (normalized) current density](figures/enc7/thickness_current.svg){#fig-comp-map}
+<!-- References
+-   @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
 
-## Comparison between Alfven speed and plasma speed change
+    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensification of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
 
-For rotational discontinuities, the plasma velocity jump across them: the plasma flow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$.
+-->
 
-![](figures/enc7/dvl.png)
+# Appendix
 
-K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
+::: {#fig-properties-hist-cross}
+![](figures/properties_hist-cross.png)
 
-## Estimated Anisotropy
+Same as @fig-properties-hist but using cross product to determine the normal direction to the current sheet.
+:::
 
-The equation for $Δv_A$ includes a factor depending on the anisotropy of the plasma.
+::: {#fig-joint-properties-cross}
+![](figures/joint_properties-cross.png)
 
-Pressure anisotropy $Λ = \mu (P_∥ - P_⊥) / B^2$.
-
-![](figures/enc7/anisotropy_theory.png)
-
-## Comparison between Estimated and Observed Anisotropy
-
-![](figures/enc7/anisotropy_comparison_2d.png)
-
-# Discussion
-
-- The properties of the discontinuities is related to the local plasma parameters
-  - Thickness => ion inertial length
-  - Current density => Alfven velocity (current density)
-
-- Normalized thickness and current density of discontinuities remain constant with radial distance.
-In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease  in normalized thickness and increase in normalized current density with radial distance.
-
-Assuming the 
-Anisotropy of tAzdhe plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
-
-# Conclusion
+Same as @fig-joint-properties but with current sheet normals determined using the magnetic field cross-product method instead of minimum variance analysis (MVA).
+:::

### 2025-10-22 article.tex
docs: methods

% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage[]{natbib}
\bibliographystyle{plainnat}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Evolution of solar wind discontinuities in the inner heliosphere},
  pdfauthor={Zijin Zhang; Anton V. Artemyev; Vassilis Angelopoulos; Tai Phan},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Evolution of solar wind discontinuities in the inner heliosphere}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{PSP and Earth conjunctions and alignments}
\author{Zijin Zhang \and Anton V. Artemyev \and Vassilis Angelopoulos \and Tai Phan}
\date{}
\begin{document}
\maketitle

\section{Abstract}\label{abstract}

We analyze three time intervals during which the Parker Solar Probe (PSP) was in close proximity to the Sun and investigate current sheets (magnetic discontinuities) observed by PSP, ARTEMIS, and Wind. Using an automated detection algorithm, we identify and examine the statistical properties of over 45,000 current sheets across the three intervals, including approximately 17,000 from PSP. The results show that current sheets broaden with increasing heliocentric distance, while their characteristic current density remains largely unchanged. The thickness and current density are strongly anti-correlated, indicating that thinner current sheets carry stronger currents, consistent with turbulent intermittency. Distinct distributions of magnetic field jumps and rotation angles are also observed among the different missions, suggesting structural evolution of current sheets as the solar wind expands. Most current sheets display small variations in magnetic field magnitude, indicating a predominantly force-free character. Significant deviations from the Walén relation persist even when pressure anisotropy is included, implying that anisotropy alone cannot explain the observed departures from ideal rotational discontinuities. Finally, the Alfvénicity of the current sheets correlates strongly with the cross helicity and residual energy of the surrounding solar wind, demonstrating that current sheet dynamics are largely governed by the ambient turbulent environment.

\section{Introduction}\label{introduction}

Current sheets are ubiquitous mesoscale structures in the solar wind, where the magnetic field changes direction abruptly over ion-scale thicknesses, while their lateral extents can exceed typical magnetohydrodynamic (MHD) scales. These current sheets most readily identified from sharp magnetic-field rotations but can also be evident in simultaneous changes of plasma density, bulk velocity, and temperature.

In turbulent solar wind plasmas, current sheets are widely recognized as signatures of intermittency, contributing to the non-Gaussian nature of magnetic field fluctuations and localized energy dissipation \citep{borovskyContributionStrongDiscontinuities2010, grecoPartialVarianceIncrements2017}. They play a crucial role in mediating the transfer of energy across scales, from large-scale MHD fluctuations down to ion and electron kinetic scales, and are believed to be important sites of plasma heating and particle acceleration \citep{osmanIntermittencyLocalHeating2012, tesseinAssociationSuprathermalParticles2013}.

Understanding the formation, structure, and evolution of current sheets at different heliocentric distances is therefore essential for elucidating the mechanisms that govern solar wind turbulence and heating. A number of statistical studies have investigated current sheet properties across a broad range of radial distances \citep{marianiStatisticalStudyMagnetohydrodynamic1983, artemyevDynamicsIntenseCurrents2018, perroneCoherentEventsIon2020, liuCharacteristicsInterplanetaryDiscontinuities2021, lotekarKineticscaleCurrentSheets2022, vaskoKineticscaleCurrentSheets2022, vaskoKineticScaleCurrentSheets2024}. Despite this progress, several important gaps remain.
First, many earlier studies rely on datasets obtained at different times and with instruments of varying temporal resolution, which complicates consistent comparisons across heliocentric distances. Few investigations have examined simultaneous observations from multiple radial positions \citep{velliUnderstandingOriginsHeliosphere2020, telloniSpacecraftRadialAlignments2023}, limiting our understanding of how current sheet properties evolve as the solar wind expands. Second, existing identification methods often depend on fixed thresholds---such as absolute magnetic-field jumps---or are highly sensitive to data resolution, as in the case of partial variance increment techniques. To enable meaningful cross-mission comparisons, more robust approaches based on normalized, resolution-independent criteria are needed. Finally, most prior work has classified discontinuities within the ideal MHD framework---for instance, distinguishing tangential from rotational discontinuities. While useful in some contexts and extensively studied, these categories become inadequate at ion scales, where kinetic and multi-fluid effects play a central role. In this study, we therefore move beyond strict MHD classifications and instead emphasize the Alfvénic character of current sheets---that is, the extent to which plasma and magnetic-field variations follow Alfvénic correlations \citep{shenComparingPlasmaAnisotropy2024}. Although this perspective is fundamental for understanding the origin and evolution of current sheets, it has received relatively limited attention.

The Parker Solar Probe (PSP) mission offers an unprecedented opportunity to probe current sheets in the near-Sun environment with high cadence and to compare those observations with near-Earth measurements. In this study, we focus on three PSP perihelion intervals (Encounters 7--9) selected for their differing geometric alignments with the near-Earth spacecraft ARTEMIS and Wind. Encounter 7 features strong radial alignment, enabling sampling of similar solar wind streams while Encounter 8 exhibits weaker alignment and Encounter 9 places PSP roughly 180° away in longitude. These contrasting configurations enable a controlled examination of current sheet properties and, more broadly, provide insight into how those properties depend on the solar wind's source region.

Using a robust automated detection algorithm, we identify and analyze more than 45,000 current sheets across the three selected intervals (approximately 17,000 from PSP). We systematically characterize their rotation profiles, thicknesses, current densities, magnetic field jumps, and Alfvénic properties. The remainder of this paper is organized as follows: Section 2 describes the datasets and analysis methods; Section 3 presents the results and discusses their physical implications; and Section 4 summarizes the main conclusions.

\section{Dataset and method}\label{dataset-and-method}

In this study, we utilize magnetic field and plasma measurements from Parker Solar Probe (PSP) \citep{foxSolarProbeMission2016}, ARTEMIS \citep{angelopoulosARTEMISMission2011} and Wind missions \citep{acunaGlobalGeospaceScience1995}. For PSP, we use high-resolution magnetic field data from the FIELDS instrument \citep{baleFIELDSInstrumentSuite2016} and plasma data from the Solar Wind Electrons Alphas and Protons (SWEAP) suite \citep{kasperSolarWindElectrons2016}. The proton and electron anisotropies are derived from the corresponding electrostatic analyzers' measurements: Solar Probe ANalyzer for Ions (SPAN-I) and Electrons (SPAN-E) \citep{liviSolarProbeANalyzer2022, whittleseySolarProbeANalyzers2020}. For ARTEMIS, we use magnetic field data measured at approximately 5 Hz resolution by the Fluxgate Magnetometer \citep{austerTHEMISFluxgateMagnetometer2008}, as well as plasma velocity and density from the electrostatic analyzer instrument with a resolution of around 4 seconds \citep{mcfaddenTHEMISESAPlasma2009}. The following data collected by Wind are used: magnetic fields with a \(\sim 11\) Hz resolution measured by the Magnetic Field Investigation (MFI) \citep{leppingWINDMagneticField1995}, the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) \citep{linThreedimensionalPlasmaEnergetic1995}.

It is worth noting that for PSP, although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution. Plasma density estimates delivered by the quasi-thermal noise spectroscopy (QTN) is also available \citep{moncuquetFirstSituMeasurements2020}. We generally find that the results using QTN data do not differ significantly from those derived from SPAN-i data. Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument's view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.

Our study investigates the evolution of current sheet properties during the radial expansion of the solar wind. To distinguish spatial variations from temporal effects, we analyze three distinct time intervals corresponding to Parker Solar Probe (PSP) Encounters 7 through 9, each characterized by different PSP--Earth alignments \citep{telloniSpacecraftRadialAlignments2023, velliUnderstandingOriginsHeliosphere2020}.
Encounter 7 features a favorable alignment between PSP and Earth, enabling nearly simultaneous multi-point observations (PSP approached perihelion on 2021-01-17 17:40; data intervals are 2021-01-15 -- 2021-01-20 for PSP and 2021-01-17 -- 2021-01-25 for ARTEMIS and Wind). Encounter 8 exhibits moderate alignment (PSP perihelion at 2021-04-29 08:48; data intervals 2021-04-27 -- 2021-05-02 for PSP and 2021-04-29 -- 2021-05-04 for ARTEMIS and Wind). In Encounter 9, PSP and Earth are located at substantially different heliolongitudes, with most PSP footpoints lying on the far side of the Sun (PSP perihelion at 2021-08-09 19:11; data intervals 2021-08-07 -- 2021-08-12 for PSP and 2021-08-09 -- 2021-08-14 for ARTEMIS and Wind). By comparing these intervals, we assess how the derived current sheet properties depend on the relative geometry and temporal context of the observations. Our results show that although certain plasma parameters vary slightly among intervals, the overall statistical characteristics of the current sheets remain largely consistent. This suggests that the observed statistics are not strongly sensitive to either the relative geometry or the temporal context of the measurements.

Figure~\ref{fig-overview} provides an overview of the selected time interval from Encounter 7, comparing measurements from the PSP (left panels) and Wind (right panels) missions. From top to bottom, the panels display 8-minute averages of the magnetic field magnitude, proton number density, and proton bulk flow speed, followed by ion and electron temperatures resolved in the parallel and perpendicular directions. To facilitate comparison, Wind data are scaled to \(20 R_\odot\) using the empirical relations \(B_{\text{scaled}}/B = ( 20 R_\odot / 1\ \text{AU} )^{-1.59}\), \(n_{\text{scaled}}/n = ( 20 R_\odot / 1\ \text{AU} )^{-1.96}\) \citep{perroneRadialEvolutionSolar2019}.
The fifth and sixth panels show the median Alfvén ratio, \(R_{VB} = |Δ 𝐕| / |Δ 𝐕_A|\), of the current sheets and the total number of current sheets identified within each four-hour window. Including the anisotropy factor \(Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2\) does not significantly affect the Alfvén ratio \(R_{VB}^* = R_{VB} / \sqrt{1 - Λ}\); its average value is approximately 0.5 for PSP and 0.4 for Wind over the entire time interval. The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
Panel (a.7) and (b.7) present the cross helicity and residual energy, which describe the Alfvénic nature and energetic balance of the ambient plasma, respectively, calculated every 8 minutes. The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind. These parameters offer critical insights into identifying the source regions of different solar wind streams \citep{altermanCrossHelicityHelium2025}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/overview-7-all.png}}

}

\caption{\label{fig-overview}Overview of Encounter 7 comparing PSP (left) and Wind (right) observations. Panels show 8-minute averages of (a.1, b.1) magnetic field magnitude, (a.2, b.2) proton density, (a.3, b.3) flow speed, (a.4, b.4) ion and electron temperatures, (a.5, b.5) Alfvén ratio, (a.6, b.6) current-sheet counts, (a.7, b.7) cross helicity and residual energy, (a.8, b.8) helium abundance, and (a.9, b.9) plasma beta. Wind measurements are radially scaled to \(20 R_\odot\) for comparison.}

\end{figure}%

\subsection{Methodology}\label{methodology}

To identify current sheets, we employ an improved automated detection algorithm adapted from previous studies \citep{zhangSolarWindDiscontinuities2025b, liuMagneticDiscontinuitiesSolar2022}. The magnetic field data are divided into consecutive time intervals, each lagged by a time \(T\). For each interval, we compute the standard deviation of the vector magnetic field, \(σ(𝐁)\), and compare it with those of the adjacent intervals, \(σ(𝐁_{-} )\) and \(σ(𝐁_{+})\). An interval is flagged as a potential current sheet when its standard deviation significantly exceeds those of its neighbors, indicating a sharp magnetic field variation: \(σ(𝐁) > 2 \max(σ(𝐁_{-} ), σ(𝐁_{+}))\).
For each candidate interval, we refine the boundaries of the potential current sheet by computing the distance between two magnetic field vectors, \(d(t_a, t_b) = \|𝐁(t_a) - 𝐁(t_b)\|\). The leading and trailing edges, \(t_a\) and \(t_b\) (\(t_a < t_b\)), are defined such that \(d(t_a, t_b)\) attains its maximum value within the interval. To minimize false detections---particularly those caused by wave-like or hole-like structures that may mimic current sheet signatures---we impose the additional requirement \(|Δ𝐁| / \bar{B} \ge 1/10\). We also evaluate the magnetic field orientation across each candidate structure by computing the angles between magnetic field vectors at the leading and trailing edges and comparing them with the angles between each edge and the interval midpoint. Only intervals in which the edge-to-edge angle exceeds all interior angles are retained as valid current sheet candidates. Because current sheets span a range of spatial and temporal scales, we performed the identification procedure using multiple time lags (\(T = 2, 4, 8, 16, 32, 64\ \mathrm{s}\)). The resulting event lists from each search were merged into a comprehensive catalog after removing duplicates. A subset of automatically detected intervals was visually inspected. All verified cases exhibit clear current sheet--like signatures, confirming the robustness and reliability of the automated procedure.

We also evaluated the Partial Variance of Increments (PVI) method for current sheet identification \citep{grecoPartialVarianceIncrements2017}. Although the PVI technique is effective for detecting short-duration, kinetic-scale current sheets characterized by sharp gradients, it often fails to capture larger-scale structures that display smoother yet coherent magnetic field variations. In addition, the PVI method is highly sensitive to data resolution, complicating cross-mission comparisons where instruments have differing temporal cadences. For these reasons, we do not report PVI-based results here.

Once the current sheets are identified, we apply a minimum variance analysis (MVA) to transform the magnetic field and plasma data into the local LMN coordinate system, where \(L\), \(M\), and \(N\) correspond to the directions of maximum, intermediate, and minimum variance, respectively. The maximum variance component, \(B_L\), is then fitted with a hyperbolic tangent profile to extract parameters characterizing each current sheet, following the standard Harris current sheet model \citep{harrisPlasmaSheathSeparating1962}: \(B_L(t) = B_{L,i} \tanh (\frac{t-t_i}{Δt_i/2} ) + c_i\) where \(B_{L,i}\) is the amplitude of the magnetic field change in the maximum variance direction, \(t_i\) is the detection time, \(Δt_i\) is the temporal duration, and \(c_i\) is a magnetic field offset.

Assuming that the current sheets are one-dimensional, planar structures, their spatial scale (thickness) can be estimated once the normal direction is determined. The normal vector can be obtained either from the minimum variance direction given by MVA or from the cross product of the magnetic field vectors at the current sheet boundaries. However, previous studies have shown that the MVA-derived normal direction can often be unreliable \citep{knetterFourpointDiscontinuityObservations2004, wangSolarWindCurrent2024}. The accuracy can be improved by imposing additional constraints such as \(Δ|B|/ |B| > 0.05\) or \(ω > 60°\) \citep{liuFailuresMinimumVariance2023}, where \(Δ|B|\) denotes the change in magnetic field magnitude and \(ω\) is the field rotation angle across the discontinuity. The cross-product method, on the other hand, requires that the magnetic field component along the normal direction (\(B_n\)) be small, making it unsuitable when \(B_n\) is large. In this study, we apply both methods and report results based on the subset of events satisfying \(Δ|B|/ |B| > 0.05\) or \(ω > 60°\). The results derived using the cross-product method are presented in the Appendix.

The spatial thickness of each current sheet is estimated as \(δ = V_n \Delta t\), where \(V_n\) is the plasma velocity projected along the normal direction. The current density associated with the main magnetic field reversal is calculated from \(J_m = - \frac{1}{\mu_0 V_n} \frac{d B_l}{d t}\). Within our fitting framework, the magnetic field derivative can be approximated as \(\max(dB_L/ dt) = 2 B_{L,i}/ Δt_i\). This approach provides a more robust estimate than direct differentiation, as it is less sensitive to measurement noise and limited temporal resolution.Mean proton density, temperature, and alpha-particle density values from each interval are used to compute the Alfvén velocity, pressure anisotropy factor, plasma beta, and alpha-particle abundance, thereby providing a comprehensive characterization of the plasma environment associated with each current sheet.
the upstream and downstream conditions are defined using timestamps immediately before and after the current sheet boundaries, respectively, such that \(Δ𝐕 = 𝐕_{downstream} - 𝐕_{upstream}\).
The cosine of the angle between the velocity jump \(Δ𝐕\) and the Alfvén velocity jump \(Δ𝐕_A\) is then calculated as \(\cos θ = \frac{Δ𝐕 \cdot Δ𝐕_A}{\|Δ𝐕\| \|𝐕_A\|}\), serving as a measure of Alfvénic alignment.
Finally, the cross helicity \(σ_c = \frac{2 ⟨ δ 𝐕 \cdot δ 𝐁 ⟩}{ ⟨δ𝐕^2⟩ + ⟨δ𝐁^2⟩ }\) and residual energy \(σ_r = \frac{⟨δ 𝐕^2⟩-⟨δ 𝐁^2⟩}{⟨δ 𝐕^2⟩+⟨δ 𝐁^2⟩}\) are computed within intervals extending from each current sheet edge to eight times the current sheet duration (or at least 30 s on either side). These parameters quantify the degree of Alfvénicity and the relative contributions of kinetic and magnetic energy fluctuations in the ambient solar wind.

Figure~\ref{fig-event-example} presents two representative current sheet examples observed by PSP (left panels) and ARTEMIS (right panels). From top to bottom, the panels display, in LMN coordinates, the magnetic field, proton velocity, and the shifted Alfvén velocity \(𝐕_A = \frac{𝐁}{\sqrt{\mu_0 \rho}} - 𝐕_{A,0}\), where \(𝐕_{A,0}\) is the Alfvén velocity at the center of the current sheet. The cosine of the angle between the velocity jump \(Δ𝐕\) and the Alfvén velocity jump \(Δ𝐕_A\) is approximately -0.82 for PSP and -0.95 for ARTEMIS, indicating strong anti-correlation. The corresponding Alfvén ratio \(R_{VB}\) is approximately 0.32 for both PSP and ARTEMIS.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/event-example.png}}

}

\caption{\label{fig-event-example}Representative examples of current sheets observed by the Parker Solar Probe (PSP; panels a.1--a.3) and ARTEMIS (panels b.1--b.3) in the local LMN coordinate system. Panels (a.1) and (b.1) show the magnetic field components \(B_L\), \(B_M\), and \(B_N\), together with the magnetic field magnitude \(B\). The red dashed lines indicate the hyperbolic tangent fits used to derive current sheet parameters. Panels (a.2) and (b.2) display the corresponding proton bulk velocity components \(V_L\), \(V_M\), and \(V_N\). Panels (a.3) and (b.3) show the shifted Alfvén velocity components \(V_{A,L}\), \(V_{A,M}\), and \(V_{A,N}\). The vertical gray dashed lines mark the leading and trailing edges of each identified current sheet.}

\end{figure}%

\section{Results and Discussion}\label{results-and-discussion}

Figure~\ref{fig-properties-hist} presents the statistical distributions of current sheet thickness \(δ\), current density \(J\), and magnetic field jump magnitude \(|Δ𝐁|\) derived from different missions and time intervals.
For thickness and current density, we display here a subset of the all dataset where MVA normals are trustable. The result of using cross product for the current sheet normals are displayed in the appendix Figure~\ref{fig-properties-hist-cross} and do not show any significant difference. Note that we do not need to subset the dataset for magnetic field jump magnitude since it does not depend on the normal direction.
To better understand how these properties relate to the local plasma environment, we normalize the current sheet thickness by the ion (proton) inertial length, \(d_i=c/\omega_{pi}\), and the current density by the Alfvén current density, \(J_A = e N V_A = B / \mu_0 d_i\). Both parameters represent natural plasma scales: the ion inertial length characterizes the spatial scale where ions decouple from the magnetic field, while the Alfvén current density corresponds to the characteristic current generated by the relative drift of electrons and ions moving at the local Alfvén speed \(V_A\). These quantities are particularly relevant in studies of MHD turbulence and magnetic reconnection \citep{zhdankinStatisticalAnalysisCurrent2013, franciMagneticReconnectionDriver2017}.

Despite differing heliocentric distances and instrumental conditions, the normalized current density \(J_m / J_A\) shows remarkably similar distributions across the PSP, Wind, and ARTEMIS datasets. This suggests that the relative strength of current sheets, when expressed in local plasma units, is largely independent of radial distance from the Sun. In contrast, the absolute thickness \(δ\) increases from PSP to ARTEMIS and Wind, indicating a broadening of current sheets with solar wind expansion. After normalization by the ion inertial length, however, the characteristic scale \(δ / d_i\) decreases slightly with increasing distance. This trend is consistent with previous analyses using Juno observations between 1 and 5 AU \citep{zhangSolarWindDiscontinuities2025b} and Maven observations between 1 and 1.5 AU \citep{artemyevDynamicsIntenseCurrents2018}, which found that normalized current density remains nearly constant while normalized thickness gradually decreases with heliocentric distance. Similar behavior has been reported by \citet{madarDirectionalDiscontinuitiesInner2024} using Parker Solar Probe and Solar Orbiter data, where the thickness of rotational discontinuities in ion inertial length units decreases rapidly until approximately 0.3 AU.

The distributions of magnetic field jumps (\(|Δ𝐁|\) and \(|Δ𝐁|/\langle|𝐁|\rangle\)) exhibit pronounced differences across the missions. In particular, the PSP data display a markedly distinct distribution compared with Wind and ARTEMIS, characterized by substantially larger magnetic field jumps---even after normalization---and a relatively flatter tail in the probability density function. These large jumps indicate stronger magnetic field reversals in the near-Sun environment, likely associated with the frequent occurrence of switchbacks. Such switchbacks, especially those embedded within switchback patches, have been observed to dissipate with increasing heliocentric distance \citep{soniSwitchbackPatchesEvolve2024, shiPatchesMagneticSwitchbacks2022}. The difference in the shape of the probability density functions thus suggests the coexistence of multiple populations of current sheets in the near-Sun region, potentially generated by distinct physical mechanisms or linked to different solar wind source regions. As the solar wind expands and the turbulence undergoes nonlinear evolution \citep{telloniObservationModelingSolar2022, telloniEvolutionSolarWind2021}, these separate populations likely interact and merge, resulting in the smoother and more homogeneous distributions observed at 1 AU.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/properties_hist-mva.png}}

}

\caption{\label{fig-properties-hist}Probability density functions (PDFs) of current sheet properties obtained from different missions (color-coded) and encounters (distinguished by line styles). The left column shows unnormalized quantities, while the right column presents values normalized by characteristic plasma scales. From top to bottom, panels display the distributions of (a) current sheet thickness \(δ\) and its normalized form \(δ / d_i\); (b) current density \(J_m\) and normalized current density \(J_m / J_A\); and (c) magnetic field jump magnitude \(|Δ𝐁|\) and its normalized value \(|Δ𝐁| / \langle |𝐁| \rangle\). The ion inertial length is \(d_i = c / \omega_{pi}\), and the Alfvén current density is \(J_A = e N V_A = B / \mu_0 d_i\).}

\end{figure}%

Figure~\ref{fig-joint-properties} presents the joint distributions between (a) current density and current sheet thickness, (b) normalized current density and normalized thickness, (c) normalized thickness and normalized magnetic field jump, and (d) normalized current density and normalized magnetic field jump. A clear inverse correlation is evident between the (normalized) current density and (normalized) current sheet thickness, indicating that stronger currents are generally associated with thinner sheets---that is, smaller-scale current sheets tend to be more intense.
After normalization, the scatter distributions of current density versus thickness are highly similar across different missions, both in overall shape and in the range of values. This similarity suggests that the statistical relationship between current density and scale is largely independent of heliocentric distance.
In contrast, the relationship between the magnetic field jump and current sheet thickness, shown in Panel (c), is relatively weak. For a given range of magnetic field jump amplitudes, the corresponding spatial scales exhibit a broad distribution, spanning up to two orders of magnitude. Moreover, as seen in Panel (d), there is no clear one-to-one correspondence between the magnetic field jump amplitude and the current density.
Scale-dependent properties of current sheets have been reported by several previous studies using PSP, Wind, and Ulysses observations \citep{lotekarKineticscaleCurrentSheets2022, vaskoKineticscaleCurrentSheets2022, vaskoKineticScaleCurrentSheets2024}. However, whereas earlier studies primarily focused on kinetic-scale current sheets, our analysis extends this investigation to a broader range of spatial scales---covering nearly two additional orders of magnitude in the logarithmic space of normalized current density and normalized current sheet thickness.
Similar trends are found when the current sheet normal is determined using the magnetic field cross-product method rather than the minimum variance analysis. This consistency across methods confirms that the observed correlations are not strongly affected by the specific approach used to estimate the current sheet geometry.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/joint_properties-mva.png}}

}

\caption{\label{fig-joint-properties}Joint probability distributions of (a) current density versus current sheet thickness, (b) normalized current density versus normalized current sheet thickness, (c) normalized current sheet thickness versus magnetic field jump magnitude, and (d) normalized current density versus normalized magnetic field jump magnitude.}

\end{figure}%

For an ideal MHD rotational discontinuity (RD), the plasma velocity and magnetic field variations satisfy the Walén relation, \(Δ 𝐕 = \pm Δ 𝐕_A\), and the force-free condition ( \(Δ B \approx 0\)) holds across the current sheet. The Walén relation requires agreement in both magnitude and direction between the plasma velocity change and the corresponding Alfvén velocity change. However, most observed current sheets deviate from these ideal conditions.

To quantify the degree of Alfvénicity and the deviations from ideal RD behavior, we examine both the magnitude and angular differences between \(Δ 𝐕\) and \(Δ 𝐕_A\), as well as the variation in magnetic field strength across each current sheet.
Figure~\ref{fig-Alfvenicities} summarizes the statistical results. Panel (a) shows the ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude. Across all missions, the ratio is generally less than unity, with mean values of approximately 0.6 for PSP and 0.5 for the combined Wind and ARTEMIS datasets.
Panel (b) displays the cosine of the angle between the velocity and Alfvén velocity jumps. All missions show clustering near 0° and 180°, corresponding to correlated and anti-correlated states, respectively. PSP observations exhibit stronger alignment (cosine values closer to ±1), whereas Wind and ARTEMIS data show a broader angular spread.
Panels (c) and (d) present the fractional change in magnetic field magnitude across current sheets. These variations are small (about 0.1 on average) for all missions, with PSP showing slightly smaller changes than Wind and ARTEMIS. This indicates that most current sheets are nearly incompressible, consistent with an approximately force-free magnetic structure.

We also calculate the Alfvén velocity including the anisotropy factor \(Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2\), for PSP and Wind observations when the necessary plasma data are available. In most cases, including this anisotropy correction does not significantly alter the velocity-jump ratio. The persistent discrepancy between the observed ratios (\(R < 1\)) and the predictions of anisotropic MHD theory may have several explanations. First, the limited temporal resolution of the plasma anisotropy measurements---typically much lower than that of the magnetic field data---may cause underestimation of instantaneous variations at current sheet crossings \citep{huangProtonTemperatureAnisotropy2020, shenComparingPlasmaAnisotropy2024}. Second, kinetic-scale magnetic discontinuities often deviate from the assumptions of MHD theory: their non-Maxwellian particle velocity distributions, including plasma agyrotropies and field-aligned beams \citep{artemyevIonNongyrotropySolar2020, neukirchKineticModelsTangential2020}, are not accounted for in the fluid equations but can strongly influence the measured velocity ratios. Finally, uncertainties in deriving the parallel and perpendicular temperatures---typically obtained from nonlinear fits to complex velocity distribution functions---may introduce additional errors, especially when multiple particle populations are present \citep{huangProtonTemperatureAnisotropy2020, halekasElectronsYoungSolar2020}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/Alfvenicities.png}}

}

\caption{\label{fig-Alfvenicities}Statistical distributions of parameters used to characterize the Alfvénicity of current sheets: (a) ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude, (b) cosine of the angle between the two vectors, (c) the variation in magnetic field magnitude between the leading and trailing edges of each current sheet; and
(d) the maximum variation in magnetic field magnitude observed within each current sheet.}

\end{figure}%

To further investigate the physical origins of the observed deviations from Alfvénic behavior, we use a single scalar parameter, \(Q^{ \pm}\), introduced by \citep{sonnerupQualityMeasureWalen2018}, to quantify the Alfvénicity of current sheets and examine how \(Q^{ \pm}\) correlates with key current sheet and plasma parameters.

The parameter \(Q^{\pm}\) is defined as \(Q^{\pm} = \pm \left(1 - \frac{|\Delta 𝐕 \mp \Delta 𝐕_A|}{|\Delta 𝐕| + |\Delta 𝐕_A|}\right)\), which combines both magnitude and directional discrepancies between the velocity and Alfvén velocity jumps, and satisfies \(-1 < Q^{\pm} < 1\). The upper sign is used for cases where \(\cos \theta > 0\) and the lower sign for \(\cos \theta < 0\). Values of \(Q^{\pm}\) approaching ±1 correspond to highly Alfvénic behavior. The joint distribution of \(|\Delta 𝐕| / |\Delta 𝐕_A|\) and \(\cos \theta\) is shown in the first panel of Figure~\ref{fig-Q_sonnerup_joint_dist_den}.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/Q_sonnerup_joint_dist_den.png}}

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  Joint distribution of the velocity-jump ratio (\(|\Delta 𝐕| / |\Delta 𝐕_A|\)) and the cosine of the alignment angle (\(\cos \theta\)), used in computing the Sonnerup (\(Q^{\pm}\)) parameter. (b) Joint distribution of cross helicity (\(\sigma_c\)) and (\(Q^{\pm}\)). (c) Joint distribution of residual energy (\(\sigma_r\)) and (\(Q^{\pm}\)). (d) Joint distribution of temporal duration and (\(Q^{\pm}\)).
\end{enumerate}

}

\caption{\label{fig-Q_sonnerup_joint_dist_den}}

\end{figure}%

We examine the relationship between \(Q^{\pm}\) and various current sheet and ambient solar wind properties. Most parameters show little or no correlation with \(Q^{\pm}\); however, two quantities exhibit strong correlations: the cross helicity \(\sigma_c\) and residual energy \(\sigma_r\) of the surrounding solar wind. These parameters describe, respectively, the degree of velocity--magnetic field correlation and the partition of energy between velocity and magnetic field fluctuations. Both serve as indicators of the Alfvénic character of the background solar wind rather than of individual current sheets.

Panels (b) and (c) of Figure~\ref{fig-Q_sonnerup_joint_dist_den} show that the Alfvénicity of current sheets, represented by \(Q^{+}\), increases with higher cross helicity and larger (more positive) residual energy, while \(Q^{-}\) increases with higher cross helicity and smaller (more negative) residual energy. This trend suggests that current sheets embedded within highly Alfvénic solar wind streams tend to preserve stronger velocity--magnetic field alignment, whereas those located in more turbulent or energy-imbalanced regions---where magnetic energy \((E_B)\) exceeds kinetic energy \((E_V)\)---exhibit greater departures from Alfvénic expectations.

Additionally, observations reveal a weak positive correlation between \(Q^{\pm}\) and the temporal duration of current sheets, as shown in Panel (d) of Figure~\ref{fig-Q_sonnerup_joint_dist_den}. Longer-duration current sheets tend to exhibit slightly higher \(Q^{\pm}\) values, suggesting a more coherent Alfvénic structure. However, this correlation may be partially influenced by instrumental limitations, since longer events are more reliably resolved in plasma velocity measurements. Other plasma parameters, such as plasma beta and alpha-particle abundance, show no significant correlation with \(Q^{\pm}\), implying that the Alfvénic nature of current sheets is primarily governed by the local turbulent environment rather than by large-scale plasma conditions.

Since the normal component of the magnetic field plays a key role in determining both the spatial scale and the associated current density, we next examine the rotational characteristics of the current sheets and their relationship with the normalized normal magnetic field component, \(B_N/B\).
Figure~\ref{fig-B_n_ω} shows the distributions of the in-plane rotation angle (also referred to as the shear angle) and the normalized normal component \(B_N/B\), along with their joint distributions for different missions. Panel (a) reveals that PSP observes a distinctly different distribution of rotation angles compared to the Wind and ARTEMIS missions, while the distributions of \(B_N/B\) are largely similar, as shown in Panel (b). This discrepancy suggests that the rotational structure of current sheets evolves significantly as the solar wind propagates from the near-Sun environment to 1 AU.
The multiple peaks in PSP's in-plane rotation angle distribution likely reflect the coexistence of several current sheet populations, possibly formed through different mechanisms or originating from different solar wind sources. As the solar wind expands and mixes, this structured distribution becomes smoother, as observed by Wind and ARTEMIS near Earth.
The distribution of \(B_N / B\) is clearly bimodal, with one population corresponding to nearly field-aligned normals and another to nearly perpendicular ones. Only a small fraction of events fall in the intermediate range. Such bimodal distributions are consistent with the coexistence of different types of discontinuities---most notably rotational and tangential discontinuities \citep{madarDirectionalDiscontinuitiesInner2024}.
Panel (c) shows the joint distribution of the in-plane rotation angle and \(B_N / B\), where each column has been normalized to highlight how the rotation angle varies with \(B_N / B\). The distinct distribution observed by PSP again indicates an evolutionary trend: current sheets closer to the Sun exhibit a more structured and varied rotational behavior, which gradually transitions to smoother and more uniform configurations at 1 AU.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/B_n_ω_-mva-subset=true.png}}

\begin{enumerate}
\def\labelenumi{(\alph{enumi})}
\tightlist
\item
  Probability density functions of the in-plane rotation angle (\(\omega_{\text{in}}\)) for Parker Solar Probe (PSP) and Wind + THEMIS. (b) Probability density functions of the normalized normal magnetic field component (\(B_N / B\)). (c) Joint distributions of \(\omega_{\text{in}}\) and \(B_N / B\) for PSP (left) and Wind + THEMIS (right).
\end{enumerate}

}

\caption{\label{fig-B_n_ω}}

\end{figure}%

Finally, Figure~\ref{fig-duration} presents the probability density functions of current sheet temporal durations observed by different missions. The distributions differ noticeably in shape, reflecting variations in the relative occurrence of short- and long-duration events among the datasets. The gradual change in slope with increasing duration suggests the presence of at least two, and possibly three, distinct regimes contributing to the overall range of current sheet durations.
The shortest-duration events are likely associated with kinetic-scale current sheets, while the longer-duration events may correspond to flux-tube boundaries, large-scale magnetic structures, or heliospheric current sheets. The similar slopes observed at longer durations across missions indicate that large-scale structures are relatively stable with heliocentric distance, whereas the short-duration population evolves more rapidly as the solar wind expands.
Assuming that current sheets propagate radially without significant distortion or dissipation, the measured temporal duration can be interpreted as a proxy for the spatial thickness of the structure, modulated by the magnetic field orientation. To account for geometric effects, we apply a correction based on the Parker spiral model, multiplying the PSP durations by the factor \(\sin(\Theta_{\text{Earth}}) / \sin(\Theta_{\text{PSP}})\), where \(\Theta \approx \arctan(B_T / B_R)\) is the angle between the magnetic field and the radial direction, with \(B_R\) and \(B_T\) denoting the radial and transverse magnetic field components, respectively. Although this correction is a simplified approximation and not physically rigorous, it provides a useful scaling comparison: after adjustment, the PSP duration distribution aligns closely with those of Wind and ARTEMIS near 1 AU for short-duration current sheets. This agreement suggests that the shortest-duration (kinetic-scale) current sheets are predominantly oriented perpendicular to the mean magnetic field and evolve substantially with distance from the Sun.

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/duration_dist.png}}

}

\caption{\label{fig-duration}Probability density functions of current sheet durations observed by different missions. Grey vertical dashed lines indicate durations of 1, 2, 4, 8, 16, and 32 s (from left to right).}

\end{figure}%

\section{Conclusion}\label{conclusion}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  We investigated three Parker Solar Probe (PSP) encounters, complemented by ARTEMIS and Wind measurements, to identify and characterize current sheets across different heliocentric distances. The results indicate that variations in the selected time intervals exert only a minor influence on key current sheet properties such as thickness, current density, and Alfvénicity. This suggests that the observed evolution of current sheet characteristics primarily reflects spatial effects associated with radial expansion rather than temporal variability.
\item
  Our analysis confirms that current sheet properties are closely linked to local plasma conditions and extends previously reported scale-dependent relationships between current sheet thickness and current density by more than two orders of magnitude, encompassing structures from kinetic to large MHD scales. Both the normalized current density and normalized thickness remain nearly constant across radial distances, with only a slight decrease in normalized thickness farther from the Sun. The pronounced anti-correlation between current density and spatial scale---stronger current densities corresponding to thinner sheets---and the similarity of normalized current densities across radial distances indicate a close connection between current sheets and MHD turbulence, since localized, non-Gaussian current density enhancements are a hallmark of intermittency in turbulent plasmas.
\item
  The Alfvénicity of most current sheets, quantified by the parameter \(Q\), remains below unity for the majority of events. The magnitude ratios reported by PSP and Wind are broadly consistent, while PSP observations show smaller angular deviations than those from Wind and ARTEMIS. Pressure anisotropy alone does not account for the observed velocity and magnetic field jumps. Instead, the degree of Alfvénicity appears to be primarily controlled by the surrounding turbulent plasma state---specifically, by cross helicity and residual energy. Most current sheets are nearly force-free, exhibiting low compressibility (typically \textless0.1). These findings support a picture in which current sheets are embedded within, and shaped by, the local turbulent cascade rather than being isolated structures produced by single local processes. In other words, the macroscopic turbulence environment determines whether a boundary appears Alfvénic or non-Alfvénic when sampled in situ.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  A comparison between PSP and near-Earth missions reveals that the statistical properties of solar wind current sheets undergo systematic evolution with heliocentric distance. Clear differences are observed in the distributions of unnormalized current density, thickness, magnetic field jump, rotation angle, and temporal duration. Processes that may drive this evolution include global solar wind expansion \citep{matteiniIonKineticsSolar2012}, nonlinear dynamics of Alfvén waves and Alfvénic turbulence \citep{medvedevDissipativeDynamicsCollisionless1997}, and interactions with other coherent structures. This evolution has important implications for the role of current sheets in plasma heating \citep{sioulasStatisticalAnalysisIntermittency2022}, particle energization and transport \citep{zhangQuantificationIonScattering2025}, which are expected to depend strongly on radial distance.
\end{enumerate}

Taken together, our results support a picture in which current sheets are predominantly turbulence-embedded, dynamically evolving structures whose Alfvénic character is governed by the ambient solar wind turbulence---through cross helicity and residual energy. The tight coupling between current sheet intensity and spatial scale, the coexistence of at least two structural regimes, and the systematic radial evolution of their properties collectively point to a complex interplay between turbulent intermittency, solar wind expansion, and kinetic processes. Resolving these remaining discrepancies will require higher-resolution particle measurements, multi-spacecraft observations, and dedicated kinetic modeling.

\section{Appendix}\label{appendix}

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/properties_hist-cross.png}}

}

\caption{\label{fig-properties-hist-cross}Same as Figure~\ref{fig-properties-hist} but using cross product to determine the normal direction to the current sheet.}

\end{figure}%

\begin{figure}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/joint_properties-cross.png}}

}

\caption{\label{fig-joint-properties-cross}Same as Figure~\ref{fig-joint-properties} but with current sheet normals determined using the magnetic field cross-product method instead of minimum variance analysis (MVA).}

\end{figure}%

\bibliography{files/bibliography/research.bib}

\end{document}

### 2025-10-22 notebooks/000_data.qmd
docs: methods

@@
-## Data
+# Data
 
@@
 
+<!-- 
+ARTEMIS:
+We use the following data collected by ARTEMIS P1: magnetic fields with a ∼4s spin resolution (Auster et al.
+2008), the ion bulk velocity v, and the ion (assumed to be proton) temperature (scalar) Tp calculated from velocity distributions measured at spin resolution by the Electrostatic Analyzer (ESA; McFadden et al.
+2008).
+Being designed for measurements of a hot, rarefied plasma in Earth’s magnetosphere, ESA typically overestimates the proton temperature in the solar wind, because the solar wind proton beam is narrower than ESA’s energy and angular resolution.
+TODO: check if the ESA is in solar wind mode
+-->
+
 Notes: `thb_peim_t3_magQ` is not accurate in solar wind mode.
@@
 
-### Wind
+## Wind
+
+### Wind 3D Plasma Analyzer
+
+> The Wind 3DP instrument consists of six different sensors.
+There are two electron (EESA) and two ion (PESA) electrostatic analyzers with different geometrical factors and field-of-views covering the energy range from 3 eV to 30 keV.
+There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie...
+
+Wind 3dp, PESA LOW 1 spin resolution ion (proton and alpha) moments
+
+Instrument Description
 

### 2025-10-22 src/psp/plot.py

@@ -52,18 +52,3 @@ def plot_event(
         timebar(td_stop)
 
     return tplot(tnames2plot, return_plot_objects=True)
-
-
-def plot_candidate_tplot(
-    event,
-    mag_tname: str = PSP_MAG_TNAME,
-    vec_tname: str = PSP_VEL_TNAME,
-    den_tname: str = PSP_DEN_TNAME,
-    offset=timedelta(seconds=0),
-):
-    """Plot the candidate event with velocity profiles"""
-
-    start = event[start_col]
-    end = event[end_col]
-
-    return tplot_Alfvenicity(start, end, mag_tname, vec_tname, den_tname, offset)

### 2025-10-29 index.qmd
docs: methods (#1)

--- 2025-10-04 index.qmd
@@
----
-title: Evolution of solar wind discontinuities in the inner heliosphere
-subtitle: PSP and Earth conjunctions and alignments
-author:
-  - name: Zijin Zhang
-    email: zijin@ucla.edu
-    orcid: 0000-0002-9968-067X
-    affiliation: University of California, Los Angeles
-    roles: writing
-    corresponding: true
-  - name: Anton V. Artemyev
-    email: aartemyev@igpp.ucla.edu
-    orcid: 0000-0001-8823-4474
-    affiliation: University of California, Los Angeles
-  - name: Vassilis Angelopoulos
-    email: vassilis@ucla.edu
-    orcid: 0000-0001-7024-1561
-    affiliation: University of California, Los Angeles
-  - name: Tai Phan
-    email: phan@ssl.berkeley.edu
-    orcid: 0000-0002-6924-9408
-    affiliation: Space Sciences Laboratory, University of California, Berkeley
----
+See [article.qmd](article.qmd) for the main article.
 
-# Motivation
+See [notebooks/00_index.qmd](notebooks/00_index.qmd), [notebooks/02_stats.qmd](notebooks/02_stats.qmd), and [notebooks/10_results.qmd](notebooks/10_results.qmd) for the data analysis.
 
-Studying the radial evolution of solar wind discontinuities from synergistic observations of PSP and Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.
-
-- How does the discontinuities change with the radial distance from the Sun?
-
-- How is solar wind discontinuities formed? What is the physical mechanisms?
-
-  - Generated at or near the sun?
-
-  - Locally generated in the interplanetary space by turbulence?
-
-# Introduction
-
-@lotekarKineticscaleCurrentSheets2022
-@perroneCoherentEventsIon2020
-
-The study of the spatial evolution of solar wind discontinuities is important for understanding the dynamics of the solar wind
-
-Previous statistical studies of solar wind discontinuities in the inner heliosphere @marianiStatisticalStudyMagnetohydrodynamic1983 @liuCharacteristicsInterplanetaryDiscontinuities2021
-
-Alignement study of solar wind discontinuities @artemyevDynamicsIntenseCurrents2018
-
-By indentifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions
-
-@hudsonDiscontinuitiesAnisotropicPlasma1970
-
-“Knetter [2005] extended this work to intervals in 2002 and 2003 which also included fast wind intervals.
-He obtained similar results to above and amassed a final total collection of 366 discontinuities.
-All of the discontinuities had normal field components consistent with zero.
-He concluded that the discontinuities are best explained as TDs regardless of the amount of dB/B.” ([Vasquez et al., 2007, p.
-2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))
-
-# Dataset and method
-
-Our study focuses on the evolution of solar wind discontinuities within plasma parcels as they undergo expansion.
-We analyze datasets from the Parker Solar Probe (PSP) and Earth-orbiting missions (e.g., ARTEMIS, DSCOVR, and Wind) at various radial distances in the inner heliosphere, during periods of conjunctions and alignments between PSP and these Earth-orbiting missions.
-
-To achieve this, we utilize a configuration where two spacecraft are radially aligned in the Heliographic (HG) frame, with the longitude fixed on the Sun.
-It is important to note that the plasma parcels observed by the two spacecraft may differ in composition, as solar wind particles propagate at varying velocities.
-For instance, protons often exhibit a beam in their velocity distribution function, while the thermal speed of electrons is much higher than their bulk speed.
-Nonetheless, observing plasma that passes through both spacecraft offers the best opportunity to study the evolution of solar wind discontinuities with minimal influence from other processes during propagation.
-It is also expected that these plasma parcels evolve due to heating and other processes.
-
-<!-- ::: {#fig-plasma-adiabatic-evolution .column-page}
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
-
-![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
-
-Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
-Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
-::: -->
-
-The plasma parcels in question are large-scale structures.
-As the scale size decreases below the mesoscale [@viallMesoscaleStructureSolar2021] (with radial sizes ranging from approximately 5 × 10³ km to 10⁷ km), it becomes increasingly unlikely to identify the same structure, depending on the latitude difference between the two spacecraft.
-Furthermore, although large-scale structures (especially density enhancements) can be identified as passing through both spacecraft [@berriotIdentificationSinglePlasma2024], it is nearly impossible to detect kinetic-scale structures, such as solar wind discontinuities (with time scales on the order of seconds), by both spacecraft simultaneously.
-Therefore, our study focuses on the statistical properties of solar wind discontinuities within the "same" large-scale structures that pass through both spacecraft.
-
-After identifying the periods of conjunctions and alignments between PSP and Earth-orbiting missions, we apply the methodology described in [@???] to identify and characterize solar wind discontinuities.
-Generally, discontinuities observed by PSP are shorter (1-5 seconds) and exhibit higher current density.
-Consequently, we use different time windows for identifying discontinuities: 15 seconds for PSP and 30 seconds for Earth-orbiting missions.
-A example of the discontinuities observed by PSP is shown in @fig-examples.
-
-::: {#fig-examples .column-page}
-
-![](figures/examples/psp_e2_example.png)
-
-Solar wind discontinuities examples observed by PSP fitted by a logistic function in LMN coordinates.
-:::
-
-<!-- 
-PSP:
-SWEAP consists of four separate sensors that measure the ions and electrons that make up the plasma in the solar wind and solar corona.
-The Solar Probe ANalyzer (SPAN) instruments are electrostatic analyzers (ESAs) that use curved plates to measure the 3-D particle distribution from within the shadow cast by the spacecraft thermal shield.
-Two of the sensors are co-located on the ram side of the spacecraft: SPAN-Ai measures ions, and SPAN-Ae measures electrons.
-SPAN-B measures electrons and is on the anti-ram side of the spacecraft.
-The Solar Probe Cup (SPC) is a Faraday Cup instrument that is directly illuminated by the Sun and measures both ions and electrons.
-
-"Looking at your intervals, which occurred during the early phase of the mission when PSP was far from the Sun, I realize that the plasma data wasn't good for your purpose because (1) SPAN-ion during at least the first 3-4 orbits did not measure the solar wind well, since a good portion of the solar wind distributions was out of view of that instrument, and (2) data from SPC (Farady Cup) does not give good temperature data.
-I am wondering if you have conjunction events that occurred later, say starting Encounter 7, when data from SPAN would be accurate.
-If not, some parts of Encounters 4-6 might be OK."
--->
-
-For this study
-
-We utilized high-resolution magnetic field and plasma data from the FIELDS and SWEAP instruments aboard the Parker Solar Probe (PSP).
-For the plasma data presented in the figures of this paper, we used the dataset from SPAN-i, which measures ions in the solar wind.
-Although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution, making it more suitable for analyzing discontinuities.
-Our analysis confirms that the results obtained from SPC are consistent with those derived from SPAN-i data.
-It is also worth noting that sqtn data from the Radio Frequency Spectrometer (RFS) and Low-Frequency Receiver (LFR) for density measurements is available.
-However, we generally find that the results obtained from RFS/LFR do not differ significantly from those derived from SPAN-i data.
-Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument’s view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.
-
-<!-- 
-ARTEMIS:
-We use the following data collected by ARTEMIS P1: magnetic fields with a ∼4s spin resolution (Auster et al.
-2008), the ion bulk velocity v, and the ion (assumed to be proton) temperature (scalar) Tp calculated from velocity distributions measured at spin resolution by the Electrostatic Analyzer (ESA; McFadden et al.
-2008).
-Being designed for measurements of a hot, rarefied plasma in Earth’s magnetosphere, ESA typically overestimates the proton temperature in the solar wind, because the solar wind proton beam is narrower than ESA’s energy and angular resolution.
-TODO: check if the ESA is in solar wind mode
--->
-
-We utilized data collected by ARTEMIS, including magnetic fields measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity ($v$) and density ($n$), which were derived from velocity distribution data obtained by the Electrostatic Analyzer with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
-It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
-Therefore, any findings related to temperature anisotropy should be interpreted with caution.
-
-<!-- 
-WIND:
-Wind 3dp, PESA LOW 1 spin resolution ion (proton and alpha) moments
-Wind 3D Plasma Analyzer
-Instrument Description
-The Wind 3DP instrument consists of six different sensors.
-There are two electron (EESA) and two ion (PESA) electrostatic analyzers with different geometrical factors and field-of-views covering the energy range from 3 eV to 30 keV.
-There are also a pair of solid state telescopes (SST) that measure electrons with energies up to 400 keV and protons with energie
--->
-
-The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
-
-> We will also present plasma density estimates delivered by the quasi-thermal noise spectroscopy available at about 7 s cadence (Moncuquet et al. 2020).
-> The procedure of CS selection and methodology, briefly described below, is equivalent to those used in the paper
-
-@telloniSpacecraftRadialAlignments2023
-
-<!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
--->
-
-# Overview and Example of Current Sheets
-
-> @lotekarKineticscaleCurrentSheets2022 Figure 1 presents an overview of the considered 10 day interval.
-Over this interval, the spacecraft was at radial distances from 0.17 to 0.24 au, that is, from 35 to 50 solar radii, and remained within the inward magnetic field sector without crossing the heliospheric current sheet (Phan et al.
-2020; Szabo et al.
-2020).
-No coronal mass ejections were observed in the considered interval (Phan et al.
-2020; Szabo et al.
-2020).
-The spacecraft was approximately corotating with the Sun and connected to the same coronal hole (Bale et al.
-2019; Badman et al.
-2020).
-Panels (a)–(d) present 1 minute averages of the magnetic field magnitude, proton flow velocity, densities, and temperatures of protons and electrons as well as plasma density estimates provided by the quasi-thermal noise spectroscopy.
-The magnetic field magnitude was about 100 nT at the perihelion on November 6, and around 50 nT as the spacecraft moved to a radial distance of 50 solar radii from the Sun on November 1 and 10.
-The solar wind was typically slow  with a proton flow velocity below 400 km s−1, except for the ≈20 hr period of fast solar wind between November 9 and 10.
-The three plasma density estimates in panel (c) are consistent with each other within a few tens of percent over the entire interval, except for the fast solar wind interval, where the proton densities were about 4 times smaller than the plasma density estimates provided by the quasi-thermal noise spectroscopy.
-We will use the electron density estimates, calibrated to best match proton densities and the results of quasi-thermal noise spectroscopy, as plasma density estimates.
-The proton temperature during the considered interval varied between about 10 and 100 eV, while the electron temperature remained around 30 eV.
-Panel (e) presents 1 minute averages of proton and electron betas and shows that both quantities varied in the range from 0.1 to 5.
-> Figure 2 presents several CSs from our data set.
-
-## Examples of discontinuities
-
-![](figures/examples/psp_e2_example.png)
-
-In general discontinuities observed by PSP are with
-
-- shorter duration (1~5 secs)
-
-  compared with 5-10 secs
-
-- large current density (100-1000 nA/m^2)
-
-  compared with 1-10 nA/m^2
-
-# Results
-
-![](figures/overview-7-all.pdf){#fig-overview}
-
-![](figures/properties_hist-mva.pdf){#fig-properties-hist}
-
-![](figures/joint_properties-mva.pdf){#fig-joint-properties}
-
-![](figures/Alfvenicities.pdf)
-
-![](figures/Q_sonnerup_joint_dist_den.pdf)
-
-![](figures/B_n_ω_subset=true.pdf)
-
-Comparison between Alfven speed and plasma speed change
-
-For rotational discontinuities, the plasma velocity jump across them: the plasma flow velocity $v_l$ (the solar wind velocity projected onto $l$) changes due to changes in $B_l$, $Δv_l=±Δv_A$ with $v_A= B_l / \sqrt{4 n m}$.
-
-![](figures/enc7/dvl.png)
-
-K2: $Δv_l$,l demonstrates a strong correlation with $Δv_{A}$, albeit being consistently smaller.
-
-## The effect of alignment on discontinuity properties
-
-![](figures/thickness_current.png)
-
-![](figures/B_angle.png)
-
-# Discussion
-
-K1: Normalized discontinuities properties does not vary much with radial distance
-
-Thickness and current density relationship, scale-dependent properties of current sheets in the solar wind
-
-# Conclusion
-
-- The properties of the discontinuities is related to the local plasma parameters
-  - Thickness => ion inertial length
-  - Current density => Alfven velocity (current density)
-- Normalized thickness and current density of discontinuities remain constant with radial distance
-- Anisotropy of the plasma is expected to be larger near the sun to explain the observed speed change ratio $Δv_i/Δv_A$.
-
-- Normalized thickness and current density of discontinuities remain constant with radial distance (negligible change compared to their spread).
-In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease in normalized thickness and increase in normalized current density with radial distance.
-
-- Better alignment period has a slightly better agreement of the properties of the discontinuities (normalized thickness, current density, $|\Delta \mathbf{B}/B|$ and rotation angle) between PSP and Earth-orbiting missions.
-- $B_N/B$ and in-plane rotation angle are significantly different between PSP and Earth-orbiting missions independent of the alignment period.
-
-# References
-
--   @velliUnderstandingOriginsHeliosphere2020
-
--   @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
-
-    ```         
-    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensification of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
-    ```
-
-# Appendix
+See [github](https://github.com/beforerr/psp_conjunction) for the code.

### 2025-10-29 notebooks/00_index.qmd
docs: methods (#1)

@@
 using SPEDAS: setmeta, setmeta!
-using Beforerr: _theme_legend, easy_save, hideylabel!
+using Beforerr: _theme_legend, easy_save, hideylabel!, align_ylabels!
 using PartialFunctions
@@
 includet("../src/plot.jl")
+
+set_Z_theme!()
 ```
@@
 let add_fit = true, add_Va = true
-    f = Figure(; size=(450, 400))
-    faxs, = plot_candidate(f[1, 1], filter_low_mva_quality(psp_df)[20, :], psp_conf, Second(4); add_fit, legend=nothing, add_Va)
-    faxs, = plot_candidate(f[1, 2], filter_low_mva_quality(thm_df)[12, :], thm_conf, Second(2); add_fit, add_Va)
+    f = Figure(; size=(600, 400))
+    psp_row = filter_low_mva_quality(psp_df)[20, :]
+    faxs, = plot_candidate(f[1, 1], psp_row, psp_conf, Second(6); add_fit, legend=nothing, add_Va)
+    align_ylabels!(faxs.axes)
+    thm_row = filter_low_mva_quality(thm_df)[18, :]
+    faxs, = plot_candidate(f[1, 2], thm_row, thm_conf, Second(8); add_fit, add_Va)
     hideylabel!.(faxs.axes)
@@
     # hideylabel!.(faxs.axes)
+
+    @info "PSP" psp_row.ΔV_ratio psp_row.ΔV_cosθ
+    @info "THEMIS" thm_row.ΔV_ratio thm_row.ΔV_cosθ
+
     colgap!(f.layout, 1)
@@
 ```
+
+![](../figures/event-example.png)
+
+┌ Info: PSP
+│   psp_row.ΔV_ratio = 0.31703819329006777
+└   psp_row.ΔV_cosθ = -0.8208860063945036
+┌ Info: THEMIS
+│   thm_row.ΔV_ratio = 0.3268322029115623
+└   thm_row.ΔV_cosθ = -0.9457794099717979
 
@@
 ## Overview
-
-<!-- TODO: add Alfvénicity over time -->
 
@@
 
-set_Z_theme!()
 ```
@@
 # tmax_wind = DateTime("2021-01-18")
-```
-
-```{julia}
-tvars_themis = [
-    set(tnorm_combine ∘ THEMIS.B_GSE; ylabel=𝒀.B, labels=𝑳.B_XYZ),
-    set(THEMIS.n; ylabel=𝒀.n),
-    replace_outliers! ∘ set(THEMIS.V_GSE; ylabel=𝒀.V, labels=𝑳.V_XYZ),
-    set(THEMIS.eTemp; ylabel=𝒀.T)
-]
 ```
@@
 ```{julia}
+using Beforerr: add_labels!, align_ylabels!
 update_theme!(; Lines=(linewidth=1, alpha=0.9), figure_padding=(1, 1, 1, 15))
 
-for enc in 7:9
+function add_wind_twin!(gl, wind_axs)
+    # Create a twin axis for Wind magnetic field and density (multiply by the radial ratio)
+    # 1AU / 1Rsun =215
+    B_ax = wind_axs.axes[1]
+    B_ax2 = Axis(gl[1, 1]; yaxisposition=:right, rightspinevisible=true, rightspinecolor=:darkgray)
+    hidexdecorations!(B_ax2, grid=false)
+    ylims!(B_ax, 0.1, 9.9)
+    ylims!(B_ax2, 0.1 * (0.1)^(-1.59), 9.9 * (0.1)^(-1.59))
+    n_ax = wind_axs.axes[2]
+    n_ax2 = Axis(gl[2, 1]; yaxisposition=:right, rightspinevisible=true, rightspinecolor=:darkgray)
+    hidexdecorations!(n_ax2, grid=false)
+    ylims!(n_ax, 3, 16)
+    ylims!(n_ax2, 3 * (0.1)^(-1.96), 16 * (0.1)^(-1.96))222
+end
+
+function overview_plot(enc)
     (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)
     legend = (; position=Top())
-    labels = '1':'9'
-    padding = (0, 30, 0, -30)
+
     f = Figure(; size=(1000, 800))
-    faxs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
-    modify_faxs_base!(faxs)
-    faxs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
-    modify_faxs_base!(faxs)
+    psp_axs = plot_PSP(f[1, 1], tmin_psp, tmax_psp, get_vl_ratio_ts(psp_df)...; legend)
+    modify_faxs_base!(psp_axs)
+    gl = GridLayout(f[1, 2])
+    wind_axs = plot_Wind(f[1, 2], tmin_wind, tmax_wind - Day(1), get_vl_ratio_ts(wind_df)...; legend)
+    modify_faxs_base!(wind_axs)
 
-    add_labels!(f[1, 1]; labels, open="(a.", padding)
-    add_labels!(f[1, 2]; labels, open="(b.", padding)
-    display(f)
+    labels = (; labels='1':'9', position=Left(), padding=(32, -32, 0, 0))
+    add_labels!(f[1, 1]; labels..., open="(a.")
+    add_labels!(f[1, 2]; labels..., open="(b.")
+    colgap!(f.layout, 2)
+
+    hideylabel!.(wind_axs.axes)
+    add_wind_twin!(gl, wind_axs)
+    align_ylabels!(psp_axs.axes)
     easy_save("overview-$enc-all")
+    return f
 end
+
+overview_plot(7)
+# overview_plot.(7:9)
 ```
+
+![](../figures/overview-7-all.png)
+![](../figures/overview-8-all.png)
+![](../figures/overview-9-all.png)
 

### 2025-10-29 notebooks/02_stats.qmd
docs: methods (#1)

@@
 using CairoMakie
-using Beforerr: _theme_legend, easy_save
+using Beforerr: _theme_legend, easy_save, hide_facet_labels!, add_labels!
 using AlgebraOfGraphics
@@
 
+includet("../src/plot.jl")
+
 # https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
@@
 set_Z_theme!()
-formats = (:pdf, :png)
 ```
@@
 # taus = Second.(2 .^ (0:6))
-df = workload(taus)
+wdf = workload(taus)
 
@@
 
-@chain df begin
+df = @chain wdf begin
     DC.compute_Alfvenicity_params!()
     DC.compute_params!()
-    @transform! @astable begin
+    @transform @astable begin
         :Δ𝐁 = @. norm(:B_us - :B_ds)
@@
         :duration = _float64.(ustrip.(:duration .|> u"s"))
+        :L_n_mva = _float64.(ustrip.(:L_n_mva))
+        :J_m_max_mva = _float64.(ustrip.(:J_m_max_mva))
+        :L_n_cross = _float64.(ustrip.(:L_n_cross))
+        :J_m_max_cross = _float64.(ustrip.(:J_m_max_cross))
     end
@@
 subset_𝐧(df, 𝐧) = 𝐧 == :mva ? filter_low_mva_quality(df) : df
+const datalimits = x -> quantile(x, [0.01, 0.99])
 ```
@@
 
-fs = map([:mva]) do 𝐧
+update_theme!(;
+    Legend=(; framevisible=false, padding=(0, 0, 0, 0)),
+)
+
+function plot_properties_hist(df, 𝐧)
     figure = (; size=(450, 600))
@@
 
+    l_sym = first(𝒎.l_norm)
     tdf = @chain df begin
-        @subset(.!isnan.(:L_n_mva_norm); view=true)
+        @subset(.!isnan.($l_sym); view=true)
         subset_𝐧(𝐧)
-        dropmissing(:L_n_mva_norm)
+        dropmissing(l_sym)
     end
 
-    vars = [𝒎.l_log, 𝒎.l_norm_log, 𝒎.j_log, 𝒎.j_norm_log, 𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
-    labels = ["Thickness", "Normalized thickness", "Current density", "Normalized current density", "|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]
-    # append!(vars, [ :Δ𝐁_fit => log10 => "Log Δ𝐁_fit", :Δ𝐁_fit_norm => log10 => "Log Δ𝐁_fit_norm"])
-    # append!(labels, ["Δ𝐁_fit", "Δ𝐁_fit_norm"])
+    l_vars = [𝒎.l_log, 𝒎.l_norm_log]
+    j_vars = [𝒎.j_log, 𝒎.j_norm_log]
+    B_vars = [𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
+    l_labels = ["Thickness", "Normalized thickness"]
+    j_labels = ["Current density", "Normalized current density"]
+    B_labels = ["|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]
 
-    plt = AoG.data(tdf) *
-          mapping(vars, layout=AoG.dims(1) => renamer(labels)) *
-          mapping(color=:id, linestyle=:enc) *
+    facet = (; linkxaxes=:none, linkyaxes=:none)
+    layer = mapping(color=:id, linestyle=:enc) *
             AoG.density(; datalimits) * visual(Lines)
-    f = draw(plt, scales(Layout=(; palette=wrapped(cols=2))); axis=(; yscale=log10), figure, legend=(; position=:top))
-    hide_facet_labels!(f)
+    axis = (; yscale=log10)
+
+    plt = AoG.data(tdf) * mapping(l_vars, layout=AoG.dims(1)) * layer
+    f = draw(plt; axis, figure, legend=(; position=:top))
+    ylims!.(getproperty.(f.grid, :axis), 10^(-1.6), 10^(0.1))
+
+    gl2 = GridLayout(f.figure[2, 1:end])
+    f2 = draw!(gl2, AoG.data(tdf) * mapping(j_vars, layout=AoG.dims(1)) * layer; axis)
+
+    gl3 = GridLayout(f.figure[3, 1:end])
+    # no need to subset and dropmissing
+    f3 = draw!(gl3, AoG.data(df) * mapping(B_vars, layout=AoG.dims(1)) * layer; axis)
+
+    hide_facet_labels!.((f, f2, f3))
     rowgap!(f.figure.layout, 1)
-    easy_save("$fname-$𝐧"; formats, force=true)
+    add_labels!(f.figure; position=Left(), padding=(20, -20, 0, 0))
+    colgap!.((f.figure.layout, gl2, gl3), 1)
+
+    return f
+end
+
+fs = map([:mva, :cross]) do 𝐧
+    plot_properties_hist(df, 𝐧)
+    # subset df by plasma beta
+    # plot_properties_hist(@rsubset(df, :β < 1), 𝐧)
+    # plot_properties_hist(@rsubset(df, :β > 3), 𝐧)
+    # easy_save("$fname-$𝐧"; force=true)
+    easy_save("$fname-$𝐧")
 end
@@
 ```
+
+![properties_hist-mva](../figures/properties_hist-mva.png)
+![properties_hist-cross](../figures/properties_hist-cross.png)
 
@@
 ```{julia}
-let df = dropmissing(df, :duration)
-    layer = AoG.density(; datalimits=x -> quantile(x, [0.02, 0.99])) * visual(Lines)
-    # layer = AoG.histogram(; datalimits=x -> quantile(x, [0.02, 0.99]), bins = 0:0.3:30) * mapping(col=:id)
-    plt = data(df) * mapping(:duration, linestyle=:enc, color=:id) * layer
-    plt = plt + mapping(2 .^ (1:4)) * visual(VLines, color=:gray, linestyle=:dash)
-    # plt *= (mapping(col=direct("col1")) + mapping(color=:tau, col=direct("col2")))
-    # scales(Col=(; legend=false))
-    draw(plt, axis=(; yscale=log10))
-    easy_save("duration_dist"; formats)
+let tdf = dropmissing(df, :duration)
+    psp_df = @chain tdf begin
+        @rsubset(:id == "PSP"; view=true)
+        @transform(:duration = :duration .* 4, :id = "PSP (4x)")
+    end
+    fdf = vcat(tdf, psp_df)
+    axis = (; yscale=log10)
+    layer = mapping(:duration) * AoG.density(; datalimits=x -> quantile(x, [0.01, 0.99])) * visual(Lines)
+    plt = data(fdf) * mapping(color=:id) * layer
+    plt = plt + mapping(2 .^ (0:5)) * visual(VLines, color=:gray, linestyle=:dash)
+    fg = draw(plt; axis)
+
+    easy_save("duration_dist")
 end
 ```
+
+![](../figures/duration_dist.png)
 
@@
     draw(plt, axis=(; yscale=log10), facet=(; linkxaxes=:none, linkyaxes=:none))
-    easy_save("duration_dist_tau"; formats)
+    easy_save("duration_dist_tau")
 end
@@
 
-for 𝐧 in [:mva]
+for 𝐧 in [:mva, :cross]
     view = true
     𝒎 = var_mapping(; 𝐧)
+
+    l_sym = first(𝒎.l_norm)
+
     tdf = @chain df begin
-        dropmissing(:L_n_mva)
-        @transform(:L_n_mva = Float64.(ustrip.(:L_n_mva)), :J_m_max_mva = Float64.(ustrip.(:J_m_max_mva)))
+        dropmissing(l_sym)
         subset_𝐧(𝐧)
@@
     spec2 = plt * mapping(𝒎.l_norm, 𝒎.j_norm)
-    B_l_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.l_norm) # Not strong correlation
-    B_j_spec = plt * mapping(𝒎.Δ𝐁_norm, 𝒎.j_norm) # Not strong correlation
+    B_l_spec = plt * mapping(𝒎.l_norm, 𝒎.Δ𝐁_norm) # Not strong correlation
+    B_j_spec = plt * mapping(𝒎.j_norm, 𝒎.Δ𝐁_norm) # Not strong correlation
+
+    d_lims = (10^(-2.5), 10^3.5)
+    j_lims = (10^(-3.6), 10^2.4)
+    B_lims = (10^(-3), 10^3)
 
     grid1 = draw!(fig[1, 1], spec1; axis)
-    grid2 = draw!(fig[2, 1], spec2; axis)
-    grid3 = draw!(fig[3, 1], B_l_spec; axis)
-    grid4 = draw!(fig[4, 1], B_j_spec; axis)
+    grid2 = draw!(fig[2, 1], spec2; axis=(; axis..., limits=(d_lims, j_lims)))
+    grid3 = draw!(fig[3, 1], B_l_spec; axis=(; axis..., limits=(d_lims, nothing)))
+    grid4 = draw!(fig[4, 1], B_j_spec; axis=(; axis..., limits=(j_lims, nothing)))
 
     hide_facet_labels!.((grid2, grid3, grid4))
+    rowgap!(fig.layout, 4)
 
-    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 37, 0, 0))
+    add_labels!([fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]]; position=Left(), padding=(0, 37, 0, 0))
     display(fig)
-    easy_save("joint_properties-$𝐧"; formats, force=true)
+    # easy_save("joint_properties-$𝐧"; force=true)
+    easy_save("joint_properties-$𝐧")
 end
@@
 
+![](../figures/joint_properties-mva.png)
+![](../figures/joint_properties-cross.png)
+
 ### In-plane rotation angle, Bn
+
+![](../figures/B_n_ω_subset=true.png) and ![](../figures/B_n_ω_subset=false.png)
+
+```{julia}
+layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
+
+for 𝐧 in [:mva, :cross], subset in (true)
+    normalization = :column
+    𝒎 = var_mapping(; 𝐧)
+    B_sym = Symbol(:B_n_, 𝐧)
+    tdf = dropmissing(df, B_sym)
+    # tdf = subset ? subset_𝐧(tdf, 𝐧) : tdf
+    tdf = subset_𝐧(tdf, 𝐧)
+    plt = AoG.data(tdf) * mapping(col=:id => layout_func)
+    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
+    f = draw(B_n_ω_spec)
+    colgap!(f.figure.layout, 10)
+
+    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
+    ff = f.figure[0, 1:3]
+    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
+    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
+    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
+    rowgap!(f.figure.layout, 4)
+    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
+    # easy_save("B_n_ω_subset=$subset"; force=true)
+    easy_save("B_n_ω_-$𝐧-subset=$subset")
+end
+```
 
@@
     plt = AoG.data(tdf) * mapping(col=:id => layout_func)
-    B_n_ω_spec = plt * mapping(𝒎.bn, 𝒎.ω_in) * fhist(; binedges=(0:0.03:0.99, 0:6:180), normalization)
-    f = draw(B_n_ω_spec)
-    colgap!(f.figure.layout, 10)
-
-    den_base = AoG.data(tdf) * mapping(color=:id => layout_func) * AoG.density(; datalimits) * visual(Lines)
-    ff = f.figure[0, 1:3]
-    grid1 = draw!(ff[1, 1], den_base * mapping(𝒎.ω_in))
-    grid2 = draw!(ff[1, 2], den_base * mapping(𝒎.bn); axis=(; ylabel="", yscale=log10))
-    legend!(ff[1, 1], grid1; tellheight=false, tellwidth=false, halign=:right, valign=:top)
-    rowgap!(f.figure.layout, 4)
-    add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
-    easy_save("B_n_ω_subset=$subset"; formats, force=true)
+    duration_spec = plt * mapping(:duration, 𝒎.ω_in)
+    f = draw(duration_spec)
+    display(f)
 end
@@
     ΔV_spec = plt * mapping(𝒎.ΔV_ratio, 𝒎.ΔV_cosθ) * AoG.density(; datalimits=((0, 1.1), (-1, 1)))
-    duration_Q_spec = plt * mapping(:duration, 𝒎.Q) * AoG.density(; datalimits=((0, 3.1), Q_limit))
+    # duration_Q_spec = plt * mapping(:duration, 𝒎.Q) * AoG.density(; datalimits=((0, 3.1), Q_limit))
+    duration_Q_spec = plt * mapping(:duration => log10 => "Log Duration (s)", 𝒎.Q) * AoG.density(; datalimits=((-0.9, 1.1), Q_limit))
+    # duration_Q_spec = plt * mapping(:duration => log10, 𝒎.Q) * fhist(; binedges=(-0.9:0.1:1.1, -0.99:0.1:0.99), normalization=:column)
     σc_Q_spec = plt * mapping(:σ_c => L"σ_c", 𝒎.Q) * AoG.density()
@@
     hide_facet_labels!.((grid2, grid3, grid4))
-    easy_save("Q_sonnerup_joint_dist_den"; formats, force=true)
-    display(fig)
+    easy_save("Q_sonnerup_joint_dist_den")
 end

### 2025-10-29 notes.qmd
docs: methods (#1)

@@
 
-##
-
-![](images/paste-20.png)
-
 Given timeseries $(R_a, \phi_a$, $R_b(t)$,
@@
 
+<!-- ::: {#fig-plasma-adiabatic-evolution .column-page}
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR-next.svg)
+
+![](figures/evolution/plasma-adiabatic-evolution_e2-DSCOVR.svg)
+
+Comparison of plasma dimensionless quantities (plasma beta and normalized plasma speed by Alfven speed) between PSP (red) and DSCOVR (blue).
+Yellow dots are predicted plasma beta and normalized speed using formulary from @perroneRadialEvolutionSolar2019.
+::: -->
+
+<!-- sensing solar wind emitted from the same region on the solar surface, with the caveat that dynamical processes at the chromosphere–corona interface have not dramatically altered the solar footpoint within the time corresponding to the radial propagation from the measurement of one spacecraft to that of the other.
+-->
+
+<!-- OUTDATED
+To achieve this, we utilize a configuration where two spacecraft are radially aligned in the Heliographic (HG) frame, with the longitude fixed on the Sun.
+It is important to note that the plasma parcels observed by the two spacecraft may differ in composition, as solar wind particles propagate at varying velocities.
+For instance, protons often exhibit a beam in their velocity distribution function, while the thermal speed of electrons is much higher than their bulk speed.
+Nonetheless, observing plasma that passes through both spacecraft offers the best opportunity to study the evolution of solar wind discontinuities with minimal influence from other processes during propagation.
+It is also expected that these plasma parcels evolve due to heating and other processes.
+
+The plasma parcels in question are large-scale structures.
+As the scale size decreases below the mesoscale [@viallMesoscaleStructureSolar2021] (with radial sizes ranging from approximately 5 × 10³ km to 10⁷ km), it becomes increasingly unlikely to identify the same structure, depending on the latitude difference between the two spacecraft.
+Furthermore, although large-scale structures (especially density enhancements) can be identified as passing through both spacecraft [@berriotIdentificationSinglePlasma2024], it is nearly impossible to detect kinetic-scale structures, such as solar wind discontinuities (with time scales on the order of seconds), by both spacecraft simultaneously.
+Therefore, our study focuses on the statistical properties of solar wind discontinuities within the "same" large-scale structures that pass through both spacecraft.
+-->
+
 ## Anisotropy

### 2025-10-29 src/plot.jl

@@ -1,7 +1,7 @@
 import AlgebraOfGraphics as AoG
 import AlgebraOfGraphics: draw!
 import Discontinuity
-using SPEDAS: tvec, setmeta, setmeta!
+using SPEDAS: tvec, setmeta, setmeta!, Product
 using Statistics
 using CairoMakie
 using TimeseriesUtilities: times
@@ -20,7 +20,7 @@ export set_Z_theme!
 set_Z_theme!() = begin
     AoG.set_aog_theme!()
     update_theme!(;
-        figure_padding = 1,
+        figure_padding = 2,
         fonts = (; regular = AoG.firasans("Regular"), bold = AoG.firasans("Medium")),
         Legend = (; framevisible = false, padding = (0, 0, 0, -15)),
         Axis = (; xlabelfont = :bold, ylabelfont = :bold),
@@ -76,13 +76,16 @@ function plot_candidate(f, event, B::Union{AbstractArray, Product}, toffset = no
     return fax
 end
 
+using NaNStatistics
+
+subtract_func(x; dims) = mean.(nanextrema(x; dims))
 
 function plot_candidate(f, event, config::AbstractDict, toffset = Second(0); add_Va = false, add_J = false, add_fit = false, kwargs...)
     tmin, tmax = event.t_us, event.t_ds
     t0 = tmin - toffset
     t1 = tmax + toffset
-    B = setmeta(config["B"](t0, t1); ylabel = "B (nT)")
-    V = setmeta(config["V"](t0, t1); ylabel = "V (km/s)")
+    B = setmeta(config["B"](t0, t1); ylabel = "(nT)")
+    V = setmeta(config["V"](t0, t1); ylabel = "(km/s)")
 
     B_subset = tview(B, tmin, tmax)
     B_mva = setmeta(mva(B, B_subset); labels = 𝑳.B_LMN)
@@ -91,8 +94,8 @@ function plot_candidate(f, event, config::AbstractDict, toffset = Second(0); add
 
     if add_Va
         n = config["n"](t0, t1)
-        Va = setmeta(Alfven_velocity_ts(B_mva, n) ./ u"km/s"; labels = 𝑳.Va_LMN, ylabel = "V (km/s)")
-        result = (result..., tsubtract(Va))
+        Va = setmeta(Alfven_velocity_ts(B_mva, n) ./ u"km/s"; labels = 𝑳.Va_LMN, ylabel = "(km/s)")
+        result = (result..., tsubtract(Va, subtract_func))
     end
 
     if add_J

### 2025-12-01 article.qmd
docs: update figures and text

@@
 The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
-Panel (a.7) and (b.7) present the cross helicity and residual energy, which describe the Alfvénic nature and energetic balance of the ambient plasma, respectively, calculated every 8 minutes.
+Panels (a.7) and (b.7) present the cross helicity and residual energy, calculated every 8 minutes, which characterize the Alfvénic nature and energetic balance of the ambient plasma.
+We compute these quantities in the standard form: $\sigma_c = \frac{2 \langle \delta \mathbf{V} \cdot \delta \mathbf{V}_A \rangle}{ \langle\delta\mathbf{V}^2\rangle + \langle\delta\mathbf{V}_A^2\rangle }, \quad \sigma_r = \frac{\langle\delta \mathbf{V}^2\rangle-\langle\delta \mathbf{V}_A^2\rangle}{\langle\delta \mathbf{V}^2\rangle+\langle\delta \mathbf{V}_A^2\rangle},$ where $\delta \mathbf{V}$ and $\delta \mathbf{V}_A=\delta( \mathbf{B} / \sqrt{\mu_0 \rho})$ are the fluctuating velocity and Alfvén velocity, respectively.
 The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind.

### 2025-12-01 notebooks/01_demo.qmd
docs: update figures and text

@@
 
-TODO: Check Wind examples
+## Check events with $B_n/B > 0.75$
 
 ```{julia}
-using Random
+f = Figure(size=(1800, 1000))
+let df = filter_low_mva_quality(@subset(wind_df, :B_n_mva_norm .> 0.75)), 𝐁 = wind_conf["B"]
+    rows = rand(eachrow(df), min(5, nrow(df)))
+    for (plot_idx, row) in enumerate(rows)
+        plot_candidate(f[1, plot_idx], row, 𝐁; add_B_mva=true)
+    end
+end
 
-f = Figure(size=(1800, 1000))
-
+let df = filter_low_mva_quality(@subset(psp_df, :B_n_mva_norm .> 0.75)), 𝐁 = psp_conf["B"]
     rows = rand(eachrow(df), min(5, nrow(df)))
-for (plot_idx, i) in enumerate(rows)
-    plot_candidate(f[1, plot_idx], i, B_p; add_B_mva=true, add_fit=true)
+    for (plot_idx, row) in enumerate(rows)
+        plot_candidate(f[2, plot_idx], row, 𝐁; add_B_mva=true)
     end
+end
+delete_legends!(f[1:2,1:4])
 f
@@
 ```{julia}
-let df = dropmissing(psp_df, :duration)
-    long_events = df[df.duration.> Second(30), :]
+(Ølet df = dropmissing(psp_df, :duration)
+    long_events = df[df.duration.>Second(30), :]
     println("Found $(nrow(long_events)) events with duration > 30 seconds")
@@
     df = dropmissing(_df, :duration)
-    short_events = df[df.duration.< dt, :]
+    short_events = df[df.duration.<dt, :]
     n = nrow(short_events)

### 2025-12-01 notebooks/02_stats.qmd
docs: update figures and text

@@
 using Beforerr: _theme_legend, easy_save, hide_facet_labels!, add_labels!
+using Beforerr
+using CategoricalArrays
 using AlgebraOfGraphics
@@
 # https://github.com/MakieOrg/AlgebraOfGraphics.jl/issues/464
-foreach([:log10, :log2, :log]) do f
-    @eval import Base: $f
-    @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
-end
+# foreach([:log10, :log2, :log]) do f
+# @eval import Base: $f
+# @eval $f(x::Unitful.Quantity) = $f(ustrip(x))
+# end
 set_Z_theme!()
@@
 
-_float64(x) = Float64(x)
-_float64(::Missing) = missing
+_float64(x) = passmissing(Float64)(x)
 
@@
 end
+
+thm_df = @rsubset(df, :id == "THEMIS"; view=true)
+thm_df.id .= "ARTEMIS"
+df.id = categorical(df.id)
+levels!(df.id, ["PSP", "ARTEMIS", "Wind"])
 
@@
 
-function plot_properties_hist(df, 𝐧)
-    figure = (; size=(450, 600))
-    𝒎 = var_mapping(; 𝐧)
-
-    datalimits = x -> quantile(x, [0.01, 0.99])
-
-    l_sym = first(𝒎.l_norm)
-    tdf = @chain df begin
-        @subset(.!isnan.($l_sym); view=true)
-        subset_𝐧(𝐧)
-        dropmissing(l_sym)
-    end
-
-    l_vars = [𝒎.l_log, 𝒎.l_norm_log]
-    j_vars = [𝒎.j_log, 𝒎.j_norm_log]
-    B_vars = [𝒎.Δ𝐁, 𝒎.Δ𝐁_norm_log]
-    l_labels = ["Thickness", "Normalized thickness"]
-    j_labels = ["Current density", "Normalized current density"]
-    B_labels = ["|Δ𝐁|", "|Δ𝐁|/⟨|𝐁|⟩"]
-
-    facet = (; linkxaxes=:none, linkyaxes=:none)
-    layer = mapping(color=:id, linestyle=:enc) *
-            AoG.density(; datalimits) * visual(Lines)
-    axis = (; yscale=log10)
-
-    plt = AoG.data(tdf) * mapping(l_vars, layout=AoG.dims(1)) * layer
-    f = draw(plt; axis, figure, legend=(; position=:top))
-    ylims!.(getproperty.(f.grid, :axis), 10^(-1.6), 10^(0.1))
-
-    gl2 = GridLayout(f.figure[2, 1:end])
-    f2 = draw!(gl2, AoG.data(tdf) * mapping(j_vars, layout=AoG.dims(1)) * layer; axis)
-
-    gl3 = GridLayout(f.figure[3, 1:end])
-    # no need to subset and dropmissing
-    f3 = draw!(gl3, AoG.data(df) * mapping(B_vars, layout=AoG.dims(1)) * layer; axis)
-
-    hide_facet_labels!.((f, f2, f3))
-    rowgap!(f.figure.layout, 1)
-    add_labels!(f.figure; position=Left(), padding=(20, -20, 0, 0))
-    colgap!.((f.figure.layout, gl2, gl3), 1)
-
-    return f
-end
-
 fs = map([:mva, :cross]) do 𝐧
@@
     # plot_properties_hist(@rsubset(df, :β > 3), 𝐧)
-    # easy_save("$fname-$𝐧"; force=true)
-    easy_save("$fname-$𝐧")
+    easy_save("$fname-$𝐧"; force=true)
+    # easy_save("$fname-$𝐧")
 end
@@
 
-    easy_save("duration_dist")
+    easy_save("duration_dist"; force=true)
 end
@@
     pretty_legend!(fig, ga)
-    easy_save("Alfvenicities"; formats, force=true)
+    easy_save("Alfvenicities"; force=true)
     # vars = [ΔV_cosθ, ΔV_ratio, dB_over_B, dB_max_over_B]
@@
     psp_df = @rsubset(df, :id == "PSP"; view=true)
-    thm_df = @rsubset(df, :id == "THEMIS"; view=true)
+    thm_df = @rsubset(df, :id ∈ ("ARTEMIS", "THEMIS"); view=true)
     wind_df = @rsubset(df, :id == "Wind"; view=true)
-    (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha)) + AoG.data(psp_df)
+    AoG.data(psp_df) + (AoG.data(thm_df) + AoG.data(wind_df) * visual(; alpha))
 end
@@
 ```{julia}
-layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
-
 for 𝐧 in [:mva, :cross]
@@
     display(fig)
-    # easy_save("joint_properties-$𝐧"; force=true)
-    easy_save("joint_properties-$𝐧")
+    easy_save("joint_properties-$𝐧"; force=true)
+    # easy_save("joint_properties-$𝐧")
 end
@@
 ```{julia}
-layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
-
 for 𝐧 in [:mva, :cross], subset in (true)
@@
     add_labels!([ff[1, 1], ff[1, 2], f.figure[1, 1:end]]; position=Left(), padding=(0, 40, 0, -5))
-    # easy_save("B_n_ω_subset=$subset"; force=true)
-    easy_save("B_n_ω_-$𝐧-subset=$subset")
+    easy_save("B_n_ω_-$𝐧-subset=$subset"; force=true)
+    # easy_save("B_n_ω_-$𝐧-subset=$subset")
 end
@@
 
-![](../figures/B_n_ω_subset=true.png) and ![](../figures/B_n_ω_subset=false.png)
+![](../figures/B_n_ω_-mva-subset=true.png) and ![](../figures/B_n_ω_-mva-subset=false.png)
 
 ```{julia}
-layout_func(id) = id == "PSP" ? "PSP" : "Wind + THEMIS"
-
 for 𝐧 in [:mva], subset in (true, false)
@@
 
+fig = Figure(; size=(500, 800))
 let vars = [:Q_sonnerup, :duration, :σ_c]
@@
     end
-
-    fig = Figure(; size=(500, 800))
     plt = AoG.data(tdf) * mapping(col=:id => layout_func)
@@
     end
-    add_labels!(fig[1:4, 1]; position=Left(), padding=(0, 0, 0, -5))
+    add_labels!([fig[1, 1], fig[2, 1], fig[3, 1], fig[4, 1]]; position=Left(), padding=(0, 0, 0, -5))
     hide_facet_labels!.((grid2, grid3, grid4))
-    easy_save("Q_sonnerup_joint_dist_den")
+    easy_save("Q_sonnerup_joint_dist_den"; force=true)
 end

### 2025-12-01 lib/zhangEvolutionSolarWind2025/src/zhangEvolutionSolarWind2025.jl

@@ -1,0 +1,30 @@
+# Accompanying package to load the results of the paper "Zhang et al. (2025) - Evolution of solar wind discontinuities in the inner heliosphere"
+module zhangEvolutionSolarWind2025
+using JLD2
+
+# Packges for reconstruction
+using DataFrames
+using StaticArrays
+using Unitful
+using CommonDataFormat: Epoch
+using Discontinuity: compute_Alfvenicity_params!, compute_params!
+
+const DATADIR = joinpath(@__DIR__, "../../../data")
+
+"""
+Load the events for a given id (available ids: "PSP", "Wind", "THEMIS").
+"""
+function load(id)
+    # Find all files matching the pattern for the given id
+    # Example: id=Wind_t0=2021-01-17_t1=2021-01-18_tau=2.0.jld2
+    pattern = Regex("id=$(id)_.*\\.jld2\$")
+    files = filter(f -> occursin(pattern, f), readdir(DATADIR; join = true))
+
+    isempty(files) && error("No files found for id: $id")
+    # Load and combine all matching files
+    return mapreduce(vcat, files) do file
+        jldopen(file)["events"] |> compute_params! |> compute_Alfvenicity_params!
+    end
+end
+
+end

### 2025-12-01 index.tex
Built site for gh-pages

--- 2025-10-22 article.tex
@@
 \makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{acacac}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
+\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
+\makeatother
+\makeatletter
 \@ifpackageloaded{caption}{}{\usepackage{caption}}
@@
 \maketitle
-
-\section{Abstract}\label{abstract}
-
+\begin{abstract}
 We analyze three time intervals during which the Parker Solar Probe (PSP) was in close proximity to the Sun and investigate current sheets (magnetic discontinuities) observed by PSP, ARTEMIS, and Wind.
@@
 Finally, the Alfvénicity of the current sheets correlates strongly with the cross helicity and residual energy of the surrounding solar wind, demonstrating that current sheet dynamics are largely governed by the ambient turbulent environment.
+\end{abstract}
+
+\begin{tcolorbox}[enhanced jigsaw, colback=white, opacitybacktitle=0.6, opacityback=0, leftrule=.75mm, toprule=.15mm, left=2mm, colframe=quarto-callout-note-color-frame, breakable, colbacktitle=quarto-callout-note-color!10!white, toptitle=1mm, titlerule=0mm, bottomtitle=1mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, arc=.35mm, rightrule=.15mm, bottomrule=.15mm, coltitle=black]
+
+This document and the accompanying website may contain outdated information.
+
+\end{tcolorbox}
 
@@
 The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
-Panel (a.7) and (b.7) present the cross helicity and residual energy, which describe the Alfvénic nature and energetic balance of the ambient plasma, respectively, calculated every 8 minutes.
+The PSP occurrence rates are broadly consistent with previous studies at similar heliocentric distances \citep{lotekarKineticscaleCurrentSheets2022}.
+We detect significantly more current sheets than the ∼150 events reported at 1 AU by \citet{vaskoKineticscaleCurrentSheets2022, zhangSolarWindDiscontinuities2025b}, largely because our detection is not restricted to only the most intense kinetic-scale current sheets (see methods below).
+Panels (a.7) and (b.7) present the cross helicity and residual energy, calculated every 8 minutes, which characterize the Alfvénic nature and energetic balance of the ambient plasma.
+We compute these quantities in the standard form: \(\sigma_c = \frac{2 \langle \delta \mathbf{V} \cdot \delta \mathbf{V}_A \rangle}{ \langle\delta\mathbf{V}^2\rangle + \langle\delta\mathbf{V}_A^2\rangle }, \quad \sigma_r = \frac{\langle\delta \mathbf{V}^2\rangle-\langle\delta \mathbf{V}_A^2\rangle}{\langle\delta \mathbf{V}^2\rangle+\langle\delta \mathbf{V}_A^2\rangle},\) where \(\delta \mathbf{V}\) and \(\delta \mathbf{V}_A=\delta( \mathbf{B} / \sqrt{\mu_0 \rho})\) are the fluctuating velocity and Alfvén velocity, respectively.
 The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind.

### 2025-12-01 index.qmd
docs: publish as manuscript

@@
-See [article.qmd](article.qmd) for the main article.
+---
+title: Evolution of solar wind discontinuities in the inner heliosphere
+subtitle: PSP and Earth conjunctions and alignments
+author:
+  - name: Zijin Zhang
+    email: zijin@ucla.edu
+    orcid: 0000-0002-9968-067X
+    affiliation: University of California, Los Angeles
+    roles: writing
+    corresponding: true
+  - name: Anton V. Artemyev
+    email: aartemyev@igpp.ucla.edu
+    orcid: 0000-0001-8823-4474
+    affiliation: University of California, Los Angeles
+  - name: Vassilis Angelopoulos
+    email: vassilis@ucla.edu
+    orcid: 0000-0001-7024-1561
+    affiliation: University of California, Los Angeles
+  - name: Tai Phan
+    email: phan@ssl.berkeley.edu
+    orcid: 0000-0002-6924-9408
+    affiliation: Space Sciences Laboratory, University of California, Berkeley
+format:
+  html: default
+  # latex: 
+    # cite-method: natbib
+  typst: default
+abstract: We analyze three time intervals during which the Parker Solar Probe (PSP) was in close proximity to the Sun and investigate current sheets (magnetic discontinuities) observed by PSP, ARTEMIS, and Wind.
+Using an automated detection algorithm, we identify and examine the statistical properties of over 45,000 current sheets across the three intervals, including approximately 17,000 from PSP.
+The results show that current sheets broaden with increasing heliocentric distance, while their characteristic current density remains largely unchanged.
+The thickness and current density are strongly anti-correlated, indicating that thinner current sheets carry stronger currents, consistent with turbulent intermittency.
+Distinct distributions of magnetic field jumps and rotation angles are also observed among the different missions, suggesting structural evolution of current sheets as the solar wind expands.
+Most current sheets display small variations in magnetic field magnitude, indicating a predominantly force-free character.
+Significant deviations from the Walén relation persist even when pressure anisotropy is included, implying that anisotropy alone cannot explain the observed departures from ideal rotational discontinuities.
+Finally, the Alfvénicity of the current sheets correlates strongly with the cross helicity and residual energy of the surrounding solar wind, demonstrating that current sheet dynamics are largely governed by the ambient turbulent environment.
+---
 
-See [notebooks/00_index.qmd](notebooks/00_index.qmd), [notebooks/02_stats.qmd](notebooks/02_stats.qmd), and [notebooks/10_results.qmd](notebooks/10_results.qmd) for the data analysis.
+::: {.callout-note}
+This document and the accompanying website may contain outdated information. 
+:::
 
-See [github](https://github.com/beforerr/psp_conjunction) for the code.
+# Introduction
+
+Current sheets are ubiquitous mesoscale structures in the solar wind, where the magnetic field changes direction abruptly over ion-scale thicknesses, while their lateral extents can exceed typical magnetohydrodynamic (MHD) scales.
+These current sheets most readily identified from sharp magnetic-field rotations but can also be evident in simultaneous changes of plasma density, bulk velocity, and temperature.
+
+In turbulent solar wind plasmas, current sheets are widely recognized as signatures of intermittency, contributing to the non-Gaussian nature of magnetic field fluctuations and localized energy dissipation [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They play a crucial role in mediating the transfer of energy across scales, from large-scale MHD fluctuations down to ion and electron kinetic scales, and are believed to be important sites of plasma heating and particle acceleration [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
+
+<!-- Because they concentrate gradients and localized dissipation, current sheets are central features of solar-wind intermittency and non-Gaussian magnetic fluctuations [@borovskyContributionStrongDiscontinuities2010; @grecoPartialVarianceIncrements2017].
+They are therefore important for understanding how energy cascades from large MHD scales to ion and electron kinetic scales, and for identifying sites of plasma heating and particle energization [@osmanIntermittencyLocalHeating2012; @tesseinAssociationSuprathermalParticles2013].
+-->
+
+Understanding the formation, structure, and evolution of current sheets at different heliocentric distances is therefore essential for elucidating the mechanisms that govern solar wind turbulence and heating.
+A number of statistical studies have investigated current sheet properties across a broad range of radial distances [@marianiStatisticalStudyMagnetohydrodynamic1983; @artemyevDynamicsIntenseCurrents2018; @perroneCoherentEventsIon2020; @liuCharacteristicsInterplanetaryDiscontinuities2021; @lotekarKineticscaleCurrentSheets2022; @vaskoKineticscaleCurrentSheets2022; @vaskoKineticScaleCurrentSheets2024].
+Despite this progress, several important gaps remain.
+First, many earlier studies rely on datasets obtained at different times and with instruments of varying temporal resolution, which complicates consistent comparisons across heliocentric distances.
+Few investigations have examined simultaneous observations from multiple radial positions [@velliUnderstandingOriginsHeliosphere2020; @telloniSpacecraftRadialAlignments2023], limiting our understanding of how current sheet properties evolve as the solar wind expands.
+Second, existing identification methods often depend on fixed thresholds—such as absolute magnetic-field jumps—or are highly sensitive to data resolution, as in the case of partial variance increment techniques.
+To enable meaningful cross-mission comparisons, more robust approaches based on normalized, resolution-independent criteria are needed.
+Finally, most prior work has classified discontinuities within the ideal MHD framework—for instance, distinguishing tangential from rotational discontinuities.
+While useful in some contexts and extensively studied, these categories become inadequate at ion scales, where kinetic and multi-fluid effects play a central role.
+In this study, we therefore move beyond strict MHD classifications and instead emphasize the Alfvénic character of current sheets—that is, the extent to which plasma and magnetic-field variations follow Alfvénic correlations [@shenComparingPlasmaAnisotropy2024].
+Although this perspective is fundamental for understanding the origin and evolution of current sheets, it has received relatively limited attention.
+
+The Parker Solar Probe (PSP) mission offers an unprecedented opportunity to probe current sheets in the near-Sun environment with high cadence and to compare those observations with near-Earth measurements.
+In this study, we focus on three PSP perihelion intervals (Encounters 7–9) selected for their differing geometric alignments with the near-Earth spacecraft ARTEMIS and Wind.
+Encounter 7 features strong radial alignment, enabling sampling of similar solar wind streams while Encounter 8 exhibits weaker alignment and Encounter 9 places PSP roughly 180° away in longitude.
+These contrasting configurations enable a controlled examination of current sheet properties and, more broadly, provide insight into how those properties depend on the solar wind's source region.
+
+Using a robust automated detection algorithm, we identify and analyze more than 45,000 current sheets across the three selected intervals (approximately 17,000 from PSP).
+We systematically characterize their rotation profiles, thicknesses, current densities, magnetic field jumps, and Alfvénic properties.
+The remainder of this paper is organized as follows: Section 2 describes the datasets and analysis methods; Section 3 presents the results and discusses their physical implications; and Section 4 summarizes the main conclusions.
+
+<!-- References
+
+@hudsonDiscontinuitiesAnisotropicPlasma1970
+
+“Knetter [2005] extended this work to intervals in 2002 and 2003 which also included fast wind intervals.
+He obtained similar results to above and amassed a final total collection of 366 discontinuities.
+All of the discontinuities had normal field components consistent with zero.
+He concluded that the discontinuities are best explained as TDs regardless of the amount of dB/B.” ([Vasquez et al., 2007, p.
+2](zotero://select/library/items/VPNY4UFZ)) ([pdf](zotero://open-pdf/library/items/DNN2ADMT?page=2&annotation=9Q8CVTE9))
+-->
+
+# Dataset and method
+
+In this study, we utilize magnetic field and plasma measurements from Parker Solar Probe (PSP) [@foxSolarProbeMission2016], ARTEMIS [@angelopoulosARTEMISMission2011] and Wind missions [@acunaGlobalGeospaceScience1995].
+For PSP, we use high-resolution magnetic field data from the FIELDS instrument [@baleFIELDSInstrumentSuite2016] and plasma data from the Solar Wind Electrons Alphas and Protons (SWEAP) suite [@kasperSolarWindElectrons2016].
+The proton and electron anisotropies are derived from the corresponding electrostatic analyzers' measurements: Solar Probe ANalyzer for Ions (SPAN-I) and Electrons (SPAN-E) [@liviSolarProbeANalyzer2022; @whittleseySolarProbeANalyzers2020].
+For ARTEMIS, we use magnetic field data measured at approximately 5 Hz resolution by the Fluxgate Magnetometer [@austerTHEMISFluxgateMagnetometer2008], as well as plasma velocity and density from the electrostatic analyzer instrument with a resolution of around 4 seconds [@mcfaddenTHEMISESAPlasma2009].
+The following data collected by Wind are used: magnetic fields with a $\sim 11$ Hz resolution measured by the Magnetic Field Investigation (MFI) [@leppingWINDMagneticField1995], the ion (proton and alpha) moments measured by ion (PESA) electrostatic analyzers of the 3D Plasma Analyzer (3DP) [@linThreedimensionalPlasmaEnergetic1995].
+
+<!-- It is important to note that the ESA tends to overestimate proton temperature in the solar wind due to the narrower proton beam compared to the ESA’s energy and angular resolution.
+Therefore, any findings related to temperature anisotropy should be interpreted with caution.
+-->
+
+It is worth noting that for PSP, although ion data is also available from SPC, the SPAN-i data was chosen due to its higher temporal resolution.
+Plasma density estimates delivered by the quasi-thermal noise spectroscopy (QTN) is also available [@moncuquetFirstSituMeasurements2020].
+We generally find that the results using QTN data do not differ significantly from those derived from SPAN-i data.
+Due to the limitations of SPAN-i data during the early mission phases, when a significant portion of the solar wind distributions was out of the instrument’s view, our study concentrates on data beginning with Encounter 7, where SPAN-i provides more accurate measurements.
+
+<!-- 
+E7,20.3,2021-01-17 17:40,Perihelion
+E8,15.9,2021-04-29 08:48,Perihelion
+E9,15.9,2021-08-09 19:11,Perihelion
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E7_orbit.png
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E8_orbit.png
+https://psp-gateway.jhuapl.edu/website/SciencePlanning/MissionEvents/E9_orbit.png
+-->
+
+Our study investigates the evolution of current sheet properties during the radial expansion of the solar wind.
+To distinguish spatial variations from temporal effects, we analyze three distinct time intervals corresponding to Parker Solar Probe (PSP) Encounters 7 through 9, each characterized by different PSP–Earth alignments [@telloniSpacecraftRadialAlignments2023; @velliUnderstandingOriginsHeliosphere2020].
+Encounter 7 features a favorable alignment between PSP and Earth, enabling nearly simultaneous multi-point observations (PSP approached perihelion on 2021-01-17 17:40; data intervals are 2021-01-15 – 2021-01-20 for PSP and 2021-01-17 – 2021-01-25 for ARTEMIS and Wind).
+Encounter 8 exhibits moderate alignment (PSP perihelion at 2021-04-29 08:48; data intervals 2021-04-27 – 2021-05-02 for PSP and 2021-04-29 – 2021-05-04 for ARTEMIS and Wind).
+In Encounter 9, PSP and Earth are located at substantially different heliolongitudes, with most PSP footpoints lying on the far side of the Sun (PSP perihelion at 2021-08-09 19:11; data intervals 2021-08-07 – 2021-08-12 for PSP and 2021-08-09 – 2021-08-14 for ARTEMIS and Wind).
+By comparing these intervals, we assess how the derived current sheet properties depend on the relative geometry and temporal context of the observations.
+Our results show that although certain plasma parameters vary slightly among intervals, the overall statistical characteristics of the current sheets remain largely consistent.
+This suggests that the observed statistics are not strongly sensitive to either the relative geometry or the temporal context of the measurements.
+
+@fig-overview provides an overview of the selected time interval from Encounter 7, comparing measurements from the PSP (left panels) and Wind (right panels) missions.
+From top to bottom, the panels display 8-minute averages of the magnetic field magnitude, proton number density, and proton bulk flow speed, followed by ion and electron temperatures resolved in the parallel and perpendicular directions.
+To facilitate comparison, Wind data are scaled to $20 R_\odot$ using the empirical relations $B_{\text{scaled}}/B = ( 20 R_\odot / 1\ \text{AU} )^{-1.59}$, $n_{\text{scaled}}/n = ( 20 R_\odot / 1\ \text{AU} )^{-1.96}$ [@perroneRadialEvolutionSolar2019].
+The fifth and sixth panels show the median Alfvén ratio, $R_{VB} = |Δ 𝐕| / |Δ 𝐕_A|$, of the current sheets and the total number of current sheets identified within each four-hour window.
+Including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$ does not significantly affect the Alfvén ratio $R_{VB}^* = R_{VB} / \sqrt{1 - Λ}$; its average value is approximately 0.5 for PSP and 0.4 for Wind over the entire time interval.
+The number of current sheets varies from 100 to 300 per four-hour window, corresponding to an average of about 1,000 and 900 current sheets per day for PSP and Wind, respectively.
+The PSP occurrence rates are broadly consistent with previous studies at similar heliocentric distances \citep{lotekarKineticscaleCurrentSheets2022}.
+We detect significantly more current sheets than the ∼150 events reported at 1 AU by \citet{vaskoKineticscaleCurrentSheets2022, zhangSolarWindDiscontinuities2025b}, largely because our detection is not restricted to only the most intense kinetic-scale current sheets (see methods below).
+Panels (a.7) and (b.7) present the cross helicity and residual energy, calculated every 8 minutes, which characterize the Alfvénic nature and energetic balance of the ambient plasma.
+We compute these quantities in the standard form: $\sigma_c = \frac{2 \langle \delta \mathbf{V} \cdot \delta \mathbf{V}_A \rangle}{ \langle\delta\mathbf{V}^2\rangle + \langle\delta\mathbf{V}_A^2\rangle }, \quad \sigma_r = \frac{\langle\delta \mathbf{V}^2\rangle-\langle\delta \mathbf{V}_A^2\rangle}{\langle\delta \mathbf{V}^2\rangle+\langle\delta \mathbf{V}_A^2\rangle},$ where $\delta \mathbf{V}$ and $\delta \mathbf{V}_A=\delta( \mathbf{B} / \sqrt{\mu_0 \rho})$ are the fluctuating velocity and Alfvén velocity, respectively.
+The final two panels display 8-minute averages of helium abundance and plasma beta, providing complementary information on the compositional and thermal conditions of the solar wind.
+These parameters offer critical insights into identifying the source regions of different solar wind streams [@altermanCrossHelicityHelium2025].
+
+::: {#fig-overview}
+
+![](figures/overview-7-all.png)
+
+Overview of Encounter 7 comparing PSP (left) and Wind (right) observations.
+Panels show 8-minute averages of (a.1, b.1) magnetic field magnitude, (a.2, b.2) proton density, (a.3, b.3) flow speed, (a.4, b.4) ion and electron temperatures, (a.5, b.5) Alfvén ratio, (a.6, b.6) current-sheet counts, (a.7, b.7) cross helicity and residual energy, (a.8, b.8) helium abundance, and (a.9, b.9) plasma beta.
+Wind measurements are radially scaled to $20 R_\odot$ for comparison.
+:::
+
+<!-- Reference
+> @lotekarKineticscaleCurrentSheets2022 Figure 1 presents an overview of the considered 10 day interval.
+Over this interval, the spacecraft was at radial distances from 0.17 to 0.24 au, that is, from 35 to 50 solar radii, and remained within the inward magnetic field sector without crossing the heliospheric current sheet (Phan et al.
+2020; Szabo et al.
+2020).
+No coronal mass ejections were observed in the considered interval (Phan et al.
+2020; Szabo et al.
+2020).
+The spacecraft was approximately corotating with the Sun and connected to the same coronal hole (Bale et al.
+2019; Badman et al.
+2020).
+Panels (a)–(d) present 1 minute averages of the magnetic field magnitude, proton flow velocity, densities, and temperatures of protons and electrons as well as plasma density estimates provided by the quasi-thermal noise spectroscopy.
+The magnetic field magnitude was about 100 nT at the perihelion on November 6, and around 50 nT as the spacecraft moved to a radial distance of 50 solar radii from the Sun on November 1 and 10.
+The solar wind was typically slow  with a proton flow velocity below 400 km s−1, except for the ≈20 hr period of fast solar wind between November 9 and 10.
+The three plasma density estimates in panel (c) are consistent with each other within a few tens of percent over the entire interval, except for the fast solar wind interval, where the proton densities were about 4 times smaller than the plasma density estimates provided by the quasi-thermal noise spectroscopy.
+We will use the electron density estimates, calibrated to best match proton densities and the results of quasi-thermal noise spectroscopy, as plasma density estimates.
+The proton temperature during the considered interval varied between about 10 and 100 eV, while the electron temperature remained around 30 eV.
+Panel (e) presents 1 minute averages of proton and electron betas and shows that both quantities varied in the range from 0.1 to 5.
+-->
+
+## Methodology
+
+To identify current sheets, we employ an improved automated detection algorithm adapted from previous studies [@zhangSolarWindDiscontinuities2025b; @liuMagneticDiscontinuitiesSolar2022].
+The magnetic field data are divided into consecutive time intervals, each lagged by a time $T$.
+For each interval, we compute the standard deviation of the vector magnetic field, $σ(𝐁)$, and compare it with those of the adjacent intervals, $σ(𝐁_{-} )$ and $σ(𝐁_{+})$.
+An interval is flagged as a potential current sheet when its standard deviation significantly exceeds those of its neighbors, indicating a sharp magnetic field variation: $σ(𝐁) > 2 \max(σ(𝐁_{-} ), σ(𝐁_{+}))$.
+For each candidate interval, we refine the boundaries of the potential current sheet by computing the distance between two magnetic field vectors, $d(t_a, t_b) = \|𝐁(t_a) - 𝐁(t_b)\|$.
+The leading and trailing edges, $t_a$ and $t_b$ ($t_a < t_b$), are defined such that $d(t_a, t_b)$ attains its maximum value within the interval.
+To minimize false detections—particularly those caused by wave-like or hole-like structures that may mimic current sheet signatures—we impose the additional requirement $|Δ𝐁| / \bar{B} \ge 1/10$.
+We also evaluate the magnetic field orientation across each candidate structure by computing the angles between magnetic field vectors at the leading and trailing edges and comparing them with the angles between each edge and the interval midpoint.
+Only intervals in which the edge-to-edge angle exceeds all interior angles are retained as valid current sheet candidates.
+Because current sheets span a range of spatial and temporal scales, we performed the identification procedure using multiple time lags ($T = 2, 4, 8, 16, 32, 64\ \mathrm{s}$).
+The resulting event lists from each search were merged into a comprehensive catalog after removing duplicates.
+A subset of automatically detected intervals was visually inspected.
+All verified cases exhibit clear current sheet–like signatures, confirming the robustness and reliability of the automated procedure.
+
+We also evaluated the Partial Variance of Increments (PVI) method for current sheet identification [@grecoPartialVarianceIncrements2017].
+Although the PVI technique is effective for detecting short-duration, kinetic-scale current sheets characterized by sharp gradients, it often fails to capture larger-scale structures that display smoother yet coherent magnetic field variations.
+In addition, the PVI method is highly sensitive to data resolution, complicating cross-mission comparisons where instruments have differing temporal cadences.
+For these reasons, we do not report PVI-based results here.
+
+Once the current sheets are identified, we apply a minimum variance analysis (MVA) to transform the magnetic field and plasma data into the local LMN coordinate system, where $L$, $M$, and $N$ correspond to the directions of maximum, intermediate, and minimum variance, respectively.
+The maximum variance component, $B_L$, is then fitted with a hyperbolic tangent profile to extract parameters characterizing each current sheet, following the standard Harris current sheet model [@harrisPlasmaSheathSeparating1962]: $B_L(t) = B_{L,i} \tanh (\frac{t-t_i}{Δt_i/2} ) + c_i$ where $B_{L,i}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_i$ is the detection time, $Δt_i$ is the temporal duration, and $c_i$ is a magnetic field offset.
+
+Assuming that the current sheets are one-dimensional, planar structures, their spatial scale (thickness) can be estimated once the normal direction is determined.
+The normal vector can be obtained either from the minimum variance direction given by MVA or from the cross product of the magnetic field vectors at the current sheet boundaries.
+However, previous studies have shown that the MVA-derived normal direction can often be unreliable [@knetterFourpointDiscontinuityObservations2004; @wangSolarWindCurrent2024].
+The accuracy can be improved by imposing additional constraints such as $Δ|B|/ |B| > 0.05$ or $ω > 60°$ [@liuFailuresMinimumVariance2023], where $Δ|B|$ denotes the change in magnetic field magnitude and $ω$ is the field rotation angle across the discontinuity.
+The cross-product method, on the other hand, requires that the magnetic field component along the normal direction ($B_n$) be small, making it unsuitable when $B_n$ is large.
+In this study, we apply both methods and report results based on the subset of events satisfying $Δ|B|/ |B| > 0.05$ or $ω > 60°$.
+The results derived using the cross-product method are presented in the Appendix.
+
+The spatial thickness of each current sheet is estimated as $δ = V_n \Delta t$, where $V_n$ is the plasma velocity projected along the normal direction.
+The current density associated with the main magnetic field reversal is calculated from $J_m = - \frac{1}{\mu_0 V_n} \frac{d B_l}{d t}$.
+Within our fitting framework, the magnetic field derivative can be approximated as $\max(dB_L/ dt) = 2 B_{L,i}/ Δt_i$.
+This approach provides a more robust estimate than direct differentiation, as it is less sensitive to measurement noise and limited temporal resolution.Mean proton density, temperature, and alpha-particle density values from each interval are used to compute the Alfvén velocity, pressure anisotropy factor, plasma beta, and alpha-particle abundance, thereby providing a comprehensive characterization of the plasma environment associated with each current sheet.
+the upstream and downstream conditions are defined using timestamps immediately before and after the current sheet boundaries, respectively, such that $Δ𝐕 = 𝐕_{downstream} - 𝐕_{upstream}$. 
+The cosine of the angle between the velocity jump $Δ𝐕$ and the Alfvén velocity jump $Δ𝐕_A$ is then calculated as $\cos θ = \frac{Δ𝐕 \cdot Δ𝐕_A}{\|Δ𝐕\| \|𝐕_A\|}$, serving as a measure of Alfvénic alignment.
+Finally, the cross helicity $σ_c = \frac{2 ⟨ δ 𝐕 \cdot δ 𝐁 ⟩}{ ⟨δ𝐕^2⟩ + ⟨δ𝐁^2⟩ }$ and residual energy $σ_r = \frac{⟨δ 𝐕^2⟩-⟨δ 𝐁^2⟩}{⟨δ 𝐕^2⟩+⟨δ 𝐁^2⟩}$ are computed within intervals extending from each current sheet edge to eight times the current sheet duration (or at least 30 s on either side).
+These parameters quantify the degree of Alfvénicity and the relative contributions of kinetic and magnetic energy fluctuations in the ambient solar wind.
+
+<!-- 
+$$
+\begin{aligned} & \frac{E^{+}-E^{-}}{E^{+}+E^{-}}=\frac{2\langle\delta \boldsymbol{v} \cdot \delta \boldsymbol{b}\rangle}{\left\langle\delta \boldsymbol{v}^2\right\rangle+\left\langle\delta \boldsymbol{b}^2\right\rangle} \\ & \frac{E^v-E^b}{E^v+E^b}=\frac{\left\langle\delta \boldsymbol{v}^2\right\rangle-\left\langle\delta \boldsymbol{b}^2\right\rangle}{\left\langle\delta \boldsymbol{v}^2\right\rangle+\left\langle\delta \boldsymbol{b}^2\right\rangle}\end{aligned}
+$$
+-->
+
+@fig-event-example presents two representative current sheet examples observed by PSP (left panels) and ARTEMIS (right panels).
+From top to bottom, the panels display, in LMN coordinates, the magnetic field, proton velocity, and the shifted Alfvén velocity $𝐕_A = \frac{𝐁}{\sqrt{\mu_0 \rho}} - 𝐕_{A,0}$, where $𝐕_{A,0}$ is the Alfvén velocity at the center of the current sheet.
+The cosine of the angle between the velocity jump $Δ𝐕$ and the Alfvén velocity jump $Δ𝐕_A$ is approximately -0.82 for PSP and -0.95 for ARTEMIS, indicating strong anti-correlation.
+The corresponding Alfvén ratio $R_{VB}$ is approximately 0.32 for both PSP and ARTEMIS.
+
+::: {#fig-event-example}
+
+![](figures/event-example.png)
+
+Representative examples of current sheets observed by the Parker Solar Probe (PSP; panels a.1–a.3) and ARTEMIS (panels b.1–b.3) in the local LMN coordinate system.
+Panels (a.1) and (b.1) show the magnetic field components $B_L$, $B_M$, and $B_N$, together with the magnetic field magnitude $B$.
+The red dashed lines indicate the hyperbolic tangent fits used to derive current sheet parameters.
+Panels (a.2) and (b.2) display the corresponding proton bulk velocity components $V_L$, $V_M$, and $V_N$.
+Panels (a.3) and (b.3) show the shifted Alfvén velocity components $V_{A,L}$, $V_{A,M}$, and $V_{A,N}$.
+The vertical gray dashed lines mark the leading and trailing edges of each identified current sheet.
+
+:::
+
+<!-- Reference: 
+Assuming that the SWD structures are planar, the normal direction can be obtained by minimizing the variance of the magnetic field{\textquoteright}s normal component in MVA.
+However, previous studies have indicated that the normal direction obtained through MVA is frequently unreliable \cite<see discussion in>{knetterFourpointDiscontinuityObservations2004,wangSolarWindCurrent2024}.
+Improved accuracy can be achieved by either using the cross product of the magnetic field measured at the boundaries as the normal direction \cite{knetterFourpointDiscontinuityObservations2004} or by enforcing conditions such as $\ensuremath{\Delta}|{\bf B}|/|{\bf B}| > 0.05$ or $\ensuremath{\omega} > 60{\degree}$ \cite{liuFailuresMinimumVariance2023}, where $\ensuremath{\Delta}|{\bf B}|$ is the change in the magnitude of the magnetic field and $\ensuremath{\omega}$ is the field rotation angle across the discontinuity.
+The former approach requires a small magnetic field component ($B_n$) along the discontinuity normal, while the latter approach limits the dataset to a subset that satisfies these conditions.
+These two methods yield closely aligned normal directions when $B_n$ is small and either $\ensuremath{\Delta}|{\bf B}|/|{\bf B}| > 0.05$ or $\ensuremath{\omega} > 60{\degree}$ is satisfied.
+In our analysis, we applied both techniques and found that they yielded statistically consistent results.
+\rev{A direct comparison of the discontinuity properties obtained from these two methods is presented in panels (e-j) of Figure~\ref{fig-juno_sw_comparison} in the Appendix, using intervals from Juno's approach to Jupiter when solar wind parameters were available.}
+-->
+
+# Results and Discussion
+
+@fig-properties-hist presents the statistical distributions of current sheet thickness $δ$, current density $J$, and magnetic field jump magnitude $|Δ𝐁|$ derived from different missions and time intervals.
+For thickness and current density, we display here a subset of the all dataset where MVA normals are trustable.
+The result of using cross product for the current sheet normals are displayed in the appendix @fig-properties-hist-cross and do not show any significant difference.
+Note that we do not need to subset the dataset for magnetic field jump magnitude since it does not depend on the normal direction.
+To better understand how these properties relate to the local plasma environment, we normalize the current sheet thickness by the ion (proton) inertial length, $d_i=c/\omega_{pi}$, and the current density by the Alfvén current density, $J_A = e N V_A = B / \mu_0 d_i$.
+Both parameters represent natural plasma scales: the ion inertial length characterizes the spatial scale where ions decouple from the magnetic field, while the Alfvén current density corresponds to the characteristic current generated by the relative drift of electrons and ions moving at the local Alfvén speed $V_A$.
+These quantities are particularly relevant in studies of MHD turbulence and magnetic reconnection [@zhdankinStatisticalAnalysisCurrent2013; @franciMagneticReconnectionDriver2017].
+
+Despite differing heliocentric distances and instrumental conditions, the normalized current density $J_m / J_A$ shows remarkably similar distributions across the PSP, Wind, and ARTEMIS datasets.
+This suggests that the relative strength of current sheets, when expressed in local plasma units, is largely independent of radial distance from the Sun.
+In contrast, the absolute thickness $δ$ increases from PSP to ARTEMIS and Wind, indicating a broadening of current sheets with solar wind expansion.
+After normalization by the ion inertial length, however, the characteristic scale $δ / d_i$ decreases slightly with increasing distance.
+This trend is consistent with previous analyses using Juno observations between 1 and 5 AU [@zhangSolarWindDiscontinuities2025b] and Maven observations between 1 and 1.5 AU [@artemyevDynamicsIntenseCurrents2018], which found that normalized current density remains nearly constant while normalized thickness gradually decreases with heliocentric distance.
+Similar behavior has been reported by @madarDirectionalDiscontinuitiesInner2024 using Parker Solar Probe and Solar Orbiter data, where the thickness of rotational discontinuities in ion inertial length units decreases rapidly until approximately 0.3 AU.
+
+The distributions of magnetic field jumps ($|Δ𝐁|$ and $|Δ𝐁|/\langle|𝐁|\rangle$) exhibit pronounced differences across the missions.
+In particular, the PSP data display a markedly distinct distribution compared with Wind and ARTEMIS, characterized by substantially larger magnetic field jumps—even after normalization—and a relatively flatter tail in the probability density function.
+These large jumps indicate stronger magnetic field reversals in the near-Sun environment, likely associated with the frequent occurrence of switchbacks.
+Such switchbacks, especially those embedded within switchback patches, have been observed to dissipate with increasing heliocentric distance [@soniSwitchbackPatchesEvolve2024; @shiPatchesMagneticSwitchbacks2022].
+The difference in the shape of the probability density functions thus suggests the coexistence of multiple populations of current sheets in the near-Sun region, potentially generated by distinct physical mechanisms or linked to different solar wind source regions.
+As the solar wind expands and the turbulence undergoes nonlinear evolution [@telloniObservationModelingSolar2022; @telloniEvolutionSolarWind2021], these separate populations likely interact and merge, resulting in the smoother and more homogeneous distributions observed at 1 AU.
+
+::: {#fig-properties-hist}
+![](figures/properties_hist-mva.png)
+
+Probability density functions (PDFs) of current sheet properties obtained from different missions (color-coded) and encounters (distinguished by line styles).
+The left column shows unnormalized quantities, while the right column presents values normalized by characteristic plasma scales.
+From top to bottom, panels display the distributions of (a) current sheet thickness $δ$ and its normalized form $δ / d_i$; (b) current density $J_m$ and normalized current density $J_m / J_A$; and (c) magnetic field jump magnitude $|Δ𝐁|$ and its normalized value $|Δ𝐁| / \langle |𝐁| \rangle$.
+The ion inertial length is $d_i = c / \omega_{pi}$, and the Alfvén current density is $J_A = e N V_A = B / \mu_0 d_i$.
+:::
+
+@fig-joint-properties presents the joint distributions between (a) current density and current sheet thickness, (b) normalized current density and normalized thickness, (c) normalized thickness and normalized magnetic field jump, and (d) normalized current density and normalized magnetic field jump.
+A clear inverse correlation is evident between the (normalized) current density and (normalized) current sheet thickness, indicating that stronger currents are generally associated with thinner sheets—that is, smaller-scale current sheets tend to be more intense.
+After normalization, the scatter distributions of current density versus thickness are highly similar across different missions, both in overall shape and in the range of values.
+This similarity suggests that the statistical relationship between current density and scale is largely independent of heliocentric distance.
+In contrast, the relationship between the magnetic field jump and current sheet thickness, shown in Panel (c), is relatively weak.
+For a given range of magnetic field jump amplitudes, the corresponding spatial scales exhibit a broad distribution, spanning up to two orders of magnitude.
+Moreover, as seen in Panel (d), there is no clear one-to-one correspondence between the magnetic field jump amplitude and the current density.
+Scale-dependent properties of current sheets have been reported by several previous studies using PSP, Wind, and Ulysses observations [@lotekarKineticscaleCurrentSheets2022; @vaskoKineticscaleCurrentSheets2022; @vaskoKineticScaleCurrentSheets2024].
+However, whereas earlier studies primarily focused on kinetic-scale current sheets, our analysis extends this investigation to a broader range of spatial scales—covering nearly two additional orders of magnitude in the logarithmic space of normalized current density and normalized current sheet thickness.
+Similar trends are found when the current sheet normal is determined using the magnetic field cross-product method rather than the minimum variance analysis.
+This consistency across methods confirms that the observed correlations are not strongly affected by the specific approach used to estimate the current sheet geometry.
+
+::: {#fig-joint-properties}
+![](figures/joint_properties-mva.png)
+
+Joint probability distributions of (a) current density versus current sheet thickness, (b) normalized current density versus normalized current sheet thickness, (c) normalized current sheet thickness versus magnetic field jump magnitude, and (d) normalized current density versus normalized magnetic field jump magnitude.
+:::
+
+For an ideal MHD rotational discontinuity (RD), the plasma velocity and magnetic field variations satisfy the Walén relation, $Δ 𝐕 = \pm Δ 𝐕_A$, and the force-free condition ( $Δ B \approx 0$) holds across the current sheet.
+The Walén relation requires agreement in both magnitude and direction between the plasma velocity change and the corresponding Alfvén velocity change.
+However, most observed current sheets deviate from these ideal conditions.
+
+To quantify the degree of Alfvénicity and the deviations from ideal RD behavior, we examine both the magnitude and angular differences between $Δ 𝐕$ and $Δ 𝐕_A$, as well as the variation in magnetic field strength across each current sheet.
+@fig-Alfvenicities summarizes the statistical results.
+Panel (a) shows the ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude.
+Across all missions, the ratio is generally less than unity, with mean values of approximately 0.6 for PSP and 0.5 for the combined Wind and ARTEMIS datasets.
+Panel (b) displays the cosine of the angle between the velocity and Alfvén velocity jumps.
+All missions show clustering near 0° and 180°, corresponding to correlated and anti-correlated states, respectively.
+PSP observations exhibit stronger alignment (cosine values closer to ±1), whereas Wind and ARTEMIS data show a broader angular spread.
+Panels (c) and (d) present the fractional change in magnetic field magnitude across current sheets.
+These variations are small (about 0.1 on average) for all missions, with PSP showing slightly smaller changes than Wind and ARTEMIS.
+This indicates that most current sheets are nearly incompressible, consistent with an approximately force-free magnetic structure.
+
+We also calculate the Alfvén velocity including the anisotropy factor $Λ = μ(p_{\parallel,e} − p_{\perp,e} + p_{\parallel,i} − p_{\perp,i})/B^2$, for PSP and Wind observations when the necessary plasma data are available.
+In most cases, including this anisotropy correction does not significantly alter the velocity-jump ratio.
+The persistent discrepancy between the observed ratios ($R < 1$) and the predictions of anisotropic MHD theory may have several explanations.
+First, the limited temporal resolution of the plasma anisotropy measurements—typically much lower than that of the magnetic field data—may cause underestimation of instantaneous variations at current sheet crossings [@huangProtonTemperatureAnisotropy2020; @shenComparingPlasmaAnisotropy2024].
+Second, kinetic-scale magnetic discontinuities often deviate from the assumptions of MHD theory: their non-Maxwellian particle velocity distributions, including plasma agyrotropies and field-aligned beams [@artemyevIonNongyrotropySolar2020; @neukirchKineticModelsTangential2020], are not accounted for in the fluid equations but can strongly influence the measured velocity ratios.
+Finally, uncertainties in deriving the parallel and perpendicular temperatures—typically obtained from nonlinear fits to complex velocity distribution functions—may introduce additional errors, especially when multiple particle populations are present [@huangProtonTemperatureAnisotropy2020; @halekasElectronsYoungSolar2020].
+
+::: {#fig-Alfvenicities}
+
+![](figures/Alfvenicities.png)
+
+Statistical distributions of parameters used to characterize the Alfvénicity of current sheets: (a) ratio of velocity-jump magnitude to Alfvén velocity-jump magnitude, (b) cosine of the angle between the two vectors, (c) the variation in magnetic field magnitude between the leading and trailing edges of each current sheet; and
+(d) the maximum variation in magnetic field magnitude observed within each current sheet.
+
+:::
+
+To further investigate the physical origins of the observed deviations from Alfvénic behavior, we use a single scalar parameter, $Q^{ \pm}$, introduced by [@sonnerupQualityMeasureWalen2018], to quantify the Alfvénicity of current sheets and examine how $Q^{ \pm}$ correlates with key current sheet and plasma parameters.
+
+The parameter $Q^{\pm}$ is defined as $Q^{\pm} = \pm \left(1 - \frac{|\Delta 𝐕 \mp \Delta 𝐕_A|}{|\Delta 𝐕| + |\Delta 𝐕_A|}\right)$, which combines both magnitude and directional discrepancies between the velocity and Alfvén velocity jumps, and satisfies $-1 < Q^{\pm} < 1$.
+The upper sign is used for cases where $\cos \theta > 0$ and the lower sign for $\cos \theta < 0$.
+Values of $Q^{\pm}$ approaching ±1 correspond to highly Alfvénic behavior.
+The joint distribution of $|\Delta 𝐕| / |\Delta 𝐕_A|$ and $\cos \theta$ is shown in the first panel of @fig-Q_sonnerup_joint_dist_den.
+
+::: {#fig-Q_sonnerup_joint_dist_den}
+
+![](figures/Q_sonnerup_joint_dist_den.png)
+
+(a) Joint distribution of the velocity-jump ratio ($|\Delta 𝐕| / |\Delta 𝐕_A|$) and the cosine of the alignment angle ($\cos \theta$), used in computing the Sonnerup ($Q^{\pm}$) parameter.
+(b) Joint distribution of cross helicity ($\sigma_c$) and ($Q^{\pm}$).
+(c) Joint distribution of residual energy ($\sigma_r$) and ($Q^{\pm}$).
+(d) Joint distribution of temporal duration and ($Q^{\pm}$).
+
+:::
+
+We examine the relationship between $Q^{\pm}$ and various current sheet and ambient solar wind properties.
+Most parameters show little or no correlation with $Q^{\pm}$; however, two quantities exhibit strong correlations: the cross helicity $\sigma_c$ and residual energy $\sigma_r$ of the surrounding solar wind.
+These parameters describe, respectively, the degree of velocity–magnetic field correlation and the partition of energy between velocity and magnetic field fluctuations.
+Both serve as indicators of the Alfvénic character of the background solar wind rather than of individual current sheets.
+
+Panels (b) and (c) of @fig-Q_sonnerup_joint_dist_den show that the Alfvénicity of current sheets, represented by $Q^{+}$, increases with higher cross helicity and larger (more positive) residual energy, while $Q^{-}$ increases with higher cross helicity and smaller (more negative) residual energy.
+This trend suggests that current sheets embedded within highly Alfvénic solar wind streams tend to preserve stronger velocity–magnetic field alignment, whereas those located in more turbulent or energy-imbalanced regions—where magnetic energy $(E_B)$ exceeds kinetic energy $(E_V)$—exhibit greater departures from Alfvénic expectations.
+
+Additionally, observations reveal a weak positive correlation between $Q^{\pm}$ and the temporal duration of current sheets, as shown in Panel (d) of @fig-Q_sonnerup_joint_dist_den.
+Longer-duration current sheets tend to exhibit slightly higher $Q^{\pm}$ values, suggesting a more coherent Alfvénic structure.
+However, this correlation may be partially influenced by instrumental limitations, since longer events are more reliably resolved in plasma velocity measurements.
+Other plasma parameters, such as plasma beta and alpha-particle abundance, show no significant correlation with $Q^{\pm}$, implying that the Alfvénic nature of current sheets is primarily governed by the local turbulent environment rather than by large-scale plasma conditions.
+
+Since the normal component of the magnetic field plays a key role in determining both the spatial scale and the associated current density, we next examine the rotational characteristics of the current sheets and their relationship with the normalized normal magnetic field component, $B_N/B$.
+@fig-B_n_ω shows the distributions of the in-plane rotation angle (also referred to as the shear angle) and the normalized normal component $B_N/B$, along with their joint distributions for different missions.
+Panel (a) reveals that PSP observes a distinctly different distribution of rotation angles compared to the Wind and ARTEMIS missions, while the distributions of $B_N/B$ are largely similar, as shown in Panel (b).
+This discrepancy suggests that the rotational structure of current sheets evolves significantly as the solar wind propagates from the near-Sun environment to 1 AU.
+The multiple peaks in PSP’s in-plane rotation angle distribution likely reflect the coexistence of several current sheet populations, possibly formed through different mechanisms or originating from different solar wind sources.
+As the solar wind expands and mixes, this structured distribution becomes smoother, as observed by Wind and ARTEMIS near Earth.
+The distribution of $B_N / B$ is clearly bimodal, with one population corresponding to nearly field-aligned normals and another to nearly perpendicular ones.
+Only a small fraction of events fall in the intermediate range.
+Such bimodal distributions are consistent with the coexistence of different types of discontinuities—most notably rotational and tangential discontinuities [@madarDirectionalDiscontinuitiesInner2024].
+Panel (c) shows the joint distribution of the in-plane rotation angle and $B_N / B$, where each column has been normalized to highlight how the rotation angle varies with $B_N / B$.
+The distinct distribution observed by PSP again indicates an evolutionary trend: current sheets closer to the Sun exhibit a more structured and varied rotational behavior, which gradually transitions to smoother and more uniform configurations at 1 AU.
+
+::: {#fig-B_n_ω}
+
+![](figures/B_n_ω_-mva-subset=true.png)
+
+(a) Probability density functions of the in-plane rotation angle ($\omega_{\text{in}}$) for Parker Solar Probe (PSP) and Wind + THEMIS.
+(b) Probability density functions of the normalized normal magnetic field component ($B_N / B$).
+(c) Joint distributions of $\omega_{\text{in}}$ and $B_N / B$ for PSP (left) and Wind + THEMIS (right).
+:::
+
+Finally, @fig-duration presents the probability density functions of current sheet temporal durations observed by different missions.
+The distributions differ noticeably in shape, reflecting variations in the relative occurrence of short- and long-duration events among the datasets.
+The gradual change in slope with increasing duration suggests the presence of at least two, and possibly three, distinct regimes contributing to the overall range of current sheet durations.
+The shortest-duration events are likely associated with kinetic-scale current sheets, while the longer-duration events may correspond to flux-tube boundaries, large-scale magnetic structures, or heliospheric current sheets.
+The similar slopes observed at longer durations across missions indicate that large-scale structures are relatively stable with heliocentric distance, whereas the short-duration population evolves more rapidly as the solar wind expands.
+Assuming that current sheets propagate radially without significant distortion or dissipation, the measured temporal duration can be interpreted as a proxy for the spatial thickness of the structure, modulated by the magnetic field orientation.
+To account for geometric effects, we apply a correction based on the Parker spiral model, multiplying the PSP durations by the factor $\sin(\Theta_{\text{Earth}}) / \sin(\Theta_{\text{PSP}})$, where $\Theta \approx \arctan(B_T / B_R)$ is the angle between the magnetic field and the radial direction, with $B_R$ and $B_T$ denoting the radial and transverse magnetic field components, respectively.
+Although this correction is a simplified approximation and not physically rigorous, it provides a useful scaling comparison: after adjustment, the PSP duration distribution aligns closely with those of Wind and ARTEMIS near 1 AU for short-duration current sheets.
+This agreement suggests that the shortest-duration (kinetic-scale) current sheets are predominantly oriented perpendicular to the mean magnetic field and evolve substantially with distance from the Sun.
+
+::: {#fig-duration}
+
+![](figures/duration_dist.png)
+
+Probability density functions of current sheet durations observed by different missions. Grey vertical dashed lines indicate durations of 1, 2, 4, 8, 16, and 32 s (from left to right).
+
+:::
+
+# Conclusion
+
+1.
+We investigated three Parker Solar Probe (PSP) encounters, complemented by ARTEMIS and Wind measurements, to identify and characterize current sheets across different heliocentric distances.
+The results indicate that variations in the selected time intervals exert only a minor influence on key current sheet properties such as thickness, current density, and Alfvénicity.
+This suggests that the observed evolution of current sheet characteristics primarily reflects spatial effects associated with radial expansion rather than temporal variability.
+
+2.
+Our analysis confirms that current sheet properties are closely linked to local plasma conditions and extends previously reported scale-dependent relationships between current sheet thickness and current density by more than two orders of magnitude, encompassing structures from kinetic to large MHD scales.
+Both the normalized current density and normalized thickness remain nearly constant across radial distances, with only a slight decrease in normalized thickness farther from the Sun.
+The pronounced anti-correlation between current density and spatial scale—stronger current densities corresponding to thinner sheets—and the similarity of normalized current densities across radial distances indicate a close connection between current sheets and MHD turbulence, since localized, non-Gaussian current density enhancements are a hallmark of intermittency in turbulent plasmas.
+
+3.
+The Alfvénicity of most current sheets, quantified by the parameter $Q$, remains below unity for the majority of events.
+The magnitude ratios reported by PSP and Wind are broadly consistent, while PSP observations show smaller angular deviations than those from Wind and ARTEMIS.
+Pressure anisotropy alone does not account for the observed velocity and magnetic field jumps.
+Instead, the degree of Alfvénicity appears to be primarily controlled by the surrounding turbulent plasma state—specifically, by cross helicity and residual energy.
+Most current sheets are nearly force-free, exhibiting low compressibility (typically <0.1).
+These findings support a picture in which current sheets are embedded within, and shaped by, the local turbulent cascade rather than being isolated structures produced by single local processes.
+In other words, the macroscopic turbulence environment determines whether a boundary appears Alfvénic or non-Alfvénic when sampled in situ.
+
+<!-- 
+The strong positive correlation between current-sheet Alfvénicity and the ambient cross-helicity, together with the negative correlation with residual energy, indicates that the degree to which a current sheet behaves like an ideal rotational discontinuity is largely set by the surrounding turbulence state.
+High cross-helicity (more Alfvénic background fluctuations) promotes velocity–magnetic-field alignment at the sheet and hence higher sheet Alfvénicity; conversely, large (negative) residual energy — a relative excess of magnetic over kinetic fluctuation energy — corresponds to less Alfvénic sheets.
+-->
+
+4.
+A comparison between PSP and near-Earth missions reveals that the statistical properties of solar wind current sheets undergo systematic evolution with heliocentric distance.
+Clear differences are observed in the distributions of unnormalized current density, thickness, magnetic field jump, rotation angle, and temporal duration.
+Processes that may drive this evolution include global solar wind expansion [@matteiniIonKineticsSolar2012], nonlinear dynamics of Alfvén waves and Alfvénic turbulence [@medvedevDissipativeDynamicsCollisionless1997], and interactions with other coherent structures.
+This evolution has important implications for the role of current sheets in plasma heating [@sioulasStatisticalAnalysisIntermittency2022], particle energization and transport [@zhangQuantificationIonScattering2025], which are expected to depend strongly on radial distance.
+
+Taken together, our results support a picture in which current sheets are predominantly turbulence-embedded, dynamically evolving structures whose Alfvénic character is governed by the ambient solar wind turbulence—through cross helicity and residual energy.
+The tight coupling between current sheet intensity and spatial scale, the coexistence of at least two structural regimes, and the systematic radial evolution of their properties collectively point to a complex interplay between turbulent intermittency, solar wind expansion, and kinetic processes.
+Resolving these remaining discrepancies will require higher-resolution particle measurements, multi-spacecraft observations, and dedicated kinetic modeling.
+
+<!-- 7. Methodological caveats and uncertainties.
+Several limitations could affect quantitative interpretation and should guide follow-up analyses: (i) single-spacecraft MVA and thickness estimates carry uncertainties in the normal direction and the projection of velocity; (ii) current density estimated from ΔB/Δl assumes a 1D geometry and neglects possible multi-dimensional structure; (iii) time-resolution differences between magnetometers and plasma instruments (SPAN, Faraday cup) can bias velocity-jump estimates; and (iv) detection thresholds and interval selection in the automated algorithm can preferentially select certain sheet types.
+-->
+
+<!-- 5. Temporal-duration effect: physical or instrumental?
+The weak positive relation between current-sheet duration and Alfvénicity (longer events appearing more Alfvénic) must be interpreted cautiously.
+Longer durations provide more plasma samples and therefore better statistical estimates of upstream/downstream velocities; thus part of the trend may be instrumental or sampling bias.
+Nevertheless, if a residual physical trend remains after accounting for resolution effects, it could indicate that more spatially extended sheets preserve the Alfvénic coupling between flows and fields more effectively than shorter, more transient sheets — again pointing to an intimate connection between sheet morphology and the ambient turbulence.
+-->
+
+<!-- 
+8. Specific, actionable follow-ups.
+To strengthen the physical interpretation and disentangle competing hypotheses, we recommend:
+	•	Cross-checking events with high-cadence particle moments and full distribution functions (to examine alpha/beams and non-Maxwellian features).
+	•	Searching for localized signatures of Hall physics or reconnection (bipolar electron jets, outflow pairs, Hall magnetic-field patterns) in high-resolution fields and particle data.
+	•	Conditioning the statistics on solar-wind type (fast vs. slow, presence of switchbacks, stream origin) to see whether the two inferred populations map to flow regimes.
+	•	Running hybrid or kinetic simulations initialized with observed upstream parameters to test whether pressure-tensor or multi-species effects reproduce the velocity–field jump mismatch.
+	•	Expanding the radial coverage (include Solar Orbiter, STEREO where possible) or employing multi-point analysis to reduce geometric ambiguities. 
+-->
+
+<!-- References
+-   @artemyevDynamicsIntenseCurrents2018 examined the evolution of transient currents in the solar wind using a data set compiled from observations of the same solar wind ﬂow at Earth’s and Mars's orbits.
+
+    > we show that it consists of several processes: discontinuity thinning (decrease in thickness normalized by the ion inertial length), intensification of currents normalized to the proton thermal current (i.e., the product of proton charge, density, and thermal velocity), and increase in the compressional component of magnetic ﬁeld variations across discontinuities.
+
+-->
+
+# Appendix
+
+::: {#fig-properties-hist-cross}
+![](figures/properties_hist-cross.png)
+
+Same as @fig-properties-hist but using cross product to determine the normal direction to the current sheet.
+:::
+
+::: {#fig-joint-properties-cross}
+![](figures/joint_properties-cross.png)
+
+Same as @fig-joint-properties but with current sheet normals determined using the magnetic field cross-product method instead of minimum variance analysis (MVA).
+:::

### 2025-12-01 lib/Discontinuity.jl

@@ -1,1 +1,0 @@
-/Users/zijin/src/Discontinuity.jl

### 2025-12-01 notebooks/000_data.qmd
chore: cleanup ipynb

@@
 "cda/STA_L2_PLA_1DMAX_1MIN/proton_Vr_RTN",
+
+## Anisotropy Data
+
+# Anisotropy
+
+- PSP_SWP_SPI_SF00_L3_MOM
+
+    - Notes: Partial moments of the Proton distribution function in the SPAN-Ion instrument, PSP spacecraft, and RTN coordinate systems.
+User should be aware that the full ion distribution is typically NOT in the FOV of the instrument.
+
+    - `T_TENSOR`  Partial Moment Temperature Tensor in instrument frame
+
+- WI_H0_SWE
+
+    - `Te_anisotropy`	Temperature anisotropy = Te_para / Te_perp
+
+- WI_PLSP_3DP
+
+    - `MOM.P.MAGT3`	---> [P.SYMM_MAGT3] Proton temperature tensor... rotated into a field-aligned coordinate basis and then taking the diagonal elements only
+
+- WI_ELM2_3DP : Wind 3dp, PESA Low (~24 sec resolution) energy spectra with ion moments
+
+    - `MAGT3`	---> [MAGT3] electron temperature tensor... rotated into a field-aligned coordinate basis and then taking the diagonal elements only
+
+- THB_L2_ESA
+
+    - `thb_peeb_magt3Q`	-----Electron Temperature, Field Aligned (Tprp1FA, Tprp2FA, TparFA)
+
+    - `thb_peef_magt3Q`	-----Electron Temperature, Field Aligned (Tprp1FA, Tprp2FA, TparFA)
+
+    - `thb_peif_magt3Q`	-----Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)
+
+- THB_L2_MOM
+
+    - `thb_peem_ptens_magQ`	-----Electron Pressure Tensor, Field Aligned
+
+    - `thb_peem_t3_magQ`	-----Electron Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)
+
+    - `thb_peim_ptens_magQ`	-----Ion Pressure Tensor, Field Aligned
+
+    - `thb_peim_t3_magQ`	-----Ion Temperature, Field Aligned (TprpFA1, TprpFA2, TparFA)

### 2025-12-20 notes.qmd
docs: update figures and text
docs: publish as manuscript
docs: add AGU25 presentation

@@
-# Updates
+# TODO / Future work
 
 - [x] Why ARTEMIS electron data and Wind ion data?
+- [ ] Why we have so many events from Wind observations?
+  - Biased by different methods.
+- [x] Show PSP and ARTEMIS examples with Bn/B~0.75?
+  - [ ] Check $B_n$ dependence to check method bias (duration / thickness)
 - [ ] Disagreement between anisotropy observed and predicted by the theory
@@
   - or maybe more complex ion distribution, where nongyrotropy is more important than anisotropy
+- [ ] Check the occurrence rates correlation with fluctuation level / residual energy at similar radial distance.
 
@@
   - Locally generated in the interplanetary space by turbulence?
-
-# TODO
-
-- [ ] Plot Bl(t), jm(l) and ion anisotropy for these cases?
 
@@
 ## 02/09/2024 (Encounter 2)
-
-::: {.column-screen-inset layout-nrow="1"}
-
-![](figures/enc2/thickness_current)
-
-![](figures/enc2/density_distribution)
-
-![](figures/enc2/dvl)
-:::
-
-Pair plot
-
-::: {.column-screen-inset layout-nrow="1"}
-
-![](figures/enc2/dn-dT)
-
-![](figures/enc2/dT-dB)
-
-![](figures/enc2/dn-dB)
-:::
 
